### 2017-10-12 cvpr2018.tex
clean

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

%\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\begin{document}

%%%%%%%%% TITLE
\title{\LaTeX\ Author Guidelines for CVPR Proceedings}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}

\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}

### 2017-10-15 cvpr2018.tex
fill parts
first draft

@@
 % Include other packages here, before hyperref.
-
+\usepackage{tabularx} % in the preamble
+\newcolumntype{Y}{>{\centering\arraybackslash}X}
+\newcommand\VRule[1][\arrayrulewidth]{\vrule width #1}
+\usepackage{array,booktabs,arydshln,xcolor} % for widening table line
+\usepackage{amsthm}
+\usepackage{epstopdf}
+\usepackage{algorithm}
+%\usepackage{algorithmic}
+\usepackage{amsthm}
+\usepackage{multirow}
+\usepackage[algo2e]{algorithm2e}
+\usepackage[outercaption]{sidecap}    
+\usepackage{float}
+\usepackage{wrapfig}
+\usepackage{subcaption}
+\usepackage{capt-of}% or \usepackage{caption}
+\usepackage{booktabs}
+\usepackage{varwidth}
 % If you comment hyperref and then uncomment it, you should delete
@@
 %%%%%%%%% TITLE
-\title{\LaTeX\ Author Guidelines for CVPR Proceedings}
+\title{Semantic Photographic Image Synthesis \\ with a Hierarchically-nested Adversarial Network}
 
@@
 \begin{abstract}
+This paper presents a novel  and effective approach to deal with the challenging task of generating synthetic photographic image conditioned on semantic image descriptions.
+We leverage the hierarchical deep representations of convolutional layers and introduce deeply-nested adversarial training to constrain the representations to be compositional for multi-scale image generation.
+To this end, we present a new network architecture, which is symmetric as well as extensile, to gradually upscale generated images to high resolutions.
+We present a  functional generative adversarial networks (GANs) training strategy to encourage more effective multimodal (i.e.
+image and text) information utilization in order to enhance multi-purpose adversary between real and fake.
+Our method, at the first time, shows a fully end-to-end trainable network that can generate $256{\times}256$ images and is stackable to $512{\times}512$ resolution or higher with arbitrary extensions.
+With extensive experimental validation on three major datasets, our method sets up a new state of the art to this field.
 
@@
 \section{Introduction}
+Generating photographic high-resolution image conditional on arbitrary semantic description is a meaningful problem in generative model research \cite{reed2016generative}.
+However, insufficient methods have been successfully developed to address this task due to its particular challenges.
+Text-to-image synthesis can be viewed as an special variation of conventional generative models, which aim to translate a vector to a RGB image space.
+Differently, the vector space of the former is induced by semantic descriptions.
+Therefore, this task requires the generated images to be semantically consistent, i.e., the generated images not only reflect the principal concept of descriptions in global images but also can reflect the fine-grained descriptive details in image pixels.
+
+Generative adversarial networks (GANs) have become the main solution to this task. 
+Scott \etal \cite{reed2016generative} takes the first step to address this task through a GAN based framework, which is similar with DCGAN \cite{}.
+But this method only handles image up to $64{\times}64$ resolution and usually is barely to generate vivid object details.
+Based on \cite{reed2016generative}, Zhang \etal \cite{} present a successful approach (StackGAN) by stacking another GAN to generate high quality and compelling $256{\times}256$ images given inputs of low resolution $64{\times}64$ synthetic images.
+This method needs individual two-stage training, which is relatively not straightforward to be applied.
+Later on, Dong \etal \ref{dong2017semantic}
+bypasses the difficult of translate vector semantic vector to RGB image and treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-renders a arbitrary-style training image according to targeting semantic descriptions.
+However, the high resolution synthesis ability is still indeterminate.
+Unfortunately, directly training from vector space and synthesize high resolution (e.g. $256{\times}256$)  images is still an open question according to current reported studies.
+
+We outline several empirical reasons for this challenges using GANs.
+The first fundamental problem comes from the difficulty of balancing the stability between generators and discriminators.
+There are many a rich number of literature trying to stabilize GAN training \cite{}.
+But especially for text-to-image synthesis, how to utilize the multimodal information between images and text in discriminator is extremely important and needs careful consideration.
+The second reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}.
+Keeping semantic consistency as well as diversity in generated images needs more specialized designs for discriminators.
+
+With careful consideration of these reasons, in our method, we propose a novel method that can directly generate high resolution images trained in fully end-to-end fashion.
+To tackle the significant space difference between text and images, we propose to leverage the hierarchical deep representations of convolutional layers through deeply compositional constraints.
+In other words, we limit feature maps in different layers to be disentangled RGB image space, such that feature maps of any layers can linearly represent targeting images at corresponding resolutions.
+We introduce accompanying adversarial objective at deep layers to achieve this goal, inspired by the deeply-supervised nets (DSN) \cite{lee2015deeply} for image classification.
+In difference of previous methods, our method has an intuitive network architecture design with hierarchically-nested adversarial objectives that is more efficient and faster to train.
+
+To tackle the instability training of GANs, \textcolor{red}{we enforce discriminators at different resolutions can differentiate real/fake image, correct/incorrect image-text pairs, and real/fake image pairs jointly.
+This multi-purpose strategy is mutually beneficially }
+
+\subsection{Summarize different architectures}
+refer to HED.
+
+\section{Method}
+First end-to-end trainable high definition model and set up a new standfsdkfm.
+
+\subsection{Preliminaries}
+
+\subsection{Scalable Deeply Supervised}
+
+\subsection{Functional Loss}
+
+\subsection{Implementation Details}
+
+\subsection{Network Architecture}
+
+\section{Experiments}
+\subsection{Evaluation metric}
+\subsection{Quantitative and qualitative results}
+
+\subsection{Case study}
+\subsubsection{Arbitrary text description}
+\subsubsection{Style transfer}
+
+\section{Ablation study}
+\subsubsection{loss study}
+\subsubsection{architecture study}
 
@@
 \bibliographystyle{ieee}
-\bibliography{egbib}
+\bibliography{reference_zizhao,egbib}
 }

### 2017-10-16 cvpr2018.tex
2nd v

@@
 Generative adversarial networks (GANs) have become the main solution to this task. 
-Scott \etal \cite{reed2016generative} takes the first step to address this task through a GAN based framework, which is similar with DCGAN \cite{}.
+Reed \etal \cite{reed2016generative} takes the first step to address this task through a GAN based framework.
 But this method only handles image up to $64{\times}64$ resolution and usually is barely to generate vivid object details.
-Based on \cite{reed2016generative}, Zhang \etal \cite{} present a successful approach (StackGAN) by stacking another GAN to generate high quality and compelling $256{\times}256$ images given inputs of low resolution $64{\times}64$ synthetic images.
+Based on \cite{reed2016generative}, Zhang \etal \cite{han2017stackganan} present a successful approach (StackGAN) by stacking another GAN to generate high quality and compelling $256{\times}256$ images given inputs of low resolution $64{\times}64$ synthetic images.
 This method needs individual two-stage training, which is relatively not straightforward to be applied.
@@
 The first fundamental problem comes from the difficulty of balancing the stability between generators and discriminators.
-There are many a rich number of literature trying to stabilize GAN training \cite{}.
+There are many a rich number of literature trying to stabilize GAN training \cite{salimans2016improved}.
 But especially for text-to-image synthesis, how to utilize the multimodal information between images and text in discriminator is extremely important and needs careful consideration.
@@
 
-With careful consideration of these reasons, in our method, we propose a novel method that can directly generate high resolution images trained in fully end-to-end fashion.
-To tackle the significant space difference between text and images, we propose to leverage the hierarchical deep representations of convolutional layers through deeply compositional constraints.
+With careful consideration of these reasons, in this paper, we propose a novel method that can directly generate high resolution images trained in fully end-to-end fashion.
+The contributions are described follows.
+
+To tackle the problem of significant space difference between text and images, we propose to leverage the hierarchical deep representations of convolutional layers through deeply compositional constraints.
 In other words, we limit feature maps in different layers to be disentangled RGB image space, such that feature maps of any layers can linearly represent targeting images at corresponding resolutions.
-We introduce accompanying adversarial objective at deep layers to achieve this goal, inspired by the deeply-supervised nets (DSN) \cite{lee2015deeply} for image classification.
-In difference of previous methods, our method has an intuitive network architecture design with hierarchically-nested adversarial objectives that is more efficient and faster to train.
+We introduce accompanying deeply-nested adversarial objective at intermediate layers to achieve this goal, inspired by the deeply-supervised nets (DSN) \cite{lee2015deeply} for image classification.
+To well cooperate with discriminators, we propose an intuitive network architecture design with hierarchically-nested adversarial objectives that is more efficient and faster to train.
 
-To tackle the instability training of GANs, \textcolor{red}{we enforce discriminators at different resolutions can differentiate real/fake image, correct/incorrect image-text pairs, and real/fake image pairs jointly.
-This multi-purpose strategy is mutually beneficially }
+To tackle the instability training of GANs, \textcolor{red}{we propose to enforce discriminators at different resolutions can differentiate real/fake image, correct/incorrect image-text pairs, and real/fake image pairs jointly with multiple losses.} We will show that this multi-purpose strategy is mutually beneficially to encourage them only focus on respect duty.
+It is a regularization to limit the discriminators to use unexpected information to make decision.
+
+We have validated our proposed method on three datasets, i.e.
+CUB birds, Oxford-102 flowers, and large-scale COCO datasets.
+Extensive experimental results demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts.
+
+\section{Related Work}
+There are substantial existing methods investigating better usage of GANs \cite{goodfellow2014generative,radford2015unsupervised} for different applications, such as image synthesis \cite{shrivastava2016learning}, (unpaired) pixel-to-pixel translation \cite{isola2016image,zhu2017unpaired},  medical imaging \cite{costa2017towards}, etc \cite{}.
+
+Text-to-image synthesis is one of the most challenging tasks requires accurate semantically consistent mapping from a text vector space to a much higher image space.
+Reed \etal \cite{reed2016generative} introduces the first method that can generate $64{\times}64$ resolution images, which is similar with DCGAN \cite{}.
+This method presents a new strategy to image-text matching aware adversarial training.
+Reed \etal \cite{reed2016learning} propose  generative
+adversarial what-where network (GAWWN) to enable "where and what" instructions in text-to-image synthesis, which uses extra information to help generate $128{\times}128$ resolution images.
+StackGAN \etal \cite{han2017stackgan} propose to a two-stage stacking GAN training approach that is able to generate $256{\times}256$ high resolution vivid images.
+Recently, \cite{dong2017semantic} proposes to learn a joint embedding of images and text so as to re-render a prototype image according to targeting descriptions.
+
+GANs suffer from optimization difficulties.
+Wide methods have been proposed to stabilize the training process, for example, one-side label smoothing and discriminator feature matching \cite{salimans2016improved}, training stronger discriminator is beneficial to encourage generators \cite{arjovsky2017wasserstein}.
+Balancing through a equilibrium enforcing method \cite{berthelot2017began}
+Preventing discriminators from forgetting past samples and re-introduces artifacts \cite{shrivastava2016learning}.
+Increasing the information richness in GANs has been shown very useful \cite{odena2016conditional}.
+
+Leveraging hierarchical representations of neural networks is an effective way to enhance implicit multi-scaling and ensembling for tasks like image classification \cite{lee2015deeply} and edge detection \cite{xie2015holistically}.
+DSN \cite{lee2015deeply} introduces deep supervision in hierarchical convolutional layers to increase the discriminativenss of feature representations.
+In aspect of unsupervised learning, Denton \etal \cite{denton2015deep} trains a cascade of GANs within a Laplacian pyramid framework (LAPGAN) and use each to generate difference images conditioned on noise and images from last pyramid, and gradually increase image resolution.
+StackGAN also shares similar strategy with LAPGAN to increase output resolution.
+Different from these methods,
+
+deep supervision
 

### 2017-10-16 cvpr2018.tex
add architecture" "

@@
 We have validated our proposed method on three datasets, i.e.
-CUB birds, Oxford-102 flowers, and large-scale COCO datasets.
+CUB birds \cite{}, Oxford-102 flowers \cite{}, and large-scale COCO datasets \cite{}.
 Extensive experimental results demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts.
@@
 
-Leveraging hierarchical representations of neural networks is an effective way to enhance implicit multi-scaling and ensembling for tasks like image classification \cite{lee2015deeply} and edge detection \cite{xie2015holistically}.
-DSN \cite{lee2015deeply} introduces deep supervision in hierarchical convolutional layers to increase the discriminativenss of feature representations.
-In aspect of unsupervised learning, Denton \etal \cite{denton2015deep} trains a cascade of GANs within a Laplacian pyramid framework (LAPGAN) and use each to generate difference images conditioned on noise and images from last pyramid, and gradually increase image resolution.
-StackGAN also shares similar strategy with LAPGAN to increase output resolution.
-Different from these methods,
+In term of high resolution image synthesis, cascade networks plays an important role.
+Denton \etal \cite{denton2015deep} trains a cascade of GANs within a Laplacian pyramid framework (LAPGAN) and use each to generate difference images, conditioned on random noises and output from last level of the pyramid, to push up output resolution through by-stage refinement.
+StackGAN also shares similar strategy with LAPGAN.
+Following this Chen \etal \cite{chen2017photographic} present a cascaded refinement networks to synthesis high-resolution scene from semantic maps.
 
-deep supervision
+Leveraging hierarchical representations of neural networks is an effective way to enhance implicit multi-scaling and ensembling for tasks like image classification \cite{lee2015deeply} and pixel or object classification \cite{xie2015holistically,cai2016unified}.
+DSN \cite{lee2015deeply} proposes deep supervision in hierarchical convolutional layers to increase the discriminativeness of feature representations.
+Inspired by DSN, our method that has accompanying deeply-nested adversarial supervision can be viewed as a way to enhance effective feature representation, so as to support end high resolution outputs.
 
@@
 First end-to-end trainable high definition model and set up a new standfsdkfm.
+
+\subsection{Architecture}
+Our proposed network, composed by a generator and a discriminator, is symmetric as well as extensile. We introduce the details as well as motivations.
+
+The generator is simpled composed by three kinds of modules, termed as $K$-repeat residual blocks, stretching layers, and linear composition layers.
+A single residual block in the $K$-repeat residual block contains two convolutional layers (with pre-activated batch normalization (BN) \cite{} and ReLU following \cite{he2016identity}).
+The stretching  layer serves to reduce feature map size and dimension.
+It simply contains an scale-$2$ nearest up-sampling followed by a convolutional layer with BN+ReLU.
+And the linear composition layer is a convolutional layer followed by a Tanh to linearly represent RGB images.
+Starting from a $1024{\times}4{\times}4$ embeddings replicated by a $1024$-d text embedding, the generator simples use $M$ $K$-repeat residual block connected by $M-1$ in-between stretching layers until the feature maps reach to the targeting resolution.
+We use $K{=}2$ in our method.
+So for $256{\times}256$ targeting resolution , there are $M{=}6$ $2$-repeat residual blocks and $5$ stretching layers.
+With a predefined side-output scales $\{S_i\}$, we apply the compositional layers at those scales to generate image at different scales and as inputs of discriminators.
 
@@
 \subsection{Implementation Details}
-
-\subsection{Network Architecture}
 

### 2017-10-18 cvpr2018.tex
4th

--- 2017-10-16 cvpr2018.tex
@@
 We leverage the hierarchical deep representations of convolutional layers and introduce deeply-nested adversarial training to constrain the representations to be compositional for multi-scale image generation.
-To this end, we present a new network architecture, which is symmetric as well as extensile, to gradually upscale generated images to high resolutions.
+To this end, we present a new network architecture, which is symmetric as well as extensile, to push generated images to high resolutions.
 We present a functional generative adversarial networks (GANs) training strategy to encourage more effective multimodal (i.e.
@@
 This method needs individual two-stage training, which is relatively not straightforward to be applied.
-Later on, Dong \etal \ref{dong2017semantic}
+Later on, Dong \etal \cite{dong2017semantic}
 bypasses the difficult of translate vector semantic vector to RGB image and treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-renders a arbitrary-style training image according to targeting semantic descriptions.
 However, the high resolution synthesis ability is still indeterminate.
-Unfortunately, directly training from vector space and synthesize high resolution (e.g. $256{\times}256$)  images is still an open question according to current reported studies.
+Unfortunately, directly training from vector space and synthesize high resolution (e.g. $256{\times}256$) and diverse images is still an open question according to current reported studies.
 
-We outline several empirical reasons for this challenges using GANs.
+We outline several empirical reasons for this challenges using GANs particularly for text-to-image synthesis.
 The first fundamental problem comes from the difficulty of balancing the stability between generators and discriminators.
@@
 The second reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}.
-Keeping semantic consistency as well as diversity in generated images needs more specialized designs for discriminators.
+Keeping semantic consistency as well as diversity in generated images needs more specialized designs for discriminators as well as generators to prevent gradient vanishing.
 
-With careful consideration of these reasons, in this paper, we propose a novel method that can directly generate high resolution images trained in fully end-to-end fashion.
+With careful consideration of these reasons, in this paper, we propose a novel method that can directly generate high resolution images trained in a fully end-to-end manner.
 The contributions are described follows.
 
-To tackle the problem of significant space difference between text and images, we propose to leverage the hierarchical deep representations of convolutional layers through deeply compositional constraints.
+To tackle the problem of significant space difference between text and images, we propose to leverage the hierarchical representations of convolutional layers through deeply compositional constraints.
 In other words, we limit feature maps in different layers to be disentangled RGB image space, such that feature maps of any layers can linearly represent targeting images at corresponding resolutions.
-We introduce accompanying deeply-nested adversarial objective at intermediate layers to achieve this goal, inspired by the deeply-supervised nets (DSN) \cite{lee2015deeply} for image classification.
+We introduce accompanying deeply-nested adversarial objective at intermediate layers to achieve this goal.
 To well cooperate with discriminators, we propose an intuitive network architecture design with hierarchically-nested adversarial objectives that is more efficient and faster to train.
@@
 \section{Related Work}
-There are substantial existing methods investigating better usage of GANs \cite{goodfellow2014generative,radford2015unsupervised} for different applications, such as image synthesis \cite{shrivastava2016learning}, (unpaired) pixel-to-pixel translation \cite{isola2016image,zhu2017unpaired},  medical imaging \cite{costa2017towards}, etc \cite{}.
+There are substantial existing methods investigating better usage of GANs \cite{goodfellow2014generative,radford2015unsupervised} for different applications, such as image synthesis \cite{shrivastava2016learning}, (unpaired) pixel-to-pixel translation \cite{isola2016image,zhu2017unpaired},  medical imaging \cite{costa2017towards}, etc \cite{ledig2016photo,huang2016stacked}.
 
@@
 
-Leveraging hierarchical representations of neural networks is an effective way to enhance implicit multi-scaling and ensembling for tasks like image classification \cite{lee2015deeply} and edge detection \cite{xie2015holistically}.
-DSN \cite{lee2015deeply} introduces deep supervision in hierarchical convolutional layers to increase the discriminativenss of feature representations.
-In aspect of unsupervised learning, Denton \etal \cite{denton2015deep} trains a cascade of GANs within a Laplacian pyramid framework (LAPGAN) and use each to generate difference images conditioned on noise and images from last pyramid, and gradually increase image resolution.
-StackGAN also shares similar strategy with LAPGAN to increase output resolution.
-Different from these methods,
+In term of high resolution image synthesis, cascade networks play an important role.
+Denton \etal \cite{denton2015deep} trains a cascade of GANs within a Laplacian pyramid framework (LAPGAN) and use each to generate difference images, conditioned on random noises and output from last level of the pyramid, to push up output resolution through by-stage refinement.
+StackGAN also shares similar strategy with LAPGAN.
+Following this Chen \etal \cite{chen2017photographic} present a cascaded refinement networks to synthesis high-resolution scene from semantic maps.
+Compared with these strategies that progressively training low- to high-resolution GANs, our method takes advantages of multi-level representation and encourage implicit multi-resolution ensembling, so as to enable end-to-end high-resolution image synthesis.
+A recent work from Huang \etal \cite{huang2016stacked}
+shows a top-down stack GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method.
+However, this method need multiple paired  bottom-up discriminators and pre-training.
+The usage for high-resolution image is difficult (e.g.
+memory bottleneck) and need verification.
+More advantages of our method compared with others will be demonstrated in the following.
 
-deep supervision
+Leveraging hierarchical representations of neural networks is an effective way to enhance implicit multi-scaling and ensembling for tasks such as image classification \cite{lee2015deeply} and pixel or object classification \cite{xie2015holistically,cai2016unified,long2015fully}.
+DSN \cite{lee2015deeply} proposes deep supervision in hierarchical convolutional layers to increase the discriminativeness of feature representations.
+Our method is partially inspired by DSN.
+We introduce accompanying hierarchically-nested adversarial supervision, which enhances and regularizes layer representations to support final high resolution outputs.
 
-\subsection{Summarize different architectures}
-refer to HED.
+%
+%
+%
+%\subsection{Summarize different architectures}
+%refer to HED.
 
@@
 First end-to-end trainable high definition model and set up a new standfsdkfm.
+
+\subsection{Architecture Design}
+Our proposed network, composed by a generator and a discriminator, is symmetric as well as extensile. We introduce the details as well as motivations.
+
+\textbf{Generator} The generator is simpled composed by three kinds of modules, termed as $K$-repeat res-blocks, stretching layers, and linear compression layers.
+A single res-block in the $K$-repeat res-block is a standard residual block  \cite{he2016identity} containing two convolutional (conv) layers (with batch normalization (BN) \cite{ioffe2015batch} and ReLU).
+The stretching layer serves to reduce feature map size and dimension.
+It simply contains an scale-$2$ nearest up-sampling layer followed by a convolutional layer with BN+ReLU.
+And the linear compression layer is a conv layer followed by a Tan, whose compact design enforces feature maps in conv blocks can linearly represent RGB images at arbitrary scales.
+Starting from a $1024{\times}4{\times}4$ embeddings replicated by a $1024$-d text embedding, the generator simples use $M$ $K$-repeat res-blocks connected by $M{-}1$ in-between stretching layers until the feature maps reach to the targeting resolution.
+We use $K{=}2$ in our method.
+So for $256{\times}256$ targeting resolution, there are $M{=}6$ $2$-repeat res-blocks and $5$ stretching layers.
+Such simple and symmetric design makes our generator very effective probably because easier gradient backpropagation.
+We will verify in experiments.
+With a predefined side-output scales $\{S_i\}$, we apply the compression layer at those scales to produce synthetic images.
+
+\textbf{Discriminator} The discriminator simply contains consecutive stride-2 convolutional layers with BN and LeakyReLU  (the depth changes according to the input size) until the feature map has $512{\times}4{\times}4$ dimension.
+There two branches are added on top of it for multi-purpose discriminator design (see next section) .
+One is a direct $4{\times}4$ conv layers to produce a 2-d vector to classify real and fake.
+Another one first concatenate $128{\times}4{\times}4$ text embedding (replicated from a $128$-d text embedding).
+Then we use an $1{\times}1$ conv to fuse text and image information; it is critical to guarantee the semantic consistency in the final results.
+Finally, a $4{\times}4$ conv layer produces a 2-d vector for classification.
+
+All intermediate conv layers use $3{\times}3$ kernels (with reflection padding and no bias).
+We remove ReLU after the skip-addition of each residual block, with an intention to reduce sparse gradients.
+We also experimented other normalization (i.e.
+instance normalization \cite{ulyanov2016instance} and layer normalization \cite{ba2016layer}) used by \cite{zhu2017unpaired,chen2017photographic}.
+Both are not satisfactory.
 
@@
 
-\subsection{Network Architecture}
+\section{Experiments}
+In this section, we evaluate the proposed method both qualitatively and quantitatively on three public datasets. We mainly compare to the state-of-the art StackGAN \cite{han2017stackgan}.
 
-\section{Experiments}
 \subsection{Evaluation metric}
@@
 
+\section{Conclusion}
+
 {\small

### 2017-10-20 cvpr2018.tex
5th

@@
 \usepackage{varwidth}
+\usepackage{bm}
 % If you comment hyperref and then uncomment it, you should delete
@@
 %%%%%%%%% TITLE
-\title{Semantic Photographic Image Synthesis \\ with a Hierarchically-nested Adversarial Network}
+\title{Semantic High-definition Image Synthesis \\ with a Hierarchically-nested Adversarial Network}
 
@@
 This paper presents a novel  and effective approach to deal with the challenging task of generating synthetic photographic image conditioned on semantic image descriptions.
-We leverage the hierarchical deep representations of convolutional layers and introduce deeply-nested adversarial training to constrain the representations to be compositional for multi-scale image generation.
+We leverage the hierarchical deep representations of convolutional layers and introduce deeply-nested adversarial training to regularize the representations to be compositional for multi-scale image generation.
 To this end, we present a new network architecture, which is symmetric as well as extensile, to push generated images to high resolutions.
 We present a functional generative adversarial networks (GANs) training strategy to encourage more effective multimodal (i.e.
-image and text) information utilization in order to enhance multi-purpose adversary between real and fake.
+image and text) information utilization in order to enhance multi-purpose adversary between real and fake distribution.
 Our method, at the first time, shows a fully end-to-end trainable network that can generate $256{\times}256$ images and is stackable to $512{\times}512$ resolution or higher with arbitrary extensions.
@@
 But this method only handles image up to $64{\times}64$ resolution and usually is barely to generate vivid object details.
-Based on \cite{reed2016generative}, Zhang \etal \cite{han2017stackganan} present a successful approach (StackGAN) by stacking another GAN to generate high quality and compelling $256{\times}256$ images given inputs of low resolution $64{\times}64$ synthetic images.
+Based on \cite{reed2016generative}, Zhang \etal \cite{han2017stackgan} present a successful approach (StackGAN) by stacking another GAN to generate high quality and compelling $256{\times}256$ images given inputs of low resolution $64{\times}64$ synthetic images.
 This method needs individual two-stage training, which is relatively not straightforward to be applied.
@@
 Extensive experimental results demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts.
+All source code will be released.
 
 \section{Related Work}
-There are substantial existing methods investigating better usage of GANs \cite{goodfellow2014generative,radford2015unsupervised} for different applications, such as image synthesis \cite{shrivastava2016learning}, (unpaired) pixel-to-pixel translation \cite{isola2016image,zhu2017unpaired},  medical imaging \cite{costa2017towards}, etc \cite{ledig2016photo,huang2016stacked}.
+Deep generative models grows wide interests recently, including GANs \cite{goodfellow2014generative}, Variational Auto-encoders (VAE) \cite{kingma2013auto}, etc \cite{oord2016pixel}. 
+There are substantial existing methods investigating better usage of GANs for different applications, such as image synthesis \cite{radford2015unsupervised, shrivastava2016learning}, (unpaired) pixel-to-pixel translation \cite{isola2016image,zhu2017unpaired},  medical imaging \cite{costa2017towards}, etc \cite{ledig2016photo,huang2016stacked}.
 
-Text-to-image synthesis is one of the most challenging tasks requires accurate semantically consistent mapping from a text vector space to a much higher image space.
+Text-to-image synthesis not only requires diverse and high-quality generation but also requires precise semantically consistent mapping in the image space.
 Reed \etal \cite{reed2016generative} introduces the first method that can generate $64{\times}64$ resolution images, which is similar with DCGAN \cite{}.
@@
 
-GANs suffer from optimization difficulties.
-Wide methods have been proposed to stabilize the training process, for example, one-side label smoothing and discriminator feature matching \cite{salimans2016improved}, training stronger discriminator is beneficial to encourage generators \cite{arjovsky2017wasserstein}.
+Learning a continuous mapping from low-dimensional embeddings to complex real data distribution is a long-standing problem.
+Although GANs have made significant progressive, there are still many not well-solved difficulties, e.g.
+training instability.
+Wide methods have been proposed to stabilize the training process, through various training techniques \cite{salimans2016improved,arjovsky2017wasserstein,berthelot2017began,shrivastava2016learning,odena2016conditional}, auxiliary regularization from outside knowledge (e.g.
+labels, imagenet CNNs , etc) \cite{dosovitskiy2016generating,ledig2016photo}.
+Moreover, such difficulties grow significantly when targeting image resolution increases.
+
+%for example, label smoothing and discriminator feature matching \cite{salimans2016improved, }, training stronger discriminator is beneficial to encourage generators \cite{arjovsky2017wasserstein}.
 Balancing through a equilibrium enforcing method \cite{berthelot2017began}
-Preventing discriminators from forgetting past samples and re-introduces artifacts \cite{shrivastava2016learning}.
+%Preventing discriminators from forgetting past samples and re-introduces artifacts \cite{shrivastava2016learning}.
 Increasing the information richness in GANs has been shown very useful \cite{odena2016conditional}.
 
-In term of high resolution image synthesis, cascade networks play an important role.
+To synthesize high resolution image, cascade networks play an important role to decompose original difficult tasks to multiple subtasks.
 Denton \etal \cite{denton2015deep} trains a cascade of GANs within a Laplacian pyramid framework (LAPGAN) and use each to generate difference images, conditioned on random noises and output from last level of the pyramid, to push up output resolution through by-stage refinement.
 StackGAN also shares similar strategy with LAPGAN.
-Following this Chen \etal \cite{chen2017photographic} present a cascaded refinement networks to synthesis high-resolution scene from semantic maps.
+Following this strategy, Chen \etal \cite{chen2017photographic} present a cascaded refinement networks to synthesis high-resolution scene from semantic maps.
+Huang \etal \cite{huang2016stacked}
+shows a top-down stack GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method.
+However, this method need multiple symmetric  bottom-up discriminators and pre-training of discriminators.
+The usage for high-resolution image is unclear \cite{han2017stackgan}.
 Compared with these strategies that progressively training low- to high-resolution GANs, our method takes advantages of multi-level representation and encourage implicit multi-resolution ensembling, so as to enable end-to-end high-resolution image synthesis.
-A recent work from Huang \etal \cite{huang2016stacked}
-shows a top-down stack GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method.
-However, this method need multiple paired  bottom-up discriminators and pre-training.
-The usage for high-resolution image is difficult (e.g.
-memory bottleneck) and need verification.
-More advantages of our method compared with others will be demonstrated in the following.
+
+%More advantages of our method compared with others will be demonstrated in the following.
 
@@
 DSN \cite{lee2015deeply} proposes deep supervision in hierarchical convolutional layers to increase the discriminativeness of feature representations.
-Our method is partially inspired by DSN.
-We introduce accompanying hierarchically-nested adversarial supervision, which enhances and regularizes layer representations to support final high resolution outputs.
+Our method is partially inspired by supervised CNNs with deep supervision \cite{lee2015deeply,xie2015holistically}.
+We introduce accompanying hierarchically-nested adversarial supervision, with a goal to enhance and regularizes layer representations to support final high resolution outputs.
 
@@
 Starting from a $1024{\times}4{\times}4$ embeddings replicated by a $1024$-d text embedding, the generator simples use $M$ $K$-repeat res-blocks connected by $M{-}1$ in-between stretching layers until the feature maps reach to the targeting resolution.
-We use $K{=}2$ in our method.
-So for $256{\times}256$ targeting resolution, there are $M{=}6$ $2$-repeat res-blocks and $5$ stretching layers.
-Such simple and symmetric design makes our generator very effective probably because easier gradient backpropagation.
+So for $256{\times}256$ targeting resolution with $K{=}1$, there are $M{=}6$ $1$-repeat res-blocks and $5$ stretching layers.
+Such simple and symmetric design makes our generator helpful for gradient flows.
 We will verify in experiments.
@@
 
-\textbf{Discriminator} The discriminator simply contains consecutive stride-2 convolutional layers with BN and LeakyReLU  (the depth changes according to the input size) until the feature map has $512{\times}4{\times}4$ dimension.
+\textbf{Discriminator} The discriminator simply contains consecutive stride-2 conv layers with BN and LeakyReLU \cite{} (the depth changes according to the input size) until the feature map has $512{\times}4{\times}4$ dimension.
 There two branches are added on top of it for multi-purpose discriminator design (see next section) .
@@
 Then we use an $1{\times}1$ conv to fuse text and image information; it is critical to guarantee the semantic consistency in the final results.
-Finally, a $4{\times}4$ conv layer produces a 2-d vector for classification.
+Finally, a $4{\times}4$ conv layer produces a 2-d vector.
 
@@
 \section{Experiments}
-In this section, we evaluate the proposed method both qualitatively and quantitatively on three public datasets. We mainly compare to the state-of-the art StackGAN \cite{han2017stackgan}.
+In this section, we evaluate the proposed method both qualitatively and quantitatively on three public datasets.
+StackGAN \cite{han2017stackgan} generates synthetic images up to  $256{\times}256$ resolution.
+We show that our method can generates images up to  $512{\times}512$.
+We denote our method as HDGAN, referring as High-definition results as well as the design of hierarchically-nested discriminators.
+
+%We mainly compare to the state-of-the art StackGAN \cite{han2017stackgan} for text-to-image synthesis and demonstrate substantially improvement.
 
 \subsection{Evaluation metric}
-\subsection{Quantitative and qualitative results}
+
+\begin{table}[t] % retrieval
+	\begin{center}
+		\begin{tabularx}{.477\textwidth}{c|ccc}
+			\specialrule{1.5pt}{0pt}{0pt}  
+			\multirow{2}{*}{Method}	& \multicolumn{3}{c}{Dataset}	\\ \cline{2-4}
+							 		&	 CUB		&	Oxford  & COCO		     \\ \hline
+			GAN-INT-CLS 	&	$2.88{\pm}.04$		& 	$2.66{\pm}.03$		& $7.88{\pm}.07$	 \\
+			GAWWN 	  &		$3.60{\pm}.07$		&     -      &          - \\ 
+			StackGAN     &		$3.70{\pm}.04$	&	 $3.20{\pm}.01$			&  $8.45{\pm}.03$		\\ \hline
+		%	StackGAN$^\star$     &		$3.89{\pm}.05$	&	 $3.16{\pm}.01$			&  $8.45{\pm}.03$		\\ \hline
+			HDGAN 		&	$\bm{4.01{\pm}.04}$	&	$ \bm{3.45{\pm}.07}$			&  -  \\ \hline
+		\end{tabularx} \vspace{-.4cm}
+	\end{center}
+	\caption{The inception-score evaluation on three datasets.
+The higher score reflects more meaningful synthetic images and higher diversity.
+The proposed HDGAN outperforms others significantly.} \label{table:score}
+\end{table}
+
+\subsection{Comparative Results}
+We compare our results with GAN-INT-CLS \cite{reed2016generative}, GAWWN \cite{reed2016learning}, and  StackGAN \cite{han2017stackgan}. StackGAN is currently the state of the art method.
+
+Table \ref{table:score} shows the quantitative evaluation.
+HDGAN achieves significantly improvement compared to other methods.
+For example, HDGAN improves GAN-INT-CLS by ${\sim}30.1\%$  and ${\sim}8.4\%$ on CUB.
+
+   Specifically, compared with StackGAN, HDGAN improves
 

### 2017-10-20 cvpr2018.tex
6th

@@
 Later on, Dong \etal \cite{dong2017semantic}
-bypasses the difficult of translate vector semantic vector to RGB image and treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-renders a arbitrary-style training image according to targeting semantic descriptions.
+bypasses the difficult of translate vector semantic vector to RGB image and treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-renders a arbitrary-style training ($128{\times}128$) image according to targeting semantic descriptions.
 However, the high resolution synthesis ability is still indeterminate.
@@
 We outline several empirical reasons for this challenges using GANs particularly for text-to-image synthesis.
-The first fundamental problem comes from the difficulty of balancing the stability between generators and discriminators.
+The first problem comes from the fundamental difficulty of balancing the stability between generators and discriminators.
 There are many a rich number of literature trying to stabilize GAN training \cite{salimans2016improved}.
@@
 The second reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}.
-Keeping semantic consistency as well as diversity in generated images needs more specialized designs for discriminators as well as generators to prevent gradient vanishing.
+Keeping semantic consistency as well as diversity in generated images needs more specialized designs for discriminators to generate effective gradients, as well as generators to prevent gradient vanishing.
 
-With careful consideration of these reasons, in this paper, we propose a novel method that can directly generate high resolution images trained in a fully end-to-end manner.
+With careful consideration of these reasons, in this paper, we propose a novel method that can directly generate high resolution images trained in a fully end-to-end manner - a Vanilla fashion.
 The contributions are described follows.
@@
 
-To tackle the instability training of GANs, \textcolor{red}{we propose to enforce discriminators at different resolutions can differentiate real/fake image, correct/incorrect image-text pairs, and real/fake image pairs jointly with multiple losses.} We will show that this multi-purpose strategy is mutually beneficially to encourage them only focus on respect duty.
+To tackle the instable training of GANs, 
+\textcolor{red}{we propose to enforce discriminators at different resolutions can differentiate real/fake image, correct/incorrect image-text pairs, and real/fake image pairs jointly with multiple losses.} We will show that this multi-purpose conditional strategy is mutually beneficial to encourage them only focus on respect duties.
 It is a regularization to limit the discriminators to use unexpected information to make decision.
@@
 Text-to-image synthesis not only requires diverse and high-quality generation but also requires precise semantically consistent mapping in the image space.
-Reed \etal \cite{reed2016generative} introduces the first method that can generate $64{\times}64$ resolution images, which is similar with DCGAN \cite{}.
+Reed \etal \cite{reed2016generative} introduces the first method that can generate $64{\times}64$ resolution images, which is similar with DCGAN \cite{radford2015unsupervised}.
 This method presents a new strategy to image-text matching aware adversarial training.
@@
 StackGAN \etal \cite{han2017stackgan} propose to a two-stage stacking GAN training approach that is able to generate $256{\times}256$ high resolution vivid images.
-Recently, \cite{dong2017semantic} proposes to learn a joint embedding of images and text so as to re-render a prototype image according to targeting descriptions.
+Recently, Dong \etal \cite{dong2017semantic} proposes to learn a joint embedding of images and text so as to re-render a prototype image according to targeting descriptions.
+Cha \etal \cite{dash2017tac} use the perceptional loss and Dash \etal \cite{dash2017tac} use image labels to assist GAN training.
 
@@
 training instability.
-Wide methods have been proposed to stabilize the training process, through various training techniques \cite{salimans2016improved,arjovsky2017wasserstein,berthelot2017began,shrivastava2016learning,odena2016conditional}, auxiliary regularization from outside knowledge (e.g.
-labels, imagenet CNNs , etc) \cite{dosovitskiy2016generating,ledig2016photo}.
-Moreover, such difficulties grow significantly when targeting image resolution increases.
+Wide methods have been proposed to address those tasks, through various stabilization training techniques \cite{salimans2016improved,arjovsky2017wasserstein,berthelot2017began,shrivastava2016learning,odena2016conditional}, regularization using outside knowledge (e.g.
+image labels, ImageNet CNNs, etc) \cite{dosovitskiy2016generating,ledig2016photo,dash2017tac,dash2017tac}.
+While our method does not use any extra information apart from input text and images.
+Moreover, such difficulties grow significantly as targeting image resolution increases.
 
@@
 The usage for high-resolution image is unclear \cite{han2017stackgan}.
-Compared with these strategies that progressively training low- to high-resolution GANs, our method takes advantages of multi-level representation and encourage implicit multi-resolution ensembling, so as to enable end-to-end high-resolution image synthesis.
+Compared with these strategies that progressively train low- to high-resolution GANs, our method takes advantages of multi-level representations for implicit subtask integration, which enables end-to-end high-resolution image synthesis.
 
@@
 We introduce accompanying hierarchically-nested adversarial supervision, with a goal to enhance and regularizes layer representations to support final high resolution outputs.
+\begin{figure}[t]
+	\centering
+	%	\includegraphics[width=0.48\textwidth]{}
+	\caption{} \label{fig:archs}
+\end{figure}
 
@@
 %refer to HED.
+\begin{figure}[t]
+	\centering
+%	\includegraphics[width=0.48\textwidth]{}
+	\caption{} \label{fig:archs-compare}
+\end{figure}
 
 \section{Method}
-First end-to-end trainable high definition model and set up a new standfsdkfm.
+Figure \ref{fig:archs} illustrate the overall method.
 
@@
 
+\textbf{Advantages} Figure \ref{fig:archs-compare} illustrates the architecture difference between widely-used cascade strategy \cite{han2017stackgan,denton2015deep} and our strategy.
+Compared with it,
+
 \subsection{Preliminaries}
@@
 In this section, we evaluate the proposed method both qualitatively and quantitatively on three public datasets.
-StackGAN \cite{han2017stackgan} generates synthetic images up to  $256{\times}256$ resolution.
-We show that our method can generates images up to  $512{\times}512$.
 We denote our method as HDGAN, referring as High-definition results as well as the design of hierarchically-nested discriminators.
@@
 
-\subsection{Evaluation metric}
+\textbf{Dataset} We use three datasets for evaluation. \textcolor{red}{Yuanpu address}
+
+\textbf{Evaluation metric}
+\textcolor{red}{Yuanpu address}
 
@@
 			GAWWN 	  &		$3.60{\pm}.07$		&     -      &          - \\ 
-			StackGAN     &		$3.70{\pm}.04$	&	 $3.20{\pm}.01$			&  $8.45{\pm}.03$		\\ \hline
+			StackGAN     &		$3.70{\pm}.04$	&	 $3.20{\pm}.01$			&  $8.45{\pm}.03$		\\ 
 		%	StackGAN$^\star$     &		$3.89{\pm}.05$	&	 $3.16{\pm}.01$			&  $8.45{\pm}.03$		\\ \hline
+			TAC-GAN	 &	-		&		$\bm{3.45{\pm}.05}$		& -	\\	\hline
 			HDGAN 		&	$\bm{4.01{\pm}.04}$	&	$ \bm{3.45{\pm}.07}$			&  -  \\ \hline
@@
 
+\begin{figure}[t]
+	\centering
+	%	\includegraphics[width=0.48\textwidth]{}
+	\caption{Results on CUB} \label{fig:vis-cub}
+\end{figure}
+\begin{figure}[t]
+	\centering
+	%	\includegraphics[width=0.48\textwidth]{}
+	\caption{Results on Oxford} \label{fig:vis-oxford}
+\end{figure}
+
+%
 \subsection{Comparative Results}
-We compare our results with GAN-INT-CLS \cite{reed2016generative}, GAWWN \cite{reed2016learning}, and  StackGAN \cite{han2017stackgan}. StackGAN is currently the state of the art method.
+We compare our results with GAN-INT-CLS \cite{reed2016generative}, GAWWN \cite{reed2016learning}, and  StackGAN \cite{han2017stackgan}, and TAC-GAN \cite{dash2017tac}.
+StackGAN is currently the state of the art method in general that is comprehensively validated.
+StackGAN \cite{han2017stackgan} generates synthetic images up to $256{\times}256$ resolution.
+We show that our method can generates images up to  $512{\times}512$.
 
@@
 
-   Specifically, compared with StackGAN, HDGAN improves
+\subsection{Case study}
+\textbf{Generalization to real user test}
+We test the generalization of our method by asking a user to write a sentence
 
-\subsection{Case study}
-\subsubsection{Arbitrary text description}
 \subsubsection{Style transfer}
+\textcolor{red}{Yuanpu address}
 
-\section{Ablation study}
-\subsubsection{loss study}
-\subsubsection{architecture study}
+\begin{table}[t] % retrieval
+	\begin{center}
+		\begin{tabularx}{.268\textwidth}{ccc|c}
+			\specialrule{1.5pt}{0pt}{0pt}  
+			\multicolumn{3}{c|}{Components}	&  \multirow{2}{*}{Score}	\\ \cline{1-3}
+				 64	& 128	& 256 			& 		\\ \hline
+					&  		&	\checkmark	&		\\ 
+						&  	\checkmark	&	\checkmark	&		\\
+				\checkmark	&  			&	\checkmark	&		\\
+				\checkmark	&  \checkmark		&	\checkmark	&	$\bm{4.01{\pm}.04}$ \\
+
+		\end{tabularx}
+	\end{center} \vspace{-.4cm}
+	\caption{Ablation study for hierarchically-nested adversarial supervision.} \label{table:deep-nest}
+\end{table}
+
+\section{On the effects of Individual Components}
+\subsection{Hierarchically-nested adversary}
+Recall that the proposed hierarchically-nested adversarial supervision plays a role of regularizing the layer representations.
+In practice, we apply it on feature maps at $\{64, 128, 256\}$.
+In Table \ref{table:deep-nest}, we show the inception score by removing partial of supervision components.
+As can be observed, ...
+
+StackGAN emphasizes the importance of using text embeddings in the (stage-II) mid-level features of the $256{\times}256$ generator by showing an large drop from $3.7$ to $3.45$ without doing so.
+The text embedding plays an important role in maintaining the diversity and semantic consistency in StackGAN.
+While in our method, we only use text embeddings at the input.
+Our improved results demonstrate that our hierarchically-nested adversarial supervision regularizes the generator to achieve the same goal.
+
+\subsection{Multi-purpose discriminator}
+\textcolor{red}{Yuanpu address}
+
+\begin{figure}[t]
+	\centering
+	%	\includegraphics[width=0.48\textwidth]{}
+	\caption{} \label{fig:vallina-res}
+\end{figure}
+
+\subsection{Design principles}
+Note that for text-to-image synthesis, StackGAN is the only successful method to generate $256{\times}256$ images.
+At the same time, it also shows the difficulty (impossibility) of directly training a vanilla $256{\times}256$ GAN, which fails to generate meaningful images. 
+We test this extreme case using our method by removing all nested supervisions (the first row of Table \ref{table:deep-nest}). 
+Our method actually can still generate fairly good.
+Figure \ref{fig:vallina-res} shows the qualitatively results.
+This strongly proves the effectiveness of our designs in generators and discriminator losses.
+
+Initially, we tried to share top layers of the hierarchical discriminators of HDGAN inspired by \cite{liu2017unsupervised} with an intuition to reduce their variances and unify their common goal (i.e.
+differentiates real and fake despite difficult scales).
+However, we did not find any benefits from this and our independent discriminators can be well-trained by themselves.
+
+BN is known to be problematic for ....
 
 \section{Conclusion}
+...
 

### 2017-10-21 cvpr2018.tex
method

--- 2017-10-18 cvpr2018.tex
@@
 \usepackage{array,booktabs,arydshln,xcolor} % for widening table line
-\usepackage{amsthm}
+\usepackage{amsthm,bm}
 \usepackage{epstopdf}
-\usepackage{algorithm}
-%\usepackage{algorithmic}
+
 \usepackage{amsthm}
 \usepackage{multirow}
-\usepackage[algo2e]{algorithm2e}
-\usepackage[outercaption]{sidecap}    
+
 \usepackage{float}
@@
 \usepackage{varwidth}
+
+\usepackage{algpseudocode,algorithm,algorithmicx}
+\newcommand*\DNA{\textsc{dna}}
+
+\newcommand*\Let[2]{\State #1 $\gets$ #2}
+\algrenewcommand\algorithmicrequire{\textbf{Precondition:}}
+\algrenewcommand\algorithmicensure{\textbf{Postcondition:}}
+
+\makeatletter
+\def\BState{\State\hskip-\ALG@thistlm}
+\makeatother
+
 % If you comment hyperref and then uncomment it, you should delete
@@
 We leverage the hierarchical deep representations of convolutional layers and introduce deeply-nested adversarial training to constrain the representations to be compositional for multi-scale image generation.
-To this end, we present a new network architecture, which is symmetric as well as extensile, to push generated images to high resolutions.
+To this end, we present a new network architecture, which is symmetric as well as extensile, to gradually upscale generated images to high resolutions.
 We present a  functional generative adversarial networks (GANs) training strategy to encourage more effective multimodal (i.e.
@@
 This method needs individual two-stage training, which is relatively not straightforward to be applied.
-Later on, Dong \etal \cite{dong2017semantic}
+Later on, Dong \etal \ref{dong2017semantic}
 bypasses the difficult of translate vector semantic vector to RGB image and treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-renders a arbitrary-style training image according to targeting semantic descriptions.
 However, the high resolution synthesis ability is still indeterminate.
-Unfortunately, directly training from vector space and synthesize high resolution (e.g. $256{\times}256$) and diverse images is still an open question according to current reported studies.
+Unfortunately, directly training from vector space and synthesize high resolution (e.g. $256{\times}256$)  images is still an open question according to current reported studies.
 
-We outline several empirical reasons for this challenges using GANs particularly for text-to-image synthesis.
+We outline several empirical reasons for this challenges using GANs.
 The first fundamental problem comes from the difficulty of balancing the stability between generators and discriminators.
@@
 The second reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}.
-Keeping semantic consistency as well as diversity in generated images needs more specialized designs for discriminators as well as generators to prevent gradient vanishing.
+Keeping semantic consistency as well as diversity in generated images needs more specialized designs for discriminators.
 
-With careful consideration of these reasons, in this paper, we propose a novel method that can directly generate high resolution images trained in a fully end-to-end manner.
+With careful consideration of these reasons, in this paper, we propose a novel method that can directly generate high resolution images trained in fully end-to-end fashion.
 The contributions are described follows.
 
-To tackle the problem of significant space difference between text and images, we propose to leverage the hierarchical representations of convolutional layers through deeply compositional constraints.
+To tackle the problem of significant space difference between text and images, we propose to leverage the hierarchical deep representations of convolutional layers through deeply compositional constraints.
 In other words, we limit feature maps in different layers to be disentangled RGB image space, such that feature maps of any layers can linearly represent targeting images at corresponding resolutions.
-We introduce accompanying deeply-nested adversarial objective at intermediate layers to achieve this goal.
+We introduce accompanying deeply-nested adversarial objective at intermediate layers to achieve this goal, inspired by the deeply-supervised nets (DSN) \cite{lee2015deeply} for image classification.
 To well cooperate with discriminators, we propose an intuitive network architecture design with hierarchically-nested adversarial objectives that is more efficient and faster to train.
@@
 We have validated our proposed method on three datasets, i.e.
-CUB birds \cite{}, Oxford-102 flowers \cite{}, and large-scale COCO datasets \cite{}.
+CUB birds, Oxford-102 flowers, and large-scale COCO datasets.
 Extensive experimental results demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts.
@@
 \section{Related Work}
-There are substantial existing methods investigating better usage of GANs \cite{goodfellow2014generative,radford2015unsupervised} for different applications, such as image synthesis \cite{shrivastava2016learning}, (unpaired) pixel-to-pixel translation \cite{isola2016image,zhu2017unpaired},  medical imaging \cite{costa2017towards}, etc \cite{ledig2016photo,huang2016stacked}.
+There are substantial existing methods investigating better usage of GANs \cite{goodfellow2014generative,radford2015unsupervised} for different applications, such as image synthesis \cite{shrivastava2016learning}, (unpaired) pixel-to-pixel translation \cite{isola2016image,zhu2017unpaired},  medical imaging \cite{costa2017towards}, etc \cite{}.
 
@@
 
-In term of high resolution image synthesis, cascade networks play an important role.
-Denton \etal \cite{denton2015deep} trains a cascade of GANs within a Laplacian pyramid framework (LAPGAN) and use each to generate difference images, conditioned on random noises and output from last level of the pyramid, to push up output resolution through by-stage refinement.
-StackGAN also shares similar strategy with LAPGAN.
-Following this Chen \etal \cite{chen2017photographic} present a cascaded refinement networks to synthesis high-resolution scene from semantic maps.
-Compared with these strategies that progressively training low- to high-resolution GANs, our method takes advantages of multi-level representation and encourage implicit multi-resolution ensembling, so as to enable end-to-end high-resolution image synthesis.
-A recent work from Huang \etal \cite{huang2016stacked}
-shows a top-down stack GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method.
-However, this method need multiple paired  bottom-up discriminators and pre-training.
-The usage for high-resolution image is difficult (e.g.
-memory bottleneck) and need verification.
-More advantages of our method compared with others will be demonstrated in the following.
+Leveraging hierarchical representations of neural networks is an effective way to enhance implicit multi-scaling and ensembling for tasks like image classification \cite{lee2015deeply} and edge detection \cite{xie2015holistically}.
+DSN \cite{lee2015deeply} introduces deep supervision in hierarchical convolutional layers to increase the discriminativenss of feature representations.
+In aspect of unsupervised learning, Denton \etal \cite{denton2015deep} trains a cascade of GANs within a Laplacian pyramid framework (LAPGAN) and use each to generate difference images conditioned on noise and images from last pyramid, and gradually increase image resolution.
+StackGAN also shares similar strategy with LAPGAN to increase output resolution.
+Different from these methods,
 
-Leveraging hierarchical representations of neural networks is an effective way to enhance implicit multi-scaling and ensembling for tasks such as image classification \cite{lee2015deeply} and pixel or object classification \cite{xie2015holistically,cai2016unified,long2015fully}.
-DSN \cite{lee2015deeply} proposes deep supervision in hierarchical convolutional layers to increase the discriminativeness of feature representations.
-Our method is partially inspired by DSN.
-We introduce accompanying hierarchically-nested adversarial supervision, which enhances and regularizes layer representations to support final high resolution outputs.
+deep supervision
 
-%
-%
-%
-%\subsection{Summarize different architectures}
-%refer to HED.
+\subsection{Summarize different architectures}
+refer to HED.
+
+\section{Preliminary}
+\subsection{Generative Adversary Network}
+Generative adversary networks (GANs) are composed of a generator $G$ and a discriminator $D$, which are alternatively trained to compete with each other in a two-player minimax game.
+The discriminator $D$ is optimized to distinguish the synthesized images from the real images, meanwhile, the generator $G$ is trained to fool the discriminator by trying to convert an input distribution $p_z$ to the true data distribution $p_{data}$.
+Concretely, the overall training procedure can be analogous to the following two-player min-max game $V(D, G)$,
+ \begin{equation}
+ \label{game}
+ \begin{split}
+  \underset{G}{\min}\ \underset{D}{\max}\ V(D, G) =  &\mathbb{E}_{x\sim p_{data}}[log D(x)] +  \\
+					  &\mathbb{E}_{z\sim p_{z}}[log (1-D(G(z)))]		   
+ \end{split}
+ \end{equation}
+where $x$ is a real image sampled from the true data distribution $p_{data}$, $z$ is a noise vector usually sampled from some predefined distribution $p_{z}$ (e.g., Gaussian distribution).
+In practice, It's been shown to work better for the generator $G$ to minimizing $-log(D(G(z)))$ rather than $log(1-D(G(z)))$, namely, the $log(D)$ trick.
+
+Conditioned GAN \cite{isola2016image} is a variation of traditional GAN where both the generator network $G$ and discriminator network $D$ are conditioned on an additional condition vector besides the noise vector.
+In this paper, we consider the task of training a deep  generative adversarial network conditioned on the embedding of the text descriptions of the images.
 
 \section{Method}
-First end-to-end trainable high definition model and set up a new standfsdkfm.
+To generate high-resolution photo-realistic images from text embeddings, we propose a simple and effective multi-level Generative Adversarial Network architecture.
+Our model mainly consists of the following key-components,
 
-\subsection{Architecture Design}
-Our proposed network, composed by a generator and a discriminator, is symmetric as well as extensile. We introduce the details as well as motivations.
+\textbf{Multi-level side output:} instead of only predicting the high resolution in the final output, our model is designed to predict multi-level images of gradually increasing dimension (e.g., 256$\times$256 as the final output with 64$\times$64 and 128$\times$128 being the side output) as the side outputs.
+In principle, the lower-resolution side output is forced to learn the rough structure (e.g., object sketch, color information and background) of the images, the subsequent higher-resolution path is used to add more details to the images.
+The lower-level side output works by regularizing the lower-level image feature.
+Since the model is trained in an end-to-end fashion, we can observe more consistent information exhibited in both lower and higher-resolution outputs than stackGan\cite{han2017stackgan}.
+This type of side output is also proven useful because it allows short path between image supervision information to the hidden feature maps, which could potentially helps training.
 
-\textbf{Generator} The generator is simpled composed by three kinds of modules, termed as $K$-repeat res-blocks, stretching layers, and linear compression layers.
-A single res-block in the $K$-repeat res-block is a standard residual block  \cite{he2016identity} containing two convolutional (conv) layers (with batch normalization (BN) \cite{ioffe2015batch} and ReLU).
-The stretching layer serves to reduce feature map size and dimension.
-It simply contains an scale-$2$ nearest up-sampling layer followed by a convolutional layer with BN+ReLU.
-And the linear compression layer is a conv layer followed by a Tan, whose compact design enforces feature maps in conv blocks can linearly represent RGB images at arbitrary scales.
-Starting from a $1024{\times}4{\times}4$ embeddings replicated by a $1024$-d text embedding, the generator simples use $M$ $K$-repeat res-blocks connected by $M{-}1$ in-between stretching layers until the feature maps reach to the targeting resolution.
-We use $K{=}2$ in our method.
-So for $256{\times}256$ targeting resolution, there are $M{=}6$ $2$-repeat res-blocks and $5$ stretching layers.
-Such simple and symmetric design makes our generator very effective probably because easier gradient backpropagation.
-We will verify in experiments.
-With a predefined side-output scales $\{S_i\}$, we apply the compression layer at those scales to produce synthetic images.
+\textbf{Component loss: } another  key component of our method is the Component Loss.
+conventional GAN only needs to differentiate fake images and real images.
+However, conditional GAN usually requires that the synthetic images matching  the input text description.
+Recent works\cite{han2017stackgan,reed2016generative} has proposed to use a matching-aware loss to achieve this goal.
+The discriminator is used to differential fake image-text pair from real image-text pair.
+However, such loss complicate the task for discriminator because it does not only need to differentiate fake images from real images, it also need to match the text to images.
+In this paper, we explicitly separate discriminator loss into 2 terms, one image loss is used to differentiating real/fake image, and 
+one matching-aware loss is used to handle matching between images and text description.
 
-\textbf{Discriminator} The discriminator simply contains consecutive stride-2 convolutional layers with BN and LeakyReLU  (the depth changes according to the input size) until the feature map has $512{\times}4{\times}4$ dimension.
-There two branches are added on top of it for multi-purpose discriminator design (see next section) .
-One is a direct $4{\times}4$ conv layers to produce a 2-d vector to classify real and fake.
-Another one first concatenate $128{\times}4{\times}4$ text embedding (replicated from a $128$-d text embedding).
-Then we use an $1{\times}1$ conv to fuse text and image information; it is critical to guarantee the semantic consistency in the final results.
-Finally, a $4{\times}4$ conv layer produces a 2-d vector for classification.
+As is shown in Fig\ref{game}, a text description $t$ is first transformed into a text embedding $\psi(t)$ using an text encoder \cite{reed2016generative}.
 
-All intermediate conv layers use $3{\times}3$ kernels (with reflection padding and no bias).
-We remove ReLU after the skip-addition of each residual block, with an intention to reduce sparse gradients.
-We also experimented other normalization (i.e.
-instance normalization \cite{ulyanov2016instance} and layer normalization \cite{ba2016layer}) used by \cite{zhu2017unpaired,chen2017photographic}.
-Both are not satisfactory.
-
-\subsection{Preliminaries}
+\textbf{Conditional augmentation: } Following the work of \cite{han2017stackgan}, instead of using the plan deterministic non-linear transformation of the origin al $\Psi(t)$, we obtain the conditional vector $c$ by sampling from a Gaussian distribution $\mathcal{N}(\mu(\psi(t)), \Sigma(\psi(t)) )$, in which the mean $\mu(\psi(t))$ and the diagonal covariance matrix $\Sigma(\psi(t))$ are non-linear transformation of the original text embedding $\psi(t)$.
+This type of conditional augmentation technique can be used to inject randomness to the text embedding vector $\psi(t)$ to mitigate the common problem that conventional conditional GAN training paradigm usually learns to $G$ that totally ignores the noise, resulting to results lacking diversity.
+In the spirit of variational auto-encoder, further Kullback-Leibler divergence regularization term  $D_{KL}(\mathcal{N}(\mu(\psi(t)), \Sigma(\psi(t)) )|| \mathcal{N}(0, \bm{I}))$ is added to the final loss function to push the Gaussian distribution to the norm distribution to address over-fitting.
+In addition, this term might also play a role in balancing the $c$ and generated condition vector $c$ by forcing $c$ to have a similar scale to $z$.
 
@@
 
+\begin{algorithm}
+	\caption{Counting mismatches between two packed \DNA{} strings
+		\label{alg:packed-dna-hamming}}
+	\begin{algorithmic}[1]
+		\Require{$x$ and $y$ are packed \DNA{} strings of equal length $n$}
+		\Statex
+		\Function{Distance}{$x, y$}
+		\Let{$z$}{$x \oplus y$} \Comment{$\oplus$: bitwise exclusive-or}
+		\Let{$\delta$}{$0$}
+		\For{$i \gets 1 \textrm{ to } n$}
+			\If{$z_i \neq 0$}
+				\Let{$\delta$}{$\delta + 1$}
+			\EndIf
+		\EndFor
+		\State \Return{$\delta$}
+		\EndFunction
+	\end{algorithmic}
+\end{algorithm}
+
 \subsection{Implementation Details}
 
+\subsection{Network Architecture}
+
 \section{Experiments}
-In this section, we evaluate the proposed method both qualitatively and quantitatively on three public datasets. We mainly compare to the state-of-the art StackGAN \cite{han2017stackgan}.
-
 \subsection{Evaluation metric}
@@
 
-\section{Conclusion}
-
 {\small

### 2017-10-21 cvpr2018.tex
add algorithm

--- 2017-10-20 cvpr2018.tex
@@
 \usepackage{varwidth}
+
+\usepackage{algpseudocode,algorithm,algorithmicx}
+\newcommand*\DNA{\textsc{dna}}
+
+\newcommand*\Let[2]{\State #1 $\gets$ #2}
+\algrenewcommand\algorithmicrequire{\textbf{Precondition:}}
+\algrenewcommand\algorithmicensure{\textbf{Postcondition:}}
+
+\makeatletter
+\def\BState{\State\hskip-\ALG@thistlm}
+\makeatother
+
 \usepackage{bm}
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
+
 \usepackage[breaklinks=true,bookmarks=false]{hyperref}
@@
 
+\section{Preliminary}
+\subsection{Generative Adversary Network}
+Generative adversary networks (GANs) are composed of a generator $G$ and a discriminator $D$, which are alternatively trained to compete with each other in a two-player minimax game.
+The discriminator $D$ is optimized to distinguish the synthesized images from the real images, meanwhile, the generator $G$ is trained to fool the discriminator by trying to convert an input distribution $p_z$ to the true data distribution $p_{data}$.
+Concretely, the overall training procedure can be analogous to the following two-player min-max game $V(D, G)$,
+ \begin{equation}
+ \label{game}
+ \begin{split}
+  \underset{G}{\min}\ \underset{D}{\max}\ V(D, G) =  &\mathbb{E}_{x\sim p_{data}}[\log D(x)] +  \\
+					  &\mathbb{E}_{z\sim p_{z}}[\log (1-D(G(z)))]		   
+ \end{split}
+ \end{equation}
+where $x$ is a real image sampled from the true data distribution $p_{data}$, $z$ is a noise vector usually sampled from some predefined distribution $p_{z}$ (e.g., Gaussian distribution).
+In practice, It's been shown to work better for the generator $G$ to minimizing $-\log(D(G(z)))$ rather than $\log(1-D(G(z)))$, namely, the $\log(D)$ trick.
+
+Conditioned GAN \cite{isola2016image} is a variation of traditional GAN where both the generator network $G$ and discriminator network $D$ are conditioned on an additional condition vector besides the noise vector.
+In this paper, we consider the task of training a deep  generative adversarial network conditioned on the embedding of the text descriptions of the images.
+
+\section{Method}
+To generate high-resolution photo-realistic images from text embeddings, we propose a simple and effective multi-level Generative Adversarial Network architecture.
+Our model mainly consists of the following key-components,
+
 \textbf{Advantages} Figure \ref{fig:archs-compare} illustrates the architecture difference between widely-used cascade strategy \cite{han2017stackgan,denton2015deep} and our strategy.
@@
 
-\subsection{Preliminaries}
+\subsection{Overview}
+In this paper, we use the following notations.
+Denote the image dimension, text embedding dimension and the dimension of the noise input as $I$, $T$ and $Z$, respectively.
+for simplicity we assume the image is all square.
+The generator is denoted $G: \mathcal{R}^{Z}: \times \mathcal{R}^{T}\rightarrow\mathcal{R}^{I}$, the image discriminator $D_i: \mathcal{R}^{I}\rightarrow\{0, 1\}$, and the matching-aware discriminator $D_m: \mathcal{R}^{I}: \times \mathcal{R}^{T}\rightarrow\{0, 1\}$.
+
+As is shown in Fig\ref{game}, In the generator $G$, we first sample a random vector $z\in \mathcal{R}^{Z} \scriptsize{\sim} \mathcal{N}(0,1)$, then text embedding vector $\psi{t}$ is obtained by applying an per-trained text encoder on the image description $t$, in this paper, we use the char-rnn based text encoder provided in \cite{reed2016generative}.
+
+\textbf{Variational text encoding: } Following the work of \cite{han2017stackgan}, instead of using the plan deterministic non-linear transformation of the origin al $\Psi(t)$, we obtain the conditional vector $c$ by sampling from a Gaussian distribution $\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )$, in which the mean $\mu(\psi_t)$ and the diagonal covariance matrix $\Sigma(\psi_t)$ are non-linear transformation of the original text embedding $\psi_t$.
+This type of conditional augmentation technique can be used to inject randomness to the text embedding vector $\psi_t$ to mitigate the common problem that conventional conditional GAN training paradigm usually learns to $G$ that totally ignores the noise, resulting to results lacking diversity.
+
+Conditioned on $c$ and the random vector $z$, a synthetic image $\hat{x}$ is generated as $\hat{x}\leftarrow G(c,z)$, it is simply a feed forward pass of the generator.
+Our generator consists of stacks of residual blocks, bilinear sampling layer is used to up-sample the feature maps.
+
+The discriminator $D$ in our model mainly consists of two branches: matching-aware pair discrimination branch $D_{pair}$, and image discrimination branch $D_{img}$, both branches share the same  image encoder.
+
+Given a pair of image and text embedding $(x, \psi{t})$ as input, in the discriminator $D$, we first transfer $x$  to an image code $Code_x$.
+$Code_x$ along with $f_{sent}(\psi_t)$ is concatenated and fed to the matching aware branch to compute a final scale value indicating the probability of the pair being real or fake, where $f_{sent}$ consists of one linear layer and one leaky ReLU transformation,  the matching-aware branch is a set of residual blocks with strid-2 convolution, more details of the architecture will be provided in the appendix.
+Besides that, the image code is also fed to an image-disc branch, whose structure is very similar to the matching-aware branch, to judge the probability of the input image being real or fake.
+We performance batch normalization on all convolutional layers.
+\textcolor{red}{like stackgan, I will add much more architecture details later}
+
+The generator $G$ and discriminator $D$ are optimized alternatively using their corresponding loss function.
 
  \subsection{Scalable Deeply Supervised}
+ \textbf{Multi-level side output:} instead of only predicting the high resolution in the final output, our model is designed to predict multi-level images of gradually increasing dimension (e.g., 256$\times$256 as the final output with 64$\times$64 and 128$\times$128 being the side output) as the side outputs.
+In principle, the lower-resolution side output is forced to learn the rough structure (e.g., object sketch, color information and background) of the images, the subsequent higher-resolution path is used to add more details to the images.
+The lower-level side output works by regularizing the lower-level image feature.
+Since the model is trained in an end-to-end fashion, we can observe more consistent information exhibited in both lower and higher-resolution outputs than stackGan\cite{han2017stackgan}.
+This type of side output is also proven useful because it allows short path between image supervision information to the hidden feature maps, which could potentially helps training.
 
-\subsection{Functional Loss}
+\subsection{Generator Loss}
+The generator's goal is to generator image that match the input text embedding and looks as real as possible.
+So the loss function for our model mainly consists of two parts, namely, matching aware loss and one image loss.
+Given a set of chosen input pair $(x, \psi_t)$, the generator is optimizing the following function
+ \begin{equation}
+ \label{genloss}
+ \begin{split}
+ \mathcal{L}_G = & \mathbb{E}_{z\sim p_{z}, t \sim p_{data}}[-\log( D_{sent}( G(z, c_t),  \psi_t) ) ] + \\
+				  & \mathbb{E}_{z\sim p_{z}, t \sim p_{data}}[-\log( D_{img}( G(z, c_t) ) ) ] + \\
+                  & D_{KL}(\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )|| \mathcal{N}(0, \bm{I})) 		   
+ \end{split}
+ \end{equation}
+ where $c_t$ is the variational conditional vector generated from $\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )$.
+To make the network differentiable, in practice, we adopted the re-parametric trick\cite{vae}, where $c_t$ is actually computed as $\mu(\psi_t)+\Sigma(\psi_t)\odot \epsilon$, where $\epsilon\in \mathcal{R}^{T}$ is draw from a normal Gaussian distribution.
+
+ In the spirit of variational auto-encoder, further Kullback-Leibler divergence regularization term  $D_{KL}(\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )|| \mathcal{N}(0, \bm{I}))$ is added to the final loss function to push the Gaussian distribution to the norm distribution to address over-fitting.
+In addition, this term might also play a role in balancing the $c_t$ and generated condition vector $c_t$ by forcing $c$ to have a similar scale to $z$.
+In the following sections, we denote $c_t$ as the variational conditional text vector.
+
+\subsection{Functional Loss of Discriminator}
+ Our goal is to generate images that not only look as realistic as real images, but also matching the given text description.
+ Therefore, the discriminator must handle errors of the following two categories: real image with mismatch conditional text information, fake image with real text.
+In order to achieve this, the previously proposed matching aware discriminator is explicitly trained with three pair configurations, namely: real image with right text as positive training sample, and the aforementioned two sources of error pairs as negative training samples.
+
+ Given a mini-batch of training data consists of images $x$ and the corresponding text $t$, mismatching text $\hat{t}$. First of all, we sample fakes images using $G$.
+ $\hat{x_1} = G(z_1, \psi_t)$ and $\hat{x_2} = G(z_2, \psi_t)$, where $z_1$ and $z_2$ are random vector sampled from norm Gaussian distribution.
+
+The loss function of the matching aware discriminator are summarized as:
+  \begin{equation}
+  \label{matchignloss}
+  \begin{split}
+  \mathcal{L}_D = 	  &\mathbb{E}_{(x, t) \sim p_{data}}[\log( D( x  \psi_t) ) ] -  0.5*(\\
+					  &\mathbb{E}_{(x, \hat{t}) \sim p_{data}}[\log(D(x, \psi_{\hat{t}} )  ] +\\
+					  &   \mathbb{E}_{t \sim p_{data}}[\log(D(\hat{x_1}, \psi_t) ) ] 
+  \end{split}
+  \end{equation}
+This loss explicit force the discriminator to differentiate correct pair from the wrong pair.
+However, there is no explicit loss that push the discriminator to differentiate real images from the fake images.
+The way that they formulate all the task into pair based solution complicate the task of the generator.
+In this paper, we propose to directly add another loss that concentrate the image quality only beside the matching loss.
+Specifically, it can be given by:
+  \begin{equation}
+  \label{discoss}
+  \begin{split}
+  \mathcal{L}_D = 	&\mathbb{E}_{(x, t) \sim p_{data}}[\log( D( x  \psi_t) ) ] -  0.5*(\\
+		  &\mathbb{E}_{(x, \hat{t}) \sim p_{data}}[\log(D_{pair}(x, \psi_{\hat{t}} )  ] +\\
+		  &\mathbb{E}_{t \sim p_{data}}[\log(D_{pair}(\hat{x_1}, \psi_t) ) ] + \\
+		  &\mathbb{E}_{x \sim p_{data}}[\log( D_{img}(x) )] - 0.5* ( \\
+		  &\mathbb{E}[\log( D_{img}(\hat{x_1}))] + \mathbb{E}[\log( D_{img}(\hat{x_2}) )  ] )
+  \end{split}
+  \end{equation}
+\textcolor{red}{equations needs to be verified, just a rough place holder}
+
+Further more, this separation of the image loss from the matching loss open further possibilities, such as utilizing the unlabeled image to improve both the genrator and discriminator.
+\textcolor{red}{maybe utilizing the imagenet for training the coco, or save as another paper.}
+
+ \begin{algorithm}
+ 	\caption{Multi scale GAN training algorithm with step size $\alpha$, number of iteration $S$, we summarize the algorithm using SGD for simplicity.\textcolor{red}{need to change to goodfellow algorithm style}}
+ 	\label{CHalgorithm}
+ 	\begin{algorithmic}[1]
+
+ 		\For{$i \gets 1 \textrm{ to } S$ }
+ 		\State $z_1, z_2 \sim \mathcal{N}(0,\bm{1})^Z$
+ 		\State $\hat{x_1}, \hat{x_2} = G(z_1, \psi_t),  G(z_2, \psi_{\hat{t}})$ %\{Forward through $G$ using matching text embedding\}
+ 		\State $d_r$ = $D_{pair}(x, \psi_t)$ \{(real image, matching text)\}
+ 		\State $d_w$ = $D_{pair}(x, \psi_{\hat{t}})$ \{(real image, wrong text)\}
+ 		\State $d_f$ = $D_{pair}(\hat{x_1}, \psi_t)$ \{(fake image, matching text)\}
+ 		\State $s_r, s_1, s_2$ = $D_{img}(x), D_{img}(\hat{x_1})$, $D_{img}(\hat{x_1})$ %\{Forward through $D_{img}$ with $\hat{x_1}$\}
+
+ 		\State $loss_{img}$ = $ (\log(1-s_1) + \log(1-s_2))/2 $
+ 		\State $loss_{pair}$ = $ (\log(1-d_w) + \log(1-d_f))/2 $
+
+ 		\State $\mathcal{L}_{D}$ = $\log(d_r) + \log(s_r) +loss_{img} + loss_{pair}$
+ 		\State $\mathcal{L}_{G}$ = $\log(1-d_f) +  ( \log(1-s_1) + \log(1-s_2) )/2 $
+ 		\State $\theta_G$ = $\theta_G$ - ${\delta \mathcal{L}_G } / {\delta \theta_G}$  \{Update generator\}
+ 		\State $\theta_D$ = $\theta_D$ - ${\delta \mathcal{L}_D} / {\delta \theta_D}$  \{Update generator\}
+
+ 		\EndFor
+
+ 	\end{algorithmic}
+ \end{algorithm}
+
+%\begin{algorithm}
+%	\caption{Multi scale GAN training algorithm with step size $\alpha$, number of iteration $S$, we summarize the algorithm using SGD for simplicity.   
+%		\label{alg:gan-train}}
+%	\begin{algorithmic}[1]
+%		\Input{sample a minibatch of images, $x$, matching text description $t$, mis-matching $\hat{t}$,
+%			}
+%		\For{$i \gets 1 \textrm{ to } S$}
+%			$z_1, z_2 \sim \mathcal{N}(0,\bm{1})^Z$
+%			\State $\hat{x_1}$=$G(z_1, \psi_t)$ \Comment{Forward through $G$ using matching text embedding}
+%			\STATE {$\hat{x_2}$}{$G(z_2, \psi_\hat{t})$} \Comment{Forward through $G$ using mis-matching text embedding}
+%			
+%			\STATE {$d_r$}{$D_{pair}(x, \psi_t)$} \Comment{(real image, matching text)}
+%			\STATE {$d_m$}{$D_{pair}(x, \psi_\hat{t})$} \Comment{(real image, mis-matching text)}
+%			\STATE {$d_f$}{$D_{pair}(\hat{x_1}, \psi_t)$} \Comment{(fake image, matching text)}
+%			\STATE {$s_r$}{$D_{img}(x)$} \Comment{Forward through $D_{img}$ with $x$}
+%			\STATE {$s_1$}{$D_{img}(\hat{x_1})$} \Comment{Forward through $D_{img}$ with $\hat{x_1}$}
+%			\STATE {$s_2$}{$D_{img}(\hat{x_1})$} \Comment{Forward through $D_{img}$ with $\hat{x_2}$}
+%			\STATE {$\mathcal{L}_{D}$}{$(d_r-1)^2 + (s_r-1)^2 + (d_m + d_f + s_1 + s2)/2 $} 
+%			\STATE {$\mathcal{L}_{G}$}{$((d_f -1)^2 + (s_1 -1)^2 + (s_2 -1)^2 $} 
+%			\STATE {$\theta_G$}{$\frac{\delta \mathcal{L}_G}{\delta \theta_G}$}  \Comment{Update generator}
+%			\STATE {$\theta_D$}{$\frac{\delta \mathcal{L}_D}{\delta \theta_D}$}  \Comment{Update generator}
+%		\EndFor	
+%	\end{algorithmic}
+%\end{algorithm}
 
 \subsection{Implementation Details}
+
+\section{Dataset}
 

### 2017-10-22 cvpr2018.tex
8th

@@
 %\ifcvprfinal\pagestyle{empty}\fi
-\setcounter{page}{4321}
+%\setcounter{page}{4321}
 \begin{document}
@@
 This paper presents a novel  and effective approach to deal with the challenging task of generating synthetic photographic image conditioned on semantic image descriptions.
-We leverage the hierarchical deep representations of convolutional layers and introduce deeply-nested adversarial training to regularize the representations to be compositional for multi-scale image generation.
-To this end, we present a new network architecture, which is symmetric as well as extensile, to push generated images to high resolutions.
+Our method leverages the deep representations of convolutional layers and introduces hierarchical-nested adversarial training to regularize the representations to be compositional of multi-scale images.
+We present a new network architecture, which is intuitive as well as extensile, to push generated images to high resolutions with symmetric convolutional blocks.
 We present a functional generative adversarial networks (GANs) training strategy to encourage more effective multimodal (i.e.
 image and text) information utilization in order to enhance multi-purpose adversary between real and fake distribution.
-Our method, at the first time, shows a fully end-to-end trainable network that can generate $256{\times}256$ images and is stackable to $512{\times}512$ resolution or higher with arbitrary extensions.
-With extensive experimental validation on three major datasets, our method sets up a new state of the art to this field.
+To our best knowledge, our method is the first to show a fully end-to-end trainable network that can generate $256{\times}256$ images and is stackable to $512{\times}512$ resolution.
+With extensive experimental validation on three major datasets, our method significantly improves previous method and sets up a new state of the art to this field.
 
@@
 \section{Introduction}
-Generating photographic high-resolution image conditional on arbitrary semantic description is a meaningful problem in generative model research \cite{reed2016generative}.
+Generating photographic high-resolution image conditional on arbitrary semantic description is an important problem in generative model research \cite{reed2016generative}.
 However, insufficient methods have been successfully developed to address this task due to its particular challenges.
-Text-to-image synthesis can be viewed as an special variation of conventional generative models, which aim to translate a vector to a RGB image space.
-Differently, the vector space of the former is induced by semantic descriptions.
-Therefore, this task requires the generated images to be semantically consistent, i.e., the generated images not only reflect the principal concept of descriptions in global images but also can reflect the fine-grained descriptive details in image pixels.
+Text-to-image synthesis can be viewed as an special variation of conventional generative models, which aim to translate a low-dimensional embedding  to a much more complex RGB image space.
+Differently, the embedding space of the former is induced by semantic descriptions.
+Therefore, this task requires the generated images to be \textit{semantically consistent}, i.e., the generated images not only preserve the principal concept of descriptions generally but also preserve the fine-grained descriptive details in image pixels.
 
 Generative adversarial networks (GANs) have become the main solution to this task. 
-Reed \etal \cite{reed2016generative} takes the first step to address this task through a GAN based framework.
-But this method only handles image up to $64{\times}64$ resolution and usually is barely to generate vivid object details.
-Based on \cite{reed2016generative}, Zhang \etal \cite{han2017stackgan} present a successful approach (StackGAN) by stacking another GAN to generate high quality and compelling $256{\times}256$ images given inputs of low resolution $64{\times}64$ synthetic images.
-This method needs individual two-stage training, which is relatively not straightforward to be applied.
+Reed \etal \cite{reed2016generative} address this task through a GAN based framework.
+But this method only handles image up to $64{\times}64$ resolution and usually can barely generate vivid object details.
+Based on \cite{reed2016generative}, Zhang \etal \cite{han2017stackgan} present a successful approach (StackGAN) by stacking another GAN to generate high-quality $256{\times}256$ images given low resolution $64{\times}64$ synthetic images.
+This method needs two-stage training to achieve the goal.
 Later on, Dong \etal \cite{dong2017semantic}
-bypasses the difficult of translate vector semantic vector to RGB image and treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-renders a arbitrary-style training ($128{\times}128$) image according to targeting semantic descriptions.
-However, the high resolution synthesis ability is still indeterminate.
-Unfortunately, directly training from vector space and synthesize high resolution (e.g. $256{\times}256$) and diverse images is still an open question according to current reported studies.
+bypasses the difficult of translate vector embedding to RGB images and treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-rendering an arbitrary-style training ($128{\times}128$) image conditioned on a targeting semantic description.
+Unfortunately, its high resolution synthesis ability is still unclear.
+At present, how to train from the low-dimensional embedding to synthesize high resolution (e.g. $256{\times}256$) and diverse images in an end-to-end manner is still an open and attractive question.
 
-We outline several empirical reasons for this challenges using GANs particularly for text-to-image synthesis.
-The first problem comes from the fundamental difficulty of balancing the stability between generators and discriminators.
-There are many a rich number of literature trying to stabilize GAN training \cite{salimans2016improved}.
-But especially for text-to-image synthesis, how to utilize the multimodal information between images and text in discriminator is extremely important and needs careful consideration.
+We outline several empirical observations for this challenges using GANs, particularly for text-to-image synthesis.
+The first comes from a fundamental difficulty of balancing the convergence between generators and discriminators.
+There are a rich number of literature tacking this issue \cite{salimans2016improved,huang2016stacked}.
+For text-to-image synthesis, how to utilize the multimodal information between images and text in discriminator is extremely important to generate effective gradients and needs careful consideration.
+The second is that huge pixel space in high resolution images \cite{han2017stackgan}.
+An effective regularization to reduce the variances in generators is critical \cite{huang2016stacked}. 
+Moreover, keeping semantic consistency and diversity in generated images needs more specialized designs in generators to better make use of gradients from discriminators.
+
+%The first reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. 
+% Keeping semantic consistency as well as diversity
+%The first reason comes from the fundamental difficulty of balancing the stability between generators and discriminators.
+There are a rich number of literature trying to stabilize GAN training \cite{salimans2016improved} and regularize networks \cite{huang2016stacked}.
+%But especially for text-to-image synthesis, how to utilize the multimodal information between images and text in discriminator is extremely important and needs careful consideration.
 The second reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}.
@@
 
-With careful consideration of these reasons, in this paper, we propose a novel method that can directly generate high resolution images trained in a fully end-to-end manner - a Vanilla fashion.
+With careful consideration of these outlined problems, in this paper, we propose a novel method that can directly generate high resolution and semantic consistent images trained in a fully end-to-end manner.
 The contributions are described follows.
 
-To tackle the problem of significant space difference between text and images, we propose to leverage the hierarchical representations of convolutional layers through deeply compositional constraints.
-In other words, we limit feature maps in different layers to be disentangled RGB image space, such that feature maps of any layers can linearly represent targeting images at corresponding resolutions.
-We introduce accompanying deeply-nested adversarial objective at intermediate layers to achieve this goal.
-To well cooperate with discriminators, we propose an intuitive network architecture design with hierarchically-nested adversarial objectives that is more efficient and faster to train.
+To tackle the problem of space leap from text and images, our method leverages the hierarchical representations of convolutional layers through a deeply-nested layer constraint, which is simply motivated by two intuitions.
+We hope feature maps in different layers are disentangled RGB image space, which can linearly represent targeting images at corresponding resolutions and maximize the implicit effectiveness of feature representations.
+We introduce accompanying hierarchically-nested adversarial objective at intermediate layers to achieve this goal.
+To better cooperate with discriminators, we present an quite intuitive network structure design to encourage more efficient and effective training.
 
@@
 CUB birds \cite{}, Oxford-102 flowers \cite{}, and large-scale COCO datasets \cite{}.
-Extensive experimental results demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts.
+Extensive experimental results and analysis demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts.
 All source code will be released.
@@
 Deep generative models grows wide interests recently, including GANs \cite{goodfellow2014generative}, Variational Auto-encoders (VAE) \cite{kingma2013auto}, etc \cite{oord2016pixel}. 
-There are substantial existing methods investigating better usage of GANs for different applications, such as image synthesis \cite{radford2015unsupervised, shrivastava2016learning}, (unpaired) pixel-to-pixel translation \cite{isola2016image,zhu2017unpaired},  medical imaging \cite{costa2017towards}, etc \cite{ledig2016photo,huang2016stacked}.
+There are substantial existing methods investigating better usage of GANs for different applications, such as image synthesis \cite{radford2015unsupervised, shrivastava2016learning}, (unpaired) pixel-to-pixel translation \cite{isola2016image,zhu2017unpaired},  medical applications \cite{costa2017towards}, etc \cite{ledig2016photo,huang2016stacked}.
 
 Text-to-image synthesis not only requires diverse and high-quality generation but also requires precise semantically consistent mapping in the image space.
-Reed \etal \cite{reed2016generative} introduces the first method that can generate $64{\times}64$ resolution images, which is similar with DCGAN \cite{radford2015unsupervised}.
+Reed \etal \cite{reed2016generative} introduce the first method that can generate $64{\times}64$ resolution images, which is similar with DCGAN \cite{radford2015unsupervised}.
 This method presents a new strategy to image-text matching aware adversarial training.
@@
 adversarial what-where network (GAWWN) to enable "where and what" instructions in text-to-image synthesis, which uses extra information to help generate $128{\times}128$ resolution images.
-StackGAN \etal \cite{han2017stackgan} propose to a two-stage stacking GAN training approach that is able to generate $256{\times}256$ high resolution vivid images.
-Recently, Dong \etal \cite{dong2017semantic} proposes to learn a joint embedding of images and text so as to re-render a prototype image according to targeting descriptions.
-Cha \etal \cite{dash2017tac} use the perceptional loss and Dash \etal \cite{dash2017tac} use image labels to assist GAN training.
+StackGAN \etal \cite{han2017stackgan} propose to a two-stage stacking GAN training approach that is able to generate $256{\times}256$ compelling results.
+Recently, Dong \etal \cite{dong2017semantic} propose to learn a joint embedding of images and text so as to re-render a prototype image conditioned on targeting descriptions.
+Cha \etal \cite{char2017perceptual} explore the usage of the perceptional loss \cite{johnson2016perceptual} and Dash \etal \cite{dash2017tac} make use of auxiliary classifiers (similar with \cite{odena2016conditional}) to assist GAN training.
 
@@
 image labels, ImageNet CNNs, etc) \cite{dosovitskiy2016generating,ledig2016photo,dash2017tac,dash2017tac}.
-While our method does not use any extra information apart from input text and images.
-Moreover, such difficulties grow significantly as targeting image resolution increases.
+While our method does not use any extra information apart from input text.
+Moreover, it is easy to see the training difficulty grows significantly as targeting image resolution increases.
 
@@
 shows a top-down stack GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method.
-However, this method need multiple symmetric  bottom-up discriminators and pre-training of discriminators.
-The usage for high-resolution image is unclear \cite{han2017stackgan}.
-Compared with these strategies that progressively train low- to high-resolution GANs, our method takes advantages of multi-level representations for implicit subtask integration, which enables end-to-end high-resolution image synthesis.
+However, this method need multiple symmetric  bottom-up discriminators and pre-training of discriminators, and the usage for high-resolution image is unclear \cite{han2017stackgan}.
+Compared with these strategies that progressively train low- to high-resolution GANs, our method takes advantages of multi-level representations that encourages implicit subtask integration, which enables end-to-end high-resolution image synthesis.
 
@@
 Our method is partially inspired by supervised CNNs with deep supervision \cite{lee2015deeply,xie2015holistically}.
-We introduce accompanying hierarchically-nested adversarial supervision, with a goal to enhance and regularizes layer representations to support final high resolution outputs.
+Our proposed hierarchically-nested adversarial supervision enhances layer representations to support final high resolution outputs.
 \begin{figure}[t]
@@
  \begin{split}
-  \underset{G}{\min}\ \underset{D}{\max}\ V(D, G) =  &\mathbb{E}_{x\sim p_{data}}[\log D(x)] +  \\
-					  &\mathbb{E}_{z\sim p_{z}}[\log (1-D(G(z)))]		   
+  \underset{G}{\min}\ \underset{D}{\max}\ V(D, G) =  &\mathbb{E}_{x\sim p_{data}}[log D(x)] +  \\
+					  &\mathbb{E}_{z\sim p_{z}}[log (1-D(G(z)))]		   
  \end{split}
@@
 where $x$ is a real image sampled from the true data distribution $p_{data}$, $z$ is a noise vector usually sampled from some predefined distribution $p_{z}$ (e.g., Gaussian distribution).
-In practice, It's been shown to work better for the generator $G$ to minimizing $-\log(D(G(z)))$ rather than $\log(1-D(G(z)))$, namely, the $\log(D)$ trick.
+In practice, It's been shown to work better for the generator $G$ to minimizing $-log(D(G(z)))$ rather than $log(1-D(G(z)))$, namely, the $log(D)$ trick.
 
@@
 
-The discriminator $D$ in our model mainly consists of two branches: matching-aware pair discrimination branch $D_{pair}$, and image discrimination branch $D_{img}$, both branches share the same  image encoder.
-
-Given a pair of image and text embedding $(x, \psi{t})$ as input, in the discriminator $D$, we first transfer $x$  to an image code $Code_x$.
-$Code_x$ along with $f_{sent}(\psi_t)$ is concatenated and fed to the matching aware branch to compute a final scale value indicating the probability of the pair being real or fake, where $f_{sent}$ consists of one linear layer and one leaky ReLU transformation,  the matching-aware branch is a set of residual blocks with strid-2 convolution, more details of the architecture will be provided in the appendix.
+Given a pair of image and text embedding pair $(x, \psi{t})$ as input, in the discriminator $D$, we first transfer the $x$  to an image code $Code(x)$.
+$Code(x)$ along with $f_{sent}(\psi_t)$ is concatenated and fed to the matching aware branch to compute a final scale value indicating the probability of the pair being real or fake, where $f_{sent}$ consists of one linear layer and one leaky ReLU transformation,  the matching-aware branch is a set of residual blocks with strid-2 convolution, more details of the architecture will be provided in the appendix.
 Besides that, the image code is also fed to an image-disc branch, whose structure is very similar to the matching-aware branch, to judge the probability of the input image being real or fake.
@@
 
- Given a mini-batch of training data consists of images $x$ and the corresponding text $t$, mismatching text $\hat{t}$. First of all, we sample fakes images using $G$.
- $\hat{x_1} = G(z_1, \psi_t)$ and $\hat{x_2} = G(z_2, \psi_t)$, where $z_1$ and $z_2$ are random vector sampled from norm Gaussian distribution.
-
+ Given an input consisting of a mini-batch of images $x$ and the corresponding text $t$, mismatching text $\hat{t}$. 
  The loss function of the matching aware discriminator are summarized as:
@@
   \begin{split}
-  \mathcal{L}_D = 	  &\mathbb{E}_{(x, t) \sim p_{data}}[\log( D( x  \psi_t) ) ] -  0.5*(\\
-					  &\mathbb{E}_{(x, \hat{t}) \sim p_{data}}[\log(D(x, \psi_{\hat{t}} )  ] +\\
-					  &   \mathbb{E}_{t \sim p_{data}}[\log(D(\hat{x_1}, \psi_t) ) ] 
+  \mathcal{L}_D = 	  &\mathbb{E}_{x, t \sim p_{data}}[\log( D( x,  \psi_t) ) ] +  0.5*(\\
+					  &\mathbb{E}_{x, \hat{t} \sim p_{data}}[-\log(D(x, \psi_{\hat{t}} )  ] +\\
+					  &   \mathbb{E}_{\hat{x}, t \sim p_{data}}[-\log(D(\hat{x}, \psi_t) ) ] 
   \end{split}
@@
   \begin{split}
-  \mathcal{L}_D = 	&\mathbb{E}_{(x, t) \sim p_{data}}[\log( D( x  \psi_t) ) ] -  0.5*(\\
-		  &\mathbb{E}_{(x, \hat{t}) \sim p_{data}}[\log(D_{pair}(x, \psi_{\hat{t}} )  ] +\\
-		  &\mathbb{E}_{t \sim p_{data}}[\log(D_{pair}(\hat{x_1}, \psi_t) ) ] + \\
-		  &\mathbb{E}_{x \sim p_{data}}[\log( D_{img}(x) )] - 0.5* ( \\
-		  &\mathbb{E}[\log( D_{img}(\hat{x_1}))] + \mathbb{E}[\log( D_{img}(\hat{x_2}) )  ] )
+  \mathcal{L}_D = 	  &\mathbb{E}_{x, t \sim p_{data}}[\log( D_{pair}( x,  \psi_t) ) ] + 0.5*( \\
+  &\mathbb{E}_{x, \hat{t} \sim p_{data}}[-\log(D_{pair}(x, \psi_{\hat{t}} )  ] +\\
+  &   \mathbb{E}_{\hat{x}, t \sim p_{data}}[-\log(D_{pair}(\hat{x}, \psi_t) ) ] + \\
+  & \mathbb{E}_{x \sim p_{data}}[\log( D_{img}(x) )] - \\
+  & \mathbb{E}_{t \sim p_{data}}[\log( D_{img}(\hat{x}) )]
   \end{split}
@@
 \begin{algorithm}
- 	\caption{Multi scale GAN training algorithm with step size $\alpha$, number of iteration $S$, we summarize the algorithm using SGD for simplicity.\textcolor{red}{need to change to goodfellow algorithm style}}
- 	\label{CHalgorithm}
+	\caption{Counting mismatches between two packed \DNA{} strings
+		\label{alg:packed-dna-hamming}}
 	\begin{algorithmic}[1]
-
- 		\For{$i \gets 1 \textrm{ to } S$ }
- 		\State $z_1, z_2 \sim \mathcal{N}(0,\bm{1})^Z$
- 		\State $\hat{x_1}, \hat{x_2} = G(z_1, \psi_t),  G(z_2, \psi_{\hat{t}})$ %\{Forward through $G$ using matching text embedding\}
- 		\State $d_r$ = $D_{pair}(x, \psi_t)$ \{(real image, matching text)\}
- 		\State $d_w$ = $D_{pair}(x, \psi_{\hat{t}})$ \{(real image, wrong text)\}
- 		\State $d_f$ = $D_{pair}(\hat{x_1}, \psi_t)$ \{(fake image, matching text)\}
- 		\State $s_r, s_1, s_2$ = $D_{img}(x), D_{img}(\hat{x_1})$, $D_{img}(\hat{x_1})$ %\{Forward through $D_{img}$ with $\hat{x_1}$\}
-
- 		\State $loss_{img}$ = $ (\log(1-s_1) + \log(1-s_2))/2 $
- 		\State $loss_{pair}$ = $ (\log(1-d_w) + \log(1-d_f))/2 $
-
- 		\State $\mathcal{L}_{D}$ = $\log(d_r) + \log(s_r) +loss_{img} + loss_{pair}$
- 		\State $\mathcal{L}_{G}$ = $\log(1-d_f) +  ( \log(1-s_1) + \log(1-s_2) )/2 $
- 		\State $\theta_G$ = $\theta_G$ - ${\delta \mathcal{L}_G } / {\delta \theta_G}$  \{Update generator\}
- 		\State $\theta_D$ = $\theta_D$ - ${\delta \mathcal{L}_D} / {\delta \theta_D}$  \{Update generator\}
-
+		\Require{$x$ and $y$ are packed \DNA{} strings of equal length $n$}
+		\Statex
+		\Function{Distance}{$x, y$}
+		\Let{$z$}{$x \oplus y$} \Comment{$\oplus$: bitwise exclusive-or}
+		\Let{$\delta$}{$0$}
+		\For{$i \gets 1 \textrm{ to } n$}
+			\If{$z_i \neq 0$}
+				\Let{$\delta$}{$\delta + 1$}
+			\EndIf
 		\EndFor
-
+		\State \Return{$\delta$}
+		\EndFunction
 	\end{algorithmic}
 \end{algorithm}
-
-%\begin{algorithm}
-%	\caption{Multi scale GAN training algorithm with step size $\alpha$, number of iteration $S$, we summarize the algorithm using SGD for simplicity.   
-%		\label{alg:gan-train}}
-%	\begin{algorithmic}[1]
-%		\Input{sample a minibatch of images, $x$, matching text description $t$, mis-matching $\hat{t}$,
-%			}
-%		\For{$i \gets 1 \textrm{ to } S$}
-%			$z_1, z_2 \sim \mathcal{N}(0,\bm{1})^Z$
-%			\State $\hat{x_1}$=$G(z_1, \psi_t)$ \Comment{Forward through $G$ using matching text embedding}
-%			\STATE {$\hat{x_2}$}{$G(z_2, \psi_\hat{t})$} \Comment{Forward through $G$ using mis-matching text embedding}
-%			
-%			\STATE {$d_r$}{$D_{pair}(x, \psi_t)$} \Comment{(real image, matching text)}
-%			\STATE {$d_m$}{$D_{pair}(x, \psi_\hat{t})$} \Comment{(real image, mis-matching text)}
-%			\STATE {$d_f$}{$D_{pair}(\hat{x_1}, \psi_t)$} \Comment{(fake image, matching text)}
-%			\STATE {$s_r$}{$D_{img}(x)$} \Comment{Forward through $D_{img}$ with $x$}
-%			\STATE {$s_1$}{$D_{img}(\hat{x_1})$} \Comment{Forward through $D_{img}$ with $\hat{x_1}$}
-%			\STATE {$s_2$}{$D_{img}(\hat{x_1})$} \Comment{Forward through $D_{img}$ with $\hat{x_2}$}
-%			\STATE {$\mathcal{L}_{D}$}{$(d_r-1)^2 + (s_r-1)^2 + (d_m + d_f + s_1 + s2)/2 $} 
-%			\STATE {$\mathcal{L}_{G}$}{$((d_f -1)^2 + (s_1 -1)^2 + (s_2 -1)^2 $} 
-%			\STATE {$\theta_G$}{$\frac{\delta \mathcal{L}_G}{\delta \theta_G}$}  \Comment{Update generator}
-%			\STATE {$\theta_D$}{$\frac{\delta \mathcal{L}_D}{\delta \theta_D}$}  \Comment{Update generator}
-%		\EndFor	
-%	\end{algorithmic}
-%\end{algorithm}
 

### 2017-10-22 cvpr2018.tex

@@
  \begin{split}
-  \underset{G}{\min}\ \underset{D}{\max}\ V(D, G) =  &\mathbb{E}_{x\sim p_{data}}[log D(x)] +  \\
-					  &\mathbb{E}_{z\sim p_{z}}[log (1-D(G(z)))]		   
+  \underset{G}{\min}\ \underset{D}{\max}\ V(D, G) =  &\mathbb{E}_{x\sim p_{data}}[\log D(x)] +  \\
+					  &\mathbb{E}_{z\sim p_{z}}[\log (1-D(G(z)))]		   
  \end{split}
@@
 where $x$ is a real image sampled from the true data distribution $p_{data}$, $z$ is a noise vector usually sampled from some predefined distribution $p_{z}$ (e.g., Gaussian distribution).
-In practice, It's been shown to work better for the generator $G$ to minimizing $-log(D(G(z)))$ rather than $log(1-D(G(z)))$, namely, the $log(D)$ trick.
+In practice, It's been shown to work better for the generator $G$ to minimizing $-\log(D(G(z)))$ rather than $\log(1-D(G(z)))$, namely, the $\log(D)$ trick.
 
@@
 
-Given a pair of image and text embedding pair $(x, \psi{t})$ as input, in the discriminator $D$, we first transfer the $x$  to an image code $Code(x)$.
-$Code(x)$ along with $f_{sent}(\psi_t)$ is concatenated and fed to the matching aware branch to compute a final scale value indicating the probability of the pair being real or fake, where $f_{sent}$ consists of one linear layer and one leaky ReLU transformation,  the matching-aware branch is a set of residual blocks with strid-2 convolution, more details of the architecture will be provided in the appendix.
+The discriminator $D$ in our model mainly consists of two branches: matching-aware pair discrimination branch $D_{pair}$, and image discrimination branch $D_{img}$, both branches share the same  image encoder.
+
+Given a pair of image and text embedding $(x, \psi{t})$ as input, in the discriminator $D$, we first transfer $x$  to an image code $Code_x$.
+$Code_x$ along with $f_{sent}(\psi_t)$ is concatenated and fed to the matching aware branch to compute a final scale value indicating the probability of the pair being real or fake, where $f_{sent}$ consists of one linear layer and one leaky ReLU transformation,  the matching-aware branch is a set of residual blocks with strid-2 convolution, more details of the architecture will be provided in the appendix.
 Besides that, the image code is also fed to an image-disc branch, whose structure is very similar to the matching-aware branch, to judge the probability of the input image being real or fake.
@@
 
- Given an input consisting of a mini-batch of images $x$ and the corresponding text $t$, mismatching text $\hat{t}$. 
+ Given a mini-batch of training data consists of images $x$ and the corresponding text $t$, mismatching text $\hat{t}$. First of all, we sample fakes images using $G$.
+ $\hat{x_1} = G(z_1, \psi_t)$ and $\hat{x_2} = G(z_2, \psi_t)$, where $z_1$ and $z_2$ are random vector sampled from norm Gaussian distribution.
+
 The loss function of the matching aware discriminator are summarized as:
@@
   \begin{split}
-  \mathcal{L}_D = 	  &\mathbb{E}_{x, t \sim p_{data}}[\log( D( x,  \psi_t) ) ] +  0.5*(\\
-					  &\mathbb{E}_{x, \hat{t} \sim p_{data}}[-\log(D(x, \psi_{\hat{t}} )  ] +\\
-					  &   \mathbb{E}_{\hat{x}, t \sim p_{data}}[-\log(D(\hat{x}, \psi_t) ) ] 
+  \mathcal{L}_D = 	  &\mathbb{E}_{(x, t) \sim p_{data}}[\log( D( x  \psi_t) ) ] -  0.5*(\\
+					  &\mathbb{E}_{(x, \hat{t}) \sim p_{data}}[\log(D(x, \psi_{\hat{t}} )  ] +\\
+					  &   \mathbb{E}_{t \sim p_{data}}[\log(D(\hat{x_1}, \psi_t) ) ] 
   \end{split}
@@
   \begin{split}
-  \mathcal{L}_D = 	  &\mathbb{E}_{x, t \sim p_{data}}[\log( D_{pair}( x,  \psi_t) ) ] + 0.5*( \\
-  &\mathbb{E}_{x, \hat{t} \sim p_{data}}[-\log(D_{pair}(x, \psi_{\hat{t}} )  ] +\\
-  &   \mathbb{E}_{\hat{x}, t \sim p_{data}}[-\log(D_{pair}(\hat{x}, \psi_t) ) ] + \\
-  & \mathbb{E}_{x \sim p_{data}}[\log( D_{img}(x) )] - \\
-  & \mathbb{E}_{t \sim p_{data}}[\log( D_{img}(\hat{x}) )]
+  \mathcal{L}_D = 	&\mathbb{E}_{(x, t) \sim p_{data}}[\log( D( x  \psi_t) ) ] -  0.5*(\\
+		  &\mathbb{E}_{(x, \hat{t}) \sim p_{data}}[\log(D_{pair}(x, \psi_{\hat{t}} )  ] +\\
+		  &\mathbb{E}_{t \sim p_{data}}[\log(D_{pair}(\hat{x_1}, \psi_t) ) ] + \\
+		  &\mathbb{E}_{x \sim p_{data}}[\log( D_{img}(x) )] - 0.5* ( \\
+		  &\mathbb{E}[\log( D_{img}(\hat{x_1}))] + \mathbb{E}[\log( D_{img}(\hat{x_2}) )  ] )
   \end{split}
@@
  \begin{algorithm}
-	\caption{Counting mismatches between two packed \DNA{} strings
-		\label{alg:packed-dna-hamming}}
+ 	\caption{Multi scale GAN training algorithm with step size $\alpha$, number of iteration $S$, we summarize the algorithm using SGD for simplicity.\textcolor{red}{need to change to goodfellow algorithm style}}
+ 	\label{CHalgorithm}
  	\begin{algorithmic}[1]
-		\Require{$x$ and $y$ are packed \DNA{} strings of equal length $n$}
-		\Statex
-		\Function{Distance}{$x, y$}
-		\Let{$z$}{$x \oplus y$} \Comment{$\oplus$: bitwise exclusive-or}
-		\Let{$\delta$}{$0$}
-		\For{$i \gets 1 \textrm{ to } n$}
-			\If{$z_i \neq 0$}
-				\Let{$\delta$}{$\delta + 1$}
-			\EndIf
+
+ 		\For{$i \gets 1 \textrm{ to } S$ }
+ 		\State $z_1, z_2 \sim \mathcal{N}(0,\bm{1})^Z$
+ 		\State $\hat{x_1}, \hat{x_2} = G(z_1, \psi_t),  G(z_2, \psi_{\hat{t}})$ %\{Forward through $G$ using matching text embedding\}
+ 		\State $d_r$ = $D_{pair}(x, \psi_t)$ \{(real image, matching text)\}
+ 		\State $d_w$ = $D_{pair}(x, \psi_{\hat{t}})$ \{(real image, wrong text)\}
+ 		\State $d_f$ = $D_{pair}(\hat{x_1}, \psi_t)$ \{(fake image, matching text)\}
+ 		\State $s_r, s_1, s_2$ = $D_{img}(x), D_{img}(\hat{x_1})$, $D_{img}(\hat{x_1})$ %\{Forward through $D_{img}$ with $\hat{x_1}$\}
+
+ 		\State $loss_{img}$ = $ (\log(1-s_1) + \log(1-s_2))/2 $
+ 		\State $loss_{pair}$ = $ (\log(1-d_w) + \log(1-d_f))/2 $
+
+ 		\State $\mathcal{L}_{D}$ = $\log(d_r) + \log(s_r) +loss_{img} + loss_{pair}$
+ 		\State $\mathcal{L}_{G}$ = $\log(1-d_f) +  ( \log(1-s_1) + \log(1-s_2) )/2 $
+ 		\State $\theta_G$ = $\theta_G$ - ${\delta \mathcal{L}_G } / {\delta \theta_G}$  \{Update generator\}
+ 		\State $\theta_D$ = $\theta_D$ - ${\delta \mathcal{L}_D} / {\delta \theta_D}$  \{Update generator\}
+
  		\EndFor
-		\State \Return{$\delta$}
-		\EndFunction
+
  	\end{algorithmic}
  \end{algorithm}
+
+%\begin{algorithm}
+%	\caption{Multi scale GAN training algorithm with step size $\alpha$, number of iteration $S$, we summarize the algorithm using SGD for simplicity.   
+%		\label{alg:gan-train}}
+%	\begin{algorithmic}[1]
+%		\Input{sample a minibatch of images, $x$, matching text description $t$, mis-matching $\hat{t}$,
+%			}
+%		\For{$i \gets 1 \textrm{ to } S$}
+%			$z_1, z_2 \sim \mathcal{N}(0,\bm{1})^Z$
+%			\State $\hat{x_1}$=$G(z_1, \psi_t)$ \Comment{Forward through $G$ using matching text embedding}
+%			\STATE {$\hat{x_2}$}{$G(z_2, \psi_\hat{t})$} \Comment{Forward through $G$ using mis-matching text embedding}
+%			
+%			\STATE {$d_r$}{$D_{pair}(x, \psi_t)$} \Comment{(real image, matching text)}
+%			\STATE {$d_m$}{$D_{pair}(x, \psi_\hat{t})$} \Comment{(real image, mis-matching text)}
+%			\STATE {$d_f$}{$D_{pair}(\hat{x_1}, \psi_t)$} \Comment{(fake image, matching text)}
+%			\STATE {$s_r$}{$D_{img}(x)$} \Comment{Forward through $D_{img}$ with $x$}
+%			\STATE {$s_1$}{$D_{img}(\hat{x_1})$} \Comment{Forward through $D_{img}$ with $\hat{x_1}$}
+%			\STATE {$s_2$}{$D_{img}(\hat{x_1})$} \Comment{Forward through $D_{img}$ with $\hat{x_2}$}
+%			\STATE {$\mathcal{L}_{D}$}{$(d_r-1)^2 + (s_r-1)^2 + (d_m + d_f + s_1 + s2)/2 $} 
+%			\STATE {$\mathcal{L}_{G}$}{$((d_f -1)^2 + (s_1 -1)^2 + (s_2 -1)^2 $} 
+%			\STATE {$\theta_G$}{$\frac{\delta \mathcal{L}_G}{\delta \theta_G}$}  \Comment{Update generator}
+%			\STATE {$\theta_D$}{$\frac{\delta \mathcal{L}_D}{\delta \theta_D}$}  \Comment{Update generator}
+%		\EndFor	
+%	\end{algorithmic}
+%\end{algorithm}
 

### 2017-10-23 cvpr2018.tex
revision

--- 2017-10-21 cvpr2018.tex
@@
 
+\section{Preliminary}
+\subsection{Generative Adversary Network}
+Generative adversary networks (GANs) are composed of a generator $G$ and a discriminator $D$, which are alternatively trained to compete with each other in a two-player minimax game.
+The discriminator $D$ is optimized to distinguish the synthesized images from the real images, meanwhile, the generator $G$ is trained to fool the discriminator by trying to convert an input distribution $p_z$ to the true data distribution $p_{data}$.
+Concretely, the overall training procedure can be analogous to the following two-player min-max game $V(D, G)$,
+\begin{equation}
+\label{game}
+\begin{split}
+\underset{G}{\min}\ \underset{D}{\max}\ V(D, G) =  &\mathbb{E}_{x\sim p_{data}}[\log D(x)] +  \\
+&\mathbb{E}_{z\sim p_{z}}[\log (1-D(G(z)))]		   
+\end{split}
+\end{equation}
+where $x$ is a real image sampled from the true data distribution $p_{data}$, $z$ is a noise vector usually sampled from some predefined distribution $p_{z}$ (e.g., Gaussian distribution).
+In practice, It's been shown to work better for the generator $G$ to minimizing $-\log(D(G(z)))$ rather than $\log(1-D(G(z)))$, namely, the $\log(D)$ trick.
+
+Conditioned GAN \cite{isola2016image} is a variation of traditional GAN where both the generator network $G$ and discriminator network $D$ are conditioned on an additional condition vector besides the noise vector.
+In this paper, we consider the task of training a deep  generative adversarial network conditioned on the embedding of the text descriptions of the images.
+
+\textbf{Advantages} Figure \ref{fig:archs-compare} illustrates the architecture difference between widely-used cascade strategy \cite{han2017stackgan,denton2015deep} and our strategy.
+Compared with it,
+\\
+
 \section{Method}
 Figure \ref{fig:archs} illustrate the overall method.
+%To generate high-resolution photo-realistic images from text embeddings, we propose a simple and effective Hierarchically-nested Generative Adversarial Network.
+Our approach is to train both generator and discriminator conditioned on sentence embedding vectors.
+We leverage functional loss for discriminator and hierarchically nested side outputs as hierarchical supervision for both generator and discriminator to achieve our goal of generating photo-realistic images from text descriptions.
+In general, the generator takes text embedding and random noise vector as input and synthesis images at different scales (e.g, $64\times64$, $128\times128$, $256\times256$).
+The discriminator, on the other hand, is trying to judge the pair of synthesized images and the corresponding text embedding as fake pairs as well as differentiating the real images from the fake images.
+$G$ and $D$ are optimized alternatively until converges.
+
+\subsection{Overview}
+In this paper, we use the following notations.
+Denote the image dimension, text embedding dimension and the dimension of the noise input as $I$, $T$ and $Z$, respectively.
+Please note that, $G$ has multiple branches and generates multiple images of different sizes and for each image size, we have a distinct $D$.
+For simplicity, we only describe one image size.
+
+The generator is denoted $G: \mathcal{R}^{Z}: \times \mathcal{R}^{T}\rightarrow\mathcal{R}^{I}$, the image discriminator $D_{img}: \mathcal{R}^{I}\rightarrow\{0, 1\}$, and the matching-aware pair discriminator $D_{pair}: \mathcal{R}^{I}: \times \mathcal{R}^{T}\rightarrow\{0, 1\}$.
+
+\textbf{Variational text embedding: } Following the work of \cite{han2017stackgan}, instead of using the plan deterministic non-linear transformation of the original $\Psi_t$, we obtain the conditional vector $c$ by sampling from a Gaussian distribution $\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )$, in which the mean $\mu(\psi_t)$ and the diagonal covariance matrix $\Sigma(\psi_t)$ are non-linear transformation of the original text embedding $\psi_t$.
+This type of conditional augmentation technique can be used to inject randomness to the text embedding vector $\psi_t$ to mitigate the common problem that conventional conditional GAN training paradigm usually learns to totally ignore the randomness, resulting to collapsing results lacking diversity \cite{reed2016generative}.
+In addition, using this kind of text embedding makes the input pure stochastic, making it more difficult for the generator to over fit the training data.
 
@@
 
-\section{Preliminary}
-\subsection{Generative Adversary Network}
-Generative adversary networks (GANs) are composed of a generator $G$ and a discriminator $D$, which are alternatively trained to compete with each other in a two-player minimax game.
-The discriminator $D$ is optimized to distinguish the synthesized images from the real images, meanwhile, the generator $G$ is trained to fool the discriminator by trying to convert an input distribution $p_z$ to the true data distribution $p_{data}$.
-Concretely, the overall training procedure can be analogous to the following two-player min-max game $V(D, G)$,
- \begin{equation}
- \label{game}
- \begin{split}
-  \underset{G}{\min}\ \underset{D}{\max}\ V(D, G) =  &\mathbb{E}_{x\sim p_{data}}[\log D(x)] +  \\
-					  &\mathbb{E}_{z\sim p_{z}}[\log (1-D(G(z)))]		   
- \end{split}
- \end{equation}
-where $x$ is a real image sampled from the true data distribution $p_{data}$, $z$ is a noise vector usually sampled from some predefined distribution $p_{z}$ (e.g., Gaussian distribution).
-In practice, It's been shown to work better for the generator $G$ to minimizing $-\log(D(G(z)))$ rather than $\log(1-D(G(z)))$, namely, the $\log(D)$ trick.
+\subsection{Scalable Deeply Supervised}
+Instead of only predicting the high resolution in the final output, our model is designed to predict multi-level images of gradually increasing dimension (e.g., 256$\times$256 as the final output with 64$\times$64 and 128$\times$128 being the side output).
 
-Conditioned GAN \cite{isola2016image} is a variation of traditional GAN where both the generator network $G$ and discriminator network $D$ are conditioned on an additional condition vector besides the noise vector.
-In this paper, we consider the task of training a deep  generative adversarial network conditioned on the embedding of the text descriptions of the images.
+In principle, the lower-resolution side output is forced to learn the rough structure (e.g., object sketch, color information and background) of the images, the subsequent higher-resolution path is used to add more details to the images.
 
-\section{Method}
-To generate high-resolution photo-realistic images from text embeddings, we propose a simple and effective multi-level Generative Adversarial Network architecture.
-Our model mainly consists of the following key-components,
-
-\textbf{Advantages} Figure \ref{fig:archs-compare} illustrates the architecture difference between widely-used cascade strategy \cite{han2017stackgan,denton2015deep} and our strategy.
-Compared with it,
-
-\subsection{Overview}
-In this paper, we use the following notations.
-Denote the image dimension, text embedding dimension and the dimension of the noise input as $I$, $T$ and $Z$, respectively.
-for simplicity we assume the image is all square.
-The generator is denoted $G: \mathcal{R}^{Z}: \times \mathcal{R}^{T}\rightarrow\mathcal{R}^{I}$, the image discriminator $D_i: \mathcal{R}^{I}\rightarrow\{0, 1\}$, and the matching-aware discriminator $D_m: \mathcal{R}^{I}: \times \mathcal{R}^{T}\rightarrow\{0, 1\}$.
-
-As is shown in Fig\ref{game}, In the generator $G$, we first sample a random vector $z\in \mathcal{R}^{Z} \scriptsize{\sim} \mathcal{N}(0,1)$, then text embedding vector $\psi{t}$ is obtained by applying an per-trained text encoder on the image description $t$, in this paper, we use the char-rnn based text encoder provided in \cite{reed2016generative}.
-
-\textbf{Variational text encoding: } Following the work of \cite{han2017stackgan}, instead of using the plan deterministic non-linear transformation of the origin al $\Psi(t)$, we obtain the conditional vector $c$ by sampling from a Gaussian distribution $\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )$, in which the mean $\mu(\psi_t)$ and the diagonal covariance matrix $\Sigma(\psi_t)$ are non-linear transformation of the original text embedding $\psi_t$.
-This type of conditional augmentation technique can be used to inject randomness to the text embedding vector $\psi_t$ to mitigate the common problem that conventional conditional GAN training paradigm usually learns to $G$ that totally ignores the noise, resulting to results lacking diversity.
-
-Conditioned on $c$ and the random vector $z$, a synthetic image $\hat{x}$ is generated as $\hat{x}\leftarrow G(c,z)$, it is simply a feed forward pass of the generator.
-Our generator consists of stacks of residual blocks, bilinear sampling layer is used to up-sample the feature maps.
-
-The discriminator $D$ in our model mainly consists of two branches: matching-aware pair discrimination branch $D_{pair}$, and image discrimination branch $D_{img}$, both branches share the same  image encoder.
-
-Given a pair of image and text embedding $(x, \psi{t})$ as input, in the discriminator $D$, we first transfer $x$  to an image code $Code_x$.
-$Code_x$ along with $f_{sent}(\psi_t)$ is concatenated and fed to the matching aware branch to compute a final scale value indicating the probability of the pair being real or fake, where $f_{sent}$ consists of one linear layer and one leaky ReLU transformation,  the matching-aware branch is a set of residual blocks with strid-2 convolution, more details of the architecture will be provided in the appendix.
-Besides that, the image code is also fed to an image-disc branch, whose structure is very similar to the matching-aware branch, to judge the probability of the input image being real or fake.
-We performance batch normalization on all convolutional layers.
-\textcolor{red}{like stackgan, I will add much more architecture details later}
-
-The generator $G$ and discriminator $D$ are optimized alternatively using their corresponding loss function.
-
- \subsection{Scalable Deeply Supervised}
- \textbf{Multi-level side output:} instead of only predicting the high resolution in the final output, our model is designed to predict multi-level images of gradually increasing dimension (e.g., 256$\times$256 as the final output with 64$\times$64 and 128$\times$128 being the side output) as the side outputs.
-In principle, the lower-resolution side output is forced to learn the rough structure (e.g., object sketch, color information and background) of the images, the subsequent higher-resolution path is used to add more details to the images.
 The lower-level side output works by regularizing the lower-level image feature.
@@
 \subsection{Generator Loss}
+As is shown in Fig\ref{game}, In the generator $G$, we first sample a random vector $z\in \mathcal{R}^{Z} \scriptsize{\sim} \mathcal{N}(0,1)$, then text embedding vector $\psi_{t}$ is obtained by applying an per-trained text encoder on the image description $t$, in this paper, we use the char-rnn based text encoder provided in \cite{reed2016generative}.
+
+Conditioned on variational text embedding $c$ and the random vector $z$, a synthetic image $\hat{x}$ is generated as $\hat{x}\leftarrow G(c,z)$, it is simply a feed forward pass of the generator.
+The generator $G$ consists of stacks of residual blocks, bilinear sampling layer is used to up-sample the feature maps.
+
 The generator's goal is to generator image that match the input text embedding and looks as real as possible.
 So the loss function for our model mainly consists of two parts, namely, matching aware loss and one image loss.
+
 Given a set of chosen input pair $(x, \psi_t)$, the generator is optimizing the following function
@@
 \subsection{Functional Loss of Discriminator}
+
+As is shown in Figure.
+\ref{overview}, the discriminator $D$ in our model mainly consists of two branches: matching-aware pair discrimination branch $D_{pair}$, and image discrimination branch $D_{img}$, both branches share the same  image encoder.
+
+Given a pair of image and text embedding $(x, \psi{t})$ as input, in the discriminator $D$, we first transfer $x$  to an image code $Code_x$.
+$Code_x$ along with $f_{sent}(\psi_t)$ is concatenated and fed to the matching aware branch to compute a final scale value indicating the probability of the pair being real or fake, where $f_{sent}$ consists of one linear layer and one leaky ReLU transformation,  the matching-aware branch is a set of residual blocks with strid-2 convolution, more details of the architecture will be provided in the appendix.
+Besides that, the image code is also fed to an image-disc branch, whose structure is very similar to the matching-aware branch, to judge the probability of the input image being real or fake.
+We performance batch normalization on all convolutional layers.
+\textcolor{red}{like stackgan, I will add much more architecture details later}
+
+The generator $G$ and discriminator $D$ are optimized alternatively using their corresponding loss function.
+
  Our goal is to generate images that not only look as realistic as real images, but also matching the given text description.

### 2017-10-23 cvpr2018.tex
merge and revision

@@
 
-\subsection{Overview}
-In this paper, we use the following notations.
+\textbf{Notation } In this paper, we use the following notations.
 Denote the image dimension, text embedding dimension and the dimension of the noise input as $I$, $T$ and $Z$, respectively.
@@
 
-\textbf{Variational text embedding: } Following the work of \cite{han2017stackgan}, instead of using the plan deterministic non-linear transformation of the original $\Psi_t$, we obtain the conditional vector $c$ by sampling from a Gaussian distribution $\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )$, in which the mean $\mu(\psi_t)$ and the diagonal covariance matrix $\Sigma(\psi_t)$ are non-linear transformation of the original text embedding $\psi_t$.
+\textbf{Variational text embedding } Following the work of \cite{han2017stackgan}, instead of using the plan deterministic non-linear transformation of the original $\Psi_t$, we obtain the conditional vector $c$ by sampling from a Gaussian distribution $\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )$, in which the mean $\mu(\psi_t)$ and the diagonal covariance matrix $\Sigma(\psi_t)$ are non-linear transformation of the original text embedding $\psi_t$.
 This type of conditional augmentation technique can be used to inject randomness to the text embedding vector $\psi_t$ to mitigate the common problem that conventional conditional GAN training paradigm usually learns to totally ignore the randomness, resulting to collapsing results lacking diversity \cite{reed2016generative}.
@@
 
-\section{Dataset}
+\section{Experiments}
 
-\section{Experiments}
+\subsection{Dataset}
+\textbf{Dataset} We use three datasets for evaluation. \textcolor{red}{Yuanpu address}
+
+\subsection{Evaluation metric}
+\textbf{Inception score }
+
+\subsection{Baseline}
+
 In this section, we evaluate the proposed method both qualitatively and quantitatively on three public datasets.
@@
 
-\textbf{Dataset} We use three datasets for evaluation. \textcolor{red}{Yuanpu address}
-
-\textbf{Evaluation metric}
 \textcolor{red}{Yuanpu address}

### 2017-10-25 cvpr2018.tex
7th

--- 2017-10-23 cvpr2018.tex
@@
 Recently, Dong \etal \cite{dong2017semantic} propose to learn a joint embedding of images and text so as to re-render a prototype image conditioned on targeting descriptions.
-Cha \etal \cite{char2017perceptual} explore the usage of the perceptional loss \cite{johnson2016perceptual} and Dash \etal \cite{dash2017tac} make use of auxiliary classifiers (similar with \cite{odena2016conditional}) to assist GAN training.
+Cha \etal \cite{char2017perceptual} explore the usage of the perceptional loss with a pretrained ImageNet CNN \cite{johnson2016perceptual} and Dash \etal \cite{dash2017tac} make use of auxiliary classifiers (similar with \cite{odena2016conditional}) to assist GAN training.
 
 Learning a continuous mapping from low-dimensional embeddings to complex real data distribution is a long-standing problem.
-Although GANs have made significant progressive, there are still many not well-solved difficulties, e.g.
-training instability.
+Although GANs have made significant progressive, there are still many  unsolved difficulties, e.g.
+training instability and high resolution.
 Wide methods have been proposed to address those tasks, through various stabilization training techniques \cite{salimans2016improved,arjovsky2017wasserstein,berthelot2017began,shrivastava2016learning,odena2016conditional}, regularization using outside knowledge (e.g.
 image labels, ImageNet CNNs, etc) \cite{dosovitskiy2016generating,ledig2016photo,dash2017tac,dash2017tac}.
-While our method does not use any extra information apart from input text.
+While note that our method does not use any extra information apart from training paired text and images.
 Moreover, it is easy to see the training difficulty grows significantly as targeting image resolution increases.
@@
 However, this method need multiple symmetric  bottom-up discriminators and pre-training of discriminators, and the usage for high-resolution image is unclear \cite{han2017stackgan}.
-Compared with these strategies that progressively train low- to high-resolution GANs, our method takes advantages of multi-level representations that encourages implicit subtask integration, which enables end-to-end high-resolution image synthesis.
+Compared with these strategies that train low- to high-resolution GANs progressively, our method has advantages of utilizing multi-level representations to encourage implicit subtask integration, which enables end-to-end high resolution image synthesis.
 
@@
 
+\section{Method}
+Figure \ref{fig:archs} illustrate the overall method.
+
+\subsection{Architecture Design}
+Our proposed network, composed by a generator and a discriminator, is symmetric as well as extensile. We introduce the details as well as motivations.
+
+\textbf{Generator} The generator is simpled composed by three kinds of modules, termed as $K$-repeat res-blocks, stretching layers, and linear compression layers.
+A single res-block in the $K$-repeat res-block is a standard residual block  \cite{he2016identity} containing two convolutional (conv) layers (with batch normalization (BN) \cite{ioffe2015batch} and ReLU).
+The stretching layer serves to reduce feature map size and dimension.
+It simply contains an scale-$2$ nearest up-sampling layer followed by a convolutional layer with BN+ReLU.
+And the linear compression layer is a conv layer followed by a Tan, whose compact design enforces feature maps in conv blocks can linearly represent RGB images at arbitrary scales.
+Starting from a $1024{\times}4{\times}4$ embeddings replicated by a $1024$-d text embedding, the generator simples use $M$ $K$-repeat res-blocks connected by $M{-}1$ in-between stretching layers until the feature maps reach to the targeting resolution.
+So for $256{\times}256$ targeting resolution with $K{=}1$, there are $M{=}6$ $1$-repeat res-blocks and $5$ stretching layers.
+Such simple and symmetric design makes our generator helpful for gradient flows.
+We will verify in experiments.
+With a predefined side-output scales $\{S_i\}$, we apply the compression layer at those scales to produce synthetic images.
+
+\textbf{Discriminator} The discriminator simply contains consecutive stride-2 conv layers with BN and LeakyReLU \cite{} (the depth depends on the input image size) until the feature map has $512{\times}4{\times}4$ dimension.
+There two branches are added on top of it for multi-purpose discriminator design (see next section) .
+One is a direct $4{\times}4$ conv layers to produce a 2-d vector to classify real and fake.
+Another one first concatenate $128{\times}4{\times}4$ text embedding (replicated from a $128$-d text embedding).
+Then we use an $1{\times}1$ conv to fuse text and image information; it is critical to guarantee the semantic consistency in the final results.
+Finally, a $4{\times}4$ conv layer produces a 2-d vector.
+
+All intermediate conv layers use $3{\times}3$ kernels (with reflection padding and no bias).
+We remove ReLU after the skip-addition of each residual block, with an intention to reduce sparse gradients.
+We also experimented other normalization (i.e.
+instance normalization \cite{ulyanov2016instance} and layer normalization \cite{ba2016layer}) used by \cite{zhu2017unpaired,chen2017photographic}.
+Both are not satisfactory.
+
 \section{Preliminary}
@@
 
+\section{Method}
+To generate high-resolution photo-realistic images from text embeddings, we propose a simple and effective multi-level Generative Adversarial Network architecture.
+Our model mainly consists of the following key-components,
+
 \textbf{Advantages} Figure \ref{fig:archs-compare} illustrates the architecture difference between widely-used cascade strategy \cite{han2017stackgan,denton2015deep} and our strategy.
 Compared with it,
-\\
-
-\section{Method}
-Figure \ref{fig:archs} illustrate the overall method.
-%To generate high-resolution photo-realistic images from text embeddings, we propose a simple and effective Hierarchically-nested Generative Adversarial Network.
-Our approach is to train both generator and discriminator conditioned on sentence embedding vectors.
-We leverage functional loss for discriminator and hierarchically nested side outputs as hierarchical supervision for both generator and discriminator to achieve our goal of generating photo-realistic images from text descriptions.
-In general, the generator takes text embedding and random noise vector as input and synthesis images at different scales (e.g, $64\times64$, $128\times128$, $256\times256$).
-The discriminator, on the other hand, is trying to judge the pair of synthesized images and the corresponding text embedding as fake pairs as well as differentiating the real images from the fake images.
-$G$ and $D$ are optimized alternatively until converges.
 
@@
 Denote the image dimension, text embedding dimension and the dimension of the noise input as $I$, $T$ and $Z$, respectively.
-Please note that, $G$ has multiple branches and generates multiple images of different sizes and for each image size, we have a distinct $D$.
-For simplicity, we only describe one image size.
+for simplicity we assume the image is all square.
+The generator is denoted $G: \mathcal{R}^{Z}: \times \mathcal{R}^{T}\rightarrow\mathcal{R}^{I}$, the image discriminator $D_i: \mathcal{R}^{I}\rightarrow\{0, 1\}$, and the matching-aware discriminator $D_m: \mathcal{R}^{I}: \times \mathcal{R}^{T}\rightarrow\{0, 1\}$.
 
-The generator is denoted $G: \mathcal{R}^{Z}: \times \mathcal{R}^{T}\rightarrow\mathcal{R}^{I}$, the image discriminator $D_{img}: \mathcal{R}^{I}\rightarrow\{0, 1\}$, and the matching-aware pair discriminator $D_{pair}: \mathcal{R}^{I}: \times \mathcal{R}^{T}\rightarrow\{0, 1\}$.
+As is shown in Fig\ref{game}, In the generator $G$, we first sample a random vector $z\in \mathcal{R}^{Z} \scriptsize{\sim} \mathcal{N}(0,1)$, then text embedding vector $\psi{t}$ is obtained by applying an per-trained text encoder on the image description $t$, in this paper, we use the char-rnn based text encoder provided in \cite{reed2016generative}.
 
-\textbf{Variational text embedding: } Following the work of \cite{han2017stackgan}, instead of using the plan deterministic non-linear transformation of the original $\Psi_t$, we obtain the conditional vector $c$ by sampling from a Gaussian distribution $\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )$, in which the mean $\mu(\psi_t)$ and the diagonal covariance matrix $\Sigma(\psi_t)$ are non-linear transformation of the original text embedding $\psi_t$.
-This type of conditional augmentation technique can be used to inject randomness to the text embedding vector $\psi_t$ to mitigate the common problem that conventional conditional GAN training paradigm usually learns to totally ignore the randomness, resulting to collapsing results lacking diversity \cite{reed2016generative}.
-In addition, using this kind of text embedding makes the input pure stochastic, making it more difficult for the generator to over fit the training data.
+\textbf{Variational text encoding: } Following the work of \cite{han2017stackgan}, instead of using the plan deterministic non-linear transformation of the origin al $\Psi(t)$, we obtain the conditional vector $c$ by sampling from a Gaussian distribution $\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )$, in which the mean $\mu(\psi_t)$ and the diagonal covariance matrix $\Sigma(\psi_t)$ are non-linear transformation of the original text embedding $\psi_t$.
+This type of conditional augmentation technique can be used to inject randomness to the text embedding vector $\psi_t$ to mitigate the common problem that conventional conditional GAN training paradigm usually learns to $G$ that totally ignores the noise, resulting to results lacking diversity.
 
-\subsection{Architecture Design}
-Our proposed network, composed by a generator and a discriminator, is symmetric as well as extensile. We introduce the details as well as motivations.
+Conditioned on $c$ and the random vector $z$, a synthetic image $\hat{x}$ is generated as $\hat{x}\leftarrow G(c,z)$, it is simply a feed forward pass of the generator.
+Our generator consists of stacks of residual blocks, bilinear sampling layer is used to up-sample the feature maps.
 
-\textbf{Generator} The generator is simpled composed by three kinds of modules, termed as $K$-repeat res-blocks, stretching layers, and linear compression layers.
-A single res-block in the $K$-repeat res-block is a standard residual block  \cite{he2016identity} containing two convolutional (conv) layers (with batch normalization (BN) \cite{ioffe2015batch} and ReLU).
-The stretching layer serves to reduce feature map size and dimension.
-It simply contains an scale-$2$ nearest up-sampling layer followed by a convolutional layer with BN+ReLU.
-And the linear compression layer is a conv layer followed by a Tan, whose compact design enforces feature maps in conv blocks can linearly represent RGB images at arbitrary scales.
-Starting from a $1024{\times}4{\times}4$ embeddings replicated by a $1024$-d text embedding, the generator simples use $M$ $K$-repeat res-blocks connected by $M{-}1$ in-between stretching layers until the feature maps reach to the targeting resolution.
-So for $256{\times}256$ targeting resolution with $K{=}1$, there are $M{=}6$ $1$-repeat res-blocks and $5$ stretching layers.
-Such simple and symmetric design makes our generator helpful for gradient flows.
-We will verify in experiments.
-With a predefined side-output scales $\{S_i\}$, we apply the compression layer at those scales to produce synthetic images.
+The discriminator $D$ in our model mainly consists of two branches: matching-aware pair discrimination branch $D_{pair}$, and image discrimination branch $D_{img}$, both branches share the same  image encoder.
 
-\textbf{Discriminator} The discriminator simply contains consecutive stride-2 conv layers with BN and LeakyReLU \cite{} (the depth changes according to the input size) until the feature map has $512{\times}4{\times}4$ dimension.
-There two branches are added on top of it for multi-purpose discriminator design (see next section) .
-One is a direct $4{\times}4$ conv layers to produce a 2-d vector to classify real and fake.
-Another one first concatenate $128{\times}4{\times}4$ text embedding (replicated from a $128$-d text embedding).
-Then we use an $1{\times}1$ conv to fuse text and image information; it is critical to guarantee the semantic consistency in the final results.
-Finally, a $4{\times}4$ conv layer produces a 2-d vector.
+Given a pair of image and text embedding $(x, \psi{t})$ as input, in the discriminator $D$, we first transfer $x$  to an image code $Code_x$.
+$Code_x$ along with $f_{sent}(\psi_t)$ is concatenated and fed to the matching aware branch to compute a final scale value indicating the probability of the pair being real or fake, where $f_{sent}$ consists of one linear layer and one leaky ReLU transformation,  the matching-aware branch is a set of residual blocks with strid-2 convolution, more details of the architecture will be provided in the appendix.
+Besides that, the image code is also fed to an image-disc branch, whose structure is very similar to the matching-aware branch, to judge the probability of the input image being real or fake.
+We performance batch normalization on all convolutional layers.
+\textcolor{red}{like stackgan, I will add much more architecture details later}
 
-All intermediate conv layers use $3{\times}3$ kernels (with reflection padding and no bias).
-We remove ReLU after the skip-addition of each residual block, with an intention to reduce sparse gradients.
-We also experimented other normalization (i.e.
-instance normalization \cite{ulyanov2016instance} and layer normalization \cite{ba2016layer}) used by \cite{zhu2017unpaired,chen2017photographic}.
-Both are not satisfactory.
+The generator $G$ and discriminator $D$ are optimized alternatively using their corresponding loss function.
 
  \subsection{Scalable Deeply Supervised}
-Instead of only predicting the high resolution in the final output, our model is designed to predict multi-level images of gradually increasing dimension (e.g., 256$\times$256 as the final output with 64$\times$64 and 128$\times$128 being the side output).
-
+ \textbf{Multi-level side output:} instead of only predicting the high resolution in the final output, our model is designed to predict multi-level images of gradually increasing dimension (e.g., 256$\times$256 as the final output with 64$\times$64 and 128$\times$128 being the side output) as the side outputs.
 In principle, the lower-resolution side output is forced to learn the rough structure (e.g., object sketch, color information and background) of the images, the subsequent higher-resolution path is used to add more details to the images.
-
 The lower-level side output works by regularizing the lower-level image feature.
@@
 \subsection{Generator Loss}
-As is shown in Fig\ref{game}, In the generator $G$, we first sample a random vector $z\in \mathcal{R}^{Z} \scriptsize{\sim} \mathcal{N}(0,1)$, then text embedding vector $\psi_{t}$ is obtained by applying an per-trained text encoder on the image description $t$, in this paper, we use the char-rnn based text encoder provided in \cite{reed2016generative}.
-
-Conditioned on variational text embedding $c$ and the random vector $z$, a synthetic image $\hat{x}$ is generated as $\hat{x}\leftarrow G(c,z)$, it is simply a feed forward pass of the generator.
-The generator $G$ consists of stacks of residual blocks, bilinear sampling layer is used to up-sample the feature maps.
-
 The generator's goal is to generator image that match the input text embedding and looks as real as possible.
 So the loss function for our model mainly consists of two parts, namely, matching aware loss and one image loss.
-
 Given a set of chosen input pair $(x, \psi_t)$, the generator is optimizing the following function
@@
 \subsection{Functional Loss of Discriminator}
-
-As is shown in Figure.
-\ref{overview}, the discriminator $D$ in our model mainly consists of two branches: matching-aware pair discrimination branch $D_{pair}$, and image discrimination branch $D_{img}$, both branches share the same  image encoder.
-
-Given a pair of image and text embedding $(x, \psi{t})$ as input, in the discriminator $D$, we first transfer $x$  to an image code $Code_x$.
-$Code_x$ along with $f_{sent}(\psi_t)$ is concatenated and fed to the matching aware branch to compute a final scale value indicating the probability of the pair being real or fake, where $f_{sent}$ consists of one linear layer and one leaky ReLU transformation,  the matching-aware branch is a set of residual blocks with strid-2 convolution, more details of the architecture will be provided in the appendix.
-Besides that, the image code is also fed to an image-disc branch, whose structure is very similar to the matching-aware branch, to judge the probability of the input image being real or fake.
-We performance batch normalization on all convolutional layers.
-\textcolor{red}{like stackgan, I will add much more architecture details later}
-
-The generator $G$ and discriminator $D$ are optimized alternatively using their corresponding loss function.
-
  Our goal is to generate images that not only look as realistic as real images, but also matching the given text description.
@@
 
-\section{Dataset}
-
 \section{Experiments}
@@
 			TAC-GAN	 &	-		&		$\bm{3.45{\pm}.05}$		& -	\\	\hline
-			HDGAN 		&	$\bm{4.01{\pm}.04}$	&	$ \bm{3.45{\pm}.07}$			&  -  \\ \hline
+			HDGAN 		&	$\bm{4.01{\pm}.06}$	&	$ \bm{3.45{\pm}.07}$			&  -  \\ \hline
 		\end{tabularx} \vspace{-.4cm}
@@
 The proposed HDGAN outperforms others significantly.} \label{table:score}
+\end{table}
+
+\begin{table}[t] % retrieval
+	\begin{center}
+		\begin{tabularx}{.42\textwidth}{c|ccc}
+			\specialrule{1.5pt}{0pt}{0pt}  
+			Scale 						& StackGAN & HDGAN & HR Test					\\ 				\hline
+            $64{\times}64$              &   ${2.95{\pm}.02}$       &  	$\bm{3.46{\pm}.04}$ &  ${3.46{\pm}.04}$	\\
+           $128{\times}128$             &   ${3.35{\pm}.02}$      &  $\bm{3.85{\pm}.04}$	& ${3.45{\pm}.04}$	\\
+           $256{\times}256$             &   $3.70{\pm}.04$     &	$\bm{4.01{\pm}.06}$ & ${3.46{\pm}.04}$ \\ \hline
+		\end{tabularx}
+	\end{center} \vspace{-.4cm}
+	\caption{Scale accuracy \textcolor{red}{changing to figure is better}.} \label{table:deep-nest}
 \end{table}
@@
 				 64	& 128	& 256 			& 		\\ \hline
-					&  		&	\checkmark	&		\\ 
+					&  		&	\checkmark	&	${3.52{\pm}.04}$	\\ 
 						&  	\checkmark	&	\checkmark	&		\\
-				\checkmark	&  			&	\checkmark	&		\\
-				\checkmark	&  \checkmark		&	\checkmark	&	$\bm{4.01{\pm}.04}$ \\
+				\checkmark	&  			&	\checkmark	&  ${4.14{\pm}.03}$		\\
+				\checkmark	&  \checkmark		&	\checkmark	&	${4.01{\pm}.04}$ \\
 

### 2017-10-26 cvpr2018.tex
9th

--- 2017-10-23 cvpr2018.tex
@@
 Recently, Dong \etal \cite{dong2017semantic} propose to learn a joint embedding of images and text so as to re-render a prototype image conditioned on targeting descriptions.
-Cha \etal \cite{char2017perceptual} explore the usage of the perceptional loss \cite{johnson2016perceptual} and Dash \etal \cite{dash2017tac} make use of auxiliary classifiers (similar with \cite{odena2016conditional}) to assist GAN training.
+Cha \etal \cite{char2017perceptual} explore the usage of the perceptional loss with a pretrained ImageNet CNN \cite{johnson2016perceptual} and Dash \etal \cite{dash2017tac} make use of auxiliary classifiers (similar with \cite{odena2016conditional}) to assist GAN training.
 
 Learning a continuous mapping from low-dimensional embeddings to complex real data distribution is a long-standing problem.
-Although GANs have made significant progressive, there are still many not well-solved difficulties, e.g.
-training instability.
+Although GANs have made significant progressive, there are still many  unsolved difficulties, e.g.
+training instability and high resolution.
 Wide methods have been proposed to address those tasks, through various stabilization training techniques \cite{salimans2016improved,arjovsky2017wasserstein,berthelot2017began,shrivastava2016learning,odena2016conditional}, regularization using outside knowledge (e.g.
-image labels, ImageNet CNNs, etc) \cite{dosovitskiy2016generating,ledig2016photo,dash2017tac,dash2017tac}.
-While our method does not use any extra information apart from input text.
+image labels, ImageNet CNNs, etc) \cite{dosovitskiy2016generating,ledig2016photo,dash2017tac,dash2017tac}, or multiple discriminators  \cite{metz2016unrolled,durugkar2016generative,yang2017lr}.
+While note that our method does not use any extra information apart from training paired text and images.
 Moreover, it is easy to see the training difficulty grows significantly as targeting image resolution increases.
@@
 \end{figure}
+
+\section{Method}
+Figure \ref{fig:archs} illustrate the overall method.
+
+\subsection{Architecture Design}
+Our proposed network, composed by a generator and a discriminator, is symmetric as well as extensile. We introduce the details as well as motivations.
+
+\textbf{Generator} The generator is simpled composed by three kinds of modules, termed as $K$-repeat res-blocks, stretching layers, and linear compression layers.
+A single res-block in the $K$-repeat res-block is a standard residual block  \cite{he2016identity} containing two convolutional (conv) layers (with batch normalization (BN) \cite{ioffe2015batch} and ReLU).
+The stretching layer serves to reduce feature map size and dimension.
+It simply contains an scale-$2$ nearest up-sampling layer followed by a convolutional layer with BN+ReLU.
+And the linear compression layer is a conv layer followed by a Tan, whose compact design enforces feature maps in conv blocks can linearly represent RGB images at arbitrary scales.
+Starting from a $1024{\times}4{\times}4$ embeddings replicated by a $1024$-d text embedding, the generator simples use $M$ $K$-repeat res-blocks connected by $M{-}1$ in-between stretching layers until the feature maps reach to the targeting resolution.
+So for $256{\times}256$ targeting resolution with $K{=}1$, there are $M{=}6$ $1$-repeat res-blocks and $5$ stretching layers.
+Such simple and symmetric design makes our generator helpful for gradient flows.
+We will verify in experiments.
+With a predefined side-output scales $\{S_i\}$, we apply the compression layer at those scales to produce synthetic images.
+
+\textbf{Discriminator} The discriminator simply contains consecutive stride-2 conv layers with BN and LeakyReLU \cite{} (the depth depends on the input image size) until the feature map has $512{\times}4{\times}4$ dimension.
+There two branches are added on top of it for multi-purpose discriminator design (see next section) .
+One is a direct $4{\times}4$ conv layers to produce a 2-d vector to classify real and fake.
+Another one first concatenate $128{\times}4{\times}4$ text embedding (replicated from a $128$-d text embedding).
+Then we use an $1{\times}1$ conv to fuse text and image information; it is critical to guarantee the semantic consistency in the final results.
+Finally, a $4{\times}4$ conv layer produces a 2-d vector.
+
+All intermediate conv layers use $3{\times}3$ kernels (with reflection padding and no bias).
+We remove ReLU after the skip-addition of each residual block, with an intention to reduce sparse gradients.
+We also experimented other normalization (i.e.
+instance normalization \cite{ulyanov2016instance} and layer normalization \cite{ba2016layer}) used by \cite{zhu2017unpaired,chen2017photographic}.
+Both are not satisfactory.
 
@@
 		%	StackGAN$^\star$     &		$3.89{\pm}.05$	&	 $3.16{\pm}.01$			&  $8.45{\pm}.03$		\\ \hline
-			TAC-GAN	 &	-		&		$\bm{3.45{\pm}.05}$		& -	\\	\hline
-			HDGAN 		&	$\bm{4.01{\pm}.04}$	&	$ \bm{3.45{\pm}.07}$			&  -  \\ \hline
+			TAC-GAN	 &	-		&		$\bm{3.45{\pm}.05}$		& -	\\	
+			StackGAN++     &		$3.84{\pm}.06$	&	 -			&  -	\\  \hline
+			HDGAN 		&	$\bm{4.01{\pm}.06}$	&	$ \bm{3.45{\pm}.07}$			&  -  \\ \hline
 		\end{tabularx} \vspace{-.4cm}
@@
 \subsection{Comparative Results}
-We compare our results with GAN-INT-CLS \cite{reed2016generative}, GAWWN \cite{reed2016learning}, and  StackGAN \cite{han2017stackgan}, and TAC-GAN \cite{dash2017tac}.
-StackGAN is currently the state of the art method in general that is comprehensively validated.
-StackGAN \cite{han2017stackgan} generates synthetic images up to $256{\times}256$ resolution.
-We show that our method can generates images up to  $512{\times}512$.
+We compare our results with GAN-INT-CLS \cite{reed2016generative}, GAWWN \cite{reed2016learning}, TAC-GAN \cite{dash2017tac}, and StackGAN \cite{han2017stackgan} and also its improved version StackGAN++\footnote{This comes from a recently released pre-print from the author of StackGAN we just noticed, which outperforms StackGAN.
+Similarly with our HDGAN, it now can train $64{-}256$ directly.
+Each generator still take images from the bottom generator and supervised by a discriminator.
+Differently, our network is more like a simple Vanilla network (or a pure inverse ImageNet CNN).}.
+
+StackGAN \cite{han2017stackgan} generates synthetic images up to $256{\times}256$ resolution. We show that our method can generates images up to $512{\times}512$.
 

### 2017-10-26 cvpr2018.tex
dataset

--- 2017-10-23 cvpr2018.tex
@@
 \subsection{Dataset}
-\textbf{Dataset} We use three datasets for evaluation. \textcolor{red}{Yuanpu address}
+\textbf{Dataset} 
+We evaluate our method extensively using three widely used datasets.
+CUB dataset contains 11,788 bird images belonging to one of the 200 different classes.
+Each image in this dataset is associated with 10 text descriptions.
+We pre-process the image using the same pipeline proposed in \cite{han2017stackgan}, which crops the birds foreground out to  ensure a object-background ratio greater than 0.75.
+The OXford-102 dataset contains 102 different categories of flowers with 8189 images in total.
+Following the similar experiment setting in \cite{han2017stackgan, reed2016generative}, we split both of these datasets into class-disjoint training and testing sets.
+Each image in both CUB and Oxford-102 is associated with 10 text descriptions.
+We also exploit the MS  COCO dataset, which contains a much more broad image category and various backgrounds.
+We use the training and validation splitting setting provided by the original COCO dataset, resulting to a training set containing 80k images and a validation set with 40k images.
+Different from CUB and Oxford-102, each image in COCO has 5 text descriptions.
+For text features, we use the pre-trained text encoder model provided in \cite{reed2016generative}, each text description is encoded into a 1024 vector.
+During the training stage, we randomly pick-up a crop view from the original images, and pick 4 image sentence embedding and use the mean as conditioning vector.
 
 \subsection{Evaluation metric}
-\textbf{Inception score }
+\textbf{Inception score. }  To evaluate the quality of generated images, we resort to the recently proposed qualitative evaluation measurement "inception score"\cite{improvedGAN},
+ \begin{equation}
+	IS = \exp(\mathbb{E}_xD_{\bm{KL}}(p(y|\bm{x})||p(y)))
+ \end{equation}
+ where $\bm{x}$ denotes generated sample images, $y$ the class label, $p(y|\bm{x})$ represents the conditional label distribution calculated by the Inception model\cite{inception}.
 
@@
 \textcolor{red}{Yuanpu address}
+
+\subsubsection{What role does noise play}
 

### 2017-10-27 cvpr2018.tex

--- 2017-10-26 cvpr2018.tex
@@
 
+\textbf{Advantages} Figure \ref{fig:archs-compare} illustrates the architecture difference between widely-used cascade strategy \cite{han2017stackgan,denton2015deep} and our strategy.
+Compared with it,
+\\
+
 \section{Preliminary}
@@
 In practice, It's been shown to work better for the generator $G$ to minimizing $-\log(D(G(z)))$ rather than $\log(1-D(G(z)))$, namely, the $\log(D)$ trick.
+In this paper, we replace the negative log likelihood loss with a least square objective\cite{lsgan}.
 
@@
 In this paper, we consider the task of training a deep  generative adversarial network conditioned on the embedding of the text descriptions of the images.
-
-\textbf{Advantages} Figure \ref{fig:archs-compare} illustrates the architecture difference between widely-used cascade strategy \cite{han2017stackgan,denton2015deep} and our strategy.
-Compared with it,
-\\
 
@@
 We leverage functional loss for discriminator and hierarchically nested side outputs as hierarchical supervision for both generator and discriminator to achieve our goal of generating photo-realistic images from text descriptions.
+
 In general, the generator takes text embedding and random noise vector as input and synthesis images at different scales (e.g, $64\times64$, $128\times128$, $256\times256$).
@@
 
-\textbf{Notation } In this paper, we use the following notations.
+\textbf{Notation } 
+We denote the training data set by $S=\{(\bm{X}^n, \bm{T}^n),n=1,...,N\}$, where $X^n$ is the $n-$th training image, and $T^n={t^1,...,t^m}$ as $m$ text descriptions corresponds to $X^n$.
+Our goal is to learn the generator $G$ that is capable of producing high resolution images of high visual quality as well as variability giving an input text description $t$.
+
 Denote the image dimension, text embedding dimension and the dimension of the noise input as $I$, $T$ and $Z$, respectively.
@@
 
-\textbf{Variational text embedding } Following the work of \cite{han2017stackgan}, instead of using the plan deterministic non-linear transformation of the original $\Psi_t$, we obtain the conditional vector $c$ by sampling from a Gaussian distribution $\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )$, in which the mean $\mu(\psi_t)$ and the diagonal covariance matrix $\Sigma(\psi_t)$ are non-linear transformation of the original text embedding $\psi_t$.
+\textbf{Variational text embedding } Following the practice of \cite{han2017stackgan}, instead of using the plan deterministic non-linear transformation of the original $\psi_t$, we obtain the conditional vector $c$ by sampling from a Gaussian distribution $\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )$, in which the mean $\mu(\psi_t)$ and the diagonal covariance matrix $\Sigma(\psi_t)$ are non-linear transformation of the original text embedding $\psi_t$.
 This type of conditional augmentation technique can be used to inject randomness to the text embedding vector $\psi_t$ to mitigate the common problem that conventional conditional GAN training paradigm usually learns to totally ignore the randomness, resulting to collapsing results lacking diversity \cite{reed2016generative}.
 In addition, using this kind of text embedding makes the input pure stochastic, making it more difficult for the generator to over fit the training data.
+
+ In the spirit of variational auto-encoder, further Kullback-Leibler divergence regularization term  $D_{KL}(\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )|| \mathcal{N}(0, \bm{I}))$ is added to the final loss function to push the Gaussian distribution to the norm distribution to address over-fitting.
+In addition, this term might also play a role in balancing the $c_t$ and generated condition vector $c_t$ by forcing $c$ to have a similar scale to $z$.
+In the following sections, we denote $c_t$ as the variational conditional text vector.
+
+\subsection{Hierarchical Deep Supervision}
+Directly predicting high resolution synthesized images are difficult, not only because of the difficulties in training but also due to the large variation and instability in the hidden layers.
+
+Our architecture of $G$ consists of a single stream network with additional multiple side outputs.
+This architecture resemble the previous proposed method in edge detection\cite{hed} and classification\cite{deepsup}, which demonstrate that additional supervision to the hidden layer can improve both generalization and optimization.
+We hypothesis that adding hidden layer supervision using side outputs can act as a regularizer to the hidden space of $G$, which reduces the over-fitting issue and provide a short path for the error signal.
+
+Given a random Gaussian noise  $z\in \mathcal{R}^{Z} \scriptsize{\sim} \mathcal{N}(0,1)$ and a text description $t$, to obtain the text embedding vector $\psi_{t}\in \mathcal{R}^{T}$, we apply a per-trained text encoder on the image description $t$, in this paper, we use the char-rnn based text encoder provided in \cite{reed2016generative}.
+$G$ will generate multiple side outputs,
+\begin{equation}
+\label{side}
+\begin{split}
+	o_1,...,o_s = G(\psi_{t}, z)	   
+\end{split}
+\end{equation}
+where $s$ is the total number of side outputs, please note that the dimension of $o_1,..,o_s$ increase gradually (e.g., 64$\times$64, 128$\times$128, and 256$\times$256).
+Denote $\mathcal{X}^i = \{X^i_1, ..
+X^i_s\}$ as the pyramid of  resized images constructed from original image $X^i$.
+
+For each $o_i$, a distinct discriminator $D_i$ is assigned to compete with it. Denote $\mathcal{D}=\{D_1, ..., D_o\}$ as the whole set of discriminators.
+We aim to solve the following optimization problem:
+
+\begin{equation}
+\label{equ:optim}
+\begin{split}
+  G^*, \mathcal{D}^* = \arg~\underset{G}{\min}\ \underset{\mathcal{D}}{\max}~ \mathcal{L}(G,\mathcal{D}, \mathcal{X}, \bm{T} , z)
+\end{split}
+\end{equation}
+where $\mathcal{D}^*$ compresses the optimal discriminators $\{D_1^*, ..., D_o^*\}$, and $ \mathcal{L}(G,\mathcal{D}, \bm{X}, \bm{T} , z)$ is the full objective of this mini-max game.
+
+Please note that in this setting, one generator competes with multiple discriminators.
+And each discriminators does not share weights with each other, thus giving them the flexibility to focus on learning different discriminative features.
+
+In principle, the lower-resolution side output is forced to learn the rough structure (e.g., object sketch, color information and background) of the images, the subsequent higher-resolution path is used to add more details to the images.
+Since the model is trained in an end-to-end fashion, we can observe more consistent information exhibited in both lower and higher-resolution outputs than stackGan\cite{han2017stackgan}.
+This type of side output is also proven useful because it allows short path between image supervision information to the hidden feature maps, which could potentially helps training.
+
+\subsection{Matching Aware Pair-Loss}
+During the setting of conditional generative adversarial learning, simply generating images of high visual quality is not enough, most importantly, we want the generated images well aligned with the conditioning information (text description in our model).
+
+%Given a pair of image and text embedding $(x, \psi{t})$ as input, in the discriminator $D_i$, we first transfer $x$  to an image code $Code_x$.
+$Code_x$ along with $f_{sent}(\psi_t)$ is concatenated and fed to the matching aware branch to compute a final scale value indicating the probability of the pair being real or fake, where $f_{sent}$ consists of one linear layer and one leaky ReLU transformation,  the matching-aware branch is a set of residual blocks with strid-2 convolution, more details of the architecture will be provided in the appendix.
+Besides that, the image code is also fed to an image-disc branch, whose structure is very similar to the matching-aware branch, to judge the probability of the input image being real or fake.
+We performance batch normalization on all convolutional layers.
+\textcolor{red}{like stackgan, I will add much more architecture details later}
+%
+%The generator $G$ and discriminator $D$ are optimized alternatively using their corresponding loss function.
+
+Therefore, the discriminator should be optimized to differentiate two errors: real image with mismatch conditional text information, fake image with real text.
+In order to achieve this, the previously proposed matching aware discriminator is explicitly trained with three pair configurations, namely: real image with right text as positive training sample, and the aforementioned two sources of error pairs as negative training samples.
+
+Given a mini-batch of training data consists of images $X$ and the corresponding text $t$, mismatching text $\hat{t}$.
+For simplicity, we omit the instance index.
+To train the discriminator,  we also need to sample fakes images $o_i$ using $G$.
+For the $i-$th discriminator $D_i$ , we can have:
+
+\begin{equation}
+\label{equ:matchignloss}
+\begin{split}
+\mathcal{L}_{pair}(D_i)  = & \mathbb{E}_{(x, t) \sim p_{data}}[(D_i( {X_i},  \bm{t}) - 1) ^ 2 ] - \frac{1}{2}*\\ 
+&   \mathbb{E}_{(X_i, \hat{t}) \sim p_{data}}[(D_i({X_i}, \hat{\bm{t}}) - 1)^2  ] - \frac{1}{2} *\\
+&   \mathbb{E}_{t \sim p_{data}}[ (D_i( {o}_i, \bm{t}))^2 ]  
+\end{split}
+\end{equation}
+
+Similarly, the pair wise objective of generator can be summarized as:
+\begin{equation}
+\label{equ:pariG}
+\begin{split}
+\mathcal{L}_{pair}(G)  = & \sum_{i=1}^{s} ( \mathbb{E}_{t \sim p_{data}}[ (D_i( {o}_i, \bm{t}) - 1) )^2 ] )
+\end{split}
+\end{equation}
+
+This type of loss is used to push the valid image-text pair away from the invalid pairs.
+
+\subsection{Local Adversarial Image Loss}
+%As is shown in Figure.
+\ref{overview}, the discriminator $D$ in our model mainly consists of two branches: matching-aware pair discrimination branch $D_{pair}$, and image discrimination branch $D_{img}$, both branches share the same  image encoder.
+
+The pair-loss is designed to differentiated invalid pairs from valid ones.
+However, at the very beginning of the training, the generated images are far away from true image distribution, the discriminator can very easily to judge a pair as valid without using much pair information.
+\textcolor{red}{need more explanationn.}
+
+Our insight has two folds:
+1.
+Image loss without using pair sentence information can be beneficial in the sense that it utilize more information as well as it directly push the generated image to the true image distribution.
+We hypothesis this type of loss can help the model to stabilize and boost the training.
+2.
+Since our model outputs a pyramid of side outputs with increasing image size.
+We expect the low resolution output can capture the global structure and color information, while the higher resolution outputs paints more details and focus on rendering the image.
+
+We don't only want the whole image is classified as true image by the discriminator, but also restrict the discriminator to classify all the local patches of high resolution output as true as well.
+To this end, we propose a hierarchical image loss, where the output of the image  discriminator is more than one scale value.
+\begin{equation}
+  d_i = D_i(X_i)
+\end{equation}
+The size of $d_i$ increases as $X_i$.
+For instance 1$\times$1 for 64$\times$64 input, 4$\times 4$ for 128$\times$128, etc.
+This type of design, gradually increase the receptive field of the discriminator.
+
+This loss explicit force the discriminator to differentiate correct pair from the wrong pair.
+However, there is no explicit loss that push the discriminator to differentiate real images from the fake images.
+The way that they formulate all the task into pair based solution complicate the task of the generator.
+In this paper, we propose to directly add another loss that concentrate the image quality only beside the matching loss.
+Specifically, it can be given by:
+\begin{equation}
+\label{equ:local}
+\begin{split}
+\mathcal{L}_{local}(K_i)  = & \mathbb{E}_{(x, t) \sim p_{data}}[(K_i( {X_i}) - 1) ^ 2 ] -  \mathbb{E}_{t \sim p_{data}}[ (K_i( {o}_i))^2 ]  
+\end{split}
+\end{equation}
+
+Similarly, the pair wise objective of generator can be summarized as:
+\begin{equation}
+\label{equ:pariG}
+\begin{split}
+\mathcal{L}_{local}(G)  = & \sum_{i=1}^{s} ( \mathbb{E}_{t \sim p_{data}}[ (K_i( {o}_i) - 1) )^2 ] )
+\end{split}
+\end{equation}
+
+\textcolor{red}{equations needs to be verified, just a rough place holder}
+
+Further more, this separation of the image loss from the matching loss open further possibilities, such as utilizing the unlabeled image to improve both the generator and discriminator.
+\textcolor{red}{maybe utilizing the imagenet for training the coco, or save as another paper.}
+
+\subsection{Total Loss}
+The total objective for both $D$ and $G$ can be given by. 
+\begin{equation}
+\label{equ:totalD}
+\begin{split}
+\mathcal{L}(D)  = & \sum_{i=1}^{s} ( \mathcal{L}_{pair}(D) + \alpha~\mathcal{L}_{local}(D) ) 
+\end{split}
+\end{equation}
+
+\begin{equation}
+\label{equ:totalG}
+\begin{split}
+\mathcal{L}(G)  = & \sum_{i=1}^{s} ( \mathcal{L}_{pair}(G) + \alpha~\mathcal{L}_{local}(G) + \\
+                  & \beta~D_{KL}(\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )|| \mathcal{N}(0, \bm{I})) )  
+\end{split}
+\end{equation}
+where $\alpha$ is coefficient used to tune the weight of the local patch loss, $\beta$ is used to tune the weights of the KL-Divergence.
+A algorithm that summarizes the training process of our model is given in Algorithm 1.
+
+%The loss function of the matching aware discriminator are summarized as:
+%\begin{equation}
+%\label{matchignloss}
+%\begin{split}
+%\mathcal{L}_D = 	  &\mathbb{E}_{(x, t) \sim p_{data}}[\log( D( x  \psi_t) ) ] -  0.5*(\\
+%&\mathbb{E}_{(x, \hat{t}) \sim p_{data}}[\log(D(x, \psi_{\hat{t}} )  ] +\\
+%&   \mathbb{E}_{t \sim p_{data}}[\log(D(\hat{x_1}, \psi_t) ) ] 
+%\end{split}
+%\end{equation}
+%
+%\begin{equation}
+%\label{matchignloss}
+%\begin{split}
+%\mathcal{L}_D = 	  &\mathbb{E}_{(x, t) \sim p_{data}}[\log( D( x  \psi_t) ) ] -  0.5*(\\
+%&\mathbb{E}_{(x, \hat{t}) \sim p_{data}}[\log(D(x, \psi_{\hat{t}} )  ] +\\
+%&   \mathbb{E}_{t \sim p_{data}}[\log(D(\hat{x_1}, \psi_t) ) ] 
+%\end{split}
+%\end{equation}
+
+\subsection{Implementation Details}
+\begin{equation}
+ \label{genloss}
+ \begin{split}
+ \mathcal{L}_G = & \mathbb{E}_{z\sim p_{z}, t \sim p_{data}}[-\log( D_{sent}( G(z, c_t),  \psi_t) ) ] + \\
+				  & \mathbb{E}_{z\sim p_{z}, t \sim p_{data}}[-\log( D_{img}( G(z, c_t) ) ) ] + \\
+                  & D_{KL}(\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )|| \mathcal{N}(0, \bm{I})) 		   
+ \end{split}
+ \end{equation}
+ where $c_t$ is the variational conditional vector generated from $\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )$.
+To make the network differentiable, in practice, we adopted the re-parametric trick\cite{vae}, where $c_t$ is actually computed as $\mu(\psi_t)+\Sigma(\psi_t)\odot \epsilon$, where $\epsilon\in \mathcal{R}^{T}$ is draw from a normal Gaussian distribution.
+
+ \begin{algorithm}
+ 	\caption{Multi scale GAN training algorithm with step size $\alpha$, number of iteration $S$, we summarize the algorithm using SGD for simplicity.\textcolor{red}{need to change to goodfellow algorithm style}}
+ 	\label{CHalgorithm}
+ 	\begin{algorithmic}[1]
+
+ 		\For{$i \gets 1 \textrm{ to } S$ }
+ 		\State $z_1, z_2 \sim \mathcal{N}(0,\bm{1})^Z$
+ 		\State $\hat{x_1}, \hat{x_2} = G(z_1, \psi_t),  G(z_2, \psi_{\hat{t}})$ %\{Forward through $G$ using matching text embedding\}
+ 		\State $d_r$ = $D_{pair}(x, \psi_t)$ \{(real image, matching text)\}
+ 		\State $d_w$ = $D_{pair}(x, \psi_{\hat{t}})$ \{(real image, wrong text)\}
+ 		\State $d_f$ = $D_{pair}(\hat{x_1}, \psi_t)$ \{(fake image, matching text)\}
+ 		\State $s_r, s_1, s_2$ = $D_{img}(x), D_{img}(\hat{x_1})$, $D_{img}(\hat{x_1})$ %\{Forward through $D_{img}$ with $\hat{x_1}$\}
+
+ 		\State $loss_{img}$ = $ (\log(1-s_1) + \log(1-s_2))/2 $
+ 		\State $loss_{pair}$ = $ (\log(1-d_w) + \log(1-d_f))/2 $
+
+ 		\State $\mathcal{L}_{D}$ = $\log(d_r) + \log(s_r) +loss_{img} + loss_{pair}$
+ 		\State $\mathcal{L}_{G}$ = $\log(1-d_f) +  ( \log(1-s_1) + \log(1-s_2) )/2 $
+ 		\State $\theta_G$ = $\theta_G$ - ${\delta \mathcal{L}_G } / {\delta \theta_G}$  \{Update generator\}
+ 		\State $\theta_D$ = $\theta_D$ - ${\delta \mathcal{L}_D} / {\delta \theta_D}$  \{Update generator\}
+
+ 		\EndFor
+
+ 	\end{algorithmic}
+ \end{algorithm}
 
@@
 Both are not satisfactory.
-
-\subsection{Scalable Deeply Supervised}
-Instead of only predicting the high resolution in the final output, our model is designed to predict multi-level images of gradually increasing dimension (e.g., 256$\times$256 as the final output with 64$\times$64 and 128$\times$128 being the side output).
-
-In principle, the lower-resolution side output is forced to learn the rough structure (e.g., object sketch, color information and background) of the images, the subsequent higher-resolution path is used to add more details to the images.
-
-The lower-level side output works by regularizing the lower-level image feature.
-Since the model is trained in an end-to-end fashion, we can observe more consistent information exhibited in both lower and higher-resolution outputs than stackGan\cite{han2017stackgan}.
-This type of side output is also proven useful because it allows short path between image supervision information to the hidden feature maps, which could potentially helps training.
-
-\subsection{Generator Loss}
-As is shown in Fig\ref{game}, In the generator $G$, we first sample a random vector $z\in \mathcal{R}^{Z} \scriptsize{\sim} \mathcal{N}(0,1)$, then text embedding vector $\psi_{t}$ is obtained by applying an per-trained text encoder on the image description $t$, in this paper, we use the char-rnn based text encoder provided in \cite{reed2016generative}.
-
-Conditioned on variational text embedding $c$ and the random vector $z$, a synthetic image $\hat{x}$ is generated as $\hat{x}\leftarrow G(c,z)$, it is simply a feed forward pass of the generator.
-The generator $G$ consists of stacks of residual blocks, bilinear sampling layer is used to up-sample the feature maps.
-
-The generator's goal is to generator image that match the input text embedding and looks as real as possible.
-So the loss function for our model mainly consists of two parts, namely, matching aware loss and one image loss.
-
-Given a set of chosen input pair $(x, \psi_t)$, the generator is optimizing the following function
- \begin{equation}
- \label{genloss}
- \begin{split}
- \mathcal{L}_G = & \mathbb{E}_{z\sim p_{z}, t \sim p_{data}}[-\log( D_{sent}( G(z, c_t),  \psi_t) ) ] + \\
-				  & \mathbb{E}_{z\sim p_{z}, t \sim p_{data}}[-\log( D_{img}( G(z, c_t) ) ) ] + \\
-                  & D_{KL}(\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )|| \mathcal{N}(0, \bm{I})) 		   
- \end{split}
- \end{equation}
- where $c_t$ is the variational conditional vector generated from $\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )$.
-To make the network differentiable, in practice, we adopted the re-parametric trick\cite{vae}, where $c_t$ is actually computed as $\mu(\psi_t)+\Sigma(\psi_t)\odot \epsilon$, where $\epsilon\in \mathcal{R}^{T}$ is draw from a normal Gaussian distribution.
-
- In the spirit of variational auto-encoder, further Kullback-Leibler divergence regularization term  $D_{KL}(\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )|| \mathcal{N}(0, \bm{I}))$ is added to the final loss function to push the Gaussian distribution to the norm distribution to address over-fitting.
-In addition, this term might also play a role in balancing the $c_t$ and generated condition vector $c_t$ by forcing $c$ to have a similar scale to $z$.
-In the following sections, we denote $c_t$ as the variational conditional text vector.
-
-\subsection{Functional Loss of Discriminator}
-
-As is shown in Figure.
-\ref{overview}, the discriminator $D$ in our model mainly consists of two branches: matching-aware pair discrimination branch $D_{pair}$, and image discrimination branch $D_{img}$, both branches share the same  image encoder.
-
-Given a pair of image and text embedding $(x, \psi{t})$ as input, in the discriminator $D$, we first transfer $x$  to an image code $Code_x$.
-$Code_x$ along with $f_{sent}(\psi_t)$ is concatenated and fed to the matching aware branch to compute a final scale value indicating the probability of the pair being real or fake, where $f_{sent}$ consists of one linear layer and one leaky ReLU transformation,  the matching-aware branch is a set of residual blocks with strid-2 convolution, more details of the architecture will be provided in the appendix.
-Besides that, the image code is also fed to an image-disc branch, whose structure is very similar to the matching-aware branch, to judge the probability of the input image being real or fake.
-We performance batch normalization on all convolutional layers.
-\textcolor{red}{like stackgan, I will add much more architecture details later}
-
-The generator $G$ and discriminator $D$ are optimized alternatively using their corresponding loss function.
-
- Our goal is to generate images that not only look as realistic as real images, but also matching the given text description.
- Therefore, the discriminator must handle errors of the following two categories: real image with mismatch conditional text information, fake image with real text.
-In order to achieve this, the previously proposed matching aware discriminator is explicitly trained with three pair configurations, namely: real image with right text as positive training sample, and the aforementioned two sources of error pairs as negative training samples.
-
- Given a mini-batch of training data consists of images $x$ and the corresponding text $t$, mismatching text $\hat{t}$. First of all, we sample fakes images using $G$.
- $\hat{x_1} = G(z_1, \psi_t)$ and $\hat{x_2} = G(z_2, \psi_t)$, where $z_1$ and $z_2$ are random vector sampled from norm Gaussian distribution.
-
-The loss function of the matching aware discriminator are summarized as:
-  \begin{equation}
-  \label{matchignloss}
-  \begin{split}
-  \mathcal{L}_D = 	  &\mathbb{E}_{(x, t) \sim p_{data}}[\log( D( x  \psi_t) ) ] -  0.5*(\\
-					  &\mathbb{E}_{(x, \hat{t}) \sim p_{data}}[\log(D(x, \psi_{\hat{t}} )  ] +\\
-					  &   \mathbb{E}_{t \sim p_{data}}[\log(D(\hat{x_1}, \psi_t) ) ] 
-  \end{split}
-  \end{equation}
-This loss explicit force the discriminator to differentiate correct pair from the wrong pair.
-However, there is no explicit loss that push the discriminator to differentiate real images from the fake images.
-The way that they formulate all the task into pair based solution complicate the task of the generator.
-In this paper, we propose to directly add another loss that concentrate the image quality only beside the matching loss.
-Specifically, it can be given by:
-  \begin{equation}
-  \label{discoss}
-  \begin{split}
-  \mathcal{L}_D = 	&\mathbb{E}_{(x, t) \sim p_{data}}[\log( D( x  \psi_t) ) ] -  0.5*(\\
-		  &\mathbb{E}_{(x, \hat{t}) \sim p_{data}}[\log(D_{pair}(x, \psi_{\hat{t}} )  ] +\\
-		  &\mathbb{E}_{t \sim p_{data}}[\log(D_{pair}(\hat{x_1}, \psi_t) ) ] + \\
-		  &\mathbb{E}_{x \sim p_{data}}[\log( D_{img}(x) )] - 0.5* ( \\
-		  &\mathbb{E}[\log( D_{img}(\hat{x_1}))] + \mathbb{E}[\log( D_{img}(\hat{x_2}) )  ] )
-  \end{split}
-  \end{equation}
-\textcolor{red}{equations needs to be verified, just a rough place holder}
-
-Further more, this separation of the image loss from the matching loss open further possibilities, such as utilizing the unlabeled image to improve both the genrator and discriminator.
-\textcolor{red}{maybe utilizing the imagenet for training the coco, or save as another paper.}
-
- \begin{algorithm}
- 	\caption{Multi scale GAN training algorithm with step size $\alpha$, number of iteration $S$, we summarize the algorithm using SGD for simplicity.\textcolor{red}{need to change to goodfellow algorithm style}}
- 	\label{CHalgorithm}
- 	\begin{algorithmic}[1]
-
- 		\For{$i \gets 1 \textrm{ to } S$ }
- 		\State $z_1, z_2 \sim \mathcal{N}(0,\bm{1})^Z$
- 		\State $\hat{x_1}, \hat{x_2} = G(z_1, \psi_t),  G(z_2, \psi_{\hat{t}})$ %\{Forward through $G$ using matching text embedding\}
- 		\State $d_r$ = $D_{pair}(x, \psi_t)$ \{(real image, matching text)\}
- 		\State $d_w$ = $D_{pair}(x, \psi_{\hat{t}})$ \{(real image, wrong text)\}
- 		\State $d_f$ = $D_{pair}(\hat{x_1}, \psi_t)$ \{(fake image, matching text)\}
- 		\State $s_r, s_1, s_2$ = $D_{img}(x), D_{img}(\hat{x_1})$, $D_{img}(\hat{x_1})$ %\{Forward through $D_{img}$ with $\hat{x_1}$\}
-
- 		\State $loss_{img}$ = $ (\log(1-s_1) + \log(1-s_2))/2 $
- 		\State $loss_{pair}$ = $ (\log(1-d_w) + \log(1-d_f))/2 $
-
- 		\State $\mathcal{L}_{D}$ = $\log(d_r) + \log(s_r) +loss_{img} + loss_{pair}$
- 		\State $\mathcal{L}_{G}$ = $\log(1-d_f) +  ( \log(1-s_1) + \log(1-s_2) )/2 $
- 		\State $\theta_G$ = $\theta_G$ - ${\delta \mathcal{L}_G } / {\delta \theta_G}$  \{Update generator\}
- 		\State $\theta_D$ = $\theta_D$ - ${\delta \mathcal{L}_D} / {\delta \theta_D}$  \{Update generator\}
-
- 		\EndFor
-
- 	\end{algorithmic}
- \end{algorithm}
 
@@
 \subsection{Dataset}
-\textbf{Dataset} We use three datasets for evaluation. \textcolor{red}{Yuanpu address}
+\textbf{Dataset} 
+We evaluate our method extensively using three widely used datasets.
+CUB dataset contains 11,788 bird images belonging to one of the 200 different classes.
+Each image in this dataset is associated with 10 text descriptions.
+We pre-process the image using the same pipeline proposed in \cite{han2017stackgan}, which crops the birds foreground out to  ensure a object-background ratio greater than 0.75.
+The OXford-102 dataset contains 102 different categories of flowers with 8189 images in total.
+Following the similar experiment setting in \cite{han2017stackgan, reed2016generative}, we split both of these datasets into class-disjoint training and testing sets.
+Each image in both CUB and Oxford-102 is associated with 10 text descriptions.
+We also exploit the MS  COCO dataset, which contains a much more broad image category and various backgrounds.
+We use the training and validation splitting setting provided by the original COCO dataset, resulting to a training set containing 80k images and a validation set with 40k images.
+Different from CUB and Oxford-102, each image in COCO has 5 text descriptions.
+For text features, we use the pre-trained text encoder model provided in \cite{reed2016generative}, each text description is encoded into a 1024 vector.
+During the training stage, we randomly pick-up a crop view from the original images, and pick 4 image sentence embedding and use the mean as conditioning vector.
 
 \subsection{Evaluation metric}
-\textbf{Inception score }
+\textbf{Inception score. }  To evaluate the quality of generated images, we resort to the recently proposed qualitative evaluation measurement "inception score"\cite{improvedGAN},
+ \begin{equation}
+	IS = \exp(\mathbb{E}_xD_{\bm{KL}}(p(y|\bm{x})||p(y)))
+ \end{equation}
+ where $\bm{x}$ denotes generated sample images, $y$ the class label, $p(y|\bm{x})$ represents the conditional label distribution calculated by the Inception model\cite{inception}.
+Inception score is found to be a good measurement of both objectiveness and diversity of generated images, it is closely correlated with human judgment on the image quality.
+For CUB and oxford-102, we use the inception model provided by \cite{han2017stackgan}, for MS COCO dataset, we use the model train on ImageNet.
+
+\textbf{Image-sentence distance.
+} Since inception score can not measure alignment between the generated images and the text description, here, we conduct a new qualitative measurement, which calculated the cosine distance between image code and the sentence vector.
+We train the model on each dataset.
+
+\textbf{zizhao's new evaluation methods.}
+
+\textbf{Image retrieval. } We also conduct image retrieval evaluation on the dataset. The results is shown in Fig1.
+
+We only conduct qualitative experiment on
 
@@
 \textbf{Generalization to real user test}
-We test the generalization of our method by asking a user to write a sentence
+We test the generalization of our method by asking a user to write a sentence, and the generated results are shown in .
 

### 2017-10-28 cvpr2018.tex
modify methods
fix methdos

@@
 
-\subsection{Architecture Design}
-Our proposed network, composed by a generator and a discriminator, is symmetric as well as extensile. We introduce the details as well as motivations.
-
-\textbf{Generator} The generator is simpled composed by three kinds of modules, termed as $K$-repeat res-blocks, stretching layers, and linear compression layers.
-A single res-block in the $K$-repeat res-block is a standard residual block  \cite{he2016identity} containing two convolutional (conv) layers (with batch normalization (BN) \cite{ioffe2015batch} and ReLU).
-The stretching layer serves to reduce feature map size and dimension.
-It simply contains an scale-$2$ nearest up-sampling layer followed by a convolutional layer with BN+ReLU.
-And the linear compression layer is a conv layer followed by a Tan, whose compact design enforces feature maps in conv blocks can linearly represent RGB images at arbitrary scales.
-Starting from a $1024{\times}4{\times}4$ embeddings replicated by a $1024$-d text embedding, the generator simples use $M$ $K$-repeat res-blocks connected by $M{-}1$ in-between stretching layers until the feature maps reach to the targeting resolution.
-So for $256{\times}256$ targeting resolution with $K{=}1$, there are $M{=}6$ $1$-repeat res-blocks and $5$ stretching layers.
-Such simple and symmetric design makes our generator helpful for gradient flows.
-We will verify in experiments.
-With a predefined side-output scales $\{S_i\}$, we apply the compression layer at those scales to produce synthetic images.
-
-\textbf{Discriminator} The discriminator simply contains consecutive stride-2 conv layers with BN and LeakyReLU \cite{} (the depth depends on the input image size) until the feature map has $512{\times}4{\times}4$ dimension.
-There two branches are added on top of it for multi-purpose discriminator design (see next section) .
-One is a direct $4{\times}4$ conv layers to produce a 2-d vector to classify real and fake.
-Another one first concatenate $128{\times}4{\times}4$ text embedding (replicated from a $128$-d text embedding).
-Then we use an $1{\times}1$ conv to fuse text and image information; it is critical to guarantee the semantic consistency in the final results.
-Finally, a $4{\times}4$ conv layer produces a 2-d vector.
-
-All intermediate conv layers use $3{\times}3$ kernels (with reflection padding and no bias).
-We remove ReLU after the skip-addition of each residual block, with an intention to reduce sparse gradients.
-We also experimented other normalization (i.e.
-instance normalization \cite{ulyanov2016instance} and layer normalization \cite{ba2016layer}) used by \cite{zhu2017unpaired,chen2017photographic}.
-Both are not satisfactory.
-
-\textbf{Advantages} Figure \ref{fig:archs-compare} illustrates the architecture difference between widely-used cascade strategy \cite{han2017stackgan,denton2015deep} and our strategy.
-Compared with it,
-\\
-
 \section{Preliminary}
@@
 We denote the training data set by $S=\{(\bm{X}^n, \bm{T}^n),n=1,...,N\}$, where $X^n$ is the $n-$th training image, and $T^n={t^1,...,t^m}$ as $m$ text descriptions corresponds to $X^n$.
+
+Since we obtain the text embedding vector  using the per-trained char-rnn text encoder provided in \cite{reed2016generative}.
+For simplicity, we don not differentiate text description and the corresponding embedding vector in this paper.
 Our goal is to learn the generator $G$ that is capable of producing high resolution images of high visual quality as well as variability giving an input text description $t$.
@@
 
-\textbf{Variational text embedding } Following the practice of \cite{han2017stackgan}, instead of using the plan deterministic non-linear transformation of the original $\psi_t$, we obtain the conditional vector $c$ by sampling from a Gaussian distribution $\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )$, in which the mean $\mu(\psi_t)$ and the diagonal covariance matrix $\Sigma(\psi_t)$ are non-linear transformation of the original text embedding $\psi_t$.
-This type of conditional augmentation technique can be used to inject randomness to the text embedding vector $\psi_t$ to mitigate the common problem that conventional conditional GAN training paradigm usually learns to totally ignore the randomness, resulting to collapsing results lacking diversity \cite{reed2016generative}.
+\textbf{Variational text embedding } Following the practice of \cite{han2017stackgan}, instead of using the plan deterministic non-linear transformation of the original $t$, we obtain the conditional vector $c$ by sampling from a Gaussian distribution $\mathcal{N}(\mu(t), \Sigma(t) )$, in which the mean $\mu(t)$ and the diagonal covariance matrix $\Sigma(t)$ are non-linear transformation of the original text embedding $t$.
+This type of conditional augmentation technique can be used to inject randomness to the text embedding vector $t$ to mitigate the common problem that conventional conditional GAN training paradigm usually learns to totally ignore the randomness, resulting to collapsing results lacking diversity \cite{reed2016generative}.
 In addition, using this kind of text embedding makes the input pure stochastic, making it more difficult for the generator to over fit the training data.
-
- In the spirit of variational auto-encoder, further Kullback-Leibler divergence regularization term  $D_{KL}(\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )|| \mathcal{N}(0, \bm{I}))$ is added to the final loss function to push the Gaussian distribution to the norm distribution to address over-fitting.
-In addition, this term might also play a role in balancing the $c_t$ and generated condition vector $c_t$ by forcing $c$ to have a similar scale to $z$.
-In the following sections, we denote $c_t$ as the variational conditional text vector.
 
@@
 Our architecture of $G$ consists of a single stream network with additional multiple side outputs.
-This architecture resemble the previous proposed method in edge detection\cite{hed} and classification\cite{deepsup}, which demonstrate that additional supervision to the hidden layer can improve both generalization and optimization.
+This architecture resemble the previous proposed method in edge detection\cite{xie2015holistically} and classification\cite{lee2015deeply}, which demonstrate that additional supervision to the hidden layer can improve both generalization and optimization.
 We hypothesis that adding hidden layer supervision using side outputs can act as a regularizer to the hidden space of $G$, which reduces the over-fitting issue and provide a short path for the error signal.
 
-Given a random Gaussian noise  $z\in \mathcal{R}^{Z} \scriptsize{\sim} \mathcal{N}(0,1)$ and a text description $t$, to obtain the text embedding vector $\psi_{t}\in \mathcal{R}^{T}$, we apply a per-trained text encoder on the image description $t$, in this paper, we use the char-rnn based text encoder provided in \cite{reed2016generative}.
-$G$ will generate multiple side outputs,
+Given a random Gaussian noise  $z\in \mathcal{R}^{Z} \scriptsize{\sim} \mathcal{N}(0,1)$ and a text description embedding $t$  $G$ will generate multiple side outputs,
 \begin{equation}
@@
 \begin{split}
-	o_1,...,o_s = G(\psi_{t}, z)	   
+	o_1,...,o_s = G(t, z)	   
 \end{split}
@@
 X^i_s\}$ as the pyramid of  resized images constructed from original image $X^i$.
+For simplicity, we represent $o=\{o_1,...,o_s\}$.
 
@@
 \begin{split}
-  G^*, \mathcal{D}^* = \arg~\underset{G}{\min}\ \underset{\mathcal{D}}{\max}~ \mathcal{L}(G,\mathcal{D}, \mathcal{X}, \bm{T} , z)
+  G^*, \mathcal{D}^* = \arg~\underset{G}{\min}\ \underset{\mathcal{D}}{\max}~ \mathcal{L}(G,\mathcal{D}, \mathcal{X}, \bm{T})
 \end{split}
 \end{equation}
-where $\mathcal{D}^*$ compresses the optimal discriminators $\{D_1^*, ..., D_o^*\}$, and $ \mathcal{L}(G,\mathcal{D}, \bm{X}, \bm{T} , z)$ is the full objective of this mini-max game.
+where $\mathcal{D}^*$ compresses the optimal discriminators $\{D_1^*, ..., D_o^*\}$, and $ \mathcal{L}(G,\mathcal{D}, \bm{X}, \bm{T} )$ is the full objective of this mini-max game.
 
@@
 \begin{split}
-\mathcal{L}_{pair}(D_i)  = & \mathbb{E}_{(x, t) \sim p_{data}}[(D_i( {X_i},  \bm{t}) - 1) ^ 2 ] - \frac{1}{2}*\\ 
-&   \mathbb{E}_{(X_i, \hat{t}) \sim p_{data}}[(D_i({X_i}, \hat{\bm{t}}) - 1)^2  ] - \frac{1}{2} *\\
-&   \mathbb{E}_{t \sim p_{data}}[ (D_i( {o}_i, \bm{t}))^2 ]  
+\mathcal{L}_{pair}(D_i)  = & \mathbb{E}_{(x, t) \sim p_{data}}[(D_i( {X_i},  {t}) - 1) ^ 2 ] - \frac{1}{2}*\\ 
+&   \mathbb{E}_{(X_i, \hat{t}) \sim p_{data}}[(D_i({X_i}, \hat{{t}}) - 1)^2  ] - \frac{1}{2} *\\
+&   \mathbb{E}_{t \sim p_{data}}[ (D_i( {o}_i, {t}))^2 ]  
 \end{split}
@@
 \begin{split}
-\mathcal{L}_{pair}(G)  = & \sum_{i=1}^{s} ( \mathbb{E}_{t \sim p_{data}}[ (D_i( {o}_i, \bm{t}) - 1) )^2 ] )
+\mathcal{L}_{pair}(G)  = & \sum_{i=1}^{s} ( \mathbb{E}_{t \sim p_{data}}[ (D_i( {o}_i, {t}) - 1) )^2 ] )
 \end{split}
@@
 
-The pair-loss is designed to differentiated invalid pairs from valid ones.
-However, at the very beginning of the training, the generated images are far away from true image distribution, the discriminator can very easily to judge a pair as valid without using much pair information.
-\textcolor{red}{need more explanationn.}
+The pair-loss is designed to differentiate invalid pairs from valid ones.
+It works by first translating the image to a compact size code, then the combination of the image code and the sentence vector is concatenated and fed to successive layers of non-linear transformation  to predict the validity of the image sentence pair.
 
+Overall, the pair loss is designed to capture the global context semantic information.
+However, this loss has two problems, firstly,  there is no explicit loss that push the discriminator to differentiate real images from the fake images.
+Combining both tasks (generating realistic images and matching image with text) into one outputs complicates the learning tasks.
+Second,  as the image resolution goes higher, it might be challenging for the global pair wise discriminator to capture the local fine-grained details.
+In addition, as is pointed in \cite{shrivastava2016learning}, a single global strong discriminator tend to over-emphasize certain image feature and may lead to artifacts.
+
+%More specifically, ideally the image patches sampled from the higher resolution outputs
+
+Our solutions is to add hierarchical local adversarial image loss which does not require sentence information, to all the side outputs.
+To make the image discriminator focus more on local details, we restrict the receptive field of the image discriminator.
 Our insight has two folds:
-1.
+\begin{itemize}
+	\item 1. Forcing the local patch of generated samples to have similar statistics to real image patch can be beneficial to rendering details. %
+
+	\item 2.
 Image loss without using pair sentence information can be beneficial in the sense that it utilize more information as well as it directly push the generated image to the true image distribution.
 We hypothesis this type of loss can help the model to stabilize and boost the training.
-2.
-Since our model outputs a pyramid of side outputs with increasing image size.
-We expect the low resolution output can capture the global structure and color information, while the higher resolution outputs paints more details and focus on rendering the image.
+\end{itemize}
+%In addition, at the very beginning of the training,  generated images are usually far away from true image distribution, the discriminator can very easily judge a pair as invalid without using much pair information.
+\textcolor{red}{need more explanationn.}
+%We not only want the whole image is classified as true image by the discriminator, but also want to restrict the discriminator to classify all the local patches of high resolution output as true as well.
+Since our model outputs a pyramid of outputs with increasing image sizes. 
+We expect the low resolution output capture the global structure and color information, while the higher resolution outputs focus on rendering the image details.
 
-We don't only want the whole image is classified as true image by the discriminator, but also restrict the discriminator to classify all the local patches of high resolution output as true as well.
-To this end, we propose a hierarchical image loss, where the output of the image  discriminator is more than one scale value.
-\begin{equation}
-  d_i = D_i(X_i)
-\end{equation}
-The size of $d_i$ increases as $X_i$.
-For instance 1$\times$1 for 64$\times$64 input, 4$\times 4$ for 128$\times$128, etc.
-This type of design, gradually increase the receptive field of the discriminator.
+To force the discriminator focus on the fine-grained details, a nature way is to fix the receptive field for all the generator.
+To this end, we propose a hierarchical image loss, where the output of image  discriminator is a grid of values.
 
-This loss explicit force the discriminator to differentiate correct pair from the wrong pair.
-However, there is no explicit loss that push the discriminator to differentiate real images from the fake images.
-The way that they formulate all the task into pair based solution complicate the task of the generator.
-In this paper, we propose to directly add another loss that concentrate the image quality only beside the matching loss.
-Specifically, it can be given by:
+Denote $K_i$ as the $i-$th local image discriminators,  the output $d_i = K_i(X_i)$ has a size increasing with input $X_i$.
+For instance 1$\times$1 for 64$\times$64 input, 4$\times 4$ for 128$\times$128 and 8$\times 8$ for 256$\times$256 etc.
+In this way, even the resolutions goes higher, the receptive field keeps unchanged.
+
+Specifically, the proposed local image loss can be given by:
 \begin{equation}
@@
 \begin{split}
-\mathcal{L}_{local}(K_i)  = & \mathbb{E}_{(x, t) \sim p_{data}}[(K_i( {X_i}) - 1) ^ 2 ] -  \mathbb{E}_{t \sim p_{data}}[ (K_i( {o}_i))^2 ]  
+\mathcal{L}_{local}(K_i, X_i, o_i, t )  = & \mathbb{E}_{(x, t) \sim p_{data}}[(K_i( {X_i}) - 1) ^ 2 ] - \\
+&  \mathbb{E}_{t \sim p_{data}}[ (K_i( {o}_i))^2 ]  
 \end{split}
@@
 \begin{split}
-\mathcal{L}_{local}(G)  = & \sum_{i=1}^{s} ( \mathbb{E}_{t \sim p_{data}}[ (K_i( {o}_i) - 1) )^2 ] )
+\mathcal{L}_{local}(G, o)  = & \sum_{i=1}^{s} ( \mathbb{E}_{t \sim p_{data}}[ (K_i( {o}_i) - 1) )^2 ] )
 \end{split}
 \end{equation}
-
-\textcolor{red}{equations needs to be verified, just a rough place holder}
-
 Further more, this separation of the image loss from the matching loss open further possibilities, such as utilizing the unlabeled image to improve both the generator and discriminator.
-\textcolor{red}{maybe utilizing the imagenet for training the coco, or save as another paper.}
 
 \subsection{Total Loss}
-The total objective for both $D$ and $G$ can be given by. 
+
+Our objective for both $D$ and $G$ thus mainly compress two types of terms: \textit{matching aware pair-loss} for matching the overall image content to the text description, and \textit{local adversarial image loss} for rendering the fine-grained details.
+
+In the spirit of variational auto-encoder and the practice of \cite{han2017stackgan}, we also add the  Kullback-Leibler divergence regularization term to the $G$ loss.
+%In addition, this term might also play a role in balancing the $c_t$ and generated condition vector $c_t$ by forcing $c$ to have a similar scale to $z$.
+In the following sections, we denote $c_t$ as the variational conditional text vector.
+
 \begin{equation}
@@
 \begin{split}
-\mathcal{L}(D)  = & \sum_{i=1}^{s} ( \mathcal{L}_{pair}(D) + \alpha~\mathcal{L}_{local}(D) ) 
+\mathcal{L}_{d}(D_i, X_i, o_i,\hat{o_i}, t, \hat{t})    = &\mathcal{L}_{pair}(D_i) + \frac{\alpha}{2}~( \\
+&\mathcal{L}_{local}(K_i, o_i) + \mathcal{L}_{local}(K_i, \hat{o_i}) )
 \end{split}
 \end{equation}
-
 \begin{equation}
@@
 \begin{split}
-\mathcal{L}(G)  = & \sum_{i=1}^{s} ( \mathcal{L}_{pair}(G) + \alpha~\mathcal{L}_{local}(G) + \\
-                  & \beta~D_{KL}(\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )|| \mathcal{N}(0, \bm{I})) )  
+\mathcal{L}_{g}(G,o,\hat{o}, t)  = &  \mathcal{L}_{pair}(G) + \frac{\alpha}{2}~(\mathcal{L}_{local}(G, o) + \mathcal{L}_{local}(G, \hat{o})) + \\
+                  & \beta~D_{KL}(\mathcal{N}(\mu({t}), \Sigma({t}) )|| \mathcal{N}(0, \bm{I})) 
 \end{split}
@@
 where $\alpha$ is coefficient used to tune the weight of the local patch loss, $\beta$ is used to tune the weights of the KL-Divergence. 
-A algorithm that summarizes the training process of our model is given in Algorithm 1.
-
+We omit the additional arguments to both $\mathcal{L}_{pair}(G) $ and $\mathcal{L}_{pair}(D_i) $ for simplicity.
 %The loss function of the matching aware discriminator are summarized as:
@@
 
-\subsection{Implementation Details}
+ \begin{algorithm}
+ 	\caption{Multi scale GAN training algorithm with step size $\alpha$, number of iteration $S$, we omit the batch index and summarize the algorithm using SGD for simplicity.}
+ 	\label{CHalgorithm}
+ 	\begin{algorithmic}[1]
+ 		\For{$i \gets 1 \textrm{ to } S$ }
+ 		\For{$k \gets 1 \textrm{ to } ncritic$}
+ 		\State Sample two noise batch $z_1, z_2 \sim p(z)$.
+ 		\State Sample one matching image text pair $\{x, t\}$ and mismatched one $\{x, \hat{t}\}$.
+ 		\State Generate fake image samples for both $t$ and $\hat{t}$
  		\begin{equation}
- \label{genloss}
  		\begin{split}
- \mathcal{L}_G = & \mathbb{E}_{z\sim p_{z}, t \sim p_{data}}[-\log( D_{sent}( G(z, c_t),  \psi_t) ) ] + \\
-				  & \mathbb{E}_{z\sim p_{z}, t \sim p_{data}}[-\log( D_{img}( G(z, c_t) ) ) ] + \\
-                  & D_{KL}(\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )|| \mathcal{N}(0, \bm{I})) 		   
+	 		& {o} = G(t, z_1) \\
+	 		& {\hat{o}} = G(\hat{t}, z_2) 
  		\end{split}
  		\end{equation}
- where $c_t$ is the variational conditional vector generated from $\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )$.
-To make the network differentiable, in practice, we adopted the re-parametric trick\cite{vae}, where $c_t$ is actually computed as $\mu(\psi_t)+\Sigma(\psi_t)\odot \epsilon$, where $\epsilon\in \mathcal{R}^{T}$ is draw from a normal Gaussian distribution.
-
- \begin{algorithm}
- 	\caption{Multi scale GAN training algorithm with step size $\alpha$, number of iteration $S$, we summarize the algorithm using SGD for simplicity.\textcolor{red}{need to change to goodfellow algorithm style}}
- 	\label{CHalgorithm}
- 	\begin{algorithmic}[1]
-
- 		\For{$i \gets 1 \textrm{ to } S$ }
- 		\State $z_1, z_2 \sim \mathcal{N}(0,\bm{1})^Z$
- 		\State $\hat{x_1}, \hat{x_2} = G(z_1, \psi_t),  G(z_2, \psi_{\hat{t}})$ %\{Forward through $G$ using matching text embedding\}
- 		\State $d_r$ = $D_{pair}(x, \psi_t)$ \{(real image, matching text)\}
- 		\State $d_w$ = $D_{pair}(x, \psi_{\hat{t}})$ \{(real image, wrong text)\}
- 		\State $d_f$ = $D_{pair}(\hat{x_1}, \psi_t)$ \{(fake image, matching text)\}
- 		\State $s_r, s_1, s_2$ = $D_{img}(x), D_{img}(\hat{x_1})$, $D_{img}(\hat{x_1})$ %\{Forward through $D_{img}$ with $\hat{x_1}$\}
-
- 		\State $loss_{img}$ = $ (\log(1-s_1) + \log(1-s_2))/2 $
- 		\State $loss_{pair}$ = $ (\log(1-d_w) + \log(1-d_f))/2 $
-
- 		\State $\mathcal{L}_{D}$ = $\log(d_r) + \log(s_r) +loss_{img} + loss_{pair}$
- 		\State $\mathcal{L}_{G}$ = $\log(1-d_f) +  ( \log(1-s_1) + \log(1-s_2) )/2 $
- 		\State $\theta_G$ = $\theta_G$ - ${\delta \mathcal{L}_G } / {\delta \theta_G}$  \{Update generator\}
- 		\State $\theta_D$ = $\theta_D$ - ${\delta \mathcal{L}_D} / {\delta \theta_D}$  \{Update generator\}
+	 		\For{each discriminator $D_i$ }
+		 		\State Update $D_i$ by descending the gradient of loss \ref{equ:totalD}:
+		 		\begin{equation}
+		 		   	\theta_{D_i} = \theta_{D_i}  - \nabla_{\theta_{D_i}} \mathcal{L}_d(D_i, X_i,o_i,\hat{o_i}, t,\hat{t})
+		 		\end{equation}
+	 		\EndFor
+ 		\EndFor
+ 		\State Update the generator by descending it's stochastic gradient of loss \ref{equ:totalG}:
+ 		\begin{equation}
+ 		\theta_{G} = \theta_{G}  - \nabla_{\theta_{G}} \mathcal{L}_g(G, o, \hat{o}, t)
+ 		\end{equation}
 
@@
 
+\subsection{Implementation Details}
+A algorithm that summarizes the training process of our model is given in Algorithm 1.
+
+\begin{equation}
+\label{genloss}
+\begin{split}
+\mathcal{L}_G = & \mathbb{E}_{z\sim p_{z}, t \sim p_{data}}[-\log( D_{sent}( G(z, c_t),  \psi_t) ) ] + \\
+& \mathbb{E}_{z\sim p_{z}, t \sim p_{data}}[-\log( D_{img}( G(z, c_t) ) ) ] + \\
+& D_{KL}(\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )|| \mathcal{N}(0, \bm{I})) 		   
+\end{split}
+\end{equation}
+where $c_t$ is the variational conditional vector generated from $\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )$.
+To make the network differentiable, in practice, we adopted the re-parametric trick\cite{vae}, where $c_t$ is actually computed as $\mu(\psi_t)+\Sigma(\psi_t)\odot \epsilon$, where $\epsilon\in \mathcal{R}^{T}$ is draw from a normal Gaussian distribution.
+
 %\begin{algorithm}
@@
 %\end{algorithm}
-
-\subsection{Implementation Details}
 

### 2017-10-28 cvpr2018.tex
fix methdos

@@
 A algorithm that summarizes the training process of our model is given in Algorithm 1.
+We train and evaluate our model with a devbox machine.
+$\alpha$ is set to 0.5, $\beta$ is set to 4.
+We decrease the learning rate by half every 100 epochs for CUB and Oxford-102 datasets, and 30 for MS COCO.
+We train our model for 600 epochs for CUB and Oxford, and 120 epochs for COCO dataset.
+Adam optimizer is used for all experiments.
+The number of repeat residual blocks is set to 1 for CUB and Oxford, 2 for COCO. We use batch size 16 for all experiments.
 
-\begin{equation}
-\label{genloss}
-\begin{split}
-\mathcal{L}_G = & \mathbb{E}_{z\sim p_{z}, t \sim p_{data}}[-\log( D_{sent}( G(z, c_t),  \psi_t) ) ] + \\
-& \mathbb{E}_{z\sim p_{z}, t \sim p_{data}}[-\log( D_{img}( G(z, c_t) ) ) ] + \\
-& D_{KL}(\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )|| \mathcal{N}(0, \bm{I})) 		   
-\end{split}
-\end{equation}
-where $c_t$ is the variational conditional vector generated from $\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )$.
+%\begin{equation}
+%\label{genloss}
+%\begin{split}
+%\mathcal{L}_G = & \mathbb{E}_{z\sim p_{z}, t \sim p_{data}}[-\log( D_{sent}( G(z, c_t),  \psi_t) ) ] + \\
+%& \mathbb{E}_{z\sim p_{z}, t \sim p_{data}}[-\log( D_{img}( G(z, c_t) ) ) ] + \\
+%& D_{KL}(\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )|| \mathcal{N}(0, \bm{I})) 		   
+%\end{split}
+%\end{equation}
+%where $c_t$ is the variational conditional vector generated from $\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )$.
 To make the network differentiable, in practice, we adopted the re-parametric trick\cite{vae}, where $c_t$ is actually computed as $\mu(\psi_t)+\Sigma(\psi_t)\odot \epsilon$, where $\epsilon\in \mathcal{R}^{T}$ is draw from a normal Gaussian distribution.
@@
 %We mainly compare to the state-of-the art StackGAN \cite{han2017stackgan} for text-to-image synthesis and demonstrate substantially improvement.
-
-\textcolor{red}{Yuanpu address}
 

### 2017-10-30 cvpr2018.tex
8th

@@
 This paper presents a novel and effective approach to deal with the challenging task of generating synthetic photographic image conditioned on semantic image descriptions.
+We show a fully end-to-end trainable network that can generate up to $512^2$ resolution.
 Our method leverages the deep representations of convolutional layers and introduces hierarchical-nested adversarial training to regularize the representations to be compositional of multi-scale images.
@@
 image and text) information utilization in order to enhance multi-purpose adversary between real and fake distribution.
-To our best knowledge, our method is the first to show a fully end-to-end trainable network that can generate $256{\times}256$ images and is stackable to $512{\times}512$ resolution.
-With extensive experimental validation on three major datasets, our method significantly improves previous method and sets up a new state of the art to this field.
+With extensive experimental validation on three major datasets, our method significantly improves previous state of the arts.
 
@@
 Unfortunately, its high resolution synthesis ability is still unclear.
-At present, how to train from the low-dimensional embedding to synthesize high resolution (e.g. $256{\times}256$) and diverse images in an end-to-end manner is still an open and attractive question.
+At present, how to train from the low-dimensional embedding to synthesize high resolution (e.g. $256^2$) and diverse images in an end-to-end manner is still an open and attractive question.
 
 We outline several empirical observations for this challenges using GANs, particularly for text-to-image synthesis.
-The first comes from a fundamental difficulty of balancing the convergence between generators and discriminators.
-There are a rich number of literature tacking this issue \cite{salimans2016improved,huang2016stacked}.
-For text-to-image synthesis, how to utilize the multimodal information between images and text in discriminator is extremely important to generate effective gradients and needs careful consideration.
+The first comes from a fundamental difficulty of balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}.
+How to utilize the multimodal information between images and text in discriminator is extremely important to generate effective gradients.
 The second is that huge pixel space in high resolution images \cite{han2017stackgan}.
@@
 Moreover, keeping semantic consistency and diversity in generated images needs more specialized designs in generators to better make use of gradients from discriminators. 
-
 %The first reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. 
@@
 Keeping semantic consistency as well as diversity in generated images needs more specialized designs for discriminators to generate effective gradients, as well as generators to prevent gradient vanishing.
-
 With careful consideration of these outlined problems, in this paper, we propose a novel method that can directly generate high resolution and semantic consistent images trained in a fully end-to-end manner.
@@
 
-To tackle the problem of space leap from text and images, our method leverages the hierarchical representations of convolutional layers through a deeply-nested layer constraint, which is simply motivated by two intuitions.
-We hope feature maps in different layers are disentangled RGB image space, which can linearly represent targeting images at corresponding resolutions and maximize the implicit effectiveness of feature representations.
-We introduce accompanying hierarchically-nested adversarial objective at intermediate layers to achieve this goal.
-To better cooperate with discriminators, we present an quite intuitive network structure design to encourage more efficient and effective training.
+To tackle the problem of space leap from text and images, our method leverages the hierarchical representations of convolutional layers through a deeply-nested layer constraint, which is motivated by two insights.
+First,
 
-To tackle the instable training of GANs, 
-\textcolor{red}{we propose to enforce discriminators at different resolutions can differentiate real/fake image, correct/incorrect image-text pairs, and real/fake image pairs jointly with multiple losses.} We will show that this multi-purpose conditional strategy is mutually beneficial to encourage them only focus on respect duties.
+First, we expect feature maps at different layers are disentangled RGB image space, which can linearly represent targeting images at corresponding resolutions.
+And second, we maximize the implicit effectiveness of feature representations with additional supervision.
+We introduce ``accompanying'' hierarchically-nested adversarial objective at intermediate layers to encourage a more effective generators. 
+To better cooperate with discriminators, we present an network structure design than can uses gradient more effectively.
+
+To better use image and text information in GAN training, 
+\textcolor{red}{we enforce discriminators at different resolutions can simultaneously differentiate real and fake image-text pairs, images, and patches.}
+This multi-purpose conditional strategy is mutually beneficial to encourage them only focus on respect duties.
 It is a regularization to limit the discriminators to use unexpected information to make decision.
@@
 However, this method need multiple symmetric  bottom-up discriminators and pre-training of discriminators, and the usage for high-resolution image is unclear \cite{han2017stackgan}.
+Karras \cite{} train progressive GAN to scale up to high resolution.
 Compared with these strategies that train low- to high-resolution GANs progressively, our method has advantages of utilizing multi-level representations to encourage implicit subtask integration, which enables end-to-end high resolution image synthesis.
@@
 
+To generate $512^2$ images, we pre-train the generator to $256^2$ (and fix it for memory saving and faster convergence).
+We use $3$-repeat res-block followed by the stretching and linear compression layer.
+Since the $256^2$ image already decides the overall semantics and details, to encourage the $512^2$ maintain these information, we also use a reconstruction loss to self-regularize the generator in case the discriminator confuses the expected output.
+
 \subsection{Implementation Details}
@@
 
-\textbf{zizhao's new evaluation methods.}
+We also adopt the multi-scale structural similarity (MS-SSIM) metric \cite{improvedGAN} for further validation.
+It tests the variation of generated outputs and can find mode collapses reliably \cite{odena2016conditional}.
+Lower score indicates higher variance.
 
@@
 \end{figure}
-
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=0.4\textwidth]{figure/ms_ssmi.pdf}
+	\caption{Class-wise MS-SSMI evaluation compared to StackGAN.
+Note that lower score indicates higher inter-class invariance.
+The points below the equality line represent classes our HDGAN wins.
+} \label{fig:msssmi}
+\end{figure}
 %
@@
 					&  		&	\checkmark	&	${3.52{\pm}.04}$	\\ 
-						&  	\checkmark	&	\checkmark	&		\\
+						&  	\checkmark	&	\checkmark	&	${3.99{\pm}.04}$	\\
 				\checkmark	&  			&	\checkmark	&  ${4.14{\pm}.03}$		\\
@@
 
-BN is known to be problematic for ....
+\textbf{Advantages}
+The advantages of our hierarchical-nested adversary are clearer from different views, compared with the popular stacking GAN strategy \cite{}.
+
+First, it is memory efficient. 
+When viewing it as ensembled multi-scale GAN (Figure \ref{}), each GAN fully uses the parameters of its lower resolution GAN.
+Usually, a deeper generator is necessary to compact a discriminator.
+Since the depth of discriminator increases as image resolution increases, if stacking separate GANs based on low resolution GAN outputs, much more layers are needed in generators as wells.
+While in our method, for instance, from a $64^2$ GAN to a $128^2$ GAN, only a minimum two conv layers ($1$-repeat res-blocks) are needed.
+
+Second, it fully enjoys top-down knowledge. 
+The low resolution can not use high resolution information in the stacking GAN strategy.
+While in our method, it is easy to see the low resolution GAN enjoys knowledge from higher resolution.
+As an evidence, our $64^2$ synthetic images have higher inception score than $64^2$ and even $128^2$ images of StackGAN (see Section 5).
 

### 2017-10-31 cvpr2018.tex
10th

@@
 \begin{abstract}
-This paper presents a novel and effective approach to deal with the challenging task of generating synthetic photographic image conditioned on semantic image descriptions.
-We show a fully end-to-end trainable network that can generate up to $512^2$ resolution.
-Our method leverages the deep representations of convolutional layers and introduces hierarchical-nested adversarial training to regularize the representations to be compositional of multi-scale images.
-We present a new network architecture, which is intuitive as well as extensile, to push generated images to high resolutions with symmetric convolutional blocks.
-We present a functional generative adversarial networks (GANs) training strategy to encourage more effective multimodal (i.e.
+This paper presents a novel and effective method to deal with the challenging task of generating synthetic photographic image conditioned on semantic image descriptions.
+We show a fully end-to-end trainable network that can generate high resolution images (e.g.
+$512^2$).
+Our method leverages the deep representations of convolutional layers and introduces hierarchical-nested adversarial training to regularize the representations and capture the complex image statistics.
+We present a new network architecture, which is intuitive as well as extensile, to push generated images to high resolutions.
+\textcolor{red}{We present a functional generative adversarial networks (GANs) training strategy} to encourage more effective multimodal (i.e.
 image and text) information utilization in order to enhance multi-purpose adversary between real and fake distribution.
@@
 \section{Introduction}
-Generating photographic high-resolution image conditional on arbitrary semantic description is an important problem in generative model research \cite{reed2016generative}.
+Generating photographic image conditional on arbitrary semantic description is an important problem in generative model research \cite{reed2016generative}.
 However, insufficient methods have been successfully developed to address this task due to its particular challenges.
@@
 Differently, the embedding space of the former is induced by semantic descriptions.
-Therefore, this task requires the generated images to be \textit{semantically consistent}, i.e., the generated images not only preserve the principal concept of descriptions generally but also preserve the fine-grained descriptive details in image pixels.
+Therefore, this task requires the generated images to be \textit{semantically consistent}, i.e., the generated images not only preserve sketch concepts of descriptions generally but also preserve fine-grained descriptive details in image pixels.
 
 Generative adversarial networks (GANs) have become the main solution to this task. 
-Reed \etal \cite{reed2016generative} address this task through a GAN based framework.
+Reed \etal \cite{reed2016generative} is th first to address this task through a GAN based framework.
 But this method only handles image up to $64{\times}64$ resolution and usually can barely generate vivid object details.
-Based on \cite{reed2016generative}, Zhang \etal \cite{han2017stackgan} present a successful approach (StackGAN) by stacking another GAN to generate high-quality $256{\times}256$ images given low resolution $64{\times}64$ synthetic images.
+Based on this method, Zhang \etal \cite{han2017stackgan} present a successful approach (StackGAN) by stacking another GAN to generate high-quality $256{\times}256$ images given low resolution $64{\times}64$ synthetic images.
 This method needs two-stage training to achieve the goal.
@@
 Unfortunately, its high resolution synthesis ability is still unclear.
-At present, how to train from the low-dimensional embedding to synthesize high resolution (e.g. $256^2$) and diverse images in an end-to-end manner is still an open and attractive question.
+At present, how to train from the low-dimensional text space to synthesize high resolution and diverse images in an end-to-end manner is still an open and attractive question.
 
-We outline several empirical observations for this challenges using GANs, particularly for text-to-image synthesis.
+We outline several empirical reasons for this challenges using GANs to deal with text-to-image synthesis.
 The first comes from a fundamental difficulty of balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}.
@@
 The second is that huge pixel space in high resolution images \cite{han2017stackgan}.
-An effective regularization to reduce the variances in generators is critical \cite{huang2016stacked}. 
-Moreover, keeping semantic consistency and diversity in generated images needs more specialized designs in generators to better make use of gradients from discriminators. 
+An effective regularization to regularize generators is critical to help capture the complex image statistics \cite{huang2016stacked} as well as preserve semantic consistency. 
 %The first reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. 
@@
 Keeping semantic consistency as well as diversity in generated images needs more specialized designs for discriminators to generate effective gradients, as well as generators to prevent gradient vanishing.
-With careful consideration of these outlined problems, in this paper, we propose a novel method that can directly generate high resolution and semantic consistent images trained in a fully end-to-end manner.
+With careful consideration of these outlined problems, in this paper, we propose a novel fully end-to-end method that can directly model high resolution image statistics and generate semantic consistent and photographic image up to $512^2$ resolution.
 The contributions are described follows.
 
-To tackle the problem of space leap from text and images, our method leverages the hierarchical representations of convolutional layers through a deeply-nested layer constraint, which is motivated by two insights.
-First,
+Our generator is a simple Vanilla GAN, without needing any inside text conditioning \cite{han2017stackgan} or image label supervision \cite{dash2017tac}.
+To tackle the problem of the big leap from the text space to the high resolution image space, our insight is to leverage hierarchical representations with additional implicit constraints to reduce training instability.
+We introduce ``accompanying'' hierarchically-nested adversarial objective at intermediate layers to generate multi-scale images.  
+And we present an generator network structure design than can uses gradients from multi-scale nested discriminators more effectively.
 
-First, we expect feature maps at different layers are disentangled RGB image space, which can linearly represent targeting images at corresponding resolutions.
-And second, we maximize the implicit effectiveness of feature representations with additional supervision.
-We introduce ``accompanying'' hierarchically-nested adversarial objective at intermediate layers to encourage a more effective generators. 
-To better cooperate with discriminators, we present an network structure design than can uses gradient more effectively.
-
-To better use image and text information in GAN training, 
+To better make use of image and text information in GAN training, 
 \textcolor{red}{we enforce discriminators at different resolutions can simultaneously differentiate real and fake image-text pairs, images, and patches.}
-This multi-purpose conditional strategy is mutually beneficial to encourage them only focus on respect duties.
-It is a regularization to limit the discriminators to use unexpected information to make decision.
-
-We have validated our proposed method on three datasets, i.e.
-CUB birds \cite{}, Oxford-102 flowers \cite{}, and large-scale COCO datasets \cite{}.
+This multi-purpose conditional adversary is mutually beneficial to encourage each only focuses on respect duties. 
+%It is a regularization to limit the discriminators to use unexpected information to make decision. 
+We validate our proposed method on three datasets, i.e.
+CUB birds \cite{welinder2010caltech}, Oxford-102 flowers \cite{Nilsback08}, and large-scale COCO datasets \cite{lin2014microsoft}.
 Extensive experimental results and analysis demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts.
@@
 \section{Related Work}
+We discussed related methods as well as clarify the novelty of our method.
+
 Deep generative models grows wide interests recently, including GANs \cite{goodfellow2014generative}, Variational Auto-encoders (VAE) \cite{kingma2013auto}, etc \cite{oord2016pixel}. 
@@
 Text-to-image synthesis not only requires diverse and high-quality generation but also requires precise semantically consistent mapping in the image space.
-Reed \etal \cite{reed2016generative} introduce the first method that can generate $64{\times}64$ resolution images, which is similar with DCGAN \cite{radford2015unsupervised}.
+Reed \etal \cite{reed2016generative} introduce a method that can generate $64{\times}64$ resolution images, which is similar with DCGAN \cite{radford2015unsupervised}.
 This method presents a new strategy to image-text matching aware adversarial training.
@@
 
-To synthesize high resolution image, cascade networks play an important role to decompose original difficult tasks to multiple subtasks.
+To synthesize high resolution images, cascade networks play an important role to decompose original difficult tasks to multiple subtasks.
 Denton \etal \cite{denton2015deep} trains a cascade of GANs within a Laplacian pyramid framework (LAPGAN) and use each to generate difference images, conditioned on random noises and output from last level of the pyramid, to push up output resolution through by-stage refinement.
@@
 However, this method need multiple symmetric  bottom-up discriminators and pre-training of discriminators, and the usage for high-resolution image is unclear \cite{han2017stackgan}.
-Karras \cite{} train progressive GAN to scale up to high resolution.
+Recently, Karras \cite{} show a progressive training of GANs to enable high resolution image generation.
 Compared with these strategies that train low- to high-resolution GANs progressively, our method has advantages of utilizing multi-level representations to encourage implicit subtask integration, which enables end-to-end high resolution image synthesis.
@@
 
-\textbf{Discriminator} The discriminator simply contains consecutive stride-2 conv layers with BN and LeakyReLU \cite{} (the depth changes according to the input size) until the feature map has $512{\times}4{\times}4$ dimension.
+\textbf{Discriminator} The discriminator simply contains consecutive stride-2 conv layers with BN and LeakyReLU (the depth changes according to the input size) until the feature map has $512{\times}4{\times}4$ dimension.
 There two branches are added on top of it for multi-purpose discriminator design (see next section) .
@@
 
-We also adopt the multi-scale structural similarity (MS-SSIM) metric \cite{improvedGAN} for further validation.
+We also adopt the multi-scale structural similarity (MS-SSIM) metric \cite{improvedGAN} for further image quality validation.
 It tests the variation of generated outputs and can find mode collapses reliably \cite{odena2016conditional}.
@@
 		%	StackGAN$^\star$     &		$3.89{\pm}.05$	&	 $3.16{\pm}.01$			&  $8.45{\pm}.03$		\\ \hline
-			TAC-GAN	 &	-		&		$\bm{3.45{\pm}.05}$		& -	\\	
-			StackGAN++     &		$3.84{\pm}.06$	&	 -			&  -	\\  \hline
+			StackGAN++     &		$3.84{\pm}.06$	&	 -			&  -	\\  
+			TAC-GAN	 &	-		&		$3.45{\pm}.05$		& -	\\	\hline
+
 			HDGAN 		&	$\bm{4.01{\pm}.06}$	&	$ \bm{3.45{\pm}.07}$			&  -  \\ \hline
@@
 
+%\begin{table}[t] % retrieval
+%	\begin{center}
+%		\begin{tabularx}{.42\textwidth}{c|ccc}
+%			\specialrule{1.5pt}{0pt}{0pt}  
+%			Scale 						& StackGAN & HDGAN & HR Test					\\ 				\hline
+%            $64{\times}64$              &   ${2.95{\pm}.02}$       &  	$\bm{3.46{\pm}.04}$ &  ${3.46{\pm}.04}$	\\
+%           $128{\times}128$             &   ${3.35{\pm}.02}$      &  $\bm{3.85{\pm}.04}$	& ${3.45{\pm}.04}$	\\
+%           $256{\times}256$             &   $3.70{\pm}.04$     &	$\bm{4.01{\pm}.06}$ & ${3.46{\pm}.04}$ \\ \hline
+%		\end{tabularx}
+%	\end{center} \vspace{-.4cm}
+%	\caption{Scale accuracy \textcolor{red}{changing to figure is better}.} \label{table:multiscales}
+%\end{table}
 \begin{table}[t] % retrieval
 	\begin{center}
-		\begin{tabularx}{.42\textwidth}{c|ccc}
+		\begin{tabularx}{.32\textwidth}{c|cc}
 			\specialrule{1.5pt}{0pt}{0pt}  
-			Scale 						& StackGAN & HDGAN & HR Test					\\ 				\hline
-            $64{\times}64$              &   ${2.95{\pm}.02}$       &  	$\bm{3.46{\pm}.04}$ &  ${3.46{\pm}.04}$	\\
-           $128{\times}128$             &   ${3.35{\pm}.02}$      &  $\bm{3.85{\pm}.04}$	& ${3.45{\pm}.04}$	\\
-           $256{\times}256$             &   $3.70{\pm}.04$     &	$\bm{4.01{\pm}.06}$ & ${3.46{\pm}.04}$ \\ \hline
+			Scale 						& StackGAN & HDGAN 					\\ 				\hline
+			$64{\times}64$              &   ${2.95{\pm}.02}$       &  	$\bm{3.46{\pm}.04}$ \\
+			$128{\times}128$             &   ${3.35{\pm}.02}$      &  $\bm{3.85{\pm}.04}$		\\
+			$256{\times}256$             &   $3.70{\pm}.04$     &	$\bm{4.01{\pm}.06}$ \\ \hline
 		\end{tabularx}
 	\end{center} \vspace{-.4cm}
-	\caption{Scale accuracy \textcolor{red}{changing to figure is better}.} \label{table:deep-nest}
+	\caption{Multi-scale inception score comparison. See text for explanation.} \label{table:multiscales}
 \end{table}
-
 \begin{figure}[t]
@@
 \end{figure}
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.4\textwidth]{figure/ms_ssmi.pdf}
-	\caption{Class-wise MS-SSMI evaluation compared to StackGAN.
-Note that lower score indicates higher inter-class invariance.
+
+\begin{table}[t] % retrieval
+	\begin{minipage}[b]{0.50\linewidth}
+		%\centering
+		\includegraphics[width=0.99\textwidth,height=0.7\textwidth]{figure/ms_ssmi.pdf}
+		\vspace{-1.8cm}
+	\end{minipage} %\hfill
+	\begin{minipage}[b]{0.49\linewidth}
+		\begin{tabularx}{.9\textwidth}{c|c}
+			\specialrule{1.5pt}{0pt}{0pt}  
+			Method   &  MS-SSMI \\ \hline
+			StackGAN &   0.234   \\ 
+			Prog.GAN &   0.225    \\ \hline
+			HDGAN    &   \textbf{0.215}    \\
+		\end{tabularx}
+	\end{minipage}
+	\vspace{0.2cm}
+	\caption{Left: Class-wise MS-SSMI evaluation.
+Lower score indicates higher intraclass invariance.
 The points below the equality line represent classes our HDGAN wins.
-} \label{fig:msssmi}
-\end{figure}
-%
+Right: Overall (no class-wise) score evaluation.} \label{fig:msssmi}
+\end{table}
+
 \subsection{Comparative Results}
-We compare our results with GAN-INT-CLS \cite{reed2016generative}, GAWWN \cite{reed2016learning}, TAC-GAN \cite{dash2017tac}, and StackGAN \cite{han2017stackgan} and also its improved version StackGAN++\footnote{This comes from a recently released pre-print from the author of StackGAN we just noticed, which outperforms StackGAN.
-Similarly with our HDGAN, it now can train $64{-}256$ directly.
+To validate our method, we compare our results with GAN-INT-CLS \cite{reed2016generative}, GAWWN \cite{reed2016learning}, TAC-GAN \cite{dash2017tac}, StackGAN \cite{han2017stackgan} and also its improved version StackGAN++ \cite{}, and Progressive GAN \cite{} \footnote{Note that StackGAN++ and Prog.GAN are two very recent released pre-prints we noticed before submission.
+We acknowledge them as they also target at generating high resolution images, in spite of their differences in motivations and network and training designs from ours.
+}
+
+% Similarly with our HDGAN, it now can train $64{-}256$ directly.
 Each generator still take images from the bottom generator and supervised by a discriminator.
@@
 
-StackGAN \cite{han2017stackgan} generates synthetic images up to $256{\times}256$ resolution. We show that our method can generates images up to $512{\times}512$.
+%StackGAN \cite{han2017stackgan} generates synthetic images up to $256{\times}256$ resolution. We show that our method can generates images up to $512{\times}512$.
 
@@
 For example, HDGAN improves GAN-INT-CLS by ${\sim}30.1\%$  and ${\sim}8.4\%$ on CUB.
+
+Table \ref{table:multiscales} quantitatively compares the the multi-resolution inception score.
+Our results are from the side outputs of a single model.
+Usually higher resolution images gives rise to better inception score since they contain details.
+As can be observed, our $64^2$ images outperforms $128^2$ images of StackGAN and our $128^2$ images outperforms $256^2$ images of StackGAN substantially.
+
+Table \ref{fig:msssmi} shows the MS-SSMI image quality evaluation score compared with StackGAN and ProgressiveGAN.
+StackGAN and our HDGAN use the semantic text as input so the generated images retain class information.
+We compare the score with StackGAN using the provided pretrained model).
+We randomly sample ${~}20,000$ image pairs (400 per class) and show the class-wise score in the left figure.
+HDGAN shows better performance in majority of classes and also has lower inter-class standard divition (0.023 vs.
+0.032).
+Prog.GAN takes noises rather than text.
+Since MS-SSMI evaluates the image quality without text or class involvement, we can compare with it.
+Following the procedure of Prog.GAN, we randomly sample ${~}10,000$ image pairs for each comparing method (For Prog.GAN, we use generated $256^2$ images provided by the author) and show the results in the right table.
+Our method outperforms both StackGAN and Prog.GAN.
 
@@
 We test this extreme case using our method by removing all nested supervisions (the first row of Table \ref{table:deep-nest}).
-Our method actually can still generate fairly good.
+Our method still generates fairly good results.
 Figure \ref{fig:vallina-res} shows the qualitatively results.

### 2017-11-01 cvpr2018.tex
backup

--- 2017-10-28 cvpr2018.tex
@@
  		\State Sample two noise batch $z_1, z_2 \sim p(z)$.
- 		\State Sample one matching image text pair $\{x, t\}$ and mismatched one $\{x, \hat{t}\}$.
+ 		\State Sample one batch of matching and mismatching image text pair $\{X, t\}$,  $\{X, \hat{t}\}$.
  		\State Generate fake image samples for both $t$ and $\hat{t}$
@@
 $\alpha$ is set to 0.5, $\beta$ is set to 4.
-We decrease the learning rate by half every 100 epochs for CUB and Oxford-102 datasets, and 30 for MS COCO.
 We train our model for 600 epochs for CUB and Oxford, and 120 epochs for COCO dataset.
-Adam optimizer is used for all experiments.
+Adam optimizer with momentum 0.5 is used for all experiments.
+The initial learning rate is set as 0.0002 and we decrease the learning rate by half every 100 epochs for CUB and Oxford-102 datasets, and 30 for MS COCO.
 The number of repeat residual blocks is set to 1 for CUB and Oxford, 2 for COCO. We use batch size 16 for all experiments.
@@
 
+\begin{table}[t] % retrieval
+	\begin{center}
+		\begin{tabularx}{.268\textwidth}{ccc|c}
+			\specialrule{1.5pt}{0pt}{0pt}  
+			\multicolumn{3}{c|}{Components}	&  \multirow{2}{*}{Score}	\\ \cline{1-3}
+			64	& 128	& 256 			& 		\\ \hline
+			&  		&	\checkmark	&	${3.52{\pm}.04}$	\\ 
+			&  	\checkmark	&	\checkmark	&		\\
+			\checkmark	&  			&	\checkmark	&  ${4.14{\pm}.03}$		\\
+			\checkmark	&  \checkmark		&	\checkmark	&	${4.01{\pm}.04}$ \\
+
+		\end{tabularx}
+	\end{center} \vspace{-.4cm}
+	\caption{Ablation study for hierarchically-nested adversarial supervision.} \label{table:deep-nest}
+\end{table}
+
 \subsection{Design principles}

### 2017-11-02 cvpr2018.tex
text ready

@@
 The discriminator $D$ is optimized to distinguish the synthesized images from the real images, meanwhile, the generator $G$ is trained to fool the discriminator by trying to convert an input distribution $p_z$ to the true data distribution $p_{data}$.
-Concretely, the overall training procedure can be analogous to the following two-player min-max game $V(D, G)$,
+Concretely, the overall training procedure can be analogous to the following two-player min-max game $V(D, G)$, where the optimal $G$ and $D$ can be obtained by
 \begin{equation}
-\label{game}
+\label{equ:GAN}
 \begin{split}
-\underset{G}{\min}\ \underset{D}{\max}\ V(D, G) =  &\mathbb{E}_{x\sim p_{data}}[\log D(x)] +  \\
-&\mathbb{E}_{z\sim p_{z}}[\log (1-D(G(z)))]		   
+G^*, {D}^* = \arg~\underset{G}{\min}\ \underset{\mathcal{D}}{\max}~ V(D, G)
 \end{split}
 \end{equation}
-where $x$ is a real image sampled from the true data distribution $p_{data}$, $z$ is a noise vector usually sampled from some predefined distribution $p_{z}$ (e.g., Gaussian distribution).
-In practice, It's been shown to work better for the generator $G$ to minimizing $-\log(D(G(z)))$ rather than $\log(1-D(G(z)))$, namely, the $\log(D)$ trick.
-In this paper, we replace the negative log likelihood loss with a least square objective\cite{lsgan}.
+
+%\begin{equation}
+%\label{game}
+%\begin{split}
+%\underset{G}{\min}\ \underset{D}{\max}\ V(D, G) =  &\mathbb{E}_{x\sim p_{data}}[\log D(x)] +  \\
+%&\mathbb{E}_{z\sim p_{z}}[\log (1-D(G(z)))]		   
+%\end{split}
+%\end{equation}
+%where $x$ is a real image sampled from the true data distribution $p_{data}$, $z$ is a noise vector usually sampled from some predefined distribution $p_{z}$ (e.g., Gaussian distribution).
+%In practice, It's been shown to work better for the generator $G$ to minimizing $-\log(D(G(z)))$ rather than $\log(1-D(G(z)))$, namely, the $\log(D)$ trick.
+%In this paper, we replace the negative log likelihood loss with a least square objective\cite{lsgan}.
 
@@
 \textbf{Notation } 
-We denote the training data set by $S=\{(\bm{X}^n, \bm{T}^n),n=1,...,N\}$, where $X^n$ is the $n-$th training image, and $T^n={t^1,...,t^m}$ as $m$ text descriptions corresponds to $X^n$.
+We denote the training data set by $S=\{({X}^n, {T}^n),n=1,...,N\}$, where $X^n$ is the $n-$th training image, and $T^n={t^1,...,t^m}$ as $m$ text descriptions corresponds to $X^n$.
 
 Since we obtain the text embedding vector  using the per-trained char-rnn text encoder provided in \cite{reed2016generative}.
-For simplicity, we don not differentiate text description and the corresponding embedding vector in this paper.
-Our goal is to learn the generator $G$ that is capable of producing high resolution images of high visual quality as well as variability giving an input text description $t$.
+For simplicity, we do not differentiate text description and it's corresponding text embedding vector in this paper.
+Our goal is to learn a generator $G$ that could produce high resolution images of high visual quality as well as variability giving an input text description $t$.
 
+The input to $G$ compress input sentence embedding, and one noise input.
 Denote the image dimension, text embedding dimension and the dimension of the noise input as $I$, $T$ and $Z$, respectively.
-Please note that, $G$ has multiple branches and generates multiple images of different sizes and for each image size, we have a distinct $D$.
-For simplicity, we only describe one image size.
+Please note that, $G$ has multiple branches and generates multiple images of different sizes.
+For each image size, we have a distinct discriminator $D$ associated with it.
+%For simplicity, we only describe one image size.
 
@@
 \textbf{Variational text embedding } Following the practice of \cite{han2017stackgan}, instead of using the plan deterministic non-linear transformation of the original $t$, we obtain the conditional vector $c$ by sampling from a Gaussian distribution $\mathcal{N}(\mu(t), \Sigma(t) )$, in which the mean $\mu(t)$ and the diagonal covariance matrix $\Sigma(t)$ are non-linear transformation of the original text embedding $t$.
-This type of conditional augmentation technique can be used to inject randomness to the text embedding vector $t$ to mitigate the common problem that conventional conditional GAN training paradigm usually learns to totally ignore the randomness, resulting to collapsing results lacking diversity \cite{reed2016generative}.
+This type of conditional augmentation technique can be used to inject randomness into the text embedding vector $t$ to mitigate the common problem that conventional conditional GAN training paradigm usually learns to totally ignore the randomness, resulting to collapsing results lacking diversity \cite{reed2016generative}.
 In addition, using this kind of text embedding makes the input pure stochastic, making it more difficult for the generator to over fit the training data.
@@
 \subsection{Hierarchical Deep Supervision}
-Directly predicting high resolution synthesized images are difficult, not only because of the difficulties in training but also due to the large variation and instability in the hidden layers.
+Directly predicting high resolution synthesized images are challenging, not only because of the difficulties in training but also due to the large variation and instability in the hidden layers.
 
 Our architecture of $G$ consists of a single stream network with additional multiple side outputs.
-This architecture resemble the previous proposed method in edge detection\cite{xie2015holistically} and classification\cite{lee2015deeply}, which demonstrate that additional supervision to the hidden layer can improve both generalization and optimization.
-We hypothesis that adding hidden layer supervision using side outputs can act as a regularizer to the hidden space of $G$, which reduces the over-fitting issue and provide a short path for the error signal.
+This architecture resemble the previous proposed method in edge detection\cite{xie2015holistically} and classification\cite{lee2015deeply}, which demonstrate that additional supervision to  hidden layers can improve model generalization and boost optimization.
+We conjecture that adding hidden layer supervision using side outputs can act as a regularizer to the hidden space of $G$, which reduces the over-fitting issue and provide a short path for the error signal.
 
@@
 where $s$ is the total number of side outputs, please note that the dimension of $o_1,..,o_s$ increase gradually (e.g., 64$\times$64, 128$\times$128, and 256$\times$256).
+For simplicity, we denote $o=\{o_1,...,o_s\}$.
 Denote $\mathcal{X}^i = \{X^i_1, ..
 X^i_s\}$ as the pyramid of  resized images constructed from original image $X^i$.
-For simplicity, we represent $o=\{o_1,...,o_s\}$.
 
@@
 \subsection{Matching Aware Pair-Loss}
-During the setting of conditional generative adversarial learning, simply generating images of high visual quality is not enough, most importantly, we want the generated images well aligned with the conditioning information (text description in our model).
-
+During the setting of conditional generative adversarial learning, simply generating images of high visual quality is not enough, most importantly, we want the generated images well aligned with the conditioning information (ie, text description in our model).
 %Given a pair of image and text embedding $(x, \psi{t})$ as input, in the discriminator $D_i$, we first transfer $x$  to an image code $Code_x$.
@@
 %The generator $G$ and discriminator $D$ are optimized alternatively using their corresponding loss function. 
-
-Therefore, the discriminator should be optimized to differentiate two errors: real image with mismatch conditional text information, fake image with real text.
-In order to achieve this, the previously proposed matching aware discriminator is explicitly trained with three pair configurations, namely: real image with right text as positive training sample, and the aforementioned two sources of error pairs as negative training samples.
+Therefore, the discriminator are designed to take image and sentence pair as input and should be able to identify two types of errors: real image with mismatch conditional text information and fake image with real text.
+In our case, the discriminator is explicitly trained with three pair configurations, namely: real image with right text as positive training sample, and the aforementioned two sources of error pairs as negative training samples.
 
 Given a mini-batch of training data consists of images $X$ and the corresponding text $t$, mismatching text $\hat{t}$.
-For simplicity, we omit the instance index.
+For simplicity, we omit the batch index.
 To train the discriminator,  we also need to sample fakes images $o_i$ using $G$.
@@
 \begin{split}
-\mathcal{L}_{pair}(D_i)  = & \mathbb{E}_{(x, t) \sim p_{data}}[(D_i( {X_i},  {t}) - 1) ^ 2 ] - \frac{1}{2}*\\ 
+\mathcal{L}_{pair}(D_i)  = & \mathbb{E}_{(X_i, \hat{t}) \sim p_{data}}[(D_i( {X_i},  {t}) - 1) ^ 2 ] - \frac{1}{2}*\\ 
 &   \mathbb{E}_{(X_i, \hat{t}) \sim p_{data}}[(D_i({X_i}, \hat{{t}}) - 1)^2  ] - \frac{1}{2} *\\
@@
 
-This type of loss is used to push the valid image-text pair away from the invalid pairs.
+where $o_i$ is the $i-$th output of the $G$,  this type of loss is used to push the valid image-text pair away from the invalid pairs.
 
@@
 The pair-loss is designed to differentiate invalid pairs from valid ones.
-It works by first translating the image to a compact size code, then the combination of the image code and the sentence vector is concatenated and fed to successive layers of non-linear transformation  to predict the validity of the image sentence pair.
+It works by first translating the image to a compact size code, then the image code and the sentence vector is concatenated and fed to successive layers to predict the validity of the input image-sentence pair.
 
@@
 However, this loss has two problems, firstly,  there is no explicit loss that push the discriminator to differentiate real images from the fake images.
-Combining both tasks (generating realistic images and matching image with text) into one outputs complicates the learning tasks.
-Second,  as the image resolution goes higher, it might be challenging for the global pair wise discriminator to capture the local fine-grained details.
-In addition, as is pointed in \cite{shrivastava2016learning}, a single global strong discriminator tend to over-emphasize certain image feature and may lead to artifacts.
+Combining both tasks (generating realistic images and matching image with text) into one output further complicates the learning tasks, which is already challenging.
+Second,  as the image resolution goes higher, it might be challenging for the global pair wise discriminator to capture local fine-grained details.
+In addition, as is also pointed in \cite{shrivastava2016learning}, a single global strong discriminator tend to over-emphasize certain image feature and may lead to artifacts.
 
@@
 \begin{itemize}
-	\item 1. Forcing the local patch of generated samples to have similar statistics to real image patch can be beneficial to rendering details. %
+	\item 1. Forcing the local patch of generated samples to have similar statistics to real image patch can be beneficial to rendering fine-grained details. %
 
@@
 %We not only want the whole image is classified as true image by the discriminator, but also want to restrict the discriminator to classify all the local patches of high resolution output as true as well.
-Since our model outputs a pyramid of outputs with increasing image sizes. 
-We expect the low resolution output capture the global structure and color information, while the higher resolution outputs focus on rendering the image details.
+Since our model generates a pyramid of outputs with increasing image sizes. 
+We expect the low resolution output capture the global structure and color information, while the higher resolution outputs focus on local image details.
 
@@
 In this way, even the resolutions goes higher, the receptive field keeps unchanged.
-
 Specifically, the proposed local image loss can be given by:
@@
 \begin{split}
-\mathcal{L}_{local}(K_i, X_i, o_i, t )  = & \mathbb{E}_{(x, t) \sim p_{data}}[(K_i( {X_i}) - 1) ^ 2 ] - \\
-&  \mathbb{E}_{t \sim p_{data}}[ (K_i( {o}_i))^2 ]  
+\mathcal{L}_{local}(K_i, X_i, o_i, t )  = & \mathbb{E}_{(x, t) \sim p_{data}}[ \mathbb{E}(K_i( {X_i}) - 1) ^ 2 ] - \\
+&  \mathbb{E}_{t \sim p_{data}}[  \mathbb{E}(K_i( {o}_i))^2 ]  
 \end{split}
@@
 \begin{split}
-\mathcal{L}_{local}(G, o)  = & \sum_{i=1}^{s} ( \mathbb{E}_{t \sim p_{data}}[ (K_i( {o}_i) - 1) )^2 ] )
+\mathcal{L}_{local}(G, o)  = & \sum_{i=1}^{s} ( \mathbb{E}_{t \sim p_{data}}[ \mathbb{E} (K_i( {o}_i) - 1) )^2 ] )
 \end{split}
@@
 Our objective for both $D$ and $G$ thus mainly compress two types of terms: \textit{matching aware pair-loss} for matching the overall image content to the text description, and \textit{local adversarial image loss} for rendering the fine-grained details.
-
 In the spirit of variational auto-encoder and the practice of \cite{han2017stackgan}, we also add the  Kullback-Leibler divergence regularization term to the $G$ loss.
@@
 \subsection{Implementation Details}
-A algorithm that summarizes the training process of our model is given in Algorithm 1.
-We train and evaluate our model with a devbox machine.
-$\alpha$ is set to 0.5, $\beta$ is set to 4.
+The algorithm that summarizes the training process of our model is given in Algorithm 1. We train and evaluate our model with a devbox machine. $\alpha$ is set to 0.5, $\beta$ is set to 4.
  We train our model for 600 epochs for CUB and Oxford, and 120 epochs for COCO dataset.
@@
 \textbf{Dataset} 
-We evaluate our method extensively using three widely used datasets.
-CUB dataset contains 11,788 bird images belonging to one of the 200 different classes.
-Each image in this dataset is associated with 10 text descriptions.
+We evaluate our method extensively using three widely used datasets.  CUB dataset contains 11,788 bird images belonging to one of the 200 different classes. 
+%Each image in this dataset is associated with 10 text descriptions. 
 We pre-process the image using the same pipeline proposed in \cite{han2017stackgan}, which crops the birds foreground out to  ensure a object-background ratio greater than 0.75.
@@
 \subsection{Evaluation metric}
-\textbf{Inception score. }  To evaluate the quality of generated images, we resort to the recently proposed qualitative evaluation measurement "inception score"\cite{improvedGAN},
+\textbf{Inception score.}  To evaluate the quality of generated images, we resort to the recently proposed qualitative evaluation measurement "inception score"\cite{improvedGAN},
  \begin{equation}
@@
 
-\textbf{Image-sentence distance.
-} Since inception score can not measure alignment between the generated images and the text description, here, we conduct a new qualitative measurement, which calculated the cosine distance between image code and the sentence vector.
+\textbf{Neural image-sentence distance.} Since inception score can not measure alignment between the generated images and the text description, here, we conduct a new qualitative measurement, which calculated the cosine distance between image code and the sentence vector.
 We train the model on each dataset.
 
+\textbf{MS-SSIM.}
 We also adopt the multi-scale structural similarity (MS-SSIM) metric \cite{improvedGAN} for further image quality validation.
@@
 
-\textbf{Image retrieval. } We also conduct image retrieval evaluation on the dataset. The results is shown in Fig1.
+%\textbf{Image retrieval. } We also conduct image retrieval evaluation on the dataset. The results is shown in Fig1.
 
-We only conduct qualitative experiment on
+%We only conduct qualitative experiment on
 
@@
 		%\centering
-		\includegraphics[width=0.99\textwidth,height=0.7\textwidth]{figure/ms_ssmi.pdf}
+		%\includegraphics[width=0.99\textwidth,height=0.7\textwidth]{figure/ms_ssmi.pdf}
 		\vspace{-1.8cm}
@@
 
-\subsection{Case study}
-\textbf{Generalization to real user test}
-We test the generalization of our method by asking a user to write a sentence, and the generated results are shown in .
+\subsubsection{Style Transfer Using Sentence Interpolation}
 
-\subsubsection{Style transfer}
-\textcolor{red}{Yuanpu address}
+Ideally, a trained model should learn a smooth linear latent manifold of the images.
+To demonstrate our model's generalization capability, we generate images using the linearly interpolated  embedding using two source sentences.
+During this experiment, we fix the all the random noises to make the object and background consistent.
+As is shown in Figure~\ref{}, the generated images show gradual and smooth changes reflecting the semantic changing in sentences, while still maintaining plausible object pose and shape.
+In the first row, the generated birds gradually turn the color from red to yellow, in the second row, more complicated sentences containing more detailed appearance information (e.g., blue peaks, and yellow wing) are used, we can see that our model is still be able to successfully capture these subtle information and tune the bird appearance gradually.
+
+We also evaluate some sentences that generated by ourself, the resulting images are shown in Figure~\ref{}, as we can see, our model are robust and generalize well to human descriptions that never seen before.
 
 \subsubsection{What role does noise play}
-
-\begin{table}[t] % retrieval
-	\begin{center}
-		\begin{tabularx}{.268\textwidth}{ccc|c}
-			\specialrule{1.5pt}{0pt}{0pt}  
-			\multicolumn{3}{c|}{Components}	&  \multirow{2}{*}{Score}	\\ \cline{1-3}
-				 64	& 128	& 256 			& 		\\ \hline
-					&  		&	\checkmark	&	${3.52{\pm}.04}$	\\ 
-						&  	\checkmark	&	\checkmark	&	${3.99{\pm}.04}$	\\
-				\checkmark	&  			&	\checkmark	&  ${4.14{\pm}.03}$		\\
-				\checkmark	&  \checkmark		&	\checkmark	&	${4.01{\pm}.04}$ \\
-
-		\end{tabularx}
-	\end{center} \vspace{-.4cm}
-	\caption{Ablation study for hierarchically-nested adversarial supervision.} \label{table:deep-nest}
-\end{table}
+In our model, there are two kinds of randomness injected to the input of the Generator, ie, epsilon $\epsilon$ and Gaussian noise vector $z$.
+In this experiment, we fix the sentence embedding and one noise, and change the other random variable.
+For each random noise, we generate 4 different values.
+So In total 16 images are generated using all noise combinations, the resulting images are shown in Figure~\ref{}, $\epsilon$ and $z$ corresponds to row and column dimension, respectively.
+As is shown in the image, we can see that, $\epsilon$ can change the pose of the image, while $z$ is mainly responsible for the background variations.
+This clearly demonstrate that, our model learns to disentangle the semantic information from the pose and background information.
 
@@
 
-\subsection{Multi-purpose discriminator}
-\textcolor{red}{Yuanpu address}
+\subsection{On the Local Image Loss}
+\begin{table}[t] % retrieval
+	\label{tab:local_loss}
+	\begin{center}
+		\begin{tabularx}{.32\textwidth}{c|cc}
+			\specialrule{1.5pt}{0pt}{0pt}  
+			Scale 						&   No Local 	& With Local				\\ 				\hline
+			$64{\times}64$              &   ${2.95{\pm}.02}$       &  	$\bm{3.46{\pm}.04}$ \\
+			$256{\times}256$             &   $3.70{\pm}.04$     &	$\bm{4.01{\pm}.06}$ \\ \hline
+		\end{tabularx}
+	\end{center} \vspace{-.4cm}
+	\caption{Multi-scale inception score comparison. See text for explanation.} \label{table:multiscales}
+\end{table}
+
+We also study the effectiveness of the proposed local image loss. We conduct experiments with using architecture with side output 64$\times$64 and 256 $\times$ 256. 
+As can be seen in Table\ref{tab:local_loss}, we can see that by removing local image loss (denoted as "No Local"), the inception score drop from \textcolor{red}{4.27} to \textcolor{red}{3.8}.
+To quantitatively compare the results, we also show generated results using two model in Figure \ref{local_or_not}, We can see that, also both models can successfully capture the semantic correspondence between image and sentence, 256$\times$ 256 results generated by model trained with local image loss provide more details, thus improving the visual quality.
 

### 2017-11-02 cvpr2018.tex
11th

--- 2017-11-01 cvpr2018.tex
@@
 \begin{abstract}
-This paper presents a novel and effective method to deal with the challenging task of generating synthetic photographic image conditioned on semantic image descriptions.
-We show a fully end-to-end trainable network that can generate high resolution images (e.g.
+This paper presents an novel method to deal with the challenging task of generating synthetic photographic image conditioned on semantic image descriptions, which is an effective end-to-end trainable single stream (vanilla-like) network that can generate high resolution images (e.g.
 $512^2$).
-Our method leverages the deep representations of convolutional layers and introduces hierarchical-nested adversarial training to regularize the representations and capture the complex image statistics.
-We present a new network architecture, which is intuitive as well as extensile, to push generated images to high resolutions.
-\textcolor{red}{We present a functional generative adversarial networks (GANs) training strategy} to encourage more effective multimodal (i.e.
-image and text) information utilization in order to enhance multi-purpose adversary between real and fake distribution.
+Our method leverages the deep representations of convolutional layers and introduces accompanying hierarchical-nested adversarial training to regularize intermediate representations in order to capture the complex image statistics.
+We present an intuitive as well as extensile network architecture to push generated images to high resolutions as well as preserve semantics and details.
+We apply multi-purpose adversarial learning at multiple nested scales to encourage more effective multimodal (i.e.
+image and text) information alignment in order to enhance generators to approach real distributions.
 With extensive experimental validation on three major datasets, our method significantly improves previous state of the arts.
@@
 However, insufficient methods have been successfully developed to address this task due to its particular challenges.
-Text-to-image synthesis can be viewed as an special variation of conventional generative models, which aim to translate a low-dimensional embedding  to a much more complex RGB image space.
+Text-to-image synthesis is similar to conventional generative tasks, which aim to translate a low-dimensional embedding  to a much more complex RGB image space.
 Differently, the embedding space of the former is induced by semantic descriptions.
-Therefore, this task requires the generated images to be \textit{semantically consistent}, i.e., the generated images not only preserve sketch concepts of descriptions generally but also preserve fine-grained descriptive details in image pixels.
+Therefore, this task requires the generated images to be \textit{semantically consistent}, i.e., the generated images not only preserve sketch concepts of descriptions but also fine-grained descriptive details in image pixels.
 
@@
 Reed \etal \cite{reed2016generative} is th first to address this task through a GAN based framework.
-But this method only handles image up to $64{\times}64$ resolution and usually can barely generate vivid object details.
-Based on this method, Zhang \etal \cite{han2017stackgan} present a successful approach (StackGAN) by stacking another GAN to generate high-quality $256{\times}256$ images given low resolution $64{\times}64$ synthetic images.
-This method needs two-stage training to achieve the goal.
-Later on, Dong \etal \cite{dong2017semantic}
-bypasses the difficult of translate vector embedding to RGB images and treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-rendering an arbitrary-style training ($128{\times}128$) image conditioned on a targeting semantic description.
-Unfortunately, its high resolution synthesis ability is still unclear.
+But this method only handles image up to $64^2$ resolution and can barely generate vivid object details.
+Based on this method, Zhang \etal \cite{han2017stackgan} present a successful approach (StackGAN) by stacking another low-to-high resolution GAN to generate high-quality $256^2$ images, with two separate stage training.
+Later on, Dong \etal \cite{dong2017semantic} propose to bypass the difficult of translate vector embedding to RGB images and treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-rendering an arbitrary-style training ($128^2$) image conditioned on a targeting semantic description.
+But its high resolution synthesis ability is unclear.
 At present, how to train from the low-dimensional text space to synthesize high resolution and diverse images in an end-to-end manner is still an open and attractive question.
 
-We outline several empirical reasons for this challenges using GANs to deal with text-to-image synthesis.
-The first comes from a fundamental difficulty of balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}.
-How to utilize the multimodal information between images and text in discriminator is extremely important to generate effective gradients.
-The second is that huge pixel space in high resolution images \cite{han2017stackgan}.
-An effective regularization to regularize generators is critical to help capture the complex image statistics \cite{huang2016stacked} as well as preserve semantic consistency. 
+We outline several empirical reasons for the challenges of text-to-image synthesis using GANs.
+The first is the fundamental difficulty of balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}.
+%How to utilize the multimodal information between images and text in discriminator is extremely important to generate effective gradients.
+The second is the huge pixel space in high resolution images \cite{han2017stackgan}. 
+An effective strategy to regularize generators is critical to help capture the complex image statistics \cite{huang2016stacked} as well as preserve semantic consistency. 
 %The first reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. 
@@
 
-Our generator is a simple Vanilla GAN, without needing any inside text conditioning \cite{han2017stackgan} or image label supervision \cite{dash2017tac}.
-To tackle the problem of the big leap from the text space to the high resolution image space, our insight is to leverage hierarchical representations with additional implicit constraints to reduce training instability.
-We introduce ``accompanying'' hierarchically-nested adversarial objective at intermediate layers to generate multi-scale images.  
-And we present an generator network structure design than can uses gradients from multi-scale nested discriminators more effectively.
-
+Our generator is a more like simple vanilla-like GAN, without needing any inside text conditioning \cite{han2017stackgan} or image label supervision \cite{dash2017tac}.
+To tackle the problem of the big leap from the text space to the high resolution image space, our insight is to leverage hierarchical representations with additional implicit constraints.
+We introduce accompanying hierarchically-nested objective at intermediate layers to play adversarial games to encourage the generator approaching real distribution. 
+We also propose a generator network structure design to cooperate our multi-scale nested discriminators more effectively.
 To better make use of image and text information in GAN training, 
-\textcolor{red}{we enforce discriminators at different resolutions can simultaneously differentiate real and fake image-text pairs, images, and patches.}
-This multi-purpose conditional adversary is mutually beneficial to encourage each only focuses on respect duties. 
+\textcolor{red}{we enforce nested discriminators at different scales can simultaneously differentiate real and fake, image-text pairs, images, and patches.}
+This multi-purpose conditional adversary is mutually beneficial to allow each only focuses on respect duties. 
 %It is a regularization to limit the discriminators to use unexpected information to make decision. 
@@
 \section{Related Work}
-We discussed related methods as well as clarify the novelty of our method.
+We discussed related methods as well as further clarify the novelty of our method comparing with them.
 
@@
 Text-to-image synthesis not only requires diverse and high-quality generation but also requires precise semantically consistent mapping in the image space.
-Reed \etal \cite{reed2016generative} introduce a method that can generate $64{\times}64$ resolution images, which is similar with DCGAN \cite{radford2015unsupervised}.
+Reed \etal \cite{reed2016generative} introduce a method that can generate $64^2$ resolution images, which is similar with DCGAN \cite{radford2015unsupervised}.
 This method presents a new strategy to image-text matching aware adversarial training.
 Reed \etal \cite{reed2016learning} propose generative
-adversarial what-where network (GAWWN) to enable "where and what" instructions in text-to-image synthesis, which uses extra information to help generate $128{\times}128$ resolution images.
-StackGAN \etal \cite{han2017stackgan} propose to a two-stage stacking GAN training approach that is able to generate $256{\times}256$ compelling results.
+adversarial what-where network (GAWWN) to enable "where and what" instructions in text-to-image synthesis, which uses extra information to help generate $128^2$ resolution images.
+StackGAN \etal \cite{han2017stackgan} propose to a two-stage stacking GAN training approach that is able to generate $256^2$ compelling results.
 Recently, Dong \etal \cite{dong2017semantic} propose to learn a joint embedding of images and text so as to re-render a prototype image conditioned on targeting descriptions.
@@
 image labels, ImageNet CNNs, etc) \cite{dosovitskiy2016generating,ledig2016photo,dash2017tac,dash2017tac}, or multiple discriminators  \cite{metz2016unrolled,durugkar2016generative,yang2017lr}.
-While note that our method does not use any extra information apart from training paired text and images.
+While our method does not use any extra information apart from training paired text and images.
 Moreover, it is easy to see the training difficulty grows significantly as targeting image resolution increases.
@@
 DSN \cite{lee2015deeply} proposes deep supervision in hierarchical convolutional layers to increase the discriminativeness of feature representations.
-Our method is partially inspired by supervised CNNs with deep supervision \cite{lee2015deeply,xie2015holistically}.
-Our proposed hierarchically-nested adversarial supervision enhances layer representations to support final high resolution outputs.
+Our hierarchically-nested adversarial adversarial objective is partially inspired by supervised CNNs with deep supervision \cite{lee2015deeply,xie2015holistically}. 
+%Our proposed hierarchically-nested adversarial supervision enhances layer representations to support final high resolution outputs.   
 \begin{figure}[t]
@@
  		\State Sample two noise batch $z_1, z_2 \sim p(z)$.
- 		\State Sample one batch of matching and mismatching image text pair $\{X, t\}$,  $\{X, \hat{t}\}$.
+ 		\State Sample one matching image text pair $\{x, t\}$ and mismatched one $\{x, \hat{t}\}$.
  		\State Generate fake image samples for both $t$ and $\hat{t}$
@@
 
-\textbf{Discriminator} The discriminator simply contains consecutive stride-2 conv layers with BN and LeakyReLU (the depth changes according to the input size) until the feature map has $512{\times}4{\times}4$ dimension.
+\textbf{Discriminator} The discriminator simply contains consecutive stride-2 conv layers with BN and LeakyReLU until the feature map has $512{\times}4{\times}4$ dimension.
 There two branches are added on top of it for multi-purpose discriminator design (see next section) .
@@
 $\alpha$ is set to 0.5, $\beta$ is set to 4.
+We decrease the learning rate by half every 100 epochs for CUB and Oxford-102 datasets, and 30 for MS COCO.
 We train our model for 600 epochs for CUB and Oxford, and 120 epochs for COCO dataset.
-Adam optimizer with momentum 0.5 is used for all experiments.
-The initial learning rate is set as 0.0002 and we decrease the learning rate by half every 100 epochs for CUB and Oxford-102 datasets, and 30 for MS COCO.
+Adam optimizer is used for all experiments.
 The number of repeat residual blocks is set to 1 for CUB and Oxford, 2 for COCO. We use batch size 16 for all experiments.
@@
 \subsection{Comparative Results}
-To validate our method, we compare our results with GAN-INT-CLS \cite{reed2016generative}, GAWWN \cite{reed2016learning}, TAC-GAN \cite{dash2017tac}, StackGAN \cite{han2017stackgan} and also its improved version StackGAN++ \cite{}, and Progressive GAN \cite{} \footnote{Note that StackGAN++ and Prog.GAN are two very recent released pre-prints we noticed before submission.
+To validate our method, we compare our results with GAN-INT-CLS \cite{reed2016generative}, GAWWN \cite{reed2016learning}, TAC-GAN \cite{dash2017tac}, StackGAN \cite{han2017stackgan} and also its improved version StackGAN++ \cite{}, and Progressive GAN \cite{} \footnote{Note that StackGAN++ and Prog.GAN are two very recently released pre-prints we noticed before submission.
 We acknowledge them as they also target at generating high resolution images, in spite of their differences in motivations and network and training designs from ours.
@@
 For example, HDGAN improves GAN-INT-CLS by ${\sim}30.1\%$  and ${\sim}8.4\%$ on CUB.
+It also significantly outperforms StackGAN StackGAN++.
+HDGAN achieves competitive results with TAC-GAN on the Oxford flower dataset. TAC-GAN uses image labels to increase the discriminability of generators, while we do not use any extra knowledge.
 
@@
 
-\begin{table}[t] % retrieval
-	\begin{center}
-		\begin{tabularx}{.268\textwidth}{ccc|c}
-			\specialrule{1.5pt}{0pt}{0pt}  
-			\multicolumn{3}{c|}{Components}	&  \multirow{2}{*}{Score}	\\ \cline{1-3}
-			64	& 128	& 256 			& 		\\ \hline
-			&  		&	\checkmark	&	${3.52{\pm}.04}$	\\ 
-			&  	\checkmark	&	\checkmark	&		\\
-			\checkmark	&  			&	\checkmark	&  ${4.14{\pm}.03}$		\\
-			\checkmark	&  \checkmark		&	\checkmark	&	${4.01{\pm}.04}$ \\
-
-		\end{tabularx}
-	\end{center} \vspace{-.4cm}
-	\caption{Ablation study for hierarchically-nested adversarial supervision.} \label{table:deep-nest}
-\end{table}
-
 \subsection{Design principles}

### 2017-11-08 cvpr2018.tex
12th

@@
 %%%%%%%%% TITLE
-\title{Semantic High-definition Image Synthesis \\ with a Hierarchically-nested Adversarial Network}
+\title{Photographic Text-to-Image Synthesis \\ with a Hierarchically-nested Adversarial Network}
 
@@
 \begin{abstract}
-This paper presents an novel method to deal with the challenging task of generating synthetic photographic image conditioned on semantic image descriptions, which is an effective end-to-end trainable single stream (vanilla-like) network that can generate high resolution images (e.g.
-$512^2$).
-Our method leverages the deep representations of convolutional layers and introduces accompanying hierarchical-nested adversarial training to regularize intermediate representations in order to capture the complex image statistics.
-We present an intuitive as well as extensile network architecture to push generated images to high resolutions as well as preserve semantics and details.
-We apply multi-purpose adversarial learning at multiple nested scales to encourage more effective multimodal (i.e.
-image and text) information alignment in order to enhance generators to approach real distributions.
+This paper presents a novel method to deal with the challenging task of generating images conditioned on semantic image descriptions.
+We propose an effective end-to-end trainable single-stream network that can generate photographic high-resolution images (up to $512^2$).
+Our method leverages the deep representations of convolutional layers and introduces accompanying hierarchical-nested adversarial games inside the network hierarchy, which regularize intermediate representations and assist training to capture the complex image statistics.
+We present an extensile network architecture to cooperate with discriminators and push generated images to high resolutions.
+We adopt a multi-purpose adversarial learning strategy at multiple nested hierarchical side outputs to encourage more effective multimodal (i.e.
+image and text) information alignment in order to guarantee semantic consistency and image fidelity simultaneously.
 With extensive experimental validation on three major datasets, our method significantly improves previous state of the arts.
@@
 \section{Introduction}
-Generating photographic image conditional on arbitrary semantic description is an important problem in generative model research \cite{reed2016generative}.
-However, insufficient methods have been successfully developed to address this task due to its particular challenges.
-Text-to-image synthesis is similar to conventional generative tasks, which aim to translate a low-dimensional embedding  to a much more complex RGB image space.
+Photographic text-to-image synthesis is a significant problem in generative model research \cite{reed2016generative}.
+However, insufficient methods have been developed to successfully address this task due to its particular challenges.
+It is a special case of generative learning tasks, which aim to map a low-dimensional embedding to a complex RGB image space.
 Differently, the embedding space of the former is induced by semantic descriptions.
@@
 
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=0.48\textwidth]{figure/intro.pdf}
+%	\vspace{-.7cm}
+	\caption{Overview of our method.
+It contains a single-stream generator and several hierarchically-nested discriminators and is trained end-to-end to generate high-resolution images conditioned on a sentence.} \label{fig:archs-review} %\vspace{-.2cm}
+\end{figure}
+
 Generative adversarial networks (GANs) have become the main solution to this task. 
-Reed \etal \cite{reed2016generative} is th first to address this task through a GAN based framework.
-But this method only handles image up to $64^2$ resolution and can barely generate vivid object details.
+Reed \etal \cite{reed2016generative} address this task through a GAN based framework. But this method only handles image up to $64^2$ resolution and can barely generate vivid object details.
 Based on this method, Zhang \etal \cite{han2017stackgan} present a successful approach (StackGAN) by stacking another low-to-high resolution GAN to generate high-quality $256^2$ images, with two separate stage training.
-Later on, Dong \etal \cite{dong2017semantic} propose to bypass the difficult of translate vector embedding to RGB images and treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-rendering an arbitrary-style training ($128^2$) image conditioned on a targeting semantic description.
-But its high resolution synthesis ability is unclear.
-At present, how to train from the low-dimensional text space to synthesize high resolution and diverse images in an end-to-end manner is still an open and attractive question.
+Later on, Dong \etal \cite{dong2017semantic} propose to bypass the difficult of translate vector embedding to RGB images and treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-rendering an arbitrary-style training ($128^2$) image conditioned on a targeting description.
+But its high-resolution synthesis ability is unclear.
+At present, how to train from the low-dimensional text space to synthesize high-resolution and diverse images in an end-to-end manner is still an open and attractive question.
 
@@
 %How to utilize the multimodal information between images and text in discriminator is extremely important to generate effective gradients.
-The second is the huge pixel space in high resolution images \cite{han2017stackgan}. 
-An effective strategy to regularize generators is critical to help capture the complex image statistics \cite{huang2016stacked} as well as preserve semantic consistency. 
+The second is the huge pixel space in high-resolution images \cite{han2017stackgan}. 
+An effective strategy to regularize generators is critical to help capture the complex image statistics \cite{huang2016stacked} as well as guarantee semantic consistency. 
 %The first reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. 
@@
 Keeping semantic consistency as well as diversity in generated images needs more specialized designs for discriminators to generate effective gradients, as well as generators to prevent gradient vanishing.
-With careful consideration of these outlined problems, in this paper, we propose a novel fully end-to-end method that can directly model high resolution image statistics and generate semantic consistent and photographic image up to $512^2$ resolution.
-The contributions are described follows.
+With careful consideration of these outlined problems, in this paper, we propose a novel fully end-to-end method that can directly model high-resolution image statistics and generate semantic consistent and photographic image up to $512^2$ resolution.
+The contributions are described as follows.
 
-Our generator is a more like simple vanilla-like GAN, without needing any inside text conditioning \cite{han2017stackgan} or image label supervision \cite{dash2017tac}.
-To tackle the problem of the big leap from the text space to the high resolution image space, our insight is to leverage hierarchical representations with additional implicit constraints.
-We introduce accompanying hierarchically-nested objective at intermediate layers to play adversarial games to encourage the generator approaching real distribution. 
-We also propose a generator network structure design to cooperate our multi-scale nested discriminators more effectively.
+Our generator resembles a simple vanilla-like GAN, without requiring any internal text conditioning like \cite{han2017stackgan} or outside image annotation supervision like \cite{dash2017tac}.
+To tackle the problem of the big leap from the text space to the high-resolution image space, our insight is to leverage and regularize hierarchical representations with additional deep adversarial constraints.
+We introduce accompanying hierarchically-nested objectives at multi-scale intermediate layers to play adversarial games and thereby encourage the generator approaching the real training data distribution.
+We also propose a novel generator convolutional neural network (CNN) framework to cooperate with our nested discriminators more effectively.
 To better make use of image and text information in GAN training, 
-\textcolor{red}{we enforce nested discriminators at different scales can simultaneously differentiate real and fake, image-text pairs, images, and patches.}
-This multi-purpose conditional adversary is mutually beneficial to allow each only focuses on respect duties. 
+\textcolor{red}{we enforce nested discriminators at different hierarchies can simultaneously differentiate real-and-fake image-text pairs as well as real-and-fake whole images or image patches.}
+This multi-purpose conditional adversary is mutually beneficial to allow each only focuses on its respect duties. 
 %It is a regularization to limit the discriminators to use unexpected information to make decision.
-We validate our proposed method on three datasets, i.e.
-CUB birds \cite{welinder2010caltech}, Oxford-102 flowers \cite{Nilsback08}, and large-scale COCO datasets \cite{lin2014microsoft}.
+
+We validate our proposed method on three datasets, CUB birds \cite{welinder2010caltech}, Oxford-102 flowers \cite{Nilsback08}, and large-scale MSCOCO \cite{lin2014microsoft}.
 Extensive experimental results and analysis demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts.
@@
 
+\begin{figure*}[t]
+	\centering
+	\includegraphics[width=0.95\textwidth]{figure/views2.pdf}
+	\vspace{-.2cm}
+	\caption{Overviews of some typical GAN frameworks.
+\textbf{A} decomposes tasks multi-stage GANs \cite{han2017stackgan,denton2015deep}.
+\textbf{B} uses multiple discriminators with one generator \cite{durugkar2016generative,tu_etal_nips17_d2gan}.
+\textbf{C} progressively trains symmetric discriminators and generators \cite{Karras2017progressive,huang2016stacked}.
+\textbf{A} and \textbf{C} can be viewed as decomposing high-resolution tasks to multi-stage low-to-high resolution tasks.
+\textbf{D} is our proposed framework that uses a single-stream generator with hierarchically-nested discriminators trained end-to-end.} \label{fig:archs-review}
+\end{figure*}
+
 \section{Related Work}
-We discussed related methods as well as further clarify the novelty of our method comparing with them.
+We discussed related work and further clarify the novelty of our method by comparing with them.
 
-Deep generative models grows wide interests recently, including GANs \cite{goodfellow2014generative}, Variational Auto-encoders (VAE) \cite{kingma2013auto}, etc \cite{oord2016pixel}. 
+Deep generative models attract wide interests recently, including GANs \cite{goodfellow2014generative}, Variational Auto-encoders (VAE) \cite{kingma2013auto}, etc \cite{oord2016pixel}. 
 There are substantial existing methods investigating better usage of GANs for different applications, such as image synthesis \cite{radford2015unsupervised, shrivastava2016learning}, (unpaired) pixel-to-pixel translation \cite{isola2016image,zhu2017unpaired}, medical applications \cite{costa2017towards}, etc \cite{ledig2016photo,huang2016stacked}.
@@
 Text-to-image synthesis not only requires diverse and high-quality generation but also requires precise semantically consistent mapping in the image space.
-Reed \etal \cite{reed2016generative} introduce a method that can generate $64^2$ resolution images, which is similar with DCGAN \cite{radford2015unsupervised}.
-This method presents a new strategy to image-text matching aware adversarial training.
+Reed \etal \cite{reed2016generative}  is th first to introduce a method that can generate $64^2$ resolution images, which is similar with DCGAN \cite{radford2015unsupervised}.
+This method presents a new strategy for image-text matching aware adversarial training.
 Reed \etal \cite{reed2016learning} propose generative
-adversarial what-where network (GAWWN) to enable "where and what" instructions in text-to-image synthesis, which uses extra information to help generate $128^2$ resolution images.
-StackGAN \etal \cite{han2017stackgan} propose to a two-stage stacking GAN training approach that is able to generate $256^2$ compelling results.
+adversarial what-where network (GAWWN) to enable location and content instructions in text-to-image synthesis, which uses extra information to help generate $128^2$ resolution images.
+StackGAN \etal \cite{han2017stackgan} propose a two-stage stacking GAN training approach that is able to generate $256^2$ compelling results.
 Recently, Dong \etal \cite{dong2017semantic} propose to learn a joint embedding of images and text so as to re-render a prototype image conditioned on targeting descriptions.
-Cha \etal \cite{char2017perceptual} explore the usage of the perceptional loss with a pretrained ImageNet CNN \cite{johnson2016perceptual} and Dash \etal \cite{dash2017tac} make use of auxiliary classifiers (similar with \cite{odena2016conditional}) to assist GAN training.
+Cha \etal \cite{char2017perceptual} explore the usage of the perceptional loss with a CNN pretrained on ImageNet \cite{johnson2016perceptual} and Dash \etal \cite{dash2017tac} make use of auxiliary classifiers (similar with \cite{odena2016conditional}) to assist GAN training for text-to-image synthesis.
 
-Learning a continuous mapping from low-dimensional embeddings to complex real data distribution is a long-standing problem.
-Although GANs have made significant progressive, there are still many  unsolved difficulties, e.g.
-training instability and high resolution.
+Learning a continuous mapping from low-dimensional embeddings to a complex real data distribution is a long-standing problem.
+Although GANs have made significant progress, there are still many  unsolved difficulties, e.g.
+training instability and high-resolution extensions.
 Wide methods have been proposed to address those tasks, through various stabilization training techniques \cite{salimans2016improved,arjovsky2017wasserstein,berthelot2017began,shrivastava2016learning,odena2016conditional}, regularization using outside knowledge (e.g.
 image labels, ImageNet CNNs, etc) \cite{dosovitskiy2016generating,ledig2016photo,dash2017tac,dash2017tac}, or multiple discriminators  \cite{metz2016unrolled,durugkar2016generative,yang2017lr}.
-While our method does not use any extra information apart from training paired text and images.
-Moreover, it is easy to see the training difficulty grows significantly as targeting image resolution increases.
+\textit{While our method does not use any extra information apart from training paired text and images.} Moreover, it is easy to see the training difficulty increases significantly as targeting image resolution increases.
 
@@
 
-To synthesize high resolution images, cascade networks play an important role to decompose original difficult tasks to multiple subtasks.
-Denton \etal \cite{denton2015deep} trains a cascade of GANs within a Laplacian pyramid framework (LAPGAN) and use each to generate difference images, conditioned on random noises and output from last level of the pyramid, to push up output resolution through by-stage refinement.
+To synthesize high-resolution images, cascade networks are useful to decompose original difficult tasks to multiple subtasks (Figure \ref{fig:archs-review} A).
+Denton \etal \cite{denton2015deep} train a cascade of GANs within a Laplacian pyramid framework (LAPGAN) and use each to generate difference images, conditioned on random noises and the output from last level of the pyramid, and push up the output resolution through by-stage refinement.
 StackGAN also shares similar strategy with LAPGAN.
-Following this strategy, Chen \etal \cite{chen2017photographic} present a cascaded refinement networks to synthesis high-resolution scene from semantic maps.
+Following this strategy, Chen \etal \cite{chen2017photographic} present a cascaded refinement network to synthesize high-resolution scene from semantic maps.
 Huang \etal \cite{huang2016stacked}
-shows a top-down stack GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method.
-However, this method need multiple symmetric  bottom-up discriminators and pre-training of discriminators, and the usage for high-resolution image is unclear \cite{han2017stackgan}.
-Recently, Karras \cite{} show a progressive training of GANs to enable high resolution image generation.
-Compared with these strategies that train low- to high-resolution GANs progressively, our method has advantages of utilizing multi-level representations to encourage implicit subtask integration, which enables end-to-end high resolution image synthesis.
+propose a top-down stacked GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method.
+However, this method needs multiple symmetric bottom-up discriminators and pre-training of discriminators, and the usage for high-resolution image is unclear.
+Recently, Karras \etal \cite{Karras2017progressive} propose a progressive training of GANs for high-resolution image generation (Figure \ref{fig:archs-review} C).
+\textit{Compared with these strategies that train low- to high-resolution GANs progressively, our method has advantages of utilizing multi-level representations to encourage implicit subtask integration, which makes end-to-end high-resolution image synthesis in a single vanilla-like GAN possible.}
 
@@
 
-Leveraging hierarchical representations of neural networks is an effective way to enhance implicit multi-scaling and ensembling for tasks such as image classification \cite{lee2015deeply} and pixel or object classification \cite{xie2015holistically,cai2016unified,long2015fully}.
+Leveraging hierarchical representations of neural networks is an effective way to enhance implicit multi-scaling and ensembling for tasks such as image recognition \cite{lee2015deeply} and pixel or object classification \cite{xie2015holistically,cai2016unified,long2015fully}.
 DSN \cite{lee2015deeply} proposes deep supervision in hierarchical convolutional layers to increase the discriminativeness of feature representations.
-Our hierarchically-nested adversarial adversarial objective is partially inspired by supervised CNNs with deep supervision \cite{lee2015deeply,xie2015holistically}. 
+\textit{Our hierarchically-nested adversarial objective is inspired by CNNs with deep supervision \cite{lee2015deeply,xie2015holistically}. }
 %Our proposed hierarchically-nested adversarial supervision enhances layer representations to support final high resolution outputs.
-\begin{figure}[t]
-	\centering
-	%	\includegraphics[width=0.48\textwidth]{}
-	\caption{} \label{fig:archs}
-\end{figure}
 
-%
 %
@@
 %refer to HED.
-\begin{figure}[t]
-	\centering
-%	\includegraphics[width=0.48\textwidth]{}
-	\caption{} \label{fig:archs-compare}
-\end{figure}
+
+%\section{Preliminary}
+%\subsection{Generative Adversary Network}
+%Generative adversary networks (GANs) are composed of a generator $G$ and a discriminator $D$, which are alternatively trained to compete with each other in a two-player minimax game.
+The discriminator $D$ is optimized to distinguish the synthesized images from the real images, meanwhile, the generator $G$ is trained to fool the discriminator by trying to convert an input distribution $p_z$ to the true data distribution $p_{data}$.
+Concretely, the overall training procedure can be analogous to the following two-player min-max game $V(D, G)$, where the optimal $G$ and $D$ can be obtained by
+%\begin{equation}
+%\label{equ:GAN}
+%\begin{split}
+%G^*, {D}^* = \arg~\underset{G}{\min}\ \underset{\mathcal{D}}{\max}~ V(D, G)
+%\end{split}
+%\end{equation}
+%
+%%\begin{equation}
+%%\label{game}
+%%\begin{split}
+%%\underset{G}{\min}\ \underset{D}{\max}\ V(D, G) =  &\mathbb{E}_{x\sim p_{data}}[\log D(x)] +  \\
+%%&\mathbb{E}_{z\sim p_{z}}[\log (1-D(G(z)))]		   
+%%\end{split}
+%%\end{equation}
+%%where $x$ is a real image sampled from the true data distribution $p_{data}$, $z$ is a noise vector usually sampled from some predefined distribution $p_{z}$ (e.g., Gaussian distribution).
+%%In practice, It's been shown to work better for the generator $G$ to minimizing $-\log(D(G(z)))$ rather than $\log(1-D(G(z)))$, namely, the $\log(D)$ trick.
+%%In this paper, we replace the negative log likelihood loss with a least square objective\cite{lsgan}. 
+%
+%Conditioned GAN \cite{isola2016image} is a variation of traditional GAN where both the generator network $G$ and discriminator network $D$ are conditioned on an additional condition vector besides the noise vector.
+In this paper, we consider the task of training a deep  generative adversarial network conditioned on the embedding of the text descriptions of the images.
 
 \section{Method}
-Figure \ref{fig:archs} illustrate the overall method.
+%Figure \ref{fig:archs} illustrate the overall method.
 
-\section{Preliminary}
-\subsection{Generative Adversary Network}
-Generative adversary networks (GANs) are composed of a generator $G$ and a discriminator $D$, which are alternatively trained to compete with each other in a two-player minimax game.
-The discriminator $D$ is optimized to distinguish the synthesized images from the real images, meanwhile, the generator $G$ is trained to fool the discriminator by trying to convert an input distribution $p_z$ to the true data distribution $p_{data}$.
-Concretely, the overall training procedure can be analogous to the following two-player min-max game $V(D, G)$, where the optimal $G$ and $D$ can be obtained by
+\subsection{Adversarial objective basics}
+In brief, the two-player game in GANs \cite{goodfellow2014generative} is played by a generator $G$ network and a discriminator $D$ network, which are alternatively trained to compete with each other and thereby improve each other.
+The discriminator is optimized to distinguish synthesized images from real images, meanwhile, the generator is trained to generate realistic images to fool the discriminator.
+Concretely, the overall min-max optimization objective is defined as:
+%where the optimal $G$ and $D$ can be obtained by 
+%The discriminator is optimized to distinguish synthesized images from real images, meanwhile, the generator is trained to fool the discriminator and transform an input distribution $p_z$ to the true data distribution $p_{data}$.
+Concretely, the overall training procedure can be analogous to the following two-player min-max game $\mathcal{L}(D, G)$, where the optimal $G$ and $D$ can be obtained by
 \begin{equation}
@@
 \begin{split}
-G^*, {D}^* = \arg~\underset{G}{\min}\ \underset{\mathcal{D}}{\max}~ V(D, G)
+G^*, D^* = \arg~\underset{G}{\min}\ \underset{D}{\max}~ \mathcal{L}(D, G)
 \end{split}
 \end{equation}
+where the loss $\mathcal{L}$ aims to minimize the Jensen-Shannon divergence between the data and model distributions.
 
-%\begin{equation}
-%\label{game}
-%\begin{split}
-%\underset{G}{\min}\ \underset{D}{\max}\ V(D, G) =  &\mathbb{E}_{x\sim p_{data}}[\log D(x)] +  \\
-%&\mathbb{E}_{z\sim p_{z}}[\log (1-D(G(z)))]		   
-%\end{split}
-%\end{equation}
-%where $x$ is a real image sampled from the true data distribution $p_{data}$, $z$ is a noise vector usually sampled from some predefined distribution $p_{z}$ (e.g., Gaussian distribution).
-%In practice, It's been shown to work better for the generator $G$ to minimizing $-\log(D(G(z)))$ rather than $\log(1-D(G(z)))$, namely, the $\log(D)$ trick.
-%In this paper, we replace the negative log likelihood loss with a least square objective\cite{lsgan}.
-
-Conditioned GAN \cite{isola2016image} is a variation of traditional GAN where both the generator network $G$ and discriminator network $D$ are conditioned on an additional condition vector besides the noise vector.
+%Conditioned GAN \cite{isola2016image} is a variation of traditional GAN where both the generator network $G$ and discriminator network $D$ are conditioned on an additional condition vector besides the noise vector.
 In this paper, we consider the task of training a deep generative adversarial network conditioned on the embedding of the text descriptions of the images.
 
-\section{Method}
-Figure \ref{fig:archs} illustrate the overall method.
 %To generate high-resolution photo-realistic images from text embeddings, we propose a simple and effective Hierarchically-nested Generative Adversarial Network.
-Our approach is to train both generator and discriminator conditioned on sentence embedding vectors.
+%Our approach is to train both generator and discriminator conditioned on sentence embedding vectors.
 We leverage functional loss for discriminator and hierarchically nested side outputs as hierarchical supervision for both generator and discriminator to achieve our goal of generating photo-realistic images from text descriptions.
-
-In general, the generator takes text embedding and random noise vector as input and synthesis images at different scales (e.g, $64\times64$, $128\times128$, $256\times256$).
+%
+%In general, the generator takes text embedding and random noise vector as input and synthesis images at different scales (e.g, $64\times64$, $128\times128$, $256\times256$).
 The discriminator, on the other hand, is trying to judge the pair of synthesized images and the corresponding text embedding as fake pairs as well as differentiating the real images from the fake images.
 $G$ and $D$ are optimized alternatively until converges.
-
-\textbf{Notation } 
-We denote the training data set by $S=\{({X}^n, {T}^n),n=1,...,N\}$, where $X^n$ is the $n-$th training image, and $T^n={t^1,...,t^m}$ as $m$ text descriptions corresponds to $X^n$.
-
-Since we obtain the text embedding vector  using the per-trained char-rnn text encoder provided in \cite{reed2016generative}.
+%
+%
+%\textbf{Notation } 
+%We denote the training data set by $S=\{({X}^n, {T}^n),n=1,...,N\}$, where $X^n$ is the $n-$th training image, and $T^n={t^1,...,t^m}$ as $m$ text descriptions corresponds to $X^n$. 
+%
+%Since we obtain the text embedding vector using the per-trained char-rnn text encoder provided in \cite{reed2016generative}.
 For simplicity, we do not differentiate text description and it's corresponding text embedding vector in this paper.
 Our goal is to learn a generator $G$ that could produce high resolution images of high visual quality as well as variability giving an input text description $t$.
-
-The input to $G$ compress input sentence embedding, and one noise input.
-Denote the image dimension, text embedding dimension and the dimension of the noise input as $I$, $T$ and $Z$, respectively.
+%
+%The input to $G$ compress input sentence embedding, and one noise input.
+%Denote the image dimension, text embedding dimension and the dimension of the noise input as $I$, $T$ and $Z$, respectively.
 Please note that, $G$ has multiple branches and generates multiple images of different sizes.
 For each image size, we have a distinct discriminator $D$ associated with it.
-%For simplicity, we only describe one image size.
-
-The generator is denoted $G: \mathcal{R}^{Z}: \times \mathcal{R}^{T}\rightarrow\mathcal{R}^{I}$, the image discriminator $D_{img}: \mathcal{R}^{I}\rightarrow\{0, 1\}$, and the matching-aware pair discriminator $D_{pair}: \mathcal{R}^{I}: \times \mathcal{R}^{T}\rightarrow\{0, 1\}$.
-
-\textbf{Variational text embedding } Following the practice of \cite{han2017stackgan}, instead of using the plan deterministic non-linear transformation of the original $t$, we obtain the conditional vector $c$ by sampling from a Gaussian distribution $\mathcal{N}(\mu(t), \Sigma(t) )$, in which the mean $\mu(t)$ and the diagonal covariance matrix $\Sigma(t)$ are non-linear transformation of the original text embedding $t$.
+%%For simplicity, we only describe one image size.  
+%
+%The generator is denoted $G: \mathcal{R}^{Z}: \times \mathcal{R}^{T}\rightarrow\mathcal{R}^{I}$, the image discriminator $D_{img}: \mathcal{R}^{I}\rightarrow\{0, 1\}$, and the matching-aware pair discriminator $D_{pair}: \mathcal{R}^{I}: \times \mathcal{R}^{T}\rightarrow\{0, 1\}$.
+%
+%\textbf{Variational text embedding } Following the practice of \cite{han2017stackgan}, instead of using the plan deterministic non-linear transformation of the original $t$, we obtain the conditional vector $c$ by sampling from a Gaussian distribution $\mathcal{N}(\mu(t), \Sigma(t) )$, in which the mean $\mu(t)$ and the diagonal covariance matrix $\Sigma(t)$ are non-linear transformation of the original text embedding $t$.
 This type of conditional augmentation technique can be used to inject randomness into the text embedding vector $t$ to mitigate the common problem that conventional conditional GAN training paradigm usually learns to totally ignore the randomness, resulting to collapsing results lacking diversity \cite{reed2016generative}.
@@
 
-\subsection{Hierarchical Deep Supervision}
-Directly predicting high resolution synthesized images are challenging, not only because of the difficulties in training but also due to the large variation and instability in the hidden layers.
+\subsection{Hierarchical-nested adversarial objectives}
+%Directly predicting high resolution synthesized images are challenging, not only because of the difficulties in training but also due to the large variation and instability in the hidden layers.
+Numerous methods have demonstrated a variety of ways to build GANs for image synthesis. Figure \ref{fig:archs-review} and Section 2 discuss some typical frameworks.
+Our method explores a new dimension of playing this adversarial game along the depth of a CNN (Figure \ref{fig:archs-review} D), which integrates additional discriminators at mid-level features to learn a stronger generator $\mathcal{G}$.
+The hierarchically-nested objectives 
+%We conjecture that adding hierarchical adversarial objective using side outputs can
+act as regularizers to the hidden space of $\mathcal{G}$, which can reduce the training instability and also offer a short path for better error signals.
 
-Our architecture of $G$ consists of a single stream network with additional multiple side outputs.
-This architecture resemble the previous proposed method in edge detection\cite{xie2015holistically} and classification\cite{lee2015deeply}, which demonstrate that additional supervision to  hidden layers can improve model generalization and boost optimization.
-We conjecture that adding hidden layer supervision using side outputs can act as a regularizer to the hidden space of $G$, which reduces the over-fitting issue and provide a short path for the error signal.
+The proposed $\mathcal{G}$ is a network (see Section 3.4), with $s{-}1$ side outputs at the intermediate layers:
 
-Given a random Gaussian noise  $z\in \mathcal{R}^{Z} \scriptsize{\sim} \mathcal{N}(0,1)$ and a text description embedding $t$  $G$ will generate multiple side outputs,
+%This architecture resemble the proposed inverse architectures in edge detection\cite{xie2015holistically} and classification \cite{lee2015deeply}, which demonstrate that additional supervision to hidden layers can improve model generalization and boost optimization.
 \begin{equation}
 \label{side}
-\begin{split}
-	o_1,...,o_s = G(t, z)	   
-\end{split}
+X_1,..., X_s = \mathcal{G}(\bm t, \bm z), 
 \end{equation}
-where $s$ is the total number of side outputs, please note that the dimension of $o_1,..,o_s$ increase gradually (e.g., 64$\times$64, 128$\times$128, and 256$\times$256).
-For simplicity, we denote $o=\{o_1,...,o_s\}$.
-Denote $\mathcal{X}^i = \{X^i_1, ..
-X^i_s\}$ as the pyramid of  resized images constructed from original image $X^i$.
+where $\bm z\sim\mathcal{N}(0,1)$ denotes a random noise and $\bm t\sim p(data)$ denotes sentence embedding vector in the real training data distribution.
+$\mathcal{G}$ produces $s-1$ side size-growing image outputs and a final output $X_s$ with the highest resolution.
 
-For each $o_i$, a distinct discriminator $D_i$ is assigned to compete with it. Denote $\mathcal{D}=\{D_1, ..., D_o\}$ as the whole set of discriminators.
-We aim to solve the following optimization problem:
+%$\mathcal{X}^i = \{X^i_1, .. X^i_s\}$ are side output
+%Given $z\in \mathcal{R}^{Z} \scriptsize{\sim} \mathcal{N}(0,1)$ and a text description embedding $t$, 
+%$G$ generates $s$ side outputs using intermediate layers, $o=\{o_1,...,o_s\}$,
+%Note that the dimension of $o_1,..,o_s$ increases according to the resolution
+%(e.g., 64$\times$64, 128$\times$128, and 256$\times$256). 
+%Denote $\mathcal{X}^i = \{X^i_1, .. X^i_s\}$ as the pyramid of resized images constructed from original image $X^i$.  
+%Denote $\mathcal{D}=\{D_1, ..., D_o\}$ as the whole set of discriminators.
+%e aim to solve the following optimization problem:
 
+For each side output $X_i$, we propose to apply a discriminator $D_i$ to perform independently adversarial games. Therefore, our full min-max objective can be defined as follows: 
 \begin{equation}
@@
 \begin{split}
-  G^*, \mathcal{D}^* = \arg~\underset{G}{\min}\ \underset{\mathcal{D}}{\max}~ \mathcal{L}(G,\mathcal{D}, \mathcal{X}, \bm{T})
+  \mathcal{G}^*, \mathcal{D}^*&  =  \arg~\underset{G}{\min}\ \underset{\mathcal{D}}{\max}~ \mathcal{L}(\mathcal{G},\mathcal{D}, \mathcal{Y}, \bm t, \bm z) \\
+  \text{where} \;\;	 \mathcal{D} & \in  \{D_1, ..., D_s\}, \; \mathcal{Y} = \{Y_1, ..., Y_s\}
 \end{split}
 \end{equation}
-where $\mathcal{D}^*$ compresses the optimal discriminators $\{D_1^*, ..., D_o^*\}$, and $ \mathcal{L}(G,\mathcal{D}, \bm{X}, \bm{T} )$ is the full objective of this mini-max game.
+where $ \mathcal{Y}$ denotes training images at multi-scales, $\{1,...,s\}$.
+%where $\mathcal{D}$ contains the optimal discriminators $\{D_1^*, ..., D_o^*\}$, and $ \mathcal{L}(G,\mathcal{D}, \bm{X}, \bm{T} )$ is the full objective of this mini-max game.
+%Please note that in this setting, 
+Compared with Eq. (\ref{equ:GAN}), one generator competes with multiple discriminators at different hierarchies. 
+\textcolor{red}{Discriminators do not share weights with each other, which offers them flexibility to focus on learning different discriminative features.
+In principle, the lower-resolution side output is forced to learn semantic consistent image structures (e.g., object sketch, color, and background), and the subsequent higher-resolution side outputs are used to render details to the images.
+Since the model is trained in an end-to-end fashion, we can observe more consistent information exhibited in both lower and higher-resolution outputs than StackGAN \cite{han2017stackgan}.
+More results can be founded in th experiments.
+According to this principle, we present the following adversarial losses to support more effective multi-purpose discriminators.}
 
-Please note that in this setting, one generator competes with multiple discriminators.
-And each discriminators does not share weights with each other, thus giving them the flexibility to focus on learning different discriminative features.
+\subsection{Functional adaptive adversarial losses}
+Our generator produces size-growing side outputs which compose an image pyramid. 
+We leverage the hierarchy of it and allow adversarial losses to be multi-purpose to guarantee both semantic consistency and image fidelity.
 
-In principle, the lower-resolution side output is forced to learn the rough structure (e.g., object sketch, color information and background) of the images, the subsequent higher-resolution path is used to add more details to the images.
-Since the model is trained in an end-to-end fashion, we can observe more consistent information exhibited in both lower and higher-resolution outputs than stackGan\cite{han2017stackgan}.
-This type of side output is also proven useful because it allows short path between image supervision information to the hidden feature maps, which could potentially helps training.
+To guarantee semantic consistency, we adopt the matching-aware pair loss proposed by \cite{reed2016generative}.
+The discriminator is designed to take image-text pairs as inputs and trained to identify two types of errors: real image with mismatch conditional text information and fake image with real text.
 
-\subsection{Matching Aware Pair-Loss}
-During the setting of conditional generative adversarial learning, simply generating images of high visual quality is not enough, most importantly, we want the generated images well aligned with the conditioning information (ie, text description in our model).
+The pair-loss is designed to capture the global semantic context.
+However, this loss has two major weaknesses.
+First, there is no explicit loss that force the discriminator to differentiate real images from fake images.
+%Combining both tasks (generating realistic images and matching image with text) into one output further complicates the learning tasks, which is already challenging.
+Second, as the image resolution goes higher, it might be challenging for a global pair-loss discriminator to capture local fine-grained details.
+In addition, as pointed in \cite{shrivastava2016learning}, a single global discriminator may over-emphasize certain unexpected image features and lead to artifacts.
+
+To guarantee image fidelity and overcome these two weaknesses, our solution is to add adaptive local adversarial image losses on image patches. The insights are two folds:
+\begin{itemize}\vspace{-.2cm}
+\setlength\itemsep{-0.3em}
+\item Further forcing the local patch of generated samples to have similar statistics to real image patch can be beneficial for rendering fine-grained details. %
+
+\item \textcolor{red}{Image loss without using pair sentence information can be beneficial in the sense that it utilizes more information as well as it directly push the generated image to the true image distribution.
+We hypothesis this type of loss can help the model to stabilize and boost the training.
+}
+\vspace{-.2cm}
+\end{itemize}
+We expect the low-resolution discriminator to focus on global structures, while high-resolution outputs focus more on local image details.
+Therefore, through the pyramid of the size-growing side outputs, we configure the focal range (the size of each non-overlapping image patch) to be also growing.
+The adaptive local image adversarial loss is implemented as a fully CNN \cite{shrivastava2016learning,zhu2017unpaired}.  
+ Figure \ref{fig:loss} illustrates how hierarchically-nested discriminators compute two losses on the generated images.
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=0.47\textwidth]{figure/loss.pdf}
+
+	\caption{Given an image in the side output pyramid of the generator, the corresponding discriminator $D_i$ computes the matching-aware pair loss and adaptive local image loss (outputting a $R{\times}R$ probability map to indicate real or fake patches).
+The focal range increases as image resize grows.
+Lower range results in finer results.
+}
+	\label{fig:loss}
+\end{figure}
+
+\textbf{Full Objective } Overall, our hierarchically-nested discriminators $\{D_i\}$ minimize the following objective\footnote{The objective of the generator is omitted as it can be easily inferred.}:
+\begin{equation}
+\begin{split}
+\mathcal{L}(& \mathcal{G}, \mathcal{D})  = \sum_{i=1}^{s} \Big(  L_2\big(D_i({Y}_i)\big) +  L_2\big(D_i({Y}_i, \bm t_{Y})\big) \, + \\ 
+& \overline{L_2}\big(D_i({X}_i)\big)  + \overline{L_2}\big(D_i({X}_i, \bm{t}_{X_i})\big) + \overline{L_2}\big(D_i({Y}_i,  \bm{t}_{\overline{Y}})\big) \Big)
+\end{split}
+\end{equation}
+where ${X}_i = \mathcal{G}(\bm{t}_{X}, \bm z)$.
+$L_2(x) = (x - \mathbb{I})^2$ is the mean-square loss (we do not use the original cross-entropy loss) and $\overline{L_2}(x) =(x)^2$.
+For adaptive local image loss with varying focal range, the shape of $x, \mathbb{I} \in \mathbb{R}^{R{\times}R}$ varies accordingly (see Figure \ref{fig:loss}) for the local image loss.
+$R=1$ refers to the (largest local) global range, e.g., $R\equiv1$ for the matching aware pair loss.
+For the matching-aware pair loss,
+$\{Y_i, \bm t_{Y}\}$ denotes a matched image-text pair and $\{Y_i, \bm{t}_{\overline{Y}}\}$ denotes a mismatched image-text pair.
+
+Furthermore, this separation of the image loss from the matching loss in our method opens further possibilities, such as utilizing the unlabeled image to improve both the generator and discriminator.
+\textcolor{red}{In the spirit of variational auto-encoder \cite{} and the practice of \cite{han2017stackgan} (namely conditional augmentation), we sample the input text variable $\bm t$ from a Ganssian distribution $\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}))$, where $\mu$ and $\Sigma$ are functions of $\bm t$.
+We add the Kullback-Leibler divergence regularization term, $D_{KL}(\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}) )|| \mathcal{N}(0, \bm{I}))$, to the $G$ loss to force smooth sampling over the text embedding distribution.
+}
+
+%\begin{equation}
+%{\small 
+%\label{equ:pariG}
+%\begin{split}
+% \mathcal{L}(\mathcal{G}, \mathcal{D})  = & \mathbb{E}_{ t \sim p_{t}, z \sim p_{z}  , X \sim p_{\mathcal{G}(t, z)}} \Big[ \\
+%&   \sum_{i=1}^{s} \big( M(D_i({X}_i)) + M(D_i({X}_i, \bm t)) \big)  + \\
+%&   \sum_{i=1}^{s} \big( \hat{M}(D_i({X}_i)) + \hat{M}(D_i({X}_i, \bm t)) \big) \Big] 
+%\end{split}
+% }
+%\end{equation}
+
+%\begin{equation}
+%\label{equ:totalG}
+%\begin{split}
+%\mathcal{L}_{g}(G,o,\hat{o}, t)  = &  \mathcal{L}_{pair}(G) + \frac{\alpha}{2}~(\mathcal{L}_{local}(G, o) + \mathcal{L}_{local}(G, \hat{o})) + \\
+%& \beta~D_{KL}(\mathcal{N}(\mu({t}), \Sigma({t}) )|| \mathcal{N}(0, \bm{I})) 
+%\end{split}
+%\end{equation}
+
+%In addition, at the very beginning of the training,  generated images are usually far away from true image distribution, the discriminator can very easily judge a pair as invalid without using much pair information.
+\textcolor{red}{need more explanationn.}
+%We not only want the whole image is classified as true image by the discriminator, but also want to restrict the discriminator to classify all the local patches of high resolution output as true as well.
+
+%so that they can focus more on local details, we restrict the receptive field of the image discriminator.
+
+%\subsection{Matching Aware Pair-Loss}
+%During the setting of conditional generative adversarial learning, simply generating images of high visual quality is not enough, most importantly, we want the generated images well aligned with the conditioning information (ie, text description in our model).
 %Given a pair of image and text embedding $(x, \psi{t})$ as input, in the discriminator $D_i$, we first transfer $x$  to an image code $Code_x$.
@@
 %The generator $G$ and discriminator $D$ are optimized alternatively using their corresponding loss function. 
-Therefore, the discriminator are designed to take image and sentence pair as input and should be able to identify two types of errors: real image with mismatch conditional text information and fake image with real text.
+%Therefore, the discriminator are designed to take image and sentence pair as input and should be able to identify two types of errors: real image with mismatch conditional text information and fake image with real text.
 In our case, the discriminator is explicitly trained with three pair configurations, namely: real image with right text as positive training sample, and the aforementioned two sources of error pairs as negative training samples.
 
-Given a mini-batch of training data consists of images $X$ and the corresponding text $t$, mismatching text $\hat{t}$.
+%Given a mini-batch of training data consists of images $X$ and the corresponding text $t$, mismatching text $\hat{t}$.
 For simplicity, we omit the batch index.
@@
 
-\begin{equation}
-\label{equ:matchignloss}
-\begin{split}
-\mathcal{L}_{pair}(D_i)  = & \mathbb{E}_{(X_i, \hat{t}) \sim p_{data}}[(D_i( {X_i},  {t}) - 1) ^ 2 ] - \frac{1}{2}*\\ 
-&   \mathbb{E}_{(X_i, \hat{t}) \sim p_{data}}[(D_i({X_i}, \hat{{t}}) - 1)^2  ] - \frac{1}{2} *\\
-&   \mathbb{E}_{t \sim p_{data}}[ (D_i( {o}_i, {t}))^2 ]  
-\end{split}
-\end{equation}
-
-Similarly, the pair wise objective of generator can be summarized as:
-\begin{equation}
-\label{equ:pariG}
-\begin{split}
-\mathcal{L}_{pair}(G)  = & \sum_{i=1}^{s} ( \mathbb{E}_{t \sim p_{data}}[ (D_i( {o}_i, {t}) - 1) )^2 ] )
-\end{split}
-\end{equation}
-
-where $o_i$ is the $i-$th output of the $G$,  this type of loss is used to push the valid image-text pair away from the invalid pairs.
-
-\subsection{Local Adversarial Image Loss}
-%As is shown in Figure.
+%\begin{equation}
+%\label{equ:matchignloss}
+%\begin{split}
+%\mathcal{L}_{pair}(D_i)  = & \mathbb{E}_{(X_i, \hat{t}) \sim p_{data}}[(D_i( {X_i},  {t}) - 1) ^ 2 ] - \frac{1}{2}*\\ 
+%&   \mathbb{E}_{(X_i, \hat{t}) \sim p_{data}}[(D_i({X_i}, \hat{{t}}) - 1)^2  ] - \frac{1}{2} *\\
+%&   \mathbb{E}_{t \sim p_{data}}[ (D_i( {o}_i, {t}))^2 ]  
+%\end{split}
+%\end{equation}
+%
+%Similarly, the pair wise objective of generator can be summarized as:
+%\begin{equation}
+%\label{equ:pariG}
+%\begin{split}
+%\mathcal{L}_{pair}(G)  = & \sum_{i=1}^{s} ( \mathbb{E}_{t \sim p_{data}}[ (D_i( {o}_i, {t}) - 1) )^2 ] )
+%\end{split}
+%\end{equation}
+%
+%where $o_i$ is the $i-$th output of the $G$,  this type of loss is used to push the valid image-text pair away from the invalid pairs.
+%
+%\subsection{Local Adversarial Image Loss}
+%%As is shown in Figure.
 \ref{overview}, the discriminator $D$ in our model mainly consists of two branches: matching-aware pair discrimination branch $D_{pair}$, and image discrimination branch $D_{img}$, both branches share the same  image encoder.
-
-The pair-loss is designed to differentiate invalid pairs from valid ones.
-It works by first translating the image to a compact size code, then the image code and the sentence vector is concatenated and fed to successive layers to predict the validity of the input image-sentence pair.
-
-Overall, the pair loss is designed to capture the global context semantic information.
+%
+%The pair-loss is designed to differentiate invalid pairs from valid ones.
+%It works by first translating the image to a compact size code, then the image code and the sentence vector is concatenated and fed to successive layers to predict the validity of the input image-sentence pair.
+%
+%Overall, the pair loss is designed to capture the global context semantic information.
 However, this loss has two problems, firstly,  there is no explicit loss that push the discriminator to differentiate real images from the fake images.
@@
 In addition, as is also pointed in \cite{shrivastava2016learning}, a single global strong discriminator tend to over-emphasize certain image feature and may lead to artifacts.
-
-%More specifically, ideally the image patches sampled from the higher resolution outputs
-
-Our solutions is to add hierarchical local adversarial image loss which does not require sentence information, to all the side outputs.
+%
+%%More specifically, ideally the image patches sampled from the higher resolution outputs 
+%
+%Our solutions is to add hierarchical local adversarial image loss which does not require sentence information, to all the side outputs.
 To make the image discriminator focus more on local details, we restrict the receptive field of the image discriminator.
-Our insight has two folds:
-\begin{itemize}
-	\item 1. Forcing the local patch of generated samples to have similar statistics to real image patch can be beneficial to rendering fine-grained details. %
-
-	\item 2.
+%Our insight has two folds:
+%\begin{itemize}
+%	\item 1. Forcing the local patch of generated samples to have similar statistics to real image patch can be beneficial to rendering fine-grained details. %
+%	 
+%	\item 2.
 Image loss without using pair sentence information can be beneficial in the sense that it utilize more information as well as it directly push the generated image to the true image distribution.
 We hypothesis this type of loss can help the model to stabilize and boost the training.
-\end{itemize}
-%In addition, at the very beginning of the training,  generated images are usually far away from true image distribution, the discriminator can very easily judge a pair as invalid without using much pair information.
+%\end{itemize}
+%%In addition, at the very beginning of the training,  generated images are usually far away from true image distribution, the discriminator can very easily judge a pair as invalid without using much pair information.
 \textcolor{red}{need more explanationn.}
-%We not only want the whole image is classified as true image by the discriminator, but also want to restrict the discriminator to classify all the local patches of high resolution output as true as well.
-Since our model generates a pyramid of outputs with increasing image sizes. 
-We expect the low resolution output capture the global structure and color information, while the higher resolution outputs focus on local image details.
-
-To force the discriminator focus on the fine-grained details, a nature way is to fix the receptive field for all the generator.
+%%We not only want the whole image is classified as true image by the discriminator, but also want to restrict the discriminator to classify all the local patches of high resolution output as true as well.
+%Since our model generates a pyramid of outputs with increasing image sizes. 
+%We expect the low resolution output capture the global structure and color information, while the higher resolution outputs focus on local image details. 
+%
+%To force the discriminator focus on the fine-grained details, a nature way is to fix the receptive field for all the generator.
 To this end, we propose a hierarchical image loss, where the output of image  discriminator is a grid of values.
-
-Denote $K_i$ as the $i-$th local image discriminators,  the output $d_i = K_i(X_i)$ has a size increasing with input $X_i$.
+%
+%Denote $K_i$ as the $i-$th local image discriminators,  the output $d_i = K_i(X_i)$ has a size increasing with input $X_i$.
 For instance 1$\times$1 for 64$\times$64 input, 4$\times 4$ for 128$\times$128 and 8$\times 8$ for 256$\times$256 etc.
@@
 Specifically, the proposed local image loss can be given by:
-\begin{equation}
-\label{equ:local}
-\begin{split}
-\mathcal{L}_{local}(K_i, X_i, o_i, t )  = & \mathbb{E}_{(x, t) \sim p_{data}}[ \mathbb{E}(K_i( {X_i}) - 1) ^ 2 ] - \\
-&  \mathbb{E}_{t \sim p_{data}}[  \mathbb{E}(K_i( {o}_i))^2 ]  
-\end{split}
-\end{equation}
+%\begin{equation}
+%\label{equ:local}
+%\begin{split}
+%\mathcal{L}_{local}(K_i, X_i, o_i, t )  = & \mathbb{E}_{(x, t) \sim p_{data}}[ \mathbb{E}(K_i( {X_i}) - 1) ^ 2 ] - \\
+%&  \mathbb{E}_{t \sim p_{data}}[  \mathbb{E}(K_i( {o}_i))^2 ]  
+%\end{split}
+%\end{equation}
+%
+%Similarly, the pair wise objective of generator can be summarized as:
+%\begin{equation}
+%\label{equ:pariG}
+%\begin{split}
+%\mathcal{L}_{local}(G, o)  = & \sum_{i=1}^{s} ( \mathbb{E}_{t \sim p_{data}}[ \mathbb{E} (K_i( {o}_i) - 1) )^2 ] )
+%\end{split}
+%\end{equation}
+%Further more, this separation of the image loss from the matching loss open further possibilities, such as utilizing the unlabeled image to improve both the generator and discriminator.
 
-Similarly, the pair wise objective of generator can be summarized as:
-\begin{equation}
-\label{equ:pariG}
-\begin{split}
-\mathcal{L}_{local}(G, o)  = & \sum_{i=1}^{s} ( \mathbb{E}_{t \sim p_{data}}[ \mathbb{E} (K_i( {o}_i) - 1) )^2 ] )
-\end{split}
-\end{equation}
-Further more, this separation of the image loss from the matching loss open further possibilities, such as utilizing the unlabeled image to improve both the generator and discriminator.
-
-\subsection{Total Loss}
-
-Our objective for both $D$ and $G$ thus mainly compress two types of terms: \textit{matching aware pair-loss} for matching the overall image content to the text description, and \textit{local adversarial image loss} for rendering the fine-grained details.
+%
+%\subsection{Total Loss}
+%
+%Our objective for both $D$ and $G$ thus mainly compress two types of terms: \textit{matching aware pair-loss} for matching the overall image content to the text description, and \textit{local adversarial image loss} for rendering the fine-grained details.
 In the spirit of variational auto-encoder and the practice of \cite{han2017stackgan}, we also add the  Kullback-Leibler divergence regularization term to the $G$ loss.
-%In addition, this term might also play a role in balancing the $c_t$ and generated condition vector $c_t$ by forcing $c$ to have a similar scale to $z$.
+%
+%%In addition, this term might also play a role in balancing the $c_t$ and generated condition vector $c_t$ by forcing $c$ to have a similar scale to $z$.
 In the following sections, we denote $c_t$ as the variational conditional text vector.
-
-\begin{equation}
-\label{equ:totalD}
-\begin{split}
-\mathcal{L}_{d}(D_i, X_i, o_i,\hat{o_i}, t, \hat{t})    = &\mathcal{L}_{pair}(D_i) + \frac{\alpha}{2}~( \\
-&\mathcal{L}_{local}(K_i, o_i) + \mathcal{L}_{local}(K_i, \hat{o_i}) )
-\end{split}
-\end{equation}
-\begin{equation}
-\label{equ:totalG}
-\begin{split}
-\mathcal{L}_{g}(G,o,\hat{o}, t)  = &  \mathcal{L}_{pair}(G) + \frac{\alpha}{2}~(\mathcal{L}_{local}(G, o) + \mathcal{L}_{local}(G, \hat{o})) + \\
-                  & \beta~D_{KL}(\mathcal{N}(\mu({t}), \Sigma({t}) )|| \mathcal{N}(0, \bm{I})) 
-\end{split}
-\end{equation}
-where $\alpha$ is coefficient used to tune the weight of the local patch loss, $\beta$ is used to tune the weights of the KL-Divergence. 
-We omit the additional arguments to both $\mathcal{L}_{pair}(G) $ and $\mathcal{L}_{pair}(D_i) $ for simplicity.
+%
+%\begin{equation}
+%\label{equ:totalD}
+%\begin{split}
+%\mathcal{L}_{d}(D_i, X_i, o_i,\hat{o_i}, t, \hat{t})    = &\mathcal{L}_{pair}(D_i) + \frac{\alpha}{2}~( \\
+%&\mathcal{L}_{local}(K_i, o_i) + \mathcal{L}_{local}(K_i, \hat{o_i}) )
+%\end{split}
+%\end{equation}
+%\begin{equation}
+%\label{equ:totalG}
+%\begin{split}
+%\mathcal{L}_{g}(G,o,\hat{o}, t)  = &  \mathcal{L}_{pair}(G) + \frac{\alpha}{2}~(\mathcal{L}_{local}(G, o) + \mathcal{L}_{local}(G, \hat{o})) + \\
+%                  & \beta~D_{KL}(\mathcal{N}(\mu({t}), \Sigma({t}) )|| \mathcal{N}(0, \bm{I})) 
+%\end{split}
+%\end{equation}
+%where $\alpha$ is coefficient used to tune the weight of the local patch loss, $\beta$ is used to tune the weights of the KL-Divergence. 
+%We omit the additional arguments to both $\mathcal{L}_{pair}(G) $ and $\mathcal{L}_{pair}(D_i) $ for simplicity.
 %The loss function of the matching aware discriminator are summarized as:
@@
 
- \begin{algorithm}
- 	\caption{Multi scale GAN training algorithm with step size $\alpha$, number of iteration $S$, we omit the batch index and summarize the algorithm using SGD for simplicity.}
- 	\label{CHalgorithm}
- 	\begin{algorithmic}[1]
- 		\For{$i \gets 1 \textrm{ to } S$ }
- 		\For{$k \gets 1 \textrm{ to } ncritic$}
- 		\State Sample two noise batch $z_1, z_2 \sim p(z)$.
- 		\State Sample one batch of matching and mismatching image text pair $\{X, t\}$,  $\{X, \hat{t}\}$.
- 		\State Generate fake image samples for both $t$ and $\hat{t}$
- 		\begin{equation}
- 		\begin{split}
-	 		& {o} = G(t, z_1) \\
-	 		& {\hat{o}} = G(\hat{t}, z_2) 
- 		\end{split}
- 		\end{equation}
-	 		\For{each discriminator $D_i$ }
-		 		\State Update $D_i$ by descending the gradient of loss \ref{equ:totalD}:
-		 		\begin{equation}
-		 		   	\theta_{D_i} = \theta_{D_i}  - \nabla_{\theta_{D_i}} \mathcal{L}_d(D_i, X_i,o_i,\hat{o_i}, t,\hat{t})
-		 		\end{equation}
-	 		\EndFor
- 		\EndFor
- 		\State Update the generator by descending it's stochastic gradient of loss \ref{equ:totalG}:
- 		\begin{equation}
- 		\theta_{G} = \theta_{G}  - \nabla_{\theta_{G}} \mathcal{L}_g(G, o, \hat{o}, t)
- 		\end{equation}
-
- 		\EndFor
-
- 	\end{algorithmic}
- \end{algorithm}
+% \begin{algorithm}
+% 	\caption{Multi scale GAN training algorithm with step size $\alpha$, number of iteration $S$, we omit the batch index and summarize the algorithm using SGD for simplicity.}
+% 	\label{CHalgorithm}
+% 	\begin{algorithmic}[1]
+% 		\For{$i \gets 1 \textrm{ to } S$ }
+% 		\For{$k \gets 1 \textrm{ to } ncritic$}
+% 		\State Sample two noise batch $z_1, z_2 \sim p(z)$.
+% 		\State Sample one batch of matching and mismatching image text pair $\{X, t\}$,  $\{X, \hat{t}\}$.
+% 		\State Generate fake image samples for both $t$ and $\hat{t}$
+% 		\begin{equation}
+% 		\begin{split}
+%	 		& {o} = G(t, z_1) \\
+%	 		& {\hat{o}} = G(\hat{t}, z_2) 
+% 		\end{split}
+% 		\end{equation}
+%	 		\For{each discriminator $D_i$ }
+%		 		\State Update $D_i$ by descending the gradient of loss \ref{equ:totalD}:
+%		 		\begin{equation}
+%		 		   	\theta_{D_i} = \theta_{D_i}  - \nabla_{\theta_{D_i}} \mathcal{L}_d(D_i, X_i,o_i,\hat{o_i}, t,\hat{t})
+%		 		\end{equation}
+%	 		\EndFor
+% 		\EndFor
+% 		\State Update the generator by descending it's stochastic gradient of loss \ref{equ:totalG}:
+% 		\begin{equation}
+% 		\theta_{G} = \theta_{G}  - \nabla_{\theta_{G}} \mathcal{L}_g(G, o, \hat{o}, t)
+% 		\end{equation}
+% 		
+% 		
+% 		\EndFor
+% 		
+% 	\end{algorithmic}
+% \end{algorithm}
+%
 
 \subsection{Architecture Design}
-Our proposed network, composed by a generator and a discriminator, is symmetric as well as extensile. We introduce the details as well as motivations.
+%We introduce framework details as well as motivations.
 
-\textbf{Generator} The generator is simpled composed by three kinds of modules, termed as $K$-repeat res-blocks, stretching layers, and linear compression layers.
-A single res-block in the $K$-repeat res-block is a standard residual block  \cite{he2016identity} containing two convolutional (conv) layers (with batch normalization (BN) \cite{ioffe2015batch} and ReLU).
+\textbf{Generator} The generator is simply composed by three kinds of modules, termed as $K$-repeat res-blocks, stretching layers, and linear compression layers.
+A single res-block in the $K$-repeat res-block is a modified\footnote{We remove ReLU after the skip-addition of each residual block, with an intention to reduce sparse gradients.} residual block \cite{he2016identity}, which contains two convolutional (conv) layers (with batch normalization (BN) \cite{ioffe2015batch} and ReLU).
 The stretching layer serves to reduce feature map size and dimension.
 It simply contains an scale-$2$ nearest up-sampling layer followed by a convolutional layer with BN+ReLU.
-And the linear compression layer is a conv layer followed by a Tan, whose compact design enforces feature maps in conv blocks can linearly represent RGB images at arbitrary scales.
+The linear compression layer is one conv layer followed by a Tanh to directly compress features map to the RGB space (as side outputs) linearly.
+We prevent any non-linear functions that could impede the gradient signals.
+%, whose compact design enforces feature maps in conv blocks can linearly represent RGB images at arbitrary scales.
 Starting from a $1024{\times}4{\times}4$ embeddings replicated by a $1024$-d text embedding, the generator simples use $M$ $K$-repeat res-blocks connected by $M{-}1$ in-between stretching layers until the feature maps reach to the targeting resolution.
-So for $256{\times}256$ targeting resolution with $K{=}1$, there are $M{=}6$ $1$-repeat res-blocks and $5$ stretching layers.
-Such simple and symmetric design makes our generator helpful for gradient flows.
-We will verify in experiments.
-With a predefined side-output scales $\{S_i\}$, we apply the compression layer at those scales to produce synthetic images.
+So for $256{\times}256$ resolution with $K{=}1$, there are $M{=}6$ $1$-repeat res-blocks and $5$ stretching layers.
+%Such simple and symmetric design makes our generator helpful for gradient flows. We will verify in experiments. 
+With a predefined side-output scales $\{1,...,s\}$, we apply the compression layer at those scales to produce synthetic images (i.e., side outputs).
 
-\textbf{Discriminator} The discriminator simply contains consecutive stride-2 conv layers with BN and LeakyReLU until the feature map has $512{\times}4{\times}4$ dimension.
-There two branches are added on top of it for multi-purpose discriminator design (see next section) .
-One is a direct $4{\times}4$ conv layers to produce a 2-d vector to classify real and fake.
+\textbf{Discriminator} The discriminator simply contains consecutive stride-2 conv layers with BN and LeakyReLU.
+There are two branches are added on the upper layer for the proposed functional discriminator design (see next section).
+One is a direct fully convolutional layers to produce a $R{\times}R$ probability map (see Figure \ref{fig:loss}) and classify each location as real or fake.
 Another one first concatenate $128{\times}4{\times}4$ text embedding (replicated from a $128$-d text embedding).
-Then we use an $1{\times}1$ conv to fuse text and image information; it is critical to guarantee the semantic consistency in the final results.
-Finally, a $4{\times}4$ conv layer produces a 2-d vector.
+Then we use an $1{\times}1$ conv to fuse text and image information and  a $4{\times}4$ conv layer to classify the the pair is real or fake.
+%it is critical to guarantee the semantic consistency in the final results.
 
-All intermediate conv layers use $3{\times}3$ kernels (with reflection padding and no bias).
-We remove ReLU after the skip-addition of each residual block, with an intention to reduce sparse gradients.
+\textcolor{red}{All intermediate conv layers for both generators and discriminators use $3{\times}3$ kernels (with reflection padding and no bias).
 We also experimented other normalization (i.e.
-instance normalization \cite{ulyanov2016instance} and layer normalization \cite{ba2016layer}) used by \cite{zhu2017unpaired,chen2017photographic}.
+instance normalization \cite{ulyanov2016instance} and layer normalization \cite{ba2016layer}) used by recent advances \cite{zhu2017unpaired,chen2017photographic}.
 Both are not satisfactory.
+}
 
-To generate $512^2$ images, we pre-train the generator to $256^2$ (and fix it for memory saving and faster convergence).
+\subsection{Training Details}
+%The algorithm that summarizes the training process of our model is given in Algorithm 1. 
+%We train and evaluate our model with a devbox machine. $\alpha$ is set to 0.5, $\beta$ is set to 4.
+The Adam optimizer is used for all experiments.
+The initial learning rate is set as 0.0002 and decreased by half for every 100 epochs (30 for COCO).
+The CUB and Oxford-102 datasets are trained for 500 epochs in total (250 epochs for COCO with 4 GPUs).
+For the adaptive local image loss, we set $R=1$ for $64^2$ side output, $R=3$ for $128^2$ side output and $R=5$ for $256^2$ and $512^2$ outputs.
+We use 1-repeat residual block for the generator till $256^2$ resolution.
+To generate $512^2$ images, we pre-train the generator to $256^2$ for the consideration of memory saving and faster convergence.
 We use $3$-repeat res-block followed by the stretching and linear compression layer.
 Since the $256^2$ image already decides the overall semantics and details, to encourage the $512^2$ maintain these information, we also use a reconstruction loss to self-regularize the generator in case the discriminator confuses the expected output.
-
-\subsection{Implementation Details}
-The algorithm that summarizes the training process of our model is given in Algorithm 1. We train and evaluate our model with a devbox machine. $\alpha$ is set to 0.5, $\beta$ is set to 4.
- We train our model for 600 epochs for CUB and Oxford, and 120 epochs for COCO dataset.
-Adam optimizer with momentum 0.5 is used for all experiments.
-The initial learning rate is set as 0.0002 and we decrease the learning rate by half every 100 epochs for CUB and Oxford-102 datasets, and 30 for MS COCO.
-The number of repeat residual blocks is set to 1 for CUB and Oxford, 2 for COCO. We use batch size 16 for all experiments.
 
@@
 %& \mathbb{E}_{z\sim p_{z}, t \sim p_{data}}[-\log( D_{img}( G(z, c_t) ) ) ] + \\
-%& D_{KL}(\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )|| \mathcal{N}(0, \bm{I})) 		   
+%& D_{KL}(\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )|| \mathcal{N}(0,` \bm{I})) 		   
 %\end{split}
@@
 \section{Experiments}
+This section evaluates the proposed method both qualitatively and quantitatively on three public datasets.
+We denote our method as \textbf{HDGAN}, referring as High-definition results as well as the idea of Hierarchically-nested Discriminators.
 
-\subsection{Dataset}
 \textbf{Dataset} 
-We evaluate our method extensively using three widely used datasets.  CUB dataset contains 11,788 bird images belonging to one of the 200 different classes. 
-%Each image in this dataset is associated with 10 text descriptions. 
-We pre-process the image using the same pipeline proposed in \cite{han2017stackgan}, which crops the birds foreground out to  ensure a object-background ratio greater than 0.75.
-The OXford-102 dataset contains 102 different categories of flowers with 8189 images in total.
-Following the similar experiment setting in \cite{han2017stackgan, reed2016generative}, we split both of these datasets into class-disjoint training and testing sets.
-Each image in both CUB and Oxford-102 is associated with 10 text descriptions.
-We also exploit the MS  COCO dataset, which contains a much more broad image category and various backgrounds.
-We use the training and validation splitting setting provided by the original COCO dataset, resulting to a training set containing 80k images and a validation set with 40k images.
-Different from CUB and Oxford-102, each image in COCO has 5 text descriptions.
-For text features, we use the pre-trained text encoder model provided in \cite{reed2016generative}, each text description is encoded into a 1024 vector.
-During the training stage, we randomly pick-up a crop view from the original images, and pick 4 image sentence embedding and use the mean as conditioning vector.
+\textcolor{red}{We evaluate our method extensively using three widely used datasets.
+The CUB dataset \cite{welinder2010caltech} contains 11,788 bird images belonging to 200 different categories.
+We pre-process and split the images using the same pipeline in \cite{reed2016generative,han2017stackgan}
+%, which crops the bird region and ensure the foreground occupies greater than 0.75.  
+The Oxford-102 dataset \cite{Nilsback08} contains 8189 flow images in 102 different categories. 
+%We follow \cite{han2017stackgan, reed2016generative} to split both of these datasets into class-disjoint training and testing sets. 
+Each image in both datasets is associated with 10 text descriptions.
+\textcolor{red}{In the COCO dataset, \cite{lin2014microsoft} there are 80k training images and a validation 40k images.
+Each image has 5 text descriptions.
+}
+We use the pre-trained text encoder model provided in \cite{reed2016generative} to encode each text description of the three datasets into a 1024 vector.
+%During the training stage, we randomly pick-up a crop view from the original images, and pick 4 image sentence embedding and use the mean as conditioning vector.
+}
 
-\subsection{Evaluation metric}
-\textbf{Inception score.}  To evaluate the quality of generated images, we resort to the recently proposed qualitative evaluation measurement "inception score"\cite{improvedGAN},
- \begin{equation}
-	IS = \exp(\mathbb{E}_xD_{\bm{KL}}(p(y|\bm{x})||p(y)))
- \end{equation}
- where $\bm{x}$ denotes generated sample images, $y$ the class label, $p(y|\bm{x})$ represents the conditional label distribution calculated by the Inception model\cite{inception}.
-Inception score is found to be a good measurement of both objectiveness and diversity of generated images, it is closely correlated with human judgment on the image quality.
-For CUB and oxford-102, we use the inception model provided by \cite{han2017stackgan}, for MS COCO dataset, we use the model train on ImageNet.
-
-\textbf{Neural image-sentence distance.} Since inception score can not measure alignment between the generated images and the text description, here, we conduct a new qualitative measurement, which calculated the cosine distance between image code and the sentence vector.
-We train the model on each dataset.
-
-\textbf{MS-SSIM.}
-We also adopt the multi-scale structural similarity (MS-SSIM) metric \cite{improvedGAN} for further image quality validation.
+\textbf{Evaluation metric}
+We use three different quantitative metrics to evaluate our method.
+%\textcolor{red}{\textbf{Inception score.}}  To evaluate the quality of generated images, we resort to the recently proposed qualitative evaluation measurement "inception score"\cite{improvedGAN},
+% \begin{equation}
+%	IS = \exp(\mathbb{E}_xD_{\bm{KL}}(p(y|\bm{x})||p(y)))
+% \end{equation}
+% where $\bm{x}$ denotes generated sample images, $y$ the class label, $p(y|\bm{x})$ represents the conditional label distribution calculated by the Inception model\cite{inception}. 
+1) Inception score \cite{improvedGAN} is a measurement of both objectiveness and diversity of generated images, it is closely correlated with human judgment on the image quality.
+For CUB and oxford-102, we use the fine-tuned inception model provided by StackGAN.
+For MS COCO dataset, we directly use the model train on ImageNet.
+2) We also adopt the multi-scale structural similarity (MS-SSIM) metric \cite{improvedGAN} for further validation.
 It tests the variation of generated outputs and can find mode collapses reliably \cite{odena2016conditional}.
 Lower score indicates higher variance.
-
-%\textbf{Image retrieval. } We also conduct image retrieval evaluation on the dataset. The results is shown in Fig1.
-
-%We only conduct qualitative experiment on
-
-\subsection{Baseline}
-
-In this section, we evaluate the proposed method both qualitatively and quantitatively on three public datasets.
-We denote our method as HDGAN, referring as High-definition results as well as the design of hierarchically-nested discriminators.
-
-%We mainly compare to the state-of-the art StackGAN \cite{han2017stackgan} for text-to-image synthesis and demonstrate substantially improvement.
+\textcolor{red}{3) Since inception score can not measure alignment between the generated images and the text description, here, we conduct a new qualitative measurement, namely neural image-sentence distance, which calculated the cosine distance between image code and the sentence vector.
+We train the model on each dataset.
+}
 
@@
 		%\centering
-		%\includegraphics[width=0.99\textwidth,height=0.7\textwidth]{figure/ms_ssmi.pdf}
+		\includegraphics[width=0.99\textwidth,height=0.7\textwidth]{figure/ms_ssmi.pdf}
 		\vspace{-1.8cm}
@@
 \subsection{Comparative Results}
-To validate our method, we compare our results with GAN-INT-CLS \cite{reed2016generative}, GAWWN \cite{reed2016learning}, TAC-GAN \cite{dash2017tac}, StackGAN \cite{han2017stackgan} and also its improved version StackGAN++ \cite{}, and Progressive GAN \cite{} \footnote{Note that StackGAN++ and Prog.GAN are two very recently released pre-prints we noticed before submission.
-We acknowledge them as they also target at generating high resolution images, in spite of their differences in motivations and network and training designs from ours.
+To validate our method, we compare our results with GAN-INT-CLS \cite{reed2016generative}, GAWWN \cite{reed2016learning}, TAC-GAN \cite{dash2017tac}, StackGAN \cite{han2017stackgan} and also its improved version StackGAN++ \cite{han2017stackganv2}, and Progressive GAN \cite{Karras2017progressive} \footnote{StackGAN++ and Prog.GAN are two very recently released preprints we noticed.
+We acknowledge them as they also target at generating high-resolution images, in spite of their differences in motivations and network and training designs from ours.
 }
@@
 
-Table \ref{table:score} shows the quantitative evaluation.
+\textcolor{red}{Table \ref{table:score} shows the quantitative inception-score evaluation. We follow StackGAN to sample ${~}30,000$ images for evaluation.
 HDGAN achieves significantly improvement compared to other methods.
@@
 It also significantly outperforms StackGAN StackGAN++.
-HDGAN achieves competitive results with TAC-GAN on the Oxford flower dataset. TAC-GAN uses image labels to increase the discriminability of generators, while we do not use any extra knowledge.
+HDGAN achieves competitive results with TAC-GAN on the Oxford flower dataset. TAC-GAN uses image labels to increase the discriminability of generators, while we do not use any extra knowledge.}
 
-Table \ref{table:multiscales} quantitatively compares the the multi-resolution inception score.
+Table \ref{table:multiscales} quantitatively compares the the multi-resolution inception score on CUB.
 Our results are from the side outputs of a single model.
@@
 
-Table \ref{fig:msssmi} shows the MS-SSMI image quality evaluation score compared with StackGAN and ProgressiveGAN.
+Table \ref{fig:msssmi} shows the MS-SSMI image quality evaluation score compared with StackGAN and ProgressiveGAN on CUB.
 StackGAN and our HDGAN use the semantic text as input so the generated images retain class information.
@@
 	\end{center} \vspace{-.4cm}
-	\caption{Multi-scale inception score comparison. See text for explanation.} \label{table:multiscales}
+	\caption{Multi-scale inception score comparison. See text for explanation.} \label{table:imgloss}
 \end{table}
@@
 			&  		&	\checkmark	&	${3.52{\pm}.04}$	\\ 
-			&  	\checkmark	&	\checkmark	&		\\
+			&  	\checkmark	&	\checkmark	&	${3.99{\pm}.04}$	\\
 			\checkmark	&  			&	\checkmark	&  ${4.14{\pm}.03}$		\\

### 2017-11-10 cvpr2018.tex
vs similarity

@@
 Furthermore, this separation of the image loss from the matching loss in our method opens further possibilities, such as utilizing the unlabeled image to improve both the generator and discriminator.
-\textcolor{red}{In the spirit of variational auto-encoder \cite{} and the practice of \cite{han2017stackgan} (namely conditional augmentation), we sample the input text variable $\bm t$ from a Ganssian distribution $\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}))$, where $\mu$ and $\Sigma$ are functions of $\bm t$.
+\textcolor{red}{In the spirit of variational auto-encoder \cite{vae} and the practice of \cite{han2017stackgan} (namely conditional augmentation), we sample the input text variable $\bm t$ from a Ganssian distribution $\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}))$, where $\mu$ and $\Sigma$ are functions of $\bm t$.
 We add the Kullback-Leibler divergence regularization term, $D_{KL}(\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}) )|| \mathcal{N}(0, \bm{I}))$, to the $G$ loss to force smooth sampling over the text embedding distribution.
@@
 For CUB and oxford-102, we use the fine-tuned inception model provided by StackGAN.
-For MS COCO dataset, we directly use the model train on ImageNet.
+For MS COCO dataset, we directly use the model pre-trained on ImageNet.
 2) We also adopt the multi-scale structural similarity (MS-SSIM) metric \cite{improvedGAN} for further validation.
@@
 Lower score indicates higher variance.
-\textcolor{red}{3) Since inception score can not measure alignment between the generated images and the text description, here, we conduct a new qualitative measurement, namely neural image-sentence distance, which calculated the cosine distance between image code and the sentence vector.
-We train the model on each dataset.
-}
+
+\textbf{Visual-semantic similarity~}
+Since the aforementioned evaluation methods can not measure alignment between the generated images and the text description.
+We introduce a new qualitative measurement, namely neural visual-semantic similarity (VS similarity) \cite{vsemb}.
+Denote $\bm{v}$ as the feature vector extract by a pre-trained CNN model $f_{cnn}$ (inception v2\cite{inception} pre-trained on Imagenet), and $\bm{t}$ denote the text embedding.
+We define a scoring function $s(\bm{x}, \bm{y})=\frac{\bm{x}\cdot \bm{y}}{||\bm{x}||\cdot ||\bm{y}||}$. 
+We learn two mapping functions $f_v$ and $f_t$, which map the image and sentence embeddings into one semantic space, using the following bi-directional ranking loss:
+\begin{equation}
+\begin{split}
+\mathcal{L}_{vs} &= \sum_{ \bm{v} }\sum_{ \bm{t^-} }~\max( 0, \delta- s(f_v(\bm{v}), f_t( \bm{t^-} ))) \\
+&+ \sum_{ \bm{t} }\sum_{ \bm{v-} }~\max( 0,  \delta- s(f_t(\bm{t}), f_v( \bm{v^-} )))
+\end{split}
+\end{equation}
+where $\delta$ is the margin, which is set as 0.2, every $(\bm{v}, \bm{t})$ is a ground truth image text pair, $\bm{t^-}$ denotes a mismatching text description for the image corresponding to $v$, and vice-versa for $\bm{v^-}$.
+In the testing stage, given an text embedding $\bm{t}$, and the generated images $o$, the corresponding vs-similarity will be calculated as $s(f_{cnn}(o), \bm{t})$.
 
@@
 			$128{\times}128$             &   ${3.35{\pm}.02}$      &  $\bm{3.85{\pm}.04}$		\\
-			$256{\times}256$             &   $3.70{\pm}.04$     &	$\bm{4.01{\pm}.06}$ \\ \hline
+			$256{\times}256$             &   $3.70{\pm}.04$     &	$\bm{4.15{\pm}.05}$ \\ \hline
 		\end{tabularx}
@@
 
+\begin{table}[t] % retrieval
+	\begin{center}
+		\begin{tabularx}{.477\textwidth}{c|ccc}
+			\specialrule{1.5pt}{0pt}{0pt}  
+			\multirow{2}{*}{Method}	& \multicolumn{3}{c}{Dataset}	\\ \cline{2-4}
+						&	 CUB		&	Oxford  & COCO		     \\ \hline
+			StackGAN     &	$0.234{\pm}.167$	&	 $0.278{\pm}.134$			&  $-{\pm}-$		\\
+
+			Ground Truth	&	${0.302{\pm}.151}$	&	$ {0.336{\pm}.138}$			&  -  \\ \hline
+			HDGAN 		&	$\bm{0.259{\pm}.159}$	&	$ \bm{3.45{\pm}.07}$			&  -  \\ \hline
+		\end{tabularx} \vspace{-.4cm}
+	\end{center}
+	\caption{The visual-semantic similarity evaluation on three datasets.
+The higher score represents higher degree of matching between the generated images and the text information.
+} \label{table:score}
+\end{table}
+
 \subsubsection{What role does noise play}
@@
 	\begin{center}
-		\begin{tabularx}{.32\textwidth}{c|cc}
+		\begin{tabularx}{.36\textwidth}{c|cc}
 			\specialrule{1.5pt}{0pt}{0pt}  
-			Scale 						&   No Local 	& With Local				\\ 				\hline
-			$64{\times}64$              &   ${2.95{\pm}.02}$       &  	$\bm{3.46{\pm}.04}$ \\
-			$256{\times}256$             &   $3.70{\pm}.04$     &	$\bm{4.01{\pm}.06}$ \\ \hline
+			Metric 					&   No Local 	       &    With Local	\\  \hline
+			MS-SSMI                 &   $-$                &	$0.215$ \\  \hline
+			VS similarity           &   $-$                &	$0.259{\pm}.159$ \\ \hline
+			Inception score         &   $-$   &  	$4.15{\pm}.05$ \\
 		\end{tabularx}
 	\end{center} \vspace{-.4cm}
-	\caption{Multi-scale inception score comparison. See text for explanation.} \label{table:imgloss}
+	\caption{Results using three quantitative evaluation metrics on birds dataset.} \label{table:imgloss}
 \end{table}
@@
 			\checkmark	&  			&	\checkmark	&  ${4.14{\pm}.03}$		\\
-			\checkmark	&  \checkmark		&	\checkmark	&	${4.01{\pm}.04}$ \\
+			\checkmark	&  \checkmark		&	\checkmark	&	${4.15{\pm}.05}$ \\
 

### 2017-11-10 cvpr2018.tex
exp

@@
 \end{equation}
-where $\delta$ is the margin, which is set as 0.2, every $(\bm{v}, \bm{t})$ is a ground truth image text pair, $\bm{t^-}$ denotes a mismatching text description for the image corresponding to $v$, and vice-versa for $\bm{v^-}$.
+where $\delta$ is the margin, which is set as 0.2, every $(\bm{v}, \bm{t})$ is a ground truth image text pair, $\bm{t^-}$ denotes a mismatching text description for the image corresponding to $\bm{v}$, and vice-versa for $\bm{v^-}$.
 In the testing stage, given an text embedding $\bm{t}$, and the generated images $o$, the corresponding vs-similarity will be calculated as $s(f_{cnn}(o), \bm{t})$.
@@
 
-			HDGAN 		&	$\bm{4.01{\pm}.06}$	&	$ \bm{3.45{\pm}.07}$			&  -  \\ \hline
+			HDGAN 		&	$\bm{4.15{\pm}.05}$	&	$ \bm{3.45{\pm}.07}$			&  -  \\ \hline
 		\end{tabularx} \vspace{-.4cm}
@@
 						&	 CUB		&	Oxford  & COCO		     \\ \hline
-			StackGAN     &	$0.234{\pm}.167$	&	 $0.278{\pm}.134$			&  $-{\pm}-$		\\
+			StackGAN     &	$0.228{\pm}.162$	&	 $0.278{\pm}.134$			&  $-{\pm}-$		\\
 
 			Ground Truth	&	${0.302{\pm}.151}$	&	$ {0.336{\pm}.138}$			&  -  \\ \hline
-			HDGAN 		&	$\bm{0.259{\pm}.159}$	&	$ \bm{3.45{\pm}.07}$			&  -  \\ \hline
+			HDGAN 		&	$\bm{0.259{\pm}.159}$	&	$ \bm{-{\pm}-}$			&  -  \\ \hline
 		\end{tabularx} \vspace{-.4cm}

### 2017-11-10 cvpr2018.tex
13th

--- 2017-11-08 cvpr2018.tex
@@
 \usepackage{epstopdf}
-
+\usepackage[flushleft]{threeparttable}
 \usepackage{amsthm}
@@
 image and text) information alignment in order to guarantee semantic consistency and image fidelity simultaneously.
-With extensive experimental validation on three major datasets, our method significantly improves previous state of the arts.
+With extensive experimental validation on three major datasets, our method significantly improves previous state of the arts over all datasets on three different metrics.
 
@@
 	\includegraphics[width=0.48\textwidth]{figure/intro.pdf}
-%	\vspace{-.7cm}
+	\vspace{-.4cm}
 	\caption{Overview of our method.
-It contains a single-stream generator and several hierarchically-nested discriminators and is trained end-to-end to generate high-resolution images conditioned on a sentence.} \label{fig:archs-review} %\vspace{-.2cm}
+It contains a single-stream generator and several hierarchically-nested discriminators along the depth dimension of the generator, which are trained end-to-end to generate high-resolution images conditioned on a sentence.} \label{fig:archs-review} \vspace{-.4cm}
 \end{figure}
@@
 propose a top-down stacked GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method.
-However, this method needs multiple symmetric bottom-up discriminators and pre-training of discriminators, and the usage for high-resolution image is unclear.
+However, this method needs multiple symmetric bottom-up pre-trained discriminators and the usage for high-resolution image is unclear.
 Recently, Karras \etal \cite{Karras2017progressive} propose a progressive training of GANs for high-resolution image generation (Figure \ref{fig:archs-review} C).
-\textit{Compared with these strategies that train low- to high-resolution GANs progressively, our method has advantages of utilizing multi-level representations to encourage implicit subtask integration, which makes end-to-end high-resolution image synthesis in a single vanilla-like GAN possible.}
+\textit{Compared with these strategies that train low-to-high resolution GANs progressively, our method has advantages of utilizing multi-level representations to encourage implicit subtask integration, which makes end-to-end high-resolution image synthesis in a single vanilla-like GAN possible.}
 
@@
 \end{equation}
-where $\bm z\sim\mathcal{N}(0,1)$ denotes a random noise and $\bm t\sim p(data)$ denotes sentence embedding vector in the real training data distribution.
-$\mathcal{G}$ produces $s-1$ side size-growing image outputs and a final output $X_s$ with the highest resolution.
+where $\bm z\sim\mathcal{N}(0,1)$ denotes a random noise and $\bm t\sim p(data)$ denotes a sentence embedding vector in the real training data distribution.
+$\mathcal{G}$ produces $s-1$ side outputs (size-growing images) and a final output $X_s$ with the highest resolution.
 
@@
 Compared with Eq. (\ref{equ:GAN}), one generator competes with multiple discriminators at different hierarchies. 
-\textcolor{red}{Discriminators do not share weights with each other, which offers them flexibility to focus on learning different discriminative features.
+\textcolor{red}{Discriminators do not share weights with each other, which offers them full flexibility to focus on learning diverse discriminative features in different contextual scales.
 In principle, the lower-resolution side output is forced to learn semantic consistent image structures (e.g., object sketch, color, and background), and the subsequent higher-resolution side outputs are used to render details to the images.
 Since the model is trained in an end-to-end fashion, we can observe more consistent information exhibited in both lower and higher-resolution outputs than StackGAN \cite{han2017stackgan}.
-More results can be founded in th experiments.
-According to this principle, we present the following adversarial losses to support more effective multi-purpose discriminators.}
+More results can be founded in experiments.
+According to this goal, we present the following adversarial losses to support more effective multi-purpose discriminators.}
 
@@
 
-The pair-loss is designed to capture the global semantic context.
+The pair loss is designed to capture the global semantic context.
 However, this loss has two major weaknesses.
@@
 To guarantee image fidelity and overcome these two weaknesses, our solution is to add adaptive local adversarial image losses on image patches. The insights are two folds:
-\begin{itemize}\vspace{-.2cm}
+\begin{itemize}\vspace{-.1cm}
 \setlength\itemsep{-0.3em}
-\item Further forcing the local patch of generated samples to have similar statistics to real image patch can be beneficial for rendering fine-grained details. %
+\item Further forcing the generated samples to have only only global but also local similar statistics to real image patches, which is beneficial for rendering fine-grained details.
 
-\item \textcolor{red}{Image loss without using pair sentence information can be beneficial in the sense that it utilizes more information as well as it directly push the generated image to the true image distribution.
-We hypothesis this type of loss can help the model to stabilize and boost the training.
+\item \textcolor{red}{Image loss without using paired text can be beneficial in the sense that it focus more on image information.
+The richness of discriminator supervision usually has advantages for generalization.
 }
 \vspace{-.2cm}
+
 \end{itemize}
@@
 The adaptive local image adversarial loss is implemented as a fully CNN \cite{shrivastava2016learning,zhu2017unpaired}.  
- Figure \ref{fig:loss} illustrates how hierarchically-nested discriminators compute two losses on the generated images.
+Figure \ref{fig:loss} illustrates how hierarchically-nested discriminators measure the two losses on the generated images.
 
@@
 	\includegraphics[width=0.47\textwidth]{figure/loss.pdf}
-
+	\vspace{-.2cm}
 	\caption{Given an image in the side output pyramid of the generator, the corresponding discriminator $D_i$ computes the matching-aware pair loss and adaptive local image loss (outputting a $R{\times}R$ probability map to indicate real or fake patches).
@@
 Lower range results in finer results.
-}
+}  \vspace{-.3cm}
 	\label{fig:loss}
@@
 \textbf{Full Objective } Overall, our hierarchically-nested discriminators $\{D_i\}$ minimize the following objective\footnote{The objective of the generator is omitted as it can be easily inferred.}:
+\vspace{-.2cm}
 \begin{equation}
@@
 	\begin{center}
-		\begin{tabularx}{.477\textwidth}{c|ccc}
+		\begin{tabularx}{.4999\textwidth}{c|ccc}
 			\specialrule{1.5pt}{0pt}{0pt}  
@@
 			GAWWN 	  &		$3.60{\pm}.07$		&     -      &          - \\ 
-			StackGAN     &		$3.70{\pm}.04$	&	 $3.20{\pm}.01$			&  $8.45{\pm}.03$		\\ 
-		%	StackGAN$^\star$     &		$3.89{\pm}.05$	&	 $3.16{\pm}.01$			&  $8.45{\pm}.03$		\\ \hline
+			StackGAN     &		$3.70{\pm}.04$	&	 $3.20{\pm}.01$			&  $8.45{\pm}.03^{\star}$		\\ 
+		%%	StackGAN$^\star$     &		$3.89{\pm}.05$	&	 $3.16{\pm}.01$			&  $8.45{\pm}.03$		\\ \hline
 			StackGAN++     &		$3.84{\pm}.06$	&	 -			&  -	\\  
@@
 
-			HDGAN 		&	$\bm{4.01{\pm}.06}$	&	$ \bm{3.45{\pm}.07}$			&  -  \\ \hline
-		\end{tabularx} \vspace{-.4cm}
+			HDGAN 		&	$\bm{4.01{\pm}.06}$	&	$ \bm{3.45{\pm}.07}$			&  $\bm{11.27{\pm}.18}$  \\ \hline
+		\end{tabularx} 
 	\end{center}
+	\vspace{-.4cm}
+	\begin{tablenotes}
+		\small
+		\item $^\star$Recently, it updated to ${10.62{\pm}.19}$ in its latest github.
+	\end{tablenotes} \vspace{-.1cm}
 	\caption{The inception-score evaluation on three datasets.

### 2017-11-10 cvpr2018.tex
resolve conflicts

@@
 Lower score indicates higher variance.
-\textcolor{red}{3) Since inception score can not measure alignment between the generated images and the text description, here, we conduct a new qualitative measurement, namely neural image-sentence distance, which calculated the cosine distance between image code and the sentence vector.
-We train the model on each dataset.
-}
+
+\textbf{Visual-semantic similarity~}
+Since the aforementioned evaluation methods can not measure alignment between the generated images and the text description.
+We introduce a new qualitative measurement, namely neural visual-semantic similarity (VS similarity) \cite{vsemb}.
+Denote $\bm{v}$ as the feature vector extract by a pre-trained CNN model $f_{cnn}$ (inception v2\cite{inception} pre-trained on Imagenet), and $\bm{t}$ denote the text embedding.
+We define a scoring function $s(\bm{x}, \bm{y})=\frac{\bm{x}\cdot \bm{y}}{||\bm{x}||\cdot ||\bm{y}||}$. 
+We learn two mapping functions $f_v$ and $f_t$, which map the image and sentence embeddings into one semantic space, using the following bi-directional ranking loss:
+\begin{equation}
+\begin{split}
+\mathcal{L}_{vs} &= \sum_{ \bm{v} }\sum_{ \bm{t^-} }~\max( 0, \delta- s(f_v(\bm{v}), f_t( \bm{t^-} ))) \\
+&+ \sum_{ \bm{t} }\sum_{ \bm{v-} }~\max( 0,  \delta- s(f_t(\bm{t}), f_v( \bm{v^-} )))
+\end{split}
+\end{equation}
+where $\delta$ is the margin, which is set as 0.2, every $(\bm{v}, \bm{t})$ is a ground truth image text pair, $\bm{t^-}$ denotes a mismatching text description for the image corresponding to $\bm{v}$, and vice-versa for $\bm{v^-}$.
+In the testing stage, given an text embedding $\bm{t}$, and the generated images $o$, the corresponding vs-similarity will be calculated as $s(f_{cnn}(o), \bm{t})$.
 
@@
 			TAC-GAN	 &	-		&		$3.45{\pm}.05$		& -	\\	\hline
-
-			HDGAN 		&	$\bm{4.01{\pm}.06}$	&	$ \bm{3.45{\pm}.07}$			&  $\bm{11.27{\pm}.18}$  \\ \hline
+			HDGAN 		&	$\bm{4.15{\pm}.05}$	&	$ \bm{3.45{\pm}.07}$			&  -  \\ \hline
 		\end{tabularx} 
@@
 
+\begin{table}[t] % retrieval
+	\begin{center}
+		\begin{tabularx}{.477\textwidth}{c|ccc}
+			\specialrule{1.5pt}{0pt}{0pt}  
+			\multirow{2}{*}{Method}	& \multicolumn{3}{c}{Dataset}	\\ \cline{2-4}
+						&	 CUB		&	Oxford  & COCO		     \\ \hline
+			StackGAN     &	$0.228{\pm}.162$	&	 $0.278{\pm}.134$			&  $-{\pm}-$		\\
+
+			Ground Truth	&	${0.302{\pm}.151}$	&	$ {0.336{\pm}.138}$			&  -  \\ \hline
+			HDGAN 		&	$\bm{0.259{\pm}.159}$	&	$ \bm{-{\pm}-}$			&  -  \\ \hline
+		\end{tabularx} \vspace{-.4cm}
+	\end{center}
+	\caption{The visual-semantic similarity evaluation on three datasets.
+The higher score represents higher degree of matching between the generated images and the text information.
+} \label{table:score}
+\end{table}
+
 \subsubsection{What role does noise play}

### 2017-11-11 cvpr2018.tex
experiment

--- 2017-11-10 cvpr2018.tex
@@
 The initial learning rate is set as 0.0002 and decreased by half for every 100 epochs (30 for COCO).
-The CUB and Oxford-102 datasets are trained for 500 epochs in total (250 epochs for COCO with 4 GPUs).
+The CUB and Oxford-102 datasets are trained for 500 epochs in total (250 epochs for COCO with 4 GPUs).\textcolor{red}{flower is actually 580, maybe does not matter.}
 For the adaptive local image loss, we set $R=1$ for $64^2$ side output, $R=3$ for $128^2$ side output and $R=5$ for $256^2$ and $512^2$ outputs.
 We use 1-repeat residual block for the generator till $256^2$ resolution.
-To generate $512^2$ images, we pre-train the generator to $256^2$ for the consideration of memory saving and faster convergence.
+To generate $512^2$ images, we pre-train the generator to $256^2$ due to the limitation of GPU memory.
 We use $3$-repeat res-block followed by the stretching and linear compression layer.
-Since the $256^2$ image already decides the overall semantics and details, to encourage the $512^2$ maintain these information, we also use a reconstruction loss to self-regularize the generator in case the discriminator confuses the expected output.
+\textcolor{red}{maybe delete the l1 loss description}
+%Since the $256^2$ image already captures the overall semantics and details, to encourage the $512^2$ maintain these information, we also use a reconstruction loss to self-regularize the generator in case the discriminator confuses the expected output.
+%for the consideration of memory saving and faster convergence.
 
@@
 The CUB dataset \cite{welinder2010caltech} contains 11,788 bird images belonging to 200 different categories.
-We pre-process and split the images using the same pipeline in \cite{reed2016generative,han2017stackgan}
+We pre-process and split the images following the same pipeline in \cite{reed2016generative,han2017stackgan}
 %, which crops the bird region and ensure the foreground occupies greater than 0.75.  
@@
 }
-We use the pre-trained text encoder model provided in \cite{reed2016generative} to encode each text description of the three datasets into a 1024 vector.
+We use the pre-trained text encoder model provided in \cite{reed2016generative} to encode each text description  into a 1024 embedding vector.
 %During the training stage, we randomly pick-up a crop view from the original images, and pick 4 image sentence embedding and use the mean as conditioning vector.
@@
 Lower score indicates higher variance.
+3) Visual-semantic similarity.
 
 \textbf{Visual-semantic similarity~}
-Since the aforementioned evaluation methods can not measure alignment between the generated images and the text description.
-We introduce a new qualitative measurement, namely neural visual-semantic similarity (VS similarity) \cite{vsemb}.
+Since the aforementioned evaluation methods can not measure alignment between the generated images and the text description, we introduce a new qualitative measurement, namely visual-semantic similarity (VS similarity) \cite{vsemb}.
 Denote $\bm{v}$ as the feature vector extract by a pre-trained CNN model $f_{cnn}$ (inception v2\cite{inception} pre-trained on Imagenet), and $\bm{t}$ denote the text embedding.
 We define a scoring function $s(\bm{x}, \bm{y})=\frac{\bm{x}\cdot \bm{y}}{||\bm{x}||\cdot ||\bm{y}||}$. 
-We learn two mapping functions $f_v$ and $f_t$, which map the image and sentence embeddings into one semantic space, using the following bi-directional ranking loss:
+We learn two mapping functions $f_v$ and $f_t$, which map both image and sentence embeddings into one semantic space $\mathbb{R}^{512}$, by minimizing the following bi-directional ranking loss:
 \begin{equation}
@@
 
+Table \ref{table:vss} shows the qualitative vs-similarity comparison results on three datasets.
+We also add the evaluation results on the ground truth image and sentence pair for reference.
+Our proposed method achieves much better results on both CUB and Oxford datasets.
+Since we do not have a pre-trained  StackGAN model for coco dataset, we omit the comparison.
+This results demonstrate that HDGAN is better at capturing visual semantic correlation.
+
 \subsubsection{Style Transfer Using Sentence Interpolation}
@@
 As is shown in Figure~\ref{}, the generated images show gradual and smooth changes reflecting the semantic changing in sentences, while still maintaining plausible object pose and shape.
-In the first row, the generated birds gradually turn the color from red to yellow, in the second row, more complicated sentences containing more detailed appearance information (e.g., blue peaks, and yellow wing) are used, we can see that our model is still be able to successfully capture these subtle information and tune the bird appearance gradually.
+In the first row, the generated birds gradually turn the color from yellow to red, in the second row, more complicated sentences containing more detailed appearance information (e.g., blue peaks, and yellow wing) are used, we can see that our model is still be able to successfully capture these subtle information and tune the bird appearance gradually.
 
-We also evaluate some sentences that generated by ourself, the resulting images are shown in Figure~\ref{}, as we can see, our model are robust and generalize well to human descriptions that never seen before.
+\textcolor{red}{We also evaluate some sentences that generated by ourself, the resulting images are shown in Figure~\ref{}, as we can see, our model are robust and generalize well to human descriptions that never seen before.}
 
 \begin{table}[t] % retrieval
+	\label{table:vss}
 	\begin{center}
@@
 						&	 CUB		&	Oxford  & COCO		     \\ \hline
-			StackGAN     &	$0.228{\pm}.162$	&	 $0.278{\pm}.134$			&  $-{\pm}-$		\\
+			StackGAN     &	$.228{\pm}.162$	&	 $.278{\pm}.134$			&  $-{\pm}-$		\\
 
-			Ground Truth	&	${0.302{\pm}.151}$	&	$ {0.336{\pm}.138}$			&  -  \\ \hline
-			HDGAN 		&	$\bm{0.259{\pm}.159}$	&	$ \bm{-{\pm}-}$			&  -  \\ \hline
+			Ground Truth	&	${.302{\pm}.151}$	&	$ {.336{\pm}.138}$			&  -  \\ \hline
+			HDGAN 		&	$\bm{.246{\pm}.157}$	&	$ \bm{.296{\pm}.131}$			&  -  \\ \hline
 		\end{tabularx} \vspace{-.4cm}
 	\end{center}
-	\caption{The visual-semantic similarity evaluation on three datasets.
-The higher score represents higher degree of matching between the generated images and the text information.
-} \label{table:score}
+	\caption{The visual-semantic similarity evaluation on three datasets. The higher score represents higher degree of matching between the generated images and the text information. } 
 \end{table}
@@
 	\begin{center}
-		\begin{tabularx}{.36\textwidth}{c|cc}
-			\specialrule{1.5pt}{0pt}{0pt}  
-			Metric 					&   No Local 	       &    With Local	\\  \hline
-			MS-SSMI                 &   $-$                &	$0.215$ \\  \hline
-			VS similarity           &   $-$                &	$0.259{\pm}.159$ \\ \hline
-			Inception score         &   $-$   &  	$4.15{\pm}.05$ \\
+		\begin{tabularx}{.43\textwidth}{c|ccc}
+			\specialrule{1.1pt}{0pt}{0pt}  
+			Metric 			 		&   wo/Img 	 & w/global     &   w/local	\\  \hline
+			MS-SSMI                 &   $-$      &   $-$           &	$.215$ \\  \hline
+			VS similarity           &   $-$      &   $-$           &	$.246{\pm}.157$ \\ \hline
+			Inception score         &   $-$ 	 &   $-$		   &    $4.15{\pm}.05$ \\
 		\end{tabularx}
@@
 
-We also study the effectiveness of the proposed local image loss. We conduct experiments with using architecture with side output 64$\times$64 and 256 $\times$ 256. 
+We also study the effectiveness of the proposed local image loss. We conduct experiments with using architecture with side output 64$\times$64, 128$\times$128 and 256 $\times$ 256 using CUB dataset. 
 As can be seen in Table\ref{tab:local_loss}, we can see that by removing local image loss (denoted as "No Local"), the inception score drop from \textcolor{red}{4.27} to \textcolor{red}{3.8}.
-To quantitatively compare the results, we also show generated results using two model in Figure \ref{local_or_not}, We can see that, also both models can successfully capture the semantic correspondence between image and sentence, 256$\times$ 256 results generated by model trained with local image loss provide more details, thus improving the visual quality.
+To quantitatively compare the results, we also show generated results using two model in Figure \ref{local_or_not}, We can see that, although both models can successfully capture the semantic correspondence between image and sentence, 256$\times$ 256 results generated by model trained with local image loss provide more local fine-grained details, thus improving the visual quality.
 
@@
 \section{Conclusion}
-...
-
+In this paper, we present a novel and effective method to tackle the problem of generating high resolution images using text description.
+We introduce the hierarchical nested side outputs for deeply supervising the GAN training.
+To improve the model's capability to render fine-grained local details, we propose a hierarchal local image loss to boost the training.
+We also introduce a newly evaluation method for conditional gan, which leverage visual semantic embedding to judge the matching between generated images and provided text description, thus remove the necessary for human evaluation.
+Extensive experiment results demonstrate that our method work significantly better than existing state of the arts.
 {\small

### 2017-11-11 cvpr2018.tex

@@
 			GAWWN 	  &		$3.60{\pm}.07$		&     -      &          - \\ 
-			StackGAN     &		$3.70{\pm}.04$	&	 $3.20{\pm}.01$			&  $8.45{\pm}.03$		\\ 
-		%	StackGAN$^\star$     &		$3.89{\pm}.05$	&	 $3.16{\pm}.01$			&  $8.45{\pm}.03$		\\ \hline
+			StackGAN     &		$3.70{\pm}.04$	&	 $3.20{\pm}.01$			&  $8.45{\pm}.03^{\star}$		\\ 
+		%%	StackGAN$^\star$     &		$3.89{\pm}.05$	&	 $3.16{\pm}.01$			&  $8.45{\pm}.03$		\\ \hline
 			StackGAN++     &		$3.84{\pm}.06$	&	 -			&  -	\\  
 			TAC-GAN	 &	-		&		$3.45{\pm}.05$		& -	\\	\hline
-
 			HDGAN 		&	$\bm{4.15{\pm}.05}$	&	$ \bm{3.45{\pm}.07}$			&  -  \\ \hline
-		\end{tabularx} \vspace{-.4cm}
+		\end{tabularx} 
 	\end{center}
+	\vspace{-.4cm}
+	\begin{tablenotes}
+		\small
+		\item $^\star$Recently, it updated to ${10.62{\pm}.19}$ in its latest github.
+	\end{tablenotes} \vspace{-.1cm}
 	\caption{The inception-score evaluation on three datasets.

### 2017-11-12 cvpr2018.tex
15th

@@
 \usepackage{varwidth}
+\usepackage{wrapfig}
+\usepackage{makecell}
 
@@
 This paper presents a novel method to deal with the challenging task of generating images conditioned on semantic image descriptions.
-We propose an effective end-to-end trainable single-stream network that can generate photographic high-resolution images (up to $512^2$).
+We propose an effective end-to-end single-stream network that can generate photographic high-resolution images (up to $512^2$).
 Our method leverages the deep representations of convolutional layers and introduces accompanying hierarchical-nested adversarial games inside the network hierarchy, which regularize intermediate representations and assist training to capture the complex image statistics.
 We present an extensile network architecture to cooperate with discriminators and push generated images to high resolutions.
-We adopt a multi-purpose adversarial learning strategy at multiple nested hierarchical side outputs to encourage more effective multimodal (i.e.
-image and text) information alignment in order to guarantee semantic consistency and image fidelity simultaneously.
-With extensive experimental validation on three major datasets, our method significantly improves previous state of the arts over all datasets on three different metrics.
-
+We adopt a multi-purpose adversarial learning strategy at multiple nested hierarchical side outputs to encourage more effective image-text alignment in order to guarantee the semantic consistency and image fidelity simultaneously.
+Furthermore, we introduce a new visual-semantic similarity measure to evaluate the semantic consistency of generated images.
+With extensive experimental validation on three major datasets, our method significantly improves previous state of the arts on all datasets over different evaluation metrics. 
 \end{abstract}
@@
 \section{Introduction}
-Photographic text-to-image synthesis is a significant problem in generative model research \cite{reed2016generative}.
-However, insufficient methods have been developed to successfully address this task due to its particular challenges.
-It is a special case of generative learning tasks, which aim to map a low-dimensional embedding to a complex RGB image space.
+Photographic text-to-image synthesis is a significant problem in generative model research \cite{reed2016generative}, which aims to learn a translation from a semantic text embedding space to a complex RGB image space.
+This task requires the generated images to be \textit{semantically consistent}, i.e., the generated images not only preserve sketch concepts in descriptions but also fine-grained descriptive details in image pixels.
+However, insufficient methods are developed to successfully address this task due to its particular challenges.
+
+%It is a special case of generative learning tasks, which aim to map a low-dimensional embedding to a complex RGB image space.
 Differently, the embedding space of the former is induced by semantic descriptions.
@@
 \begin{figure}[t]
+%	\begin{center}
 	\centering
-	\includegraphics[width=0.48\textwidth]{figure/intro.pdf}
-	\vspace{-.4cm}
-	\caption{Overview of our method.
-It contains a single-stream generator and several hierarchically-nested discriminators along the depth dimension of the generator, which are trained end-to-end to generate high-resolution images conditioned on a sentence.} \label{fig:archs-review} \vspace{-.4cm}
+	\begin{subfigure}[t]{0.5\textwidth}
+	%	\centering
+		\includegraphics[width=0.95\textwidth]{figure/intro.pdf}
+	\end{subfigure} \\
+\centering
+	\begin{subfigure}[t]{0.5\textwidth}
+	%	\centering
+		\includegraphics[width=0.95\textwidth,height=0.55\textwidth]{figure/single_view.pdf}
+	\end{subfigure}
+	\vspace{-.6cm}
+	\caption{Top: Overview of our hierarchically-nested adversarial network. Bottom: Two fine-grained sample results. \label{fig:intro}} 	\vspace{-.3cm}
+	%\end{center}
 \end{figure}
 
+%\begin{figure}[t]
+%	\centering
+%	\includegraphics[width=0.4\textwidth]{figure/intro.pdf}
+%	\vspace{-.3cm}
+%	\caption{Overview of our hierarchically-nested adversarial network.
+It contains a single-stream generator and several nested discriminators along the depth dimension of the generator, which can generate high-resolution images conditioned on a sentence.} \label{fig:archs-review} \vspace{-.3cm}
+%\end{figure}
+%\begin{figure}[t]
+%	\centering
+%	\includegraphics[width=0.4\textwidth]{figure/single_view.pdf}
+%	\vspace{-.3cm}
+%	\caption{Overview of our hierarchically-nested adversarial network.
+It contains a single-stream generator and several nested discriminators along the depth dimension of the generator, which can generate high-resolution images conditioned on a sentence.} \label{fig:archs-review} \vspace{-.3cm}
+%\end{figure}
 Generative adversarial networks (GANs) have become the main solution to this task. 
@@
 But its high-resolution synthesis ability is unclear.
-At present, how to train from the low-dimensional text space to synthesize high-resolution and diverse images in an end-to-end manner is still an open and attractive question.
+At present, how to train from the low-dimensional text space to synthesize high-resolution and diverse images in an fully end-to-end manner is still an open and attractive question.
 
@@
 %How to utilize the multimodal information between images and text in discriminator is extremely important to generate effective gradients.
-The second is the huge pixel space in high-resolution images \cite{han2017stackgan}. 
+The second is stably modeling the huge pixel space in high-resolution images \cite{han2017stackgan}. 
 An effective strategy to regularize generators is critical to help capture the complex image statistics \cite{huang2016stacked} as well as guarantee semantic consistency. 
@@
 Keeping semantic consistency as well as diversity in generated images needs more specialized designs for discriminators to generate effective gradients, as well as generators to prevent gradient vanishing.
-With careful consideration of these outlined problems, in this paper, we propose a novel fully end-to-end method that can directly model high-resolution image statistics and generate semantic consistent and photographic image up to $512^2$ resolution.
+With careful consideration of these problems, in this paper, we propose a novel end-to-end method that can directly model high-resolution image statistics and generate semantically consistent and photographic image (see Figure \ref{fig:intro}).
 The contributions are described as follows.
@@
 We introduce accompanying hierarchically-nested objectives at multi-scale intermediate layers to play adversarial games and thereby encourage the generator approaching the real training data distribution.
-We also propose a novel generator convolutional neural network (CNN) framework to cooperate with our nested discriminators more effectively.
-To better make use of image and text information in GAN training, 
-\textcolor{red}{we enforce nested discriminators at different hierarchies can simultaneously differentiate real-and-fake image-text pairs as well as real-and-fake whole images or image patches.}
-This multi-purpose conditional adversary is mutually beneficial to allow each only focuses on its respect duties. 
-%It is a regularization to limit the discriminators to use unexpected information to make decision.
+We also propose a novel convolutional neural network (CNN) framework for the generator to cooperate with our nested discriminators more effectively.
+To guarantee the image diversity and semantic consistency,
+\textcolor{red}{we enforce nested discriminators at different hierarchies to simultaneously differentiate real-and-fake image-text pairs as well as real-and-fake global images or local image patches with certain focal ranges.}
+This multi-purpose conditional adversary is mutually beneficial to allow each focus on its respect duty. 
+%% It is a regularization to limit the discriminators to use unexpected information to make decision.
 
 We validate our proposed method on three datasets, CUB birds \cite{welinder2010caltech}, Oxford-102 flowers \cite{Nilsback08}, and large-scale MSCOCO \cite{lin2014microsoft}.
-Extensive experimental results and analysis demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts.
+In complement of the image diversity evaluation metric (inception score \cite{improvedGAN}), we introduce a new visual-semantic similarity measurement to evaluate th alignment between generated images and corresponded text.
+Extensive experimental results and analysis demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts on three metrics.
 All source code will be released.
@@
 	\caption{Overviews of some typical GAN frameworks.
-\textbf{A} decomposes tasks multi-stage GANs \cite{han2017stackgan,denton2015deep}.
+\textbf{A} uses multi-stage GANs \cite{han2017stackgan,denton2015deep}.
 \textbf{B} uses multiple discriminators with one generator \cite{durugkar2016generative,tu_etal_nips17_d2gan}.
@@
 StackGAN \etal \cite{han2017stackgan} propose a two-stage stacking GAN training approach that is able to generate $256^2$ compelling results.
-Recently, Dong \etal \cite{dong2017semantic} propose to learn a joint embedding of images and text so as to re-render a prototype image conditioned on targeting descriptions.
+Recently, Dong \etal \cite{dong2017semantic} propose to learn a joint embedding of images and text so as to re-render a prototype image conditioned on a targeting description.
 Cha \etal \cite{char2017perceptual} explore the usage of the perceptional loss with a CNN pretrained on ImageNet \cite{johnson2016perceptual} and Dash \etal \cite{dash2017tac} make use of auxiliary classifiers (similar with \cite{odena2016conditional}) to assist GAN training for text-to-image synthesis.
@@
 To synthesize high-resolution images, cascade networks are useful to decompose original difficult tasks to multiple subtasks (Figure \ref{fig:archs-review} A).
-Denton \etal \cite{denton2015deep} train a cascade of GANs within a Laplacian pyramid framework (LAPGAN) and use each to generate difference images, conditioned on random noises and the output from last level of the pyramid, and push up the output resolution through by-stage refinement.
+Denton \etal \cite{denton2015deep} train a cascade of GANs within a Laplacian pyramid framework (LAPGAN) and use each to generate difference images, conditioned on random noises and the output from the last pyramid level, and thereby push up the output resolution through by-stage refinement.
 StackGAN also shares similar strategy with LAPGAN.
@@
 However, this method needs multiple symmetric bottom-up pre-trained discriminators and the usage for high-resolution image is unclear.
-Recently, Karras \etal \cite{Karras2017progressive} propose a progressive training of GANs for high-resolution image generation (Figure \ref{fig:archs-review} C).
-\textit{Compared with these strategies that train low-to-high resolution GANs progressively, our method has advantages of utilizing multi-level representations to encourage implicit subtask integration, which makes end-to-end high-resolution image synthesis in a single vanilla-like GAN possible.}
+Recently, Karras \etal \cite{Karras2017progressive} propose a progressive training of GANs for very high-resolution image generation (Figure \ref{fig:archs-review} C).
+\textit{Compared with these strategies that train low-to-high resolution GANs progressively, our method has advantages of leveraging multi-level representations to encourage implicit subtask integration, which makes end-to-end high-resolution image synthesis in a single vanilla-like GAN possible.}
 
@@
 DSN \cite{lee2015deeply} proposes deep supervision in hierarchical convolutional layers to increase the discriminativeness of feature representations.
-\textit{Our hierarchically-nested adversarial objective is inspired by CNNs with deep supervision \cite{lee2015deeply,xie2015holistically}. }
+\textit{Our hierarchically-nested adversarial objective is inspired by these kinds of CNNs with deep supervision. }
 %Our proposed hierarchically-nested adversarial supervision enhances layer representations to support final high resolution outputs.
@@
 \begin{split}
-G^*, D^* = \arg~\underset{G}{\min}\ \underset{D}{\max}~ \mathcal{L}(D, G)
+G^*, D^* = \arg~\underset{G}{\min}\ \underset{D}{\max}~ \mathcal{L}(D, G, Y, \bm z)
 \end{split}
 \end{equation}
-where the loss $\mathcal{L}$ aims to minimize the Jensen-Shannon divergence between the data and model distributions.
+\textcolor{red}{where $Y$ denotes training images and $\bm z\sim\mathcal{N}(0,1)$ denotes a random noise.
+The loss $\mathcal{L}$ aims to minimize the Jensen-Shannon divergence between the data and model distributions.
+}
 
@@
 %Directly predicting high resolution synthesized images are challenging, not only because of the difficulties in training but also due to the large variation and instability in the hidden layers.
-Numerous methods have demonstrated a variety of ways to build GANs for image synthesis. Figure \ref{fig:archs-review} and Section 2 discuss some typical frameworks.
-Our method explores a new dimension of playing this adversarial game along the depth of a CNN (Figure \ref{fig:archs-review} D), which integrates additional discriminators at mid-level features to learn a stronger generator $\mathcal{G}$.
+Numerous methods have demonstrated ways to unite generators and discriminators for image synthesis. Figure \ref{fig:archs-review} and Section 2 discuss some typical frameworks.
+Our method actually explores a new dimension of playing this adversarial game along the depth of a CNN (Figure \ref{fig:archs-review} D), which integrates additional discriminators at mid-level features of the generator $\mathcal{G}$.
 The hierarchically-nested objectives 
@@
 \end{equation}
-where $\bm z\sim\mathcal{N}(0,1)$ denotes a random noise and $\bm t\sim p(data)$ denotes a sentence embedding vector in the real training data distribution.
+where  $\bm t\sim p(data)$ denotes a sentence embedding vector in the real training data distribution (generated by a text character encoder).
 $\mathcal{G}$ produces $s-1$ side outputs (size-growing images) and a final output $X_s$ with the highest resolution.
@@
 
-For each side output $X_i$, we propose to apply a discriminator $D_i$ to perform independently adversarial games. Therefore, our full min-max objective can be defined as follows: 
+For each side output $X_i$, we propose to apply a discriminator $D_i$ to perform independently adversarial games. Therefore, our full min-max objective is defined as follows: 
 \begin{equation}
@@
 \end{equation}
-where $ \mathcal{Y}$ denotes training images at multi-scales, $\{1,...,s\}$.
+where $ \mathcal{Y}$ denotes a set of training images at multi-scales, $\{1,...,s\}$.
 %where $\mathcal{D}$ contains the optimal discriminators $\{D_1^*, ..., D_o^*\}$, and $ \mathcal{L}(G,\mathcal{D}, \bm{X}, \bm{T} )$ is the full objective of this mini-max game.
 %Please note that in this setting, 
-Compared with Eq. (\ref{equ:GAN}), one generator competes with multiple discriminators at different hierarchies. 
+Compared with Eq. (\ref{equ:GAN}), one generator competes with multiple discriminators at different hierarchies (Figure \ref{fig:archs-review} D). 
 \textcolor{red}{Discriminators do not share weights with each other, which offers them full flexibility to focus on learning diverse discriminative features in different contextual scales.
 In principle, the lower-resolution side output is forced to learn semantic consistent image structures (e.g., object sketch, color, and background), and the subsequent higher-resolution side outputs are used to render details to the images.
-Since the model is trained in an end-to-end fashion, we can observe more consistent information exhibited in both lower and higher-resolution outputs than StackGAN \cite{han2017stackgan}.
+Since the model is trained in an end-to-end fashion, we can obtain more consistent information exhibited in both lower and higher-resolution outputs compared with StackGAN.
 More results can be founded in experiments.
@@
 
-\subsection{Functional adaptive adversarial losses}
+\subsection{Functional adversarial losses}
 Our generator produces size-growing side outputs which compose an image pyramid. 
@@
 To guarantee semantic consistency, we adopt the matching-aware pair loss proposed by \cite{reed2016generative}.
-The discriminator is designed to take image-text pairs as inputs and trained to identify two types of errors: real image with mismatch conditional text information and fake image with real text.
+The discriminator is designed to take image-text pairs as inputs and is trained to identify two types of fakes: real image with mismatched text and fake image with conditioned text.
 
@@
 
-To guarantee image fidelity and overcome these two weaknesses, our solution is to add adaptive local adversarial image losses on image patches. The insights are two folds:
+To guarantee image fidelity and overcome these two weaknesses, our solution is to add local adversarial image losses on image patches. The insights are two folds:
 \begin{itemize}\vspace{-.1cm}
@@
 We expect the low-resolution discriminator to focus on global structures, while high-resolution outputs focus more on local image details.
-Therefore, through the pyramid of the size-growing side outputs, we configure the focal range (the size of each non-overlapping image patch) to be also growing.
-The adaptive local image adversarial loss is implemented as a fully CNN \cite{shrivastava2016learning,zhu2017unpaired}.  
+Therefore, through the pyramid of the size-growing side outputs, we configure the focal range (the size of each non-overlapping image patch need to classify) to be also growing.
+The local image adversarial loss is implemented as a fully CNN \cite{shrivastava2016learning,zhu2017unpaired}.  
 Figure \ref{fig:loss} illustrates how hierarchically-nested discriminators measure the two losses on the generated images.
@@
 	\centering
-	\includegraphics[width=0.47\textwidth]{figure/loss.pdf}
+	\includegraphics[width=0.49\textwidth]{figure/loss.pdf}
 	\vspace{-.2cm}
@@
 Furthermore, this separation of the image loss from the matching loss in our method opens further possibilities, such as utilizing the unlabeled image to improve both the generator and discriminator.
-\textcolor{red}{In the spirit of variational auto-encoder \cite{vae} and the practice of \cite{han2017stackgan} (namely conditional augmentation), we sample the input text variable $\bm t$ from a Ganssian distribution $\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}))$, where $\mu$ and $\Sigma$ are functions of $\bm t$.
-We add the Kullback-Leibler divergence regularization term, $D_{KL}(\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}) )|| \mathcal{N}(0, \bm{I}))$, to the $G$ loss to force smooth sampling over the text embedding distribution.
+\textcolor{red}{In the spirit of variational auto-encoder \cite{vae} and the practice of \cite{han2017stackgan}, namely conditional augmentation (CA), we sample the input text variable $\bm t$ from a Ganssian distribution $\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}))$, where $\mu$ and $\Sigma$ are functions of $\bm t$, which produces a $256$-d text input used as the input of the generator.
+We add the Kullback-Leibler divergence regularization term, $D_{KL}(\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}) )|| \mathcal{N}(0, \bm{I}))$ \cite{vae}, to the $G$ loss to force the smooth sampling over the text embedding distribution.
 }
@@
 %, whose compact design enforces feature maps in conv blocks can linearly represent RGB images at arbitrary scales.
-Starting from a $1024{\times}4{\times}4$ embeddings replicated by a $1024$-d text embedding, the generator simples use $M$ $K$-repeat res-blocks connected by $M{-}1$ in-between stretching layers until the feature maps reach to the targeting resolution.
+Starting from a $1024{\times}4{\times}4$ embedding, which are computed by the CA output followed by a trainable embedding matrix, the generator simples use $M$ $K$-repeat res-blocks connected by $M{-}1$ in-between stretching layers until the feature maps reach to the targeting resolution.
 So for $256{\times}256$ resolution with $K{=}1$, there are $M{=}6$ $1$-repeat res-blocks and $5$ stretching layers. 
@@
 There are two branches are added on the upper layer for the proposed functional discriminator design (see next section).
-One is a direct fully convolutional layers to produce a $R{\times}R$ probability map (see Figure \ref{fig:loss}) and classify each location as real or fake.
-Another one first concatenate $128{\times}4{\times}4$ text embedding (replicated from a $128$-d text embedding).
-Then we use an $1{\times}1$ conv to fuse text and image information and  a $4{\times}4$ conv layer to classify the the pair is real or fake.
+One branch is a direct fully convolutional layers to produce a $R{\times}R$ probability map (see Figure \ref{fig:loss}) and classify each location as real or fake.
+Another branch first concatenates a $128{\times}4{\times}4$ text embedding (replicated by a reduced $128$-d text embedding).
+Then we use an $1{\times}1$ conv to fuse text and image information and  a $4{\times}4$ conv layer to classify the image-text pair is real or fake.
 %it is critical to guarantee the semantic consistency in the final results.
 
-\textcolor{red}{All intermediate conv layers for both generators and discriminators use $3{\times}3$ kernels (with reflection padding and no bias).
+\textcolor{red}{All other intermediate conv layers for both generators and discriminators use $3{\times}3$ kernels (with reflection padding).
 We also experimented other normalization (i.e.
@@
 The initial learning rate is set as 0.0002 and decreased by half for every 100 epochs (30 for COCO).
-The CUB and Oxford-102 datasets are trained for 500 epochs in total (250 epochs for COCO with 4 GPUs).\textcolor{red}{flower is actually 580, maybe does not matter.}
+The CUB and Oxford-102 datasets are trained for 500 epochs in total (250 epochs for COCO).
 For the adaptive local image loss, we set $R=1$ for $64^2$ side output, $R=3$ for $128^2$ side output and $R=5$ for $256^2$ and $512^2$ outputs.
 We use 1-repeat residual block for the generator till $256^2$ resolution.
-To generate $512^2$ images, we pre-train the generator to $256^2$ due to the limitation of GPU memory.
+\textcolor{red}{To generate $512^2$ images, we pre-train the generator to $256^2$ due to the limitation of GPU memory.
 We use $3$-repeat res-block followed by the stretching and linear compression layer.
-\textcolor{red}{maybe delete the l1 loss description}
-%Since the $256^2$ image already captures the overall semantics and details, to encourage the $512^2$ maintain these information, we also use a reconstruction loss to self-regularize the generator in case the discriminator confuses the expected output.
+maybe delete the l1 loss description.
+Since the $256^2$ image already captures the overall semantics and details, to encourage the $512^2$ maintain these information, we also use a reconstruction loss to self-regularize the generator in case the discriminator confuses the expected output.}
 %for the consideration of memory saving and faster convergence.
@@
 This section evaluates the proposed method both qualitatively and quantitatively on three public datasets.
-We denote our method as \textbf{HDGAN}, referring as High-definition results as well as the idea of Hierarchically-nested Discriminators.
+We denote our method as \textbf{HDGAN}, referring as High-Definition results and the idea of Hierarchically-nested Discriminators.
 
 \textbf{Dataset} 
-\textcolor{red}{We evaluate our method extensively using three widely used datasets.
+\textcolor{red}{We test on three widely used datasets.
 The CUB dataset \cite{welinder2010caltech} contains 11,788 bird images belonging to 200 different categories.
@@
 \textbf{Visual-semantic similarity~}
-Since the aforementioned evaluation methods can not measure alignment between the generated images and the text description, we introduce a new qualitative measurement, namely visual-semantic similarity (VS similarity) \cite{vsemb}.
-Denote $\bm{v}$ as the feature vector extract by a pre-trained CNN model $f_{cnn}$ (inception v2\cite{inception} pre-trained on Imagenet), and $\bm{t}$ denote the text embedding.
+\textcolor{red}{Since the aforementioned evaluation methods can not measure alignment between the generated images and the text description, we introduce a new qualitative measurement, namely visual-semantic similarity (VS similarity) inspired by \cite{vsemb}.} Denote $\bm{v}$ as the feature vector extract by a pre-trained CNN model $f_{cnn}$ (Inception-v2 \cite{inception} pre-trained on Imagenet), and $\bm{t}$ denote the text embedding.
 We define a scoring function $s(\bm{x}, \bm{y})=\frac{\bm{x}\cdot \bm{y}}{||\bm{x}||\cdot ||\bm{y}||}$. 
@@
 In the testing stage, given an text embedding $\bm{t}$, and the generated images $o$, the corresponding vs-similarity will be calculated as $s(f_{cnn}(o), \bm{t})$.
+Higher score indicates semantic consistency.
 
@@
 	\begin{center}
-		\begin{tabularx}{.4999\textwidth}{c|ccc}
+		\small 
+		\begin{tabularx}{.466\textwidth}{c|ccc}
+
 			\specialrule{1.5pt}{0pt}{0pt}  
@@
 			TAC-GAN	 &	-		&		$3.45{\pm}.05$		& -	\\	\hline
-			HDGAN 		&	$\bm{4.15{\pm}.05}$	&	$ \bm{3.45{\pm}.07}$			&  -  \\ \hline
+			HDGAN 		&	$\bm{4.15{\pm}.05}$	&	$ \bm{3.45{\pm}.07}$			&  $ \bm{11.29{\pm}.18}$  \\ \hline
 		\end{tabularx} 
@@
 		\small
-		\item $^\star$Recently, it updated to ${10.62{\pm}.19}$ in its latest github.
+		\item $^\star$Recently, it updated to ${10.62{\pm}.19}$ in its source code.
 	\end{tablenotes} \vspace{-.1cm}
@@
 %	\begin{center}
-%		\begin{tabularx}{.42\textwidth}{c|ccc}
+%		\begin{tabularx}{.32\textwidth}{c|cc}
 %			\specialrule{1.5pt}{0pt}{0pt}
-%			Scale 						& StackGAN & HDGAN & HR Test					\\ 				\hline
-%            $64{\times}64$              &   ${2.95{\pm}.02}$       &  	$\bm{3.46{\pm}.04}$ &  ${3.46{\pm}.04}$	\\
-%           $128{\times}128$             &   ${3.35{\pm}.02}$      &  $\bm{3.85{\pm}.04}$	& ${3.45{\pm}.04}$	\\
-%           $256{\times}256$             &   $3.70{\pm}.04$     &	$\bm{4.01{\pm}.06}$ & ${3.46{\pm}.04}$ \\ \hline
+%			Scale 						& StackGAN & HDGAN 					\\ 				\hline
+%			$64{\times}64$              &   ${2.95{\pm}.02}$       &  	$\bm{3.53{\pm}.03}$ \\
+%			$128{\times}128$             &   ${3.35{\pm}.02}$      &  $\bm{3.97{\pm}.03}$		\\
+%			$256{\times}256$             &   $3.70{\pm}.04$     &	$\bm{4.15{\pm}.05}$ \\ \hline
 %		\end{tabularx}
 %	\end{center} \vspace{-.4cm}
-%	\caption{Scale accuracy \textcolor{red}{changing to figure is better}.} \label{table:multiscales}
+%	\caption{Multi-scale inception score comparison. See text for explanation.} \label{table:multiscales}
 %\end{table}
+
+\begin{figure*}[t]
+	\centering
+	\includegraphics[width=0.99\textwidth]{figure/cub.pdf}
+	\vspace{-.2cm}
+	\caption{The generated images on CUB compared with StackGAN.
+Each sample shows the input text and generated $64^2$ (left) and $256^2$ (right) images.
+Our results have significantly higher quality and preserve more semantic details, for example, ``the brown and white feathers and read head'' in the last column is much better reflected in our images.
+Moreover, we observed our birds have more diverse poses (e.g.
+the frontal view in the the second and the back view forth columns).}
+	\vspace{-0.2cm}
+	\label{fig:vis-cub}
+\end{figure*}
+\begin{figure*}[t]
+	\centering
+	\includegraphics[width=0.99\textwidth]{figure/flowers.pdf}
+	\vspace{-.2cm}
+	\caption{The generated images on Oxford compared with StackGAN.
+Each sample shows the input text and generated $64^2$ (left) and $256^2$ (right) images.
+Our generated images perform more natural satisfiability and higher contrast.} \label{fig:vis-oxford}
+	\vspace{-.2cm}
+\end{figure*}
+
 \begin{table}[t] % retrieval
+	\small
 	\begin{center}
-		\begin{tabularx}{.32\textwidth}{c|cc}
+		\begin{tabularx}{.435\textwidth}{c|ccc}
 			\specialrule{1.5pt}{0pt}{0pt}  
-			Scale 						& StackGAN & HDGAN 					\\ 				\hline
-			$64{\times}64$              &   ${2.95{\pm}.02}$       &  	$\bm{3.46{\pm}.04}$ \\
-			$128{\times}128$             &   ${3.35{\pm}.02}$      &  $\bm{3.85{\pm}.04}$		\\
-			$256{\times}256$             &   $3.70{\pm}.04$     &	$\bm{4.15{\pm}.05}$ \\ \hline
+			\multirow{2}{*}{Method}	& \multicolumn{3}{c}{Dataset}	\\ \cline{2-4}
+			&	 CUB		&	Oxford  & COCO		     \\ \hline
+			StackGAN     &	$.228{\pm}.162$	&	 $.278{\pm}.134$			&  $-{\pm}-$		\\
+
+			Ground Truth	&	${.302{\pm}.151}$	&	$ {.336{\pm}.138}$			&  -  \\ \hline
+			HDGAN 		&	$\bm{.246{\pm}.157}$	&	$ \bm{.296{\pm}.131}$			&  -  \\ \hline
 		\end{tabularx} 
-	\end{center} \vspace{-.4cm}
-	\caption{Multi-scale inception score comparison. See text for explanation.} \label{table:multiscales}
+	\end{center}
+	\vspace{-.4cm}
+	\caption{The VS similarity evaluation on three datasets. The higher score represents higher semantic consistency between the generated images and the text information. } \label{table:vss}
 \end{table}
-\begin{figure}[t]
+
+\subsection{Comparative Results}
+To validate our method, we compare our results with GAN-INT-CLS \cite{reed2016generative}, GAWWN \cite{reed2016learning}, TAC-GAN \cite{dash2017tac}, StackGAN \cite{han2017stackgan} and also its improved version StackGAN++ \cite{han2017stackganv2}, and Progressive GAN \cite{Karras2017progressive} \footnote{StackGAN++ and Prog.GAN are two very recently released preprints we noticed.
+We acknowledge them as they also target at generating high-resolution images, in spite of their differences in motivations and network and training designs from ours.
+} We especially compare with the current state of the art, StackGAN (results are obtained from its provided model).
+
+% Similarly with our HDGAN, it now can train $64{-}256$ directly.
+Each generator still take images from the bottom generator and supervised by a discriminator.
+Differently, our network is more like a simple Vanilla network (or a pure inverse ImageNet CNN).}.
+
+%StackGAN \cite{han2017stackgan} generates synthetic images up to $256{\times}256$ resolution. We show that our method can generates images up to $512{\times}512$.
+
+Table \ref{table:score} shows the quantitative inception-score evaluation. We follow StackGAN to sample ${~}30,000$ images for evaluation.
+HDGAN achieves significantly improvement compared against other methods. For example, it improves StackGAN by $.45$ and StackGAN++ by $.31$ on CUB.
+HDGAN achieves competitive results with TAC-GAN on Oxford.
+TAC-GAN uses image labels to increase the discriminability of generators, while we do not use any extra knowledge.
+Figure \ref{fig:vis-cub} and Figure \ref{fig:vis-oxford} show the results compared with StackGAN and strongly demonstrate the superiority of HDGAN.
+Mover, we also qualitatively test the diversity of samples conditioned on the same text in Figure \ref{fig:multiple-test} left.
+It also demonstrates how well the model learned to cover the input distribution.
+HDGAN shows obvious more successful samples than StackGAN.
+
+Table \ref{table:vss} shows the qualitative vs-similarity comparison results on three datasets.
+We also add the evaluation results on the ground truth image and sentence pair for reference.
+Our proposed method achieves much better results on both CUB and Oxford datasets.
+Since we do not have a pre-trained  StackGAN model for coco dataset, we omit the comparison.
+This results demonstrate that HDGAN is better at capturing visual semantic correlation.
+
+%\begin{figure}[t]
+%	\centering
+%	\includegraphics[width=0.499\textwidth]{figure/multisample_cub.pdf}
+%	\caption{Results on Oxford} \label{fig:multires-cub}
+%\end{figure}
+
+\begin{figure*}[t]
+	%	\begin{center}
 	\centering
-	%	\includegraphics[width=0.48\textwidth]{}
-	\caption{Results on CUB} \label{fig:vis-cub}
-\end{figure}
-\begin{figure}[t]
-	\centering
-	%	\includegraphics[width=0.48\textwidth]{}
-	\caption{Results on Oxford} \label{fig:vis-oxford}
-\end{figure}
+	\begin{subfigure}[t]{0.69\textwidth}
+		%	\centering
+		\includegraphics[width=0.99\textwidth]{figure/multisample_cub.pdf}
+	\end{subfigure} 
+	\begin{subfigure}[t]{0.3\textwidth}
+		%	\centering
+		\includegraphics[width=0.99\textwidth]{figure/cub_multires.pdf}
+	\end{subfigure}
+	\vspace{-.2cm}
+	\caption{Left: Diversity test given a single input text.
+HDGAN (top) show obviously more details and higher diversity.
+Right: Side outputs of HDGAN with increasing resolutions.
+Different resolutions are semantically consistent and semantic details emerges as resolution increases.
+\label{fig:multiple-test}} 	\vspace{-.3cm}
+	%\end{center}
+\end{figure*}
 
@@
 			Prog.GAN &   0.225    \\ \hline
-			HDGAN    &   \textbf{0.215}    \\
+			HDGAN    &   \textbf{0.215}    \\ \hline
 		\end{tabularx}
@@
 Right: Overall (no class-wise) score evaluation.} \label{fig:msssmi}
+	\vspace{-0.4cm}
 \end{table}
 
-\subsection{Comparative Results}
-To validate our method, we compare our results with GAN-INT-CLS \cite{reed2016generative}, GAWWN \cite{reed2016learning}, TAC-GAN \cite{dash2017tac}, StackGAN \cite{han2017stackgan} and also its improved version StackGAN++ \cite{han2017stackganv2}, and Progressive GAN \cite{Karras2017progressive} \footnote{StackGAN++ and Prog.GAN are two very recently released preprints we noticed.
-We acknowledge them as they also target at generating high-resolution images, in spite of their differences in motivations and network and training designs from ours.
-}
-
-% Similarly with our HDGAN, it now can train $64{-}256$ directly.
-Each generator still take images from the bottom generator and supervised by a discriminator.
-Differently, our network is more like a simple Vanilla network (or a pure inverse ImageNet CNN).}.
-
-%StackGAN \cite{han2017stackgan} generates synthetic images up to $256{\times}256$ resolution. We show that our method can generates images up to $512{\times}512$.
-
-\textcolor{red}{Table \ref{table:score} shows the quantitative inception-score evaluation. We follow StackGAN to sample ${~}30,000$ images for evaluation.
-HDGAN achieves significantly improvement compared to other methods.
-For example, HDGAN improves GAN-INT-CLS by ${\sim}30.1\%$  and ${\sim}8.4\%$ on CUB.
-It also significantly outperforms StackGAN StackGAN++.
-HDGAN achieves competitive results with TAC-GAN on the Oxford flower dataset. TAC-GAN uses image labels to increase the discriminability of generators, while we do not use any extra knowledge.}
-
-Table \ref{table:multiscales} quantitatively compares the the multi-resolution inception score on CUB.
-Our results are from the side outputs of a single model.
-Usually higher resolution images gives rise to better inception score since they contain details.
-As can be observed, our $64^2$ images outperforms $128^2$ images of StackGAN and our $128^2$ images outperforms $256^2$ images of StackGAN substantially.
-
-Table \ref{fig:msssmi} shows the MS-SSMI image quality evaluation score compared with StackGAN and ProgressiveGAN on CUB.
+Table \ref{fig:msssmi} shows the MS-SSMI image quality evaluation score compared with StackGAN and Prog.GAN on CUB.
 StackGAN and our HDGAN use the semantic text as input so the generated images retain class information.
-We compare the score with StackGAN using the provided pretrained model).
+We compare the score with StackGAN.
 We randomly sample ${~}20,000$ image pairs (400 per class) and show the class-wise score in the left figure.
-HDGAN shows better performance in majority of classes and also has lower inter-class standard divition (0.023 vs.
-0.032).
+HDGAN wins in majority of classes and also has lower inter-class standard deviation ($.023$ vs.
+$.032$).
 Prog.GAN takes noises rather than text.
@@
 
-Table \ref{table:vss} shows the qualitative vs-similarity comparison results on three datasets.
-We also add the evaluation results on the ground truth image and sentence pair for reference.
-Our proposed method achieves much better results on both CUB and Oxford datasets.
-Since we do not have a pre-trained  StackGAN model for coco dataset, we omit the comparison.
-This results demonstrate that HDGAN is better at capturing visual semantic correlation.
+\begingroup
+\setlength{\intextsep}{-4pt}%
+\setlength{\columnsep}{0pt}%
+\begin{wrapfigure}{r}{0.24\textwidth}
+	\centering
+	\includegraphics[width=0.245\textwidth]{figure/multiscale_inception.pdf}
+	\vspace{-12pt}
+\end{wrapfigure}
+%Table \ref{table:multiscales}
+The right figure compares the the multi-resolution inception score on CUB.
+Our results are from the side outputs of a single model.
+As can be observed, our $64^2$ images outperforms $128^2$ images of StackGAN and our $128^2$ images outperforms $256^2$ images of StackGAN substantially.
+It strongly demonstrates our HDGAN better preserves semantically consistent information in all resolutions.
+Figure \ref{fig:multiple-test} qualitatively validate this property.
 
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=0.48\textwidth]{figure/interp.pdf}
+	\vspace{-.5cm}
+	\caption{Text embedding interpolation from the source to target sentence results in smooth image changes approaching the targeting sentence. } \label{fig:interp}
+	\vspace{-.3cm}
+\end{figure}
 \subsubsection{Style Transfer Using Sentence Interpolation}
 
-Ideally, a trained model should learn a smooth linear latent manifold of the images.
-To demonstrate our model's generalization capability, we generate images using the linearly interpolated  embedding using two source sentences.
+\textcolor{red}{Ideally, a well trained model should learn a smooth linear latent manifold of the images.
+To demonstrate our model's generalization capability, we generate images using the linearly interpolated embeddings between two source sentences.
 During this experiment, we fix the all the random noises to make the object and background consistent.
-As is shown in Figure~\ref{}, the generated images show gradual and smooth changes reflecting the semantic changing in sentences, while still maintaining plausible object pose and shape.
-In the first row, the generated birds gradually turn the color from yellow to red, in the second row, more complicated sentences containing more detailed appearance information (e.g., blue peaks, and yellow wing) are used, we can see that our model is still be able to successfully capture these subtle information and tune the bird appearance gradually.
+As is shown in Figure~\ref{fig:interp}, the generated images show gradual and smooth changes reflecting the semantic changing in sentences, while still maintaining plausible object pose and shape.
+In the first row, the generated birds gradually turn the color from yellow to brown.
+In the second row, more complicated sentences containing more detailed appearance information (e.g., blue peaks, and yellow wing) are used, we can see that our model is still be able to successfully capture these subtle information and tune the bird appearance gradually.
+}
 
-\textcolor{red}{We also evaluate some sentences that generated by ourself, the resulting images are shown in Figure~\ref{}, as we can see, our model are robust and generalize well to human descriptions that never seen before.}
-
-\begin{table}[t] % retrieval
-	\label{table:vss}
-	\begin{center}
-		\begin{tabularx}{.477\textwidth}{c|ccc}
-			\specialrule{1.5pt}{0pt}{0pt}  
-			\multirow{2}{*}{Method}	& \multicolumn{3}{c}{Dataset}	\\ \cline{2-4}
-						&	 CUB		&	Oxford  & COCO		     \\ \hline
-			StackGAN     &	$.228{\pm}.162$	&	 $.278{\pm}.134$			&  $-{\pm}-$		\\
-
-			Ground Truth	&	${.302{\pm}.151}$	&	$ {.336{\pm}.138}$			&  -  \\ \hline
-			HDGAN 		&	$\bm{.246{\pm}.157}$	&	$ \bm{.296{\pm}.131}$			&  -  \\ \hline
-		\end{tabularx} \vspace{-.4cm}
-	\end{center}
-	\caption{The visual-semantic similarity evaluation on three datasets. The higher score represents higher degree of matching between the generated images and the text information. } 
-\end{table}
-
-\subsubsection{What role does noise play}
-In our model, there are two kinds of randomness injected to the input of the Generator, ie, epsilon $\epsilon$ and Gaussian noise vector $z$. 
-In this experiment, we fix the sentence embedding and one noise, and change the other random variable.
+%\subsubsection{What role does noise play}
+%In our model, there are two kinds of randomness injected to the input of the Generator, ie, epsilon $\epsilon$ and Gaussian noise vector $z$. 
+%In this experiment, we fix the sentence embedding and one noise, and change the other random variable.
 For each random noise, we generate 4 different values.
@@
 \section{On the effects of Individual Components}
-\subsection{Hierarchically-nested adversary}
-Recall that the proposed hierarchically-nested adversarial supervision plays a role of regularizing the layer representations.
-In practice, we apply it on feature maps at $\{64, 128, 256\}$.
-In Table \ref{table:deep-nest}, we show the inception score by removing partial of supervision components.
-As can be observed, ...
-
-StackGAN emphasizes the importance of using text embeddings in the (stage-II) mid-level features of the $256{\times}256$ generator by showing an large drop from $3.7$ to $3.45$ without doing so.
-The text embedding plays an important role in maintaining the diversity and semantic consistency in StackGAN.
+\subsection{Hierarchically-nested adversarial training}
+Our hierarchically-nested adversarial discriminators a role of regularizing the layer representations (at scale $\{64, 128, 256\}$). 
+%Our full method applies it on feature maps at $\{64, 128, 256\}$. 
+In Table \ref{tab:ablation} right, we compare the results by removing part of discriminators. 
+As can be seen, increasing the usage of discriminators at different scales have positive effectives.
+And using discriminators on $64^2$ is critical (by comparing 64-256 and 128-256 cases).
+For now, we are unsure if adding more discriminators and adding on lower resolution would be helpful.
+Further investigation will be conducted to validate it.
+StackGAN emphasizes the importance of using text embeddings with mid-level features of the $256^2$ generator by showing an large drop from $3.7$ to $3.45$ without doing so, which helps maintains the diversity and semantic consistency.
 While in our method, we only use text embeddings at the input.
-Our improved results demonstrate that our hierarchically-nested adversarial supervision regularizes the generator to achieve the same goal.
+Our significantly improved results demonstrate that effectiveness of the hierarchically-nested adversarial training to achieve this goal.
 
 \subsection{On the Local Image Loss}
-\begin{table}[t] % retrieval
-	\label{tab:local_loss}
-	\begin{center}
-		\begin{tabularx}{.43\textwidth}{c|ccc}
-			\specialrule{1.1pt}{0pt}{0pt}  
-			Metric 			 		&   wo/Img 	 & w/global     &   w/local	\\  \hline
-			MS-SSMI                 &   $-$      &   $-$           &	$.215$ \\  \hline
-			VS similarity           &   $-$      &   $-$           &	$.246{\pm}.157$ \\ \hline
-			Inception score         &   $-$ 	 &   $-$		   &    $4.15{\pm}.05$ \\
-		\end{tabularx}
-	\end{center} \vspace{-.4cm}
-	\caption{Results using three quantitative evaluation metrics on birds dataset.} \label{table:imgloss}
-\end{table}
 
@@
 
-\begin{figure}[t]
-	\centering
-	%	\includegraphics[width=0.48\textwidth]{}
-	\caption{} \label{fig:vallina-res}
-\end{figure}
+%\begin{table}[t] % retrieval
+%	\begin{center}
+%		\begin{tabularx}{.268\textwidth}{ccc|c}
+%			\specialrule{1.5pt}{0pt}{0pt}  
+%			\multicolumn{3}{c|}{Components}	&  \multirow{2}{*}{Score}	\\ \cline{1-3}
+%			64	& 128	& 256 			& 		\\ \hline
+%			&  		&	\checkmark	&	${3.52{\pm}.04}$	\\ 
+%			&  	\checkmark	&	\checkmark	&	${3.99{\pm}.04}$	\\
+%			\checkmark	&  			&	\checkmark	&  ${4.14{\pm}.03}$		\\
+%			\checkmark	&  \checkmark		&	\checkmark	&	${4.15{\pm}.05}$ \\
+%			
+%		\end{tabularx}
+%	\end{center} \vspace{-.4cm}
+%	\caption{Ablation study for hierarchically-nested adversarial supervision.} \label{table:deep-nest}
+%\end{table}
+
+%\begin{table}[t] % retrieval
+%	\label{tab:local_loss}
+%	\begin{center}
+%		\begin{tabularx}{.43\textwidth}{c|ccc}
+%			\specialrule{1.1pt}{0pt}{0pt}  
+%			Metric 			 		&   wo/Img 	 & w/global     &   w/local	\\  \hline
+%			MS-SSMI                 &   $-$      &   $-$           &	$.215$ \\  \hline
+%			VS similarity           &   $-$      &   $-$           &	$.246{\pm}.157$ \\ \hline
+%			Inception score         &   $-$ 	 &   $-$		   &    $4.15{\pm}.05$ \\
+%		\end{tabularx}
+%	\end{center} \vspace{-.4cm}
+%	\caption{Results using three quantitative evaluation metrics on birds dataset.} \label{table:imgloss}
+%\end{table}
 
 \begin{table}[t] % retrieval
-	\begin{center}
-		\begin{tabularx}{.268\textwidth}{ccc|c}
+	\small
+	\begin{minipage}[b]{0.5\linewidth}
+			\begin{tabularx}{.98\textwidth}{c@{\hskip1pt}|c@{\hskip1pt}c@{\hskip1pt}}
 				\specialrule{1.5pt}{0pt}{0pt}  
-			\multicolumn{3}{c|}{Components}	&  \multirow{2}{*}{Score}	\\ \cline{1-3}
+				Metric 			&   VS 	 & MS-SSMI   	\\  \hline
+				w/o Img         &   $.25{\pm}.16$      &   $.215$           \\  \hline
+				w/ global       &   $-$      &   $-$           \\ \hline
+				w/local         &   $-$ 	 &   $-$		    \\ \hline
+			\end{tabularx}
+		\vspace{-0.8cm}
+	\end{minipage} %\hfill
+	\begin{minipage}[b]{0.49\linewidth}
+		\begin{tabularx}{.98\textwidth}{ccc|c}
+			\specialrule{1.5pt}{0pt}{0pt}  
+			\multicolumn{3}{c|}{Components}	&  \multirow{2}{*}{\thead{Inception \\ score}}	\\ \cline{1-3}
 			64	& 128	& 256 			& 		\\ \hline
@@
 			\checkmark	&  			&	\checkmark	&  ${4.14{\pm}.03}$		\\
-			\checkmark	&  \checkmark		&	\checkmark	&	${4.15{\pm}.05}$ \\
+			\checkmark	&  \checkmark		&	\checkmark	&	${4.15{\pm}.05}$ \\ \hline
 
 		\end{tabularx}
-	\end{center} \vspace{-.4cm}
-	\caption{Ablation study for hierarchically-nested adversarial supervision.} \label{table:deep-nest}
+	\end{minipage}
+	\vspace{-0.2cm}
+	\caption{Ablation study on the local adversarial loss (left table) and hierarchically-nested adversarial learning (right table). See text for detailed explanation.} \label{tab:ablation}
 \end{table}
@@
 \subsection{Design principles}
-Note that for text-to-image synthesis, StackGAN is the only successful method to generate $256{\times}256$ images.
-At the same time, it also shows the difficulty (impossibility) of directly training a vanilla $256{\times}256$ GAN, which fails to generate meaningful images. 
-We test this extreme case using our method by removing all nested supervisions (the first row of Table \ref{table:deep-nest}).
-Our method still generates fairly good results.
-Figure \ref{fig:vallina-res} shows the qualitatively results.
-This strongly proves the effectiveness of our designs in generators and discriminator losses.
+%Note that for text-to-image synthesis, StackGAN is the only successful method to generate $256{\times}256$ images.
+StackGAN shows the difficulty of directly training a vanilla $256{\times}256$ GAN to generate meaningful images. 
+We test this extreme case using our method by removing all nested intermediate discriminators (the first row of Table \ref{tab:ablation} left). Our method still generates fairly good results. 
+%Figure \ref{fig:vallina-res} shows the qualitatively results. 
+Based on our experience, the success is because of our effective generator designs that helps gradient flows.
 
@@
 differentiates real and fake despite difficult scales).
-However, we did not find any benefits from this and our independent discriminators can be well-trained by themselves.
+However, we did not find benefits from this mechanism and our independent discriminators can be trained very stably.
 
-\textbf{Advantages}
-The advantages of our hierarchical-nested adversary are clearer from different views, compared with the popular stacking GAN strategy \cite{}.
-
-First, it is memory efficient. 
-When viewing it as ensembled multi-scale GAN (Figure \ref{}), each GAN fully uses the parameters of its lower resolution GAN.
+%\textbf{Advantages}
+%The advantages of our hierarchical-nested adversary are clearer from different views, compared with the popular stacking GAN strategy \cite{}. 
+%First, it is memory efficient. 
+%When viewing it as ensembled multi-scale GAN (Figure \ref{}), each GAN fully uses the parameters of its lower resolution GAN.
 Usually, a deeper generator is necessary to compact a discriminator.
@@
 While in our method, for instance, from a $64^2$ GAN to a $128^2$ GAN, only a minimum two conv layers ($1$-repeat res-blocks) are needed.
-
-Second, it fully enjoys top-down knowledge. 
-The low resolution can not use high resolution information in the stacking GAN strategy.
+%
+%Second, it fully enjoys top-down knowledge. 
+%The low resolution can not use high resolution information in the stacking GAN strategy.
 While in our method, it is easy to see the low resolution GAN enjoys knowledge from higher resolution.
@@
 \section{Conclusion}
-In this paper, we present a novel and effective method to tackle the problem of generating high resolution images using text description.
-We introduce the hierarchical nested side outputs for deeply supervising the GAN training.
-To improve the model's capability to render fine-grained local details, we propose a hierarchal local image loss to boost the training.
-We also introduce a newly evaluation method for conditional gan, which leverage visual semantic embedding to judge the matching between generated images and provided text description, thus remove the necessary for human evaluation.
-Extensive experiment results demonstrate that our method work significantly better than existing state of the arts.
+In this paper, we present a novel, effective, and end-to-end method to tackle the problem of generating high resolution images using text description.
+We introduce the hierarchical-nested adversarial discriminators to help generator training.
+To improve the model's capability to render fine-grained local details, we propose a hierarchal local image loss to emphasize local patch realism.
+We also introduce a new evaluation metric for text-to-image synthesis to evaluate the semantic consistency between generated images and conditioned text.
+Extensive experiment results demonstrate that our method, namely HDGAN, performs significantly better than existing state of the arts.
+
 {\small

### 2017-11-13 cvpr2018.tex

@@
 \usepackage{wrapfig}
-\usepackage{makecell}
 
@@
 	\caption{Overviews of some typical GAN frameworks.
-\textbf{A} uses multi-stage GANs \cite{han2017stackgan,denton2015deep}.
+\textbf{A} decomposes tasks multi-stage GANs \cite{han2017stackgan,denton2015deep}.
 \textbf{B} uses multiple discriminators with one generator \cite{durugkar2016generative,tu_etal_nips17_d2gan}.
@@
 \begin{split}
-G^*, D^* = \arg~\underset{G}{\min}\ \underset{D}{\max}~ \mathcal{L}(D, G, Y, \bm z)
+G^*, D^* = \arg~\underset{G}{\min}\ \underset{D}{\max}~ \mathcal{L}(D, G)
 \end{split}
 \end{equation}
-\textcolor{red}{where $Y$ denotes training images and $\bm z\sim\mathcal{N}(0,1)$ denotes a random noise.
-The loss $\mathcal{L}$ aims to minimize the Jensen-Shannon divergence between the data and model distributions.
-}
+\textcolor{red}{where the loss $\mathcal{L}$ aims to minimize the Jensen-Shannon divergence between the data and model distributions. }
 
@@
 %Directly predicting high resolution synthesized images are challenging, not only because of the difficulties in training but also due to the large variation and instability in the hidden layers.
-Numerous methods have demonstrated ways to unite generators and discriminators for image synthesis. Figure \ref{fig:archs-review} and Section 2 discuss some typical frameworks.
-Our method actually explores a new dimension of playing this adversarial game along the depth of a CNN (Figure \ref{fig:archs-review} D), which integrates additional discriminators at mid-level features of the generator $\mathcal{G}$.
+Numerous methods have demonstrated a variety of ways to build GANs for image synthesis. Figure \ref{fig:archs-review} and Section 2 discuss some typical frameworks.
+Our method explores a new dimension of playing this adversarial game along the depth of a CNN (Figure \ref{fig:archs-review} D), which integrates additional discriminators at mid-level features of the generator $\mathcal{G}$.
 The hierarchically-nested objectives 
@@
 \end{equation}
-where  $\bm t\sim p(data)$ denotes a sentence embedding vector in the real training data distribution (generated by a text character encoder).
+where $\bm z\sim\mathcal{N}(0,1)$ denotes a random noise and $\bm t\sim p(data)$ denotes a sentence embedding vector in the real training data distribution (generated by a text character encoder).
 $\mathcal{G}$ produces $s-1$ side outputs (size-growing images) and a final output $X_s$ with the highest resolution.
@@
 
-For each side output $X_i$, we propose to apply a discriminator $D_i$ to perform independently adversarial games. Therefore, our full min-max objective is defined as follows: 
+For each side output $X_i$, we propose to apply a discriminator $D_i$ to perform independently adversarial games. Therefore, our full min-max objective can be defined as follows: 
 \begin{equation}
@@
 \end{equation}
-where $ \mathcal{Y}$ denotes a set of training images at multi-scales, $\{1,...,s\}$.
+where $ \mathcal{Y}$ denotes training images at multi-scales, $\{1,...,s\}$.
 %where $\mathcal{D}$ contains the optimal discriminators $\{D_1^*, ..., D_o^*\}$, and $ \mathcal{L}(G,\mathcal{D}, \bm{X}, \bm{T} )$ is the full objective of this mini-max game.
 %Please note that in this setting, 
-Compared with Eq. (\ref{equ:GAN}), one generator competes with multiple discriminators at different hierarchies (Figure \ref{fig:archs-review} D). 
+Compared with Eq. (\ref{equ:GAN}), one generator competes with multiple discriminators at different hierarchies. 
 \textcolor{red}{Discriminators do not share weights with each other, which offers them full flexibility to focus on learning diverse discriminative features in different contextual scales.
 In principle, the lower-resolution side output is forced to learn semantic consistent image structures (e.g., object sketch, color, and background), and the subsequent higher-resolution side outputs are used to render details to the images.
-Since the model is trained in an end-to-end fashion, we can obtain more consistent information exhibited in both lower and higher-resolution outputs compared with StackGAN.
+Since the model is trained in an end-to-end fashion, we can observe more consistent information exhibited in both lower and higher-resolution outputs than StackGAN \cite{han2017stackgan}.
 More results can be founded in experiments.
@@
 \textbf{Visual-semantic similarity~}
-\textcolor{red}{Since the aforementioned evaluation methods can not measure alignment between the generated images and the text description, we introduce a new qualitative measurement, namely visual-semantic similarity (VS similarity) inspired by \cite{vsemb}.} Denote $\bm{v}$ as the feature vector extract by a pre-trained CNN model $f_{cnn}$ (Inception-v2 \cite{inception} pre-trained on Imagenet), and $\bm{t}$ denote the text embedding.
+Since the aforementioned evaluation methods can not measure alignment between the generated images and the text description, we introduce a new qualitative measurement, namely visual-semantic similarity (VS similarity) \cite{vsemb}.
+Denote $\bm{v}$ as the feature vector extract by a pre-trained CNN model $f_{cnn}$ (inception v2\cite{inception} pre-trained on Imagenet), and $\bm{t}$ denote the text embedding.
 We define a scoring function $s(\bm{x}, \bm{y})=\frac{\bm{x}\cdot \bm{y}}{||\bm{x}||\cdot ||\bm{y}||}$. 
@@
 In the testing stage, given an text embedding $\bm{t}$, and the generated images $o$, the corresponding vs-similarity will be calculated as $s(f_{cnn}(o), \bm{t})$.
-Higher score indicates semantic consistency.
 
@@
 	\vspace{-.2cm}
-	\caption{The generated images on Oxford compared with StackGAN.
-Each sample shows the input text and generated $64^2$ (left) and $256^2$ (right) images.
-Our generated images perform more natural satisfiability and higher contrast.} \label{fig:vis-oxford}
+	\caption{The generated images on Oxford compared with StackGAN (second row). Our generated images perform more natural satisfiability and higher contrast.} \label{fig:vis-oxford}
 	\vspace{-.2cm}
@@
 	\begin{center}
-		\begin{tabularx}{.435\textwidth}{c|ccc}
+		\begin{tabularx}{.47\textwidth}{c|ccc}
 			\specialrule{1.5pt}{0pt}{0pt}  
@@
 
-			Ground Truth	&	${.302{\pm}.151}$	&	$ {.336{\pm}.138}$			&  -  \\ \hline
-			HDGAN 		&	$\bm{.246{\pm}.157}$	&	$ \bm{.296{\pm}.131}$			&  -  \\ \hline
+			Ground Truth	&	${.302{\pm}.151}$	&	$ {.336{\pm}.138}$			& $.426{\pm}.157$  \\ \hline
+			HDGAN 		&	$\bm{.246{\pm}.157}$	&	$ \bm{.296{\pm}.131}$ & $\bm{.178{\pm}.181}$  \\ \hline
 		\end{tabularx} 
@@
 	\caption{Left: Diversity test given a single input text.
-HDGAN (top) show obviously more details and higher diversity.
+Our results show obviously more details and higher diversity.
 Right: Side outputs of HDGAN with increasing resolutions.
-Different resolutions are semantically consistent and semantic details emerges as resolution increases.
+Different resolutions are fairly semantically consistent.
 \label{fig:multiple-test}} 	\vspace{-.3cm}
@@
 \end{table}
-
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=0.48\textwidth]{figure/interp.pdf}
+	\caption{Text interpolation visualization. } \label{fig:interp}
+\end{figure}
 Table \ref{fig:msssmi} shows the MS-SSMI image quality evaluation score compared with StackGAN and Prog.GAN on CUB.
@@
 It strongly demonstrates our HDGAN better preserves semantically consistent information in all resolutions.
-Figure \ref{fig:multiple-test} qualitatively validate this property.
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.48\textwidth]{figure/interp.pdf}
-	\vspace{-.5cm}
-	\caption{Text embedding interpolation from the source to target sentence results in smooth image changes approaching the targeting sentence. } \label{fig:interp}
-	\vspace{-.3cm}
-\end{figure}
+Figure \ref{fig:multiple-test} right shows some testing samples.
+
 \subsubsection{Style Transfer Using Sentence Interpolation}
 
-\textcolor{red}{Ideally, a well trained model should learn a smooth linear latent manifold of the images.
-To demonstrate our model's generalization capability, we generate images using the linearly interpolated embeddings between two source sentences.
+Ideally, a trained model should learn a smooth linear latent manifold of the images.
+To demonstrate our model's generalization capability, we generate images using the linearly interpolated  embedding using two source sentences.
 During this experiment, we fix the all the random noises to make the object and background consistent.
 As is shown in Figure~\ref{fig:interp}, the generated images show gradual and smooth changes reflecting the semantic changing in sentences, while still maintaining plausible object pose and shape.
-In the first row, the generated birds gradually turn the color from yellow to brown.
-In the second row, more complicated sentences containing more detailed appearance information (e.g., blue peaks, and yellow wing) are used, we can see that our model is still be able to successfully capture these subtle information and tune the bird appearance gradually.
-}
+In the first row, the generated birds gradually turn the color from yellow to red, in the second row, more complicated sentences containing more detailed appearance information (e.g., blue peaks, and yellow wing) are used, we can see that our model is still be able to successfully capture these subtle information and tune the bird appearance gradually.
+
+\textcolor{red}{We also evaluate some sentences that generated by ourself, the resulting images are shown in Figure~\ref{}, as we can see, our model are robust and generalize well to human descriptions that never seen before.}
 
@@
 %Our full method applies it on feature maps at $\{64, 128, 256\}$. 
-In Table \ref{tab:ablation} right, we compare the results by removing part of discriminators. 
-As can be seen, increasing the usage of discriminators at different scales have positive effectives.
-And using discriminators on $64^2$ is critical (by comparing 64-256 and 128-256 cases).
-For now, we are unsure if adding more discriminators and adding on lower resolution would be helpful.
-Further investigation will be conducted to validate it.
+In Table \ref{table:deep-nest}, we compare the results by removing part of discriminators. The number of 
 StackGAN emphasizes the importance of using text embeddings with mid-level features of the $256^2$ generator by showing an large drop from $3.7$ to $3.45$ without doing so, which helps maintains the diversity and semantic consistency.
@@
 	\begin{minipage}[b]{0.49\linewidth}
-		\begin{tabularx}{.98\textwidth}{ccc|c}
+		\begin{tabularx}{.96\textwidth}{ccc|c}
 			\specialrule{1.5pt}{0pt}{0pt}  
-			\multicolumn{3}{c|}{Components}	&  \multirow{2}{*}{\thead{Inception \\ score}}	\\ \cline{1-3}
+			\multicolumn{3}{c|}{Components}	&  \multirow{2}{*}{Score}	\\ \cline{1-3}
 			64	& 128	& 256 			& 		\\ \hline
@@
 	\vspace{-0.2cm}
-	\caption{Ablation study on the local adversarial loss (left table) and hierarchically-nested adversarial learning (right table). See text for detailed explanation.} \label{tab:ablation}
+	\caption{Ablation study on the local adversarial loss (left) and hierarchically-nested adversarial learning (right). See text for details. See text for details.} \label{fig:ablation}
 \end{table}
@@
 StackGAN shows the difficulty of directly training a vanilla $256{\times}256$ GAN to generate meaningful images. 
-We test this extreme case using our method by removing all nested intermediate discriminators (the first row of Table \ref{tab:ablation} left). Our method still generates fairly good results. 
-%Figure \ref{fig:vallina-res} shows the qualitatively results. 
-Based on our experience, the success is because of our effective generator designs that helps gradient flows.
+We test this extreme case using our method by removing all nested intermediate discriminators (the first row of Table \ref{table:deep-nest}).
+Our method still generates fairly good results.
+Figure \ref{fig:vallina-res} shows the qualitatively results.
+Based on our experience, the success is because of our framework designs in generators.
 
@@
 differentiates real and fake despite difficult scales).
-However, we did not find benefits from this mechanism and our independent discriminators can be trained very stably.
+However, we did not find any benefits from this and our independent discriminators can be trained very stably.
 
@@
 \section{Conclusion}
-In this paper, we present a novel, effective, and end-to-end method to tackle the problem of generating high resolution images using text description.
-We introduce the hierarchical-nested adversarial discriminators to help generator training.
-To improve the model's capability to render fine-grained local details, we propose a hierarchal local image loss to emphasize local patch realism.
-We also introduce a new evaluation metric for text-to-image synthesis to evaluate the semantic consistency between generated images and conditioned text.
-Extensive experiment results demonstrate that our method, namely HDGAN, performs significantly better than existing state of the arts.
-
+In this paper, we present a novel and effective method to tackle the problem of generating high resolution images using text description.
+We introduce the hierarchical nested side outputs for deeply supervising the GAN training.
+To improve the model's capability to render fine-grained local details, we propose a hierarchal local image loss to boost the training.
+We also introduce a newly evaluation method for conditional gan, which leverage visual semantic embedding to judge the matching between generated images and provided text description, thus remove the necessary for human evaluation.
+Extensive experiment results demonstrate that our method work significantly better than existing state of the arts.
 {\small

### 2017-11-13 cvpr2018.tex
16th

--- 2017-11-12 cvpr2018.tex
@@
 
-\usepackage[breaklinks=true,bookmarks=false]{hyperref}
+\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
 
@@
 We present an extensile network architecture to cooperate with discriminators and push generated images to high resolutions.
-We adopt a multi-purpose adversarial learning strategy at multiple nested hierarchical side outputs to encourage more effective image-text alignment in order to guarantee the semantic consistency and image fidelity simultaneously.
+We adopt a multi-purpose adversarial training strategy at multiple nested side outputs to encourage more effective image-text alignment in order to guarantee the semantic consistency and image fidelity simultaneously.
 Furthermore, we introduce a new visual-semantic similarity measure to evaluate the semantic consistency of generated images.
@@
 	%	\centering
-		\includegraphics[width=0.95\textwidth]{figure/intro.pdf}
+		\includegraphics[width=0.95\textwidth]{figure/intro2.pdf}
 	\end{subfigure} \\
@@
 	\vspace{-.6cm}
-	\caption{Top: Overview of our hierarchically-nested adversarial network. Bottom: Two fine-grained sample results. \label{fig:intro}} 	\vspace{-.3cm}
+	\caption{Top: Overview of our hierarchically-nested adversarial network. Bottom: Two fine-grained generated results. \label{fig:intro}} 	
+	\vspace{-.8cm}
 	%\end{center}
@@
 Reed \etal \cite{reed2016generative} address this task through a GAN based framework. But this method only handles image up to $64^2$ resolution and can barely generate vivid object details.
-Based on this method, Zhang \etal \cite{han2017stackgan} present a successful approach (StackGAN) by stacking another low-to-high resolution GAN to generate high-quality $256^2$ images, with two separate stage training.
+Based on this method, Zhang \etal \cite{han2017stackgan} present a successful two-state training approach (StackGAN) by stacking another low-to-high resolution GAN to generate high-quality $256^2$ images.
 Later on, Dong \etal \cite{dong2017semantic} propose to bypass the difficult of translate vector embedding to RGB images and treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-rendering an arbitrary-style training ($128^2$) image conditioned on a targeting description.
 But its high-resolution synthesis ability is unclear.
-At present, how to train from the low-dimensional text space to synthesize high-resolution and diverse images in an fully end-to-end manner is still an open and attractive question.
-
-We outline several empirical reasons for the challenges of text-to-image synthesis using GANs.
-The first is the fundamental difficulty of balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}.
+At present, how to train from the low-dimensional text space to synthesize high-resolution and diverse images in a fully end-to-end manner is still an open and attractive question.
+
+%We outline several empirical reasons for the challenges of 
+Text-to-image synthesis using GANs has two main difficulties.
+The first is the fundamental problem of balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}.
 %How to utilize the multimodal information between images and text in discriminator is extremely important to generate effective gradients.
@@
 
-Our generator resembles a simple vanilla-like GAN, without requiring any internal text conditioning like \cite{han2017stackgan} or outside image annotation supervision like \cite{dash2017tac}.
+Our generator resembles a simple vanilla GAN, without requiring any internal text conditioning like \cite{han2017stackgan} or outside image annotation supervision like \cite{dash2017tac}.
 To tackle the problem of the big leap from the text space to the high-resolution image space, our insight is to leverage and regularize hierarchical representations with additional deep adversarial constraints.
-We introduce accompanying hierarchically-nested objectives at multi-scale intermediate layers to play adversarial games and thereby encourage the generator approaching the real training data distribution.
+We introduce accompanying hierarchically-nested discriminators at multi-scale intermediate layers to play adversarial games and thereby encourage the generator approaching the real training data distribution.
 We also propose a novel convolutional neural network (CNN) framework for the generator to cooperate with our nested discriminators more effectively.
@@
 We validate our proposed method on three datasets, CUB birds \cite{welinder2010caltech}, Oxford-102 flowers \cite{Nilsback08}, and large-scale MSCOCO \cite{lin2014microsoft}.
-In complement of the image diversity evaluation metric (inception score \cite{improvedGAN}), we introduce a new visual-semantic similarity measurement to evaluate th alignment between generated images and corresponded text.
+In complement of existing evaluation metric (inception score \cite{improvedGAN}) for generative models, we also introduce a new visual-semantic similarity metric to evaluate the alignment between generated images and conditioned text.
 Extensive experimental results and analysis demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts on three metrics.
@@
 Reed \etal \cite{reed2016learning} propose generative
-adversarial what-where network (GAWWN) to enable location and content instructions in text-to-image synthesis, which uses extra information to help generate $128^2$ resolution images.
-StackGAN \etal \cite{han2017stackgan} propose a two-stage stacking GAN training approach that is able to generate $256^2$ compelling results.
+adversarial what-where network (GAWWN) to enable location and content instructions in text-to-image synthesis.
+StackGAN \etal \cite{han2017stackgan} propose a two-stage stacking GAN training approach that is able to generate $256^2$ compelling images.
 Recently, Dong \etal \cite{dong2017semantic} propose to learn a joint embedding of images and text so as to re-render a prototype image conditioned on a targeting description.
@@
 
-Learning a continuous mapping from low-dimensional embeddings to a complex real data distribution is a long-standing problem.
+Learning a continuous mapping from a low-dimensional embedding manifold to a complex real data distribution is a long-standing problem.
 Although GANs have made significant progress, there are still many unsolved difficulties, e.g.
 training instability and high-resolution extensions.
-Wide methods have been proposed to address those tasks, through various stabilization training techniques \cite{salimans2016improved,arjovsky2017wasserstein,berthelot2017began,shrivastava2016learning,odena2016conditional}, regularization using outside knowledge (e.g.
-image labels, ImageNet CNNs, etc) \cite{dosovitskiy2016generating,ledig2016photo,dash2017tac,dash2017tac}, or multiple discriminators  \cite{metz2016unrolled,durugkar2016generative,yang2017lr}.
-\textit{While our method does not use any extra information apart from training paired text and images.} Moreover, it is easy to see the training difficulty increases significantly as targeting image resolution increases.
+Wide methods have been proposed to address the training instability, through various training techniques \cite{salimans2016improved,arjovsky2017wasserstein,berthelot2017began,shrivastava2016learning,odena2016conditional}, regularization using extra knowledge (e.g.
+image labels, ImageNet CNNs, etc) \cite{dosovitskiy2016generating,ledig2016photo,dash2017tac,dash2017tac}, or different generator and discriminator combinations  \cite{metz2016unrolled,durugkar2016generative,yang2017lr,huang2016stacked}.
+\textit{While our method shows a new way to unite generators and discriminators and does not use any extra information apart from training paired text and images.} Additionally, it is easy to see the training difficulty increases significantly as targeting image resolution increases.
 
@@
 Following this strategy, Chen \etal \cite{chen2017photographic} present a cascaded refinement network to synthesize high-resolution scene from semantic maps.
-Huang \etal \cite{huang2016stacked}
-propose a top-down stacked GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method.
+%%Huang \etal \cite{huang2016stacked} propose a top-down stacked GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method.
 However, this method needs multiple symmetric bottom-up pre-trained discriminators and the usage for high-resolution image is unclear.
@@
 DSN \cite{lee2015deeply} proposes deep supervision in hierarchical convolutional layers to increase the discriminativeness of feature representations.
-\textit{Our hierarchically-nested adversarial objective is inspired by these kinds of CNNs with deep supervision. }
+\textit{Our hierarchically-nested adversarial objective is inspired by these families of CNNs with deep supervision. }
 %Our proposed hierarchically-nested adversarial supervision enhances layer representations to support final high resolution outputs.
@@
 \begin{split}
-G^*, D^* = \arg~\underset{G}{\min}\ \underset{D}{\max}~ \mathcal{L}(D, G, Y, \bm z)
+G^*, D^* = \arg~\underset{G}{\min}\ \underset{D}{\max}~ \mathcal{V}(D, G, Y, \bm z)
 \end{split}
@@
 \textcolor{red}{where $Y$ denotes training images and $\bm z\sim\mathcal{N}(0,1)$ denotes a random noise.
-The loss $\mathcal{L}$ aims to minimize the Jensen-Shannon divergence between the data and model distributions.
+The value function $\mathcal{V}$ aims to minimize the Jensen-Shannon divergence between the data and the model distribution.
+$G$ is learned to approximate $G(\bm z) \sim p(Y)$.
+The loss $\mathcal{L}$ for the valuation function is usually a cross-entropy loss, such that $\mathcal{V}(\cdot) = - \mathcal{L}(\cdot)$.
 }
@@
 \begin{split}
-  \mathcal{G}^*, \mathcal{D}^*&  =  \arg~\underset{G}{\min}\ \underset{\mathcal{D}}{\max}~ \mathcal{L}(\mathcal{G},\mathcal{D}, \mathcal{Y}, \bm t, \bm z) \\
+  \mathcal{G}^*, \mathcal{D}^*&  =  \arg~\underset{G}{\min}\ \underset{\mathcal{D}}{\max}~ \mathcal{V}(\mathcal{G},\mathcal{D}, \mathcal{Y}, \bm t, \bm z) \\
   \text{where} \;\;	 \mathcal{D} & \in  \{D_1, ..., D_s\}, \; \mathcal{Y} = \{Y_1, ..., Y_s\}
@@
 In principle, the lower-resolution side output is forced to learn semantic consistent image structures (e.g., object sketch, color, and background), and the subsequent higher-resolution side outputs are used to render details to the images.
-Since the model is trained in an end-to-end fashion, we can obtain more consistent information exhibited in both lower and higher-resolution outputs compared with StackGAN.
-More results can be founded in experiments.
-According to this goal, we present the following adversarial losses to support more effective multi-purpose discriminators.}
+To satisfy this goal, we present the following adversarial loss to support more effective multi-purpose discriminators.
+Since the model is trained in an end-to-end fashion, we can obtain more consistent information exhibited in both lower and higher-resolution outputs compared with StackGAN (see experiments).
+}
 
@@
 To guarantee semantic consistency, we adopt the matching-aware pair loss proposed by \cite{reed2016generative}.
-The discriminator is designed to take image-text pairs as inputs and is trained to identify two types of fakes: real image with mismatched text and fake image with conditioned text.
+The discriminator is designed to take image-text pairs as inputs and trained to identify two types of fakes: real image with mismatched text and fake image with conditioned text.
 
@@
 	\includegraphics[width=0.49\textwidth]{figure/loss.pdf}
-	\vspace{-.2cm}
-	\caption{Given an image in the side output pyramid of the generator, the corresponding discriminator $D_i$ computes the matching-aware pair loss and adaptive local image loss (outputting a $R{\times}R$ probability map to indicate real or fake patches).
+	\vspace{-.5cm}
+	\caption{Given an image in the side output pyramid of the generator, the corresponding discriminator $D_i$ computes the matching-aware pair loss and adaptive local image loss (outputting a $R{\times}R$ probability map to classify real or fake patches).
 The focal range increases as image resize grows.
@@
 
-\textbf{Full Objective } Overall, our hierarchically-nested discriminators $\{D_i\}$ minimize the following objective\footnote{The objective of the generator is omitted as it can be easily inferred.}:
+\textbf{Full Objective } Overall, our hierarchically-nested discriminators $\{D_i\}$ minimize the following loss\footnote{The objective of the generator is omitted as it can be easily inferred.}:
 \vspace{-.2cm}
@@
 \end{equation}
-where ${X}_i = \mathcal{G}(\bm{t}_{X}, \bm z)$.
-$L_2(x) = (x - \mathbb{I})^2$ is the mean-square loss (we do not use the original cross-entropy loss) and $\overline{L_2}(x) =(x)^2$.
-For adaptive local image loss with varying focal range, the shape of $x, \mathbb{I} \in \mathbb{R}^{R{\times}R}$ varies accordingly (see Figure \ref{fig:loss}) for the local image loss.
-$R=1$ refers to the (largest local) global range, e.g., $R\equiv1$ for the matching aware pair loss.
+where $L_2(x) = (x - \mathbb{I})^2$ is the mean-square loss (instead of the conventional cross-entropy loss) and $\overline{L_2}(x) =x^2$.
+For local image loss with varying focal ranges, the shape of $x, \mathbb{I} \in \mathbb{R}^{R{\times}R}$ varies accordingly (see Figure \ref{fig:loss}).
+$R=1$ refers to the (largest local) global range.
 For the matching-aware pair loss,
@@
 The CUB and Oxford-102 datasets are trained for 500 epochs in total (250 epochs for COCO).
-For the adaptive local image loss, we set $R=1$ for $64^2$ side output, $R=3$ for $128^2$ side output and $R=5$ for $256^2$ and $512^2$ outputs.
+For the local image loss, we set $R=1$ and for $64^2$ and $128^2$ side outputs and $R=5$ for $256^2$ and $512^2$ outputs.
 We use 1-repeat residual block for the generator till $256^2$ resolution.
@@
 We use $3$-repeat res-block followed by the stretching and linear compression layer.
-maybe delete the l1 loss description.
-Since the $256^2$ image already captures the overall semantics and details, to encourage the $512^2$ maintain these information, we also use a reconstruction loss to self-regularize the generator in case the discriminator confuses the expected output.}
+Since the $256^2$ image already captures the overall semantics and details, to encourage the $512^2$ maintain these information, we use a l1 reconstruction loss to self-regularize the generator in case the discriminator confuses the expected output.}
 %for the consideration of memory saving and faster convergence.
@@
 1) Inception score \cite{improvedGAN} is a measurement of both objectiveness and diversity of generated images, it is closely correlated with human judgment on the image quality.
-For CUB and oxford-102, we use the fine-tuned inception model provided by StackGAN.
+For CUB and Oxford-102, we use the fine-tuned inception model provided by StackGAN.
 For MS COCO dataset, we directly use the model pre-trained on ImageNet.
@@
 	\vspace{-.2cm}
-	\caption{The generated images on Oxford compared with StackGAN.
-Each sample shows the input text and generated $64^2$ (left) and $256^2$ (right) images.
-Our generated images perform more natural satisfiability and higher contrast.} \label{fig:vis-oxford}
+	\caption{The generated images on Oxford-102 compared with StackGAN.
+Our generated images perform more natural satisfiability and higher contrast and can generate complex flower structures (e.g.
+spiked petals) like the third example.} \label{fig:vis-oxford}
 	\vspace{-.2cm}
@@
 \subsection{Comparative Results}
-To validate our method, we compare our results with GAN-INT-CLS \cite{reed2016generative}, GAWWN \cite{reed2016learning}, TAC-GAN \cite{dash2017tac}, StackGAN \cite{han2017stackgan} and also its improved version StackGAN++ \cite{han2017stackganv2}, and Progressive GAN \cite{Karras2017progressive} \footnote{StackGAN++ and Prog.GAN are two very recently released preprints we noticed.
-We acknowledge them as they also target at generating high-resolution images, in spite of their differences in motivations and network and training designs from ours.
-} We especially compare with the current state of the art, StackGAN (results are obtained from its provided model).
+To validate our method, we compare our results with GAN-INT-CLS \cite{reed2016generative}, GAWWN \cite{reed2016learning}, TAC-GAN \cite{dash2017tac}, StackGAN \cite{han2017stackgan} and also its improved version StackGAN++ \cite{han2017stackganv2}, and Progressive GAN \cite{Karras2017progressive}\footnote{StackGAN++ and Prog.GAN are two very recently released preprints we noticed.
+We acknowledge them as they also target at generating high-resolution images.
+}.
+We especially compare with the current state of the art, StackGAN (results are obtained from its provided model).
 
@@
 
-Table \ref{table:score} shows the quantitative inception-score evaluation. We follow StackGAN to sample ${~}30,000$ images for evaluation.
+Table \ref{table:score} shows the quantitative inception-score evaluation. We follow StackGAN' experiment to sample ${~}30,000$ $256^2$ images for evaluation.
 HDGAN achieves significantly improvement compared against other methods. For example, it improves StackGAN by $.45$ and StackGAN++ by $.31$ on CUB.
-HDGAN achieves competitive results with TAC-GAN on Oxford.
+HDGAN achieves competitive results with TAC-GAN on Oxford-102.
 TAC-GAN uses image labels to increase the discriminability of generators, while we do not use any extra knowledge.
@@
 We also add the evaluation results on the ground truth image and sentence pair for reference.
-Our proposed method achieves much better results on both CUB and Oxford datasets.
+Our proposed method achieves much better results on both CUB and Oxford-102 datasets.
 Since we do not have a pre-trained  StackGAN model for coco dataset, we omit the comparison.
@@
 	\caption{Left: Diversity test given a single input text.
-HDGAN (top) show obviously more details and higher diversity.
+The proposed HDGAN (top) show obviously more details and higher diversity.
 Right: Side outputs of HDGAN with increasing resolutions.
@@
 	\centering
-	\includegraphics[width=0.245\textwidth]{figure/multiscale_inception.pdf}
+	\includegraphics[width=0.245\textwidth]{figure/multiscale_inception_2.pdf}
 	\vspace{-12pt}
@@
 	\vspace{-.5cm}
-	\caption{Text embedding interpolation from the source to target sentence results in smooth image changes approaching the targeting sentence. } \label{fig:interp}
+	\caption{Text embedding interpolation from the source to target sentence results in smooth image style changes to match the targeting sentence. } \label{fig:interp}
 	\vspace{-.3cm}
@@
 
-We also study the effectiveness of the proposed local image loss. We conduct experiments with using architecture with side output 64$\times$64, 128$\times$128 and 256 $\times$ 256 using CUB dataset. 
+\textcolor{red}{We also study the effectiveness of the proposed local image loss.
+We conduct experiments with using architecture with side output 64$\times$64, 128$\times$128 and 256 $\times$ 256 using CUB dataset.
 As can be seen in Table\ref{tab:local_loss}, we can see that by removing local image loss (denoted as "No Local"), the inception score drop from \textcolor{red}{4.27} to \textcolor{red}{3.8}.
 To quantitatively compare the results, we also show generated results using two model in Figure \ref{local_or_not}, We can see that, although both models can successfully capture the semantic correspondence between image and sentence, 256$\times$ 256 results generated by model trained with local image loss provide more local fine-grained details, thus improving the visual quality.
+}
 
@@
 \section{Conclusion}
-In this paper, we present a novel, effective, and end-to-end method to tackle the problem of generating high resolution images using text description.
-We introduce the hierarchical-nested adversarial discriminators to help generator training.
-To improve the model's capability to render fine-grained local details, we propose a hierarchal local image loss to emphasize local patch realism.
+In this paper, we present an effective and end-to-end method to tackle the problem of generating high-resolution images conditioned on text descriptions.
+We introduce a novel hierarchical-nested adversarial discriminators to regularize the mid-level representations of a generator.
+To improve the model's capability to render fine-grained local details, we propose a multi-purpose discriminator loss to emphasize local patch realism as well as matching aware pair.
 We also introduce a new evaluation metric for text-to-image synthesis to evaluate the semantic consistency between generated images and conditioned text.

### 2017-11-13 cvpr2018.tex

@@
 \begin{split}
-G^*, D^* = \arg~\underset{G}{\min}\ \underset{D}{\max}~ \mathcal{V}(D, G, Y, \bm z)
+G^*, D^* = \arg~\underset{G}{\min}\ \underset{D}{\max}~ \mathcal{V}(D, G, Y, \bm z),
 \end{split}
 \end{equation}
-\textcolor{red}{where $Y$ denotes training images and $\bm z\sim\mathcal{N}(0,1)$ denotes a random noise.
+where $Y$ denotes training images and $\bm z\sim\mathcal{N}(0,1)$ denotes a random noise.
 The value function $\mathcal{V}$ aims to minimize the Jensen-Shannon divergence between the data and the model distribution.
@@
 The loss $\mathcal{L}$ for the valuation function is usually a cross-entropy loss, such that $\mathcal{V}(\cdot) = - \mathcal{L}(\cdot)$.
-}
 
@@
 
-The proposed $\mathcal{G}$ is a network (see Section 3.4), with $s{-}1$ side outputs at the intermediate layers:
+The proposed $\mathcal{G}$ is a CNN (see Section 3.4) with side outputs (RGB images):
 
@@
 
-For each side output $X_i$, we propose to apply a discriminator $D_i$ to perform independently adversarial games. Therefore, our full min-max objective is defined as follows: 
+For each side output $X_i$, we propose to apply a discriminator $D_i$ to perform independently adversarial games. Therefore, our full min-max objective is defined as 
 \begin{equation}
@@
 \begin{split}
-  \mathcal{G}^*, \mathcal{D}^*&  =  \arg~\underset{G}{\min}\ \underset{\mathcal{D}}{\max}~ \mathcal{V}(\mathcal{G},\mathcal{D}, \mathcal{Y}, \bm t, \bm z) \\
-  \text{where} \;\;	 \mathcal{D} & \in  \{D_1, ..., D_s\}, \; \mathcal{Y} = \{Y_1, ..., Y_s\}
+  \mathcal{G}^*, \mathcal{D}^*&  =  \arg~\underset{G}{\min}\ \underset{\mathcal{D}}{\max}~ \mathcal{V}(\mathcal{G},\mathcal{D}, \mathcal{Y}, \bm t, \bm z), \\
+  \text{where} \;\;	 \mathcal{D} & \in  \{D_1, ..., D_s\}, \; \mathcal{Y} = \{Y_1, ..., Y_s\},
 \end{split}
@@
 %Please note that in this setting, 
-Compared with Eq. (\ref{equ:GAN}), one generator competes with multiple discriminators at different hierarchies (Figure \ref{fig:archs-review} D). 
-\textcolor{red}{Discriminators do not share weights with each other, which offers them full flexibility to focus on learning diverse discriminative features in different contextual scales.
+Compared with Eq.
+(\ref{equ:GAN}), one generator competes with multiple discriminators at different hierarchies (Figure \ref{fig:archs-review} D), where each focus on learning diverse discriminative features in different contextual scales.
+%%Discriminators do not share weights with each other, which offers them full flexibility to focus on learning diverse discriminative features in different contextual scales.
 In principle, the lower-resolution side output is forced to learn semantic consistent image structures (e.g., object sketch, color, and background), and the subsequent higher-resolution side outputs are used to render details to the images.
-To satisfy this goal, we present the following adversarial loss to support more effective multi-purpose discriminators.
-Since the model is trained in an end-to-end fashion, we can obtain more consistent information exhibited in both lower and higher-resolution outputs compared with StackGAN (see experiments).
-}
+Since the model is trained in an end-to-end fashion, the lower-resolution outputs can fully enjoy top-down knowledge from higher resolutions.
+As an evidence, we can obtain significantly more consistent information exhibited in both low- and high-resolution outputs compared with StackGAN (see experiments). 
+%%We present the following multi-purpose adversarial loss to support more effective generator training.
 
@@
 Our generator produces size-growing side outputs which compose an image pyramid. 
-We leverage the hierarchy of it and allow adversarial losses to be multi-purpose to guarantee both semantic consistency and image fidelity.
+We leverage this hierarchy property and allow adversarial losses to be multi-purpose to capture different (conditioned and unconditioned) statistics, with a goal to guarantee both semantic consistency and image fidelity.
 
@@
 
-The pair loss is designed to capture the global semantic context.
-However, this loss has two major weaknesses.
-First, there is no explicit loss that force the discriminator to differentiate real images from fake images.
+The pair loss is designed to guarantee the global semantic consistency.
+However, there is no explicit loss that forces the discriminator to differentiate real images from fake images.
+As the image resolution goes higher, discriminators might loss focus for local fine-grained image details.
+%However, this loss has two major weaknesses. First, there is no explicit loss that force the discriminator to differentiate real images from fake images. 
 %Combining both tasks (generating realistic images and matching image with text) into one output further complicates the learning tasks, which is already challenging. 
-Second, as the image resolution goes higher, it might be challenging for a global pair-loss discriminator to capture local fine-grained details.
+%Second, as the image resolution goes higher, it might be challenging for a global pair-loss discriminator to capture local fine-grained details.  
 In addition, as pointed in \cite{shrivastava2016learning}, a single global discriminator may over-emphasize certain unexpected image features and lead to artifacts.
 
-To guarantee image fidelity and overcome these two weaknesses, our solution is to add local adversarial image losses on image patches. The insights are two folds:
-\begin{itemize}\vspace{-.1cm}
-\setlength\itemsep{-0.3em}
-\item Further forcing the generated samples to have only only global but also local similar statistics to real image patches, which is beneficial for rendering fine-grained details.
-
-\item \textcolor{red}{Image loss without using paired text can be beneficial in the sense that it focus more on image information.
+To guarantee image fidelity, our solution is to add local adversarial image losses on image patches. 
+%The insights are two folds:
+%\begin{itemize}\vspace{-.1cm}
+%\setlength\itemsep{-0.3em}
+%\item Further forcing the generated samples to have only only global but also local similar statistics to real image patches, which is beneficial for rendering fine-grained details. 
+%
+%\item \textcolor{red}{Image loss without using paired text can be beneficial in the sense that it focus more on image information.
 The richness of discriminator supervision usually has advantages for generalization.
 }
-\vspace{-.2cm}
-
-\end{itemize}
+%\vspace{-.2cm}
+%\end{itemize}
 We expect the low-resolution discriminator to focus on global structures, while high-resolution outputs focus more on local image details.
@@
 The local image adversarial loss is implemented as a fully CNN \cite{shrivastava2016learning,zhu2017unpaired}.  
-Figure \ref{fig:loss} illustrates how hierarchically-nested discriminators measure the two losses on the generated images.
+Figure \ref{fig:loss} illustrates how hierarchically-nested discriminators compute the two losses on generated images.
 
@@
 	\vspace{-.5cm}
-	\caption{Given an image in the side output pyramid of the generator, the corresponding discriminator $D_i$ computes the matching-aware pair loss and adaptive local image loss (outputting a $R{\times}R$ probability map to classify real or fake patches).
-The focal range increases as image resize grows.
-Lower range results in finer results.
+	\caption{Given a set of images from the side output pyramid of the generator, the corresponding discriminator $D_i$ computes the matching-aware pair loss and adaptive local image loss (outputting a $R{\times}R$ probability map to classify real or fake patches).
+The focal range decreases as the image size grows.
 }  \vspace{-.3cm}
@@
 \mathcal{L}(& \mathcal{G}, \mathcal{D})  = \sum_{i=1}^{s} \Big(  L_2\big(D_i({Y}_i)\big) +  L_2\big(D_i({Y}_i, \bm t_{Y})\big) \, + \\ 
-& \overline{L_2}\big(D_i({X}_i)\big)  + \overline{L_2}\big(D_i({X}_i, \bm{t}_{X_i})\big) + \overline{L_2}\big(D_i({Y}_i,  \bm{t}_{\overline{Y}})\big) \Big)
+& \overline{L_2}\big(D_i({X}_i)\big)  + \overline{L_2}\big(D_i({X}_i, \bm{t}_{X_i})\big) + \overline{L_2}\big(D_i({Y}_i,  \bm{t}_{\overline{Y}})\big) \Big),
 \end{split}
@@
 Furthermore, this separation of the image loss from the matching loss in our method opens further possibilities, such as utilizing the unlabeled image to improve both the generator and discriminator.
-\textcolor{red}{In the spirit of variational auto-encoder \cite{vae} and the practice of \cite{han2017stackgan}, namely conditional augmentation (CA), we sample the input text variable $\bm t$ from a Ganssian distribution $\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}))$, where $\mu$ and $\Sigma$ are functions of $\bm t$, which produces a $256$-d text input used as the input of the generator.
+\textcolor{red}{In the spirit of variational auto-encoder \cite{vae} and the practice of StackGAN \cite{han2017stackgan}, namely conditioning augmentation (CA), we sample the input text $\bm t$ from a Ganssian distribution $\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}))$, where $\mu$ and $\Sigma$ are functions of $\bm t$, which produces a $256$-d text input.
 We add the Kullback-Leibler divergence regularization term, $D_{KL}(\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}) )|| \mathcal{N}(0, \bm{I}))$ \cite{vae}, to the $G$ loss to force the smooth sampling over the text embedding distribution.
@@
 	\begin{center}
-		\begin{tabularx}{.435\textwidth}{c|ccc}
+		\begin{tabularx}{.475\textwidth}{c|ccc}
 			\specialrule{1.5pt}{0pt}{0pt}  
@@
 			&	 CUB		&	Oxford  & COCO		     \\ \hline
+			Ground Truth	&	${.302{\pm}.151}$	&	$ {.336{\pm}.138}$			& $.426{\pm}.157$  \\ \hline
 			StackGAN     &	$.228{\pm}.162$	&	 $.278{\pm}.134$			&  $-{\pm}-$		\\ 
-
-			Ground Truth	&	${.302{\pm}.151}$	&	$ {.336{\pm}.138}$			&  -  \\ \hline
-			HDGAN 		&	$\bm{.246{\pm}.157}$	&	$ \bm{.296{\pm}.131}$			&  -  \\ \hline
+			HDGAN 		&	$\bm{.246{\pm}.157}$	&	$ \bm{.296{\pm}.131}$ & $\bm{.178{\pm}.181}$  \\ \hline
 		\end{tabularx} 
@@
 	\vspace{-.4cm}
-	\caption{The VS similarity evaluation on three datasets. The higher score represents higher semantic consistency between the generated images and the text information. } \label{table:vss}
+	\caption{The VS similarity evaluation on the three datasets. The higher score represents higher semantic consistency between the generated images and the text information. } \label{table:vss}
 \end{table}

### 2017-11-13 cvpr2018.tex
17th

@@
 This paper presents a novel method to deal with the challenging task of generating images conditioned on semantic image descriptions.
-We propose an effective end-to-end single-stream network that can generate photographic high-resolution images (up to $512^2$).
+We propose an effective end-to-end single-stream network that can generate photographic high-resolution images.
 Our method leverages the deep representations of convolutional layers and introduces accompanying hierarchical-nested adversarial games inside the network hierarchy, which regularize intermediate representations and assist training to capture the complex image statistics.
@@
 
-Text-to-image synthesis not only requires diverse and high-quality generation but also requires precise semantically consistent mapping in the image space.
+Text-to-image synthesis not only requires diverse and high-quality image generation but also requires precise semantically consistent mapping in the image space.
 Reed \etal \cite{reed2016generative}  is th first to introduce a method that can generate $64^2$ resolution images, which is similar with DCGAN \cite{radford2015unsupervised}.
@@
 training instability and high-resolution extensions.
-Wide methods have been proposed to address the training instability, through various training techniques \cite{salimans2016improved,arjovsky2017wasserstein,berthelot2017began,shrivastava2016learning,odena2016conditional}, regularization using extra knowledge (e.g.
+Wide methods have been proposed to address the training instability, such as various training techniques \cite{salimans2016improved,arjovsky2017wasserstein,berthelot2017began,shrivastava2016learning,odena2016conditional}, regularization using extra knowledge (e.g.
 image labels, ImageNet CNNs, etc) \cite{dosovitskiy2016generating,ledig2016photo,dash2017tac,dash2017tac}, or different generator and discriminator combinations  \cite{metz2016unrolled,durugkar2016generative,yang2017lr,huang2016stacked}.
@@
 Recently, Karras \etal \cite{Karras2017progressive} propose a progressive training of GANs for very high-resolution image generation (Figure \ref{fig:archs-review} C).
-\textit{Compared with these strategies that train low-to-high resolution GANs progressively, our method has advantages of leveraging multi-level representations to encourage implicit subtask integration, which makes end-to-end high-resolution image synthesis in a single vanilla-like GAN possible.}
+\textit{Compared with these strategies that train low-to-high resolution GANs progressively, our method has advantages of leveraging mid-level representations to encourage implicit subtask integration, which makes end-to-end high-resolution image synthesis in a single vanilla-like GAN possible.}
 
@@
 Leveraging hierarchical representations of neural networks is an effective way to enhance implicit multi-scaling and ensembling for tasks such as image recognition \cite{lee2015deeply} and pixel or object classification \cite{xie2015holistically,cai2016unified,long2015fully}.
-DSN \cite{lee2015deeply} proposes deep supervision in hierarchical convolutional layers to increase the discriminativeness of feature representations.
+Particularly, using deep supervision \cite{lee2015deeply} in hierarchical convolutional layers is shown to be ablue to increase the discriminativeness of feature representations.
 \textit{Our hierarchically-nested adversarial objective is inspired by these families of CNNs with deep supervision. }
@@
 
-The proposed $\mathcal{G}$ is a CNN (see Section 3.4) with side outputs (RGB images):
+The proposed $\mathcal{G}$ is a CNN (defined in Section 3.4) with side outputs:
 
@@
 \end{equation}
-where $ \mathcal{Y}$ denotes a set of training images at multi-scales, $\{1,...,s\}$.
+where $ \mathcal{Y}$ contains a set of training images at multi-scales, $\{1,...,s\}$.
 %where $\mathcal{D}$ contains the optimal discriminators $\{D_1^*, ..., D_o^*\}$, and $ \mathcal{L}(G,\mathcal{D}, \bm{X}, \bm{T} )$ is the full objective of this mini-max game.
@@
 Compared with Eq.
-(\ref{equ:GAN}), one generator competes with multiple discriminators at different hierarchies (Figure \ref{fig:archs-review} D), where each focus on learning diverse discriminative features in different contextual scales.
+(\ref{equ:GAN}), one generator competes with multiple discriminators  $\{D_i\}$ at different hierarchies (Figure \ref{fig:archs-review} D), where each focus on learning diverse discriminative features in different contextual scales.
 %%Discriminators do not share weights with each other, which offers them full flexibility to focus on learning diverse discriminative features in different contextual scales.
@@
 Since the model is trained in an end-to-end fashion, the lower-resolution outputs can fully enjoy top-down knowledge from higher resolutions.
+We hypothesize such consistency reduces the model instability.
 As an evidence, we can obtain significantly more consistent information exhibited in both low- and high-resolution outputs compared with StackGAN (see experiments). 
@@
 Furthermore, this separation of the image loss from the matching loss in our method opens further possibilities, such as utilizing the unlabeled image to improve both the generator and discriminator.
-\textcolor{red}{In the spirit of variational auto-encoder \cite{vae} and the practice of StackGAN \cite{han2017stackgan}, namely conditioning augmentation (CA), we sample the input text $\bm t$ from a Ganssian distribution $\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}))$, where $\mu$ and $\Sigma$ are functions of $\bm t$, which produces a $256$-d text input.
+\textcolor{red}{In the spirit of variational auto-encoder \cite{vae} and the practice of StackGAN \cite{han2017stackgan}, namely conditioning augmentation (CA), we sample the input text $\bm t$ from a Ganssian distribution $\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}))$, where $\mu$ and $\Sigma$ are functions of $\bm t$ (learned with the network), which produces a $256$-d text input.
 We add the Kullback-Leibler divergence regularization term, $D_{KL}(\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}) )|| \mathcal{N}(0, \bm{I}))$ \cite{vae}, to the $G$ loss to force the smooth sampling over the text embedding distribution.
@@
 2) We also adopt the multi-scale structural similarity (MS-SSIM) metric \cite{improvedGAN} for further validation.
-It tests the variation of generated outputs and can find mode collapses reliably \cite{odena2016conditional}.
-Lower score indicates higher variance.
+It tests pair-wise variation of generated outputs and can find mode collapses reliably \cite{odena2016conditional}.
+Lower score indicates higher diversity of generated images (i.e.
+less model collapses).
+
 3) Visual-semantic similarity.
-
-\textbf{Visual-semantic similarity~}
-\textcolor{red}{Since the aforementioned evaluation methods can not measure alignment between the generated images and the text description, we introduce a new qualitative measurement, namely visual-semantic similarity (VS similarity) inspired by \cite{vsemb}.} Denote $\bm{v}$ as the feature vector extract by a pre-trained CNN model $f_{cnn}$ (Inception-v2 \cite{inception} pre-trained on Imagenet), and $\bm{t}$ denote the text embedding.
-We define a scoring function $s(\bm{x}, \bm{y})=\frac{\bm{x}\cdot \bm{y}}{||\bm{x}||\cdot ||\bm{y}||}$. 
+The problem of the aforementioned metrics is that they can not measure the alignment between the generated images and conditioned text.
+We introduce a new qualitative measurement, namely visual-semantic similarity (VS similarity) inspired by \cite{vsemb}.
+Denote $\bm{v}$ as the image feature vector extract by a pre-trained CNN on ImageNet $f_v$.
+We define a scoring function $C(\bm{x}, \bm{y})=\frac{\bm{x}\cdot \bm{y}}{||\bm{x}||\cdot ||\bm{y}||}$. 
 We learn two mapping functions $f_v$ and $f_t$, which map both image and sentence embeddings into one semantic space $\mathbb{R}^{512}$, by minimizing the following bi-directional ranking loss:
-\begin{equation}
+\begin{equation}\vspace{-.2cm}
 \begin{split}
-\mathcal{L}_{vs} &= \sum_{ \bm{v} }\sum_{ \bm{t^-} }~\max( 0, \delta- s(f_v(\bm{v}), f_t( \bm{t^-} ))) \\
-&+ \sum_{ \bm{t} }\sum_{ \bm{v-} }~\max( 0,  \delta- s(f_t(\bm{t}), f_v( \bm{v^-} )))
+\mathcal{L}_{vs} &= \sum_{ \bm{v} }\sum_{ \bm{t}_{\overline{v}} }~\max( 0, \delta- C(f_v(\bm{v}), f_t( \bm{t}_{\overline{v}}))) \\
+&+ \sum_{ \bm{t} }\sum_{ \bm{v}_{\overline{v}} }~\max( 0,  \delta- C(f_t(\bm{t}), f_v( \bm{v}_{\overline{v}} )))
 \end{split}
+\vspace{-.2cm}
 \end{equation}
-where $\delta$ is the margin, which is set as 0.2, every $(\bm{v}, \bm{t})$ is a ground truth image text pair, $\bm{t^-}$ denotes a mismatching text description for the image corresponding to $\bm{v}$, and vice-versa for $\bm{v^-}$.
+where $\delta$ is the margin, which is set as 0.2.
+$\{\bm{v}, \bm{t}\}$ is a ground truth image text pair, and $\{\bm v, \bm t_{\overline{v}} \}$ and $\{ \bm v_{\overline{v}}, \bm{t} \}$ denote mismatched image-text pairs.
 In the testing stage, given an text embedding $\bm{t}$, and the generated images $o$, the corresponding vs-similarity will be calculated as $s(f_{cnn}(o), \bm{t})$.
-Higher score indicates semantic consistency.
+Higher score indicates higher semantic consistency.
 
@@
 			Ground Truth	&	${.302{\pm}.151}$	&	$ {.336{\pm}.138}$			& $.426{\pm}.157$  \\ \hline
-			StackGAN     &	$.228{\pm}.162$	&	 $.278{\pm}.134$			&  $-{\pm}-$		\\ 
+			StackGAN     &	$.228{\pm}.162$	&	 $.278{\pm}.134$			&  -		\\ 
 			HDGAN 		&	$\bm{.246{\pm}.157}$	&	$ \bm{.296{\pm}.131}$ & $\bm{.178{\pm}.181}$  \\ \hline
@@
 }.
-We especially compare with the current state of the art, StackGAN (results are obtained from its provided model).
+We especially compare with the current state of the art, StackGAN (results are obtained from its provided models).
 
@@
 
-Table \ref{table:score} shows the quantitative inception-score evaluation. We follow StackGAN' experiment to sample ${~}30,000$ $256^2$ images for evaluation.
+Table \ref{table:score} shows the quantitative inception-score evaluation. We follow StackGAN' experiment setting to sample ${~}30,000$ $256^2$ images for evaluation.
 HDGAN achieves significantly improvement compared against other methods. For example, it improves StackGAN by $.45$ and StackGAN++ by $.31$ on CUB.
@@
 	\caption{Left: Class-wise MS-SSMI evaluation.
-Lower score indicates higher intraclass invariance.
+Lower score indicates higher intraclass dissimilarity.
 The points below the equality line represent classes our HDGAN wins.
-Right: Overall (no class-wise) score evaluation.} \label{fig:msssmi}
+The inter-class std is shown in axis titles.
+Right: Overall (no class-wise)  MS-SSMI evaluation.} \label{fig:msssmi}
 	\vspace{-0.4cm}
@@
 
-Table \ref{fig:msssmi} shows the MS-SSMI image quality evaluation score compared with StackGAN and Prog.GAN on CUB.
-StackGAN and our HDGAN use the semantic text as input so the generated images retain class information.
-We compare the score with StackGAN.
+Table \ref{fig:msssmi} compares the MS-SSMI image quality evaluation score with StackGAN and Prog.GAN for bird image generation.
+StackGAN and our HDGAN use the semantic text as input so the generated images are separable in class.
 We randomly sample ${~}20,000$ image pairs (400 per class) and show the class-wise score in the left figure.
-HDGAN wins in majority of classes and also has lower inter-class standard deviation ($.023$ vs.
+HDGAN outperforms StackGAN in majority of classes and also has lower inter-class standard deviation ($.023$ vs.
 $.032$).
-Prog.GAN takes noises rather than text.
-Since MS-SSMI evaluates the image quality without text or class involvement, we can compare with it.
-Following the procedure of Prog.GAN, we randomly sample ${~}10,000$ image pairs for each comparing method (For Prog.GAN, we use generated $256^2$ images provided by the author) and show the results in the right table.
-Our method outperforms both StackGAN and Prog.GAN.
+Prog.GAN uses noise input rather than text.
+We can compare with it for general measure of synthesis diversity.
+Following the procedure of Prog.GAN, we randomly sample ${~}10,000$ image pairs from all generated samples (We use $256^2$ images provided by the Prog.GAN online) and show the results in Table \ref{fig:msssmi} right.
+Our HDGAN outperforms both methods.
 
@@
 It strongly demonstrates our HDGAN better preserves semantically consistent information in all resolutions.
-Figure \ref{fig:multiple-test} qualitatively validate this property.
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.48\textwidth]{figure/interp.pdf}
-	\vspace{-.5cm}
-	\caption{Text embedding interpolation from the source to target sentence results in smooth image style changes to match the targeting sentence. } \label{fig:interp}
-	\vspace{-.3cm}
-\end{figure}
-\subsubsection{Style Transfer Using Sentence Interpolation}
-
-\textcolor{red}{Ideally, a well trained model should learn a smooth linear latent manifold of the images.
-To demonstrate our model's generalization capability, we generate images using the linearly interpolated embeddings between two source sentences.
-During this experiment, we fix the all the random noises to make the object and background consistent.
-As is shown in Figure~\ref{fig:interp}, the generated images show gradual and smooth changes reflecting the semantic changing in sentences, while still maintaining plausible object pose and shape.
+Figure \ref{fig:multiple-test}  right qualitatively validate this property.
+However, in StackGAN, the low resolution and high resolution image sometimes are visually inconsistent (see examples in Figure \ref{fig:vis-cub} and Figure \ref{fig:vis-oxford}).
+
+\subsection{Style Transfer Using Sentence Interpolation}
+Ideally, a well trained model should learn a smooth linear latent manifold of the images.
+To demonstrate the generalization capability of HDGAN, we generate images using the linearly interpolated embeddings between two source sentences.
+%%We fix the random noise input to make the object and background consistent.
+As is shown in Figure~\ref{fig:interp}, the generated images show smooth style transformation and well reflect the semantic details in sentences. 
 In the first row, the generated birds gradually turn the color from yellow to brown.
-In the second row, more complicated sentences containing more detailed appearance information (e.g., blue peaks, and yellow wing) are used, we can see that our model is still be able to successfully capture these subtle information and tune the bird appearance gradually.
-}
+In the second row, more complicated sentences containing more detailed appearance information (e.g., blue peaks and yellow wing) are used, we can see that our model is still be able to successfully capture these subtle information and tune the bird appearance gradually.
 
@@
 
-\section{On the effects of Individual Components}
-\subsection{Hierarchically-nested adversarial training}
+\subsection{On the effects of Individual Components}
+\subsubsection{Hierarchically-nested adversarial training}
 Our hierarchically-nested adversarial discriminators a role of regularizing the layer representations (at scale $\{64, 128, 256\}$). 
@@
 
-\subsection{On the Local Image Loss}
+\subsubsection{On the Local Image Loss}
 
@@
 }
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=0.48\textwidth]{figure/interp.pdf}
+	\vspace{-.5cm}
+	\caption{Text embedding interpolation from the source to target sentence results in smooth image style changes to match the targeting sentence. } \label{fig:interp}
+	\vspace{-.3cm}
+\end{figure}
 

### 2017-11-13 supp.tex
17th

\documentclass[10pt, letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.
\usepackage{bm}
% Include other packages here, before hyperref.
% zizhao package
\usepackage{tabularx} % in the preamble
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\newcommand\VRule[1][\arrayrulewidth]{\vrule width #1}
\usepackage{array,booktabs,arydshln,xcolor} % for widening table line
\usepackage{amsthm}
\usepackage{epstopdf}
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{amsthm}
\usepackage{multirow}
\usepackage{multicol}
\usepackage[algo2e]{algorithm2e}
\usepackage[toc,page]{appendix}
\usepackage{blindtext}
% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{2871} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{1}
\begin{document}
%\tableofcontents
%\blinddocument

%%%%%%%%% TITLE
%\title{Supplementary Materials for "Understanding, Describing, and Visualizing Medical Images Through Reading Diagnostic Report Text"}

%\author{First Author\\
%Institution1\\
%Institution1 address\\
%{\tt\small firstauthor@i1.org}
%% For a paper whose authors are all at the same institution,
%% omit the following lines up until the closing ``}''.
%% Additional authors and addresses can be added with ``\and'',
%% just like the second author.
%% To save space, use either the email address or home page, not both
%\and
%Second Author\\
%Institution2\\
%First line of institution2 address\\
%{\tt\small secondauthor@i2.org}
%}

%\maketitle
%\thispagestyle{empty}

%appendicesappendices%%%%%%%% ABSTRACT
%\begin{abstract}
%   The ABSTRACT is to be in fully-justified italicized text, at the top
%   of the left-hand column, below the author and affiliation
%   information. Use the word ``Abstract'' as the title, in 12-point
%   Times, boldface type, centered relative to the column, initially
%   capitalized. The abstract is to be in 10-point, single-spaced type.
%   Leave two blank lines after the Abstract, then begin the main text.
%   Look at previous CVPR abstracts to get a feel for style and length.
%\end{abstract}

%%%%%%%%% BODY TEXT
\begin{appendices}
%\renewcommand{\thechapter}{A\arabic{chapter}}
\section{Results on the CUB bird dataset}

\end{appendices}

%{\small
%	\bibliographystyle{ieee}
%	\bibliography{egbib}
%}

\end{document}

### 2017-11-13 cvpr2018.tex
replae bird with flower

--- 2017-11-13 cvpr2018.tex
@@
 
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
+\usepackage[breaklinks=true,bookmarks=false]{hyperref}
 
@@
 We present an extensile network architecture to cooperate with discriminators and push generated images to high resolutions.
-We adopt a multi-purpose adversarial training strategy at multiple nested side outputs to encourage more effective image-text alignment in order to guarantee the semantic consistency and image fidelity simultaneously.
+We adopt a multi-purpose adversarial learning strategy at multiple nested hierarchical side outputs to encourage more effective image-text alignment in order to guarantee the semantic consistency and image fidelity simultaneously.
 Furthermore, we introduce a new visual-semantic similarity measure to evaluate the semantic consistency of generated images.
@@
 	%	\centering
-		\includegraphics[width=0.95\textwidth]{figure/intro2.pdf}
+		\includegraphics[width=0.95\textwidth]{figure/intro.pdf}
 	\end{subfigure} \\
@@
 	\vspace{-.6cm}
-	\caption{Top: Overview of our hierarchically-nested adversarial network. Bottom: Two fine-grained generated results. \label{fig:intro}} 	
-	\vspace{-.8cm}
+	\caption{Top: Overview of our hierarchically-nested adversarial network. Bottom: Two fine-grained sample results. \label{fig:intro}} 	\vspace{-.3cm}
 	%\end{center}
@@
 Reed \etal \cite{reed2016generative} address this task through a GAN based framework. But this method only handles image up to $64^2$ resolution and can barely generate vivid object details.
-Based on this method, Zhang \etal \cite{han2017stackgan} present a successful two-state training approach (StackGAN) by stacking another low-to-high resolution GAN to generate high-quality $256^2$ images.
+Based on this method, Zhang \etal \cite{han2017stackgan} present a successful approach (StackGAN) by stacking another low-to-high resolution GAN to generate high-quality $256^2$ images, with two separate stage training.
 Later on, Dong \etal \cite{dong2017semantic} propose to bypass the difficult of translate vector embedding to RGB images and treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-rendering an arbitrary-style training ($128^2$) image conditioned on a targeting description.
 But its high-resolution synthesis ability is unclear.
-At present, how to train from the low-dimensional text space to synthesize high-resolution and diverse images in a fully end-to-end manner is still an open and attractive question.
-
-%We outline several empirical reasons for the challenges of 
-Text-to-image synthesis using GANs has two main difficulties.
-The first is the fundamental problem of balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}.
+At present, how to train from the low-dimensional text space to synthesize high-resolution and diverse images in an fully end-to-end manner is still an open and attractive question.
+
+We outline several empirical reasons for the challenges of text-to-image synthesis using GANs.
+The first is the fundamental difficulty of balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}.
 %How to utilize the multimodal information between images and text in discriminator is extremely important to generate effective gradients.
@@
 
-Our generator resembles a simple vanilla GAN, without requiring any internal text conditioning like \cite{han2017stackgan} or outside image annotation supervision like \cite{dash2017tac}.
+Our generator resembles a simple vanilla-like GAN, without requiring any internal text conditioning like \cite{han2017stackgan} or outside image annotation supervision like \cite{dash2017tac}.
 To tackle the problem of the big leap from the text space to the high-resolution image space, our insight is to leverage and regularize hierarchical representations with additional deep adversarial constraints.
-We introduce accompanying hierarchically-nested discriminators at multi-scale intermediate layers to play adversarial games and thereby encourage the generator approaching the real training data distribution.
+We introduce accompanying hierarchically-nested objectives at multi-scale intermediate layers to play adversarial games and thereby encourage the generator approaching the real training data distribution.
 We also propose a novel convolutional neural network (CNN) framework for the generator to cooperate with our nested discriminators more effectively.
@@
 We validate our proposed method on three datasets, CUB birds \cite{welinder2010caltech}, Oxford-102 flowers \cite{Nilsback08}, and large-scale MSCOCO \cite{lin2014microsoft}.
-In complement of existing evaluation metric (inception score \cite{improvedGAN}) for generative models, we also introduce a new visual-semantic similarity metric to evaluate the alignment between generated images and conditioned text.
+In complement of the image diversity evaluation metric (inception score \cite{improvedGAN}), we introduce a new visual-semantic similarity measurement to evaluate th alignment between generated images and corresponded text.
 Extensive experimental results and analysis demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts on three metrics.
@@
 Reed \etal \cite{reed2016learning} propose generative
-adversarial what-where network (GAWWN) to enable location and content instructions in text-to-image synthesis.
-StackGAN \etal \cite{han2017stackgan} propose a two-stage stacking GAN training approach that is able to generate $256^2$ compelling images.
+adversarial what-where network (GAWWN) to enable location and content instructions in text-to-image synthesis, which uses extra information to help generate $128^2$ resolution images.
+StackGAN \etal \cite{han2017stackgan} propose a two-stage stacking GAN training approach that is able to generate $256^2$ compelling results.
 Recently, Dong \etal \cite{dong2017semantic} propose to learn a joint embedding of images and text so as to re-render a prototype image conditioned on a targeting description.
@@
 
-Learning a continuous mapping from a low-dimensional embedding manifold to a complex real data distribution is a long-standing problem.
+Learning a continuous mapping from low-dimensional embeddings to a complex real data distribution is a long-standing problem.
 Although GANs have made significant progress, there are still many  unsolved difficulties, e.g.
 training instability and high-resolution extensions.
-Wide methods have been proposed to address the training instability, through various training techniques \cite{salimans2016improved,arjovsky2017wasserstein,berthelot2017began,shrivastava2016learning,odena2016conditional}, regularization using extra knowledge (e.g.
-image labels, ImageNet CNNs, etc) \cite{dosovitskiy2016generating,ledig2016photo,dash2017tac,dash2017tac}, or different generator and discriminator combinations  \cite{metz2016unrolled,durugkar2016generative,yang2017lr,huang2016stacked}.
-\textit{While our method shows a new way to unite generators and discriminators and does not use any extra information apart from training paired text and images.} Additionally, it is easy to see the training difficulty increases significantly as targeting image resolution increases.
+Wide methods have been proposed to address those tasks, through various stabilization training techniques \cite{salimans2016improved,arjovsky2017wasserstein,berthelot2017began,shrivastava2016learning,odena2016conditional}, regularization using outside knowledge (e.g.
+image labels, ImageNet CNNs, etc) \cite{dosovitskiy2016generating,ledig2016photo,dash2017tac,dash2017tac}, or multiple discriminators  \cite{metz2016unrolled,durugkar2016generative,yang2017lr}.
+\textit{While our method does not use any extra information apart from training paired text and images.} Moreover, it is easy to see the training difficulty increases significantly as targeting image resolution increases.
 
@@
 Following this strategy, Chen \etal \cite{chen2017photographic} present a cascaded refinement network to synthesize high-resolution scene from semantic maps.
-%%Huang \etal \cite{huang2016stacked} propose a top-down stacked GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method.
+Huang \etal \cite{huang2016stacked}
+propose a top-down stacked GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method.
 However, this method needs multiple symmetric bottom-up pre-trained discriminators and the usage for high-resolution image is unclear.
@@
 DSN \cite{lee2015deeply} proposes deep supervision in hierarchical convolutional layers to increase the discriminativeness of feature representations.
-\textit{Our hierarchically-nested adversarial objective is inspired by these families of CNNs with deep supervision. }
+\textit{Our hierarchically-nested adversarial objective is inspired by these kinds of CNNs with deep supervision. }
 %Our proposed hierarchically-nested adversarial supervision enhances layer representations to support final high resolution outputs.
@@
 \begin{split}
-G^*, D^* = \arg~\underset{G}{\min}\ \underset{D}{\max}~ \mathcal{V}(D, G, Y, \bm z)
+G^*, D^* = \arg~\underset{G}{\min}\ \underset{D}{\max}~ \mathcal{L}(D, G, Y, \bm z)
 \end{split}
@@
 \textcolor{red}{where $Y$ denotes training images and $\bm z\sim\mathcal{N}(0,1)$ denotes a random noise.
-The value function $\mathcal{V}$ aims to minimize the Jensen-Shannon divergence between the data and the model distribution.
-$G$ is learned to approximate $G(\bm z) \sim p(Y)$.
-The loss $\mathcal{L}$ for the valuation function is usually a cross-entropy loss, such that $\mathcal{V}(\cdot) = - \mathcal{L}(\cdot)$.
+The loss $\mathcal{L}$ aims to minimize the Jensen-Shannon divergence between the data and model distributions.
 }
@@
 \begin{split}
-  \mathcal{G}^*, \mathcal{D}^*&  =  \arg~\underset{G}{\min}\ \underset{\mathcal{D}}{\max}~ \mathcal{V}(\mathcal{G},\mathcal{D}, \mathcal{Y}, \bm t, \bm z) \\
+  \mathcal{G}^*, \mathcal{D}^*&  =  \arg~\underset{G}{\min}\ \underset{\mathcal{D}}{\max}~ \mathcal{L}(\mathcal{G},\mathcal{D}, \mathcal{Y}, \bm t, \bm z) \\
   \text{where} \;\;	 \mathcal{D} & \in  \{D_1, ..., D_s\}, \; \mathcal{Y} = \{Y_1, ..., Y_s\}
@@
 In principle, the lower-resolution side output is forced to learn semantic consistent image structures (e.g., object sketch, color, and background), and the subsequent higher-resolution side outputs are used to render details to the images.
-To satisfy this goal, we present the following adversarial loss to support more effective multi-purpose discriminators.
-Since the model is trained in an end-to-end fashion, we can obtain more consistent information exhibited in both lower and higher-resolution outputs compared with StackGAN (see experiments).
-}
+Since the model is trained in an end-to-end fashion, we can obtain more consistent information exhibited in both lower and higher-resolution outputs compared with StackGAN.
+More results can be founded in experiments.
+According to this goal, we present the following adversarial losses to support more effective multi-purpose discriminators.}
 
@@
 To guarantee semantic consistency, we adopt the matching-aware pair loss proposed by \cite{reed2016generative}.
-The discriminator is designed to take image-text pairs as inputs and trained to identify two types of fakes: real image with mismatched text and fake image with conditioned text.
+The discriminator is designed to take image-text pairs as inputs and is trained to identify two types of fakes: real image with mismatched text and fake image with conditioned text.
 
@@
 	\includegraphics[width=0.49\textwidth]{figure/loss.pdf}
-	\vspace{-.5cm}
-	\caption{Given an image in the side output pyramid of the generator, the corresponding discriminator $D_i$ computes the matching-aware pair loss and adaptive local image loss (outputting a $R{\times}R$ probability map to classify real or fake patches).
+	\vspace{-.2cm}
+	\caption{Given an image in the side output pyramid of the generator, the corresponding discriminator $D_i$ computes the matching-aware pair loss and adaptive local image loss (outputting a $R{\times}R$ probability map to indicate real or fake patches).
 The focal range increases as image resize grows.
@@
 
-\textbf{Full Objective } Overall, our hierarchically-nested discriminators $\{D_i\}$ minimize the following loss\footnote{The objective of the generator is omitted as it can be easily inferred.}:
+\textbf{Full Objective } Overall, our hierarchically-nested discriminators $\{D_i\}$ minimize the following objective\footnote{The objective of the generator is omitted as it can be easily inferred.}:
 \vspace{-.2cm}
@@
 \end{equation}
-where $L_2(x) = (x - \mathbb{I})^2$ is the mean-square loss (instead of the conventional cross-entropy loss) and $\overline{L_2}(x) =x^2$.
-For local image loss with varying focal ranges, the shape of $x, \mathbb{I} \in \mathbb{R}^{R{\times}R}$ varies accordingly (see Figure \ref{fig:loss}).
-$R=1$ refers to the (largest local) global range.
+where ${X}_i = \mathcal{G}(\bm{t}_{X}, \bm z)$.
+$L_2(x) = (x - \mathbb{I})^2$ is the mean-square loss (we do not use the original cross-entropy loss) and $\overline{L_2}(x) =(x)^2$.
+For adaptive local image loss with varying focal range, the shape of $x, \mathbb{I} \in \mathbb{R}^{R{\times}R}$ varies accordingly (see Figure \ref{fig:loss}) for the local image loss.
+$R=1$ refers to the (largest local) global range, e.g., $R\equiv1$ for the matching aware pair loss.
 For the matching-aware pair loss,
@@
 The CUB and Oxford-102 datasets are trained for 500 epochs in total (250 epochs for COCO).
-For the local image loss, we set $R=1$ and for $64^2$ and $128^2$ side outputs and $R=5$ for $256^2$ and $512^2$ outputs.
+For the adaptive local image loss, we set $R=1$ for $64^2$ side output, $R=3$ for $128^2$ side output and $R=5$ for $256^2$ and $512^2$ outputs.
 We use 1-repeat residual block for the generator till $256^2$ resolution.
@@
 We use $3$-repeat res-block followed by the stretching and linear compression layer.
-Since the $256^2$ image already captures the overall semantics and details, to encourage the $512^2$ maintain these information, we use a l1 reconstruction loss to self-regularize the generator in case the discriminator confuses the expected output.}
+maybe delete the l1 loss description.
+Since the $256^2$ image already captures the overall semantics and details, to encourage the $512^2$ maintain these information, we also use a reconstruction loss to self-regularize the generator in case the discriminator confuses the expected output.}
 %for the consideration of memory saving and faster convergence.
@@
 1) Inception score \cite{improvedGAN} is a measurement of both objectiveness and diversity of generated images, it is closely correlated with human judgment on the image quality.
-For CUB and Oxford-102, we use the fine-tuned inception model provided by StackGAN.
+For CUB and oxford-102, we use the fine-tuned inception model provided by StackGAN.
 For MS COCO dataset, we directly use the model pre-trained on ImageNet.
@@
 	\vspace{-.2cm}
-	\caption{The generated images on Oxford-102 compared with StackGAN.
-Our generated images perform more natural satisfiability and higher contrast and can generate complex flower structures (e.g.
-spiked petals) like the third example.} \label{fig:vis-oxford}
+	\caption{The generated images on Oxford compared with StackGAN.
+Each sample shows the input text and generated $64^2$ (left) and $256^2$ (right) images.
+Our generated images perform more natural satisfiability and higher contrast.} \label{fig:vis-oxford}
 	\vspace{-.2cm}
@@
 \subsection{Comparative Results}
-To validate our method, we compare our results with GAN-INT-CLS \cite{reed2016generative}, GAWWN \cite{reed2016learning}, TAC-GAN \cite{dash2017tac}, StackGAN \cite{han2017stackgan} and also its improved version StackGAN++ \cite{han2017stackganv2}, and Progressive GAN \cite{Karras2017progressive}\footnote{StackGAN++ and Prog.GAN are two very recently released preprints we noticed.
-We acknowledge them as they also target at generating high-resolution images.
-}.
-We especially compare with the current state of the art, StackGAN (results are obtained from its provided model).
+To validate our method, we compare our results with GAN-INT-CLS \cite{reed2016generative}, GAWWN \cite{reed2016learning}, TAC-GAN \cite{dash2017tac}, StackGAN \cite{han2017stackgan} and also its improved version StackGAN++ \cite{han2017stackganv2}, and Progressive GAN \cite{Karras2017progressive} \footnote{StackGAN++ and Prog.GAN are two very recently released preprints we noticed.
+We acknowledge them as they also target at generating high-resolution images, in spite of their differences in motivations and network and training designs from ours.
+} We especially compare with the current state of the art, StackGAN (results are obtained from its provided model).
 
@@
 
-Table \ref{table:score} shows the quantitative inception-score evaluation. We follow StackGAN' experiment to sample ${~}30,000$ $256^2$ images for evaluation.
+Table \ref{table:score} shows the quantitative inception-score evaluation. We follow StackGAN to sample ${~}30,000$ images for evaluation.
 HDGAN achieves significantly improvement compared against other methods. For example, it improves StackGAN by $.45$ and StackGAN++ by $.31$ on CUB.
-HDGAN achieves competitive results with TAC-GAN on Oxford-102.
+HDGAN achieves competitive results with TAC-GAN on Oxford.
 TAC-GAN uses image labels to increase the discriminability of generators, while we do not use any extra knowledge.
@@
 We also add the evaluation results on the ground truth image and sentence pair for reference.
-Our proposed method achieves much better results on both CUB and Oxford-102 datasets.
+Our proposed method achieves much better results on both CUB and Oxford datasets.
 Since we do not have a pre-trained  StackGAN model for coco dataset, we omit the comparison.
@@
 	\caption{Left: Diversity test given a single input text.
-The proposed HDGAN (top) show obviously more details and higher diversity.
+HDGAN (top) show obviously more details and higher diversity.
 Right: Side outputs of HDGAN with increasing resolutions.
@@
 	\centering
-	\includegraphics[width=0.245\textwidth]{figure/multiscale_inception_2.pdf}
+	\includegraphics[width=0.245\textwidth]{figure/multiscale_inception.pdf}
 	\vspace{-12pt}
@@
 	\vspace{-.5cm}
-	\caption{Text embedding interpolation from the source to target sentence results in smooth image style changes to match the targeting sentence. } \label{fig:interp}
+	\caption{Text embedding interpolation from the source to target sentence results in smooth image changes approaching the targeting sentence. } \label{fig:interp}
 	\vspace{-.3cm}
@@
 
+\begin{table}[t] % retrieval
+	\small
+	\begin{minipage}[b]{0.5\linewidth}
+		\begin{tabularx}{1\textwidth}{c@{\hskip1pt}|c@{\hskip1pt}|c@{\hskip1pt}}
+			\specialrule{1.5pt}{0pt}{0pt}  
+			Metric 			&   Inception 	 & VS   	\\  \hline
+			wo/local        &   $3.12{\pm}.018$      &   $.263{\pm}.13$           \\  \hline
+			w/local         &   $3.45{\pm}.07$ 	 &   $.296{\pm}.13$		    \\ \hline
+		\end{tabularx}
+		\vspace{-0.8cm}
+	\end{minipage} %\hfill
+	\begin{minipage}[b]{0.49\linewidth}
+		\begin{tabularx}{.98\textwidth}{ccc|c}
+			\specialrule{1.5pt}{0pt}{0pt}  
+			\multicolumn{3}{c|}{Components}	&  \multirow{2}{*}{\thead{Inception \\ score}}	\\ \cline{1-3}
+			64	& 128	& 256 			& 		\\ \hline
+			&  		&	\checkmark	&	${3.52{\pm}.04}$	\\ 
+			&  	\checkmark	&	\checkmark	&	${3.99{\pm}.04}$	\\
+			\checkmark	&  			&	\checkmark	&  ${4.14{\pm}.03}$		\\
+			\checkmark	&  \checkmark		&	\checkmark	&	${4.15{\pm}.05}$ \\ \hline
+
+		\end{tabularx}
+	\end{minipage}
+	\vspace{-0.2cm}
+	\caption{Ablation study on the local adversarial loss (left table) and hierarchically-nested adversarial learning (right table). See text for detailed explanation.} \label{tab:ablation}
+\end{table}
+
 \subsection{On the Local Image Loss}
 
-\textcolor{red}{We also study the effectiveness of the proposed local image loss.
-We conduct experiments with using architecture with side output 64$\times$64, 128$\times$128 and 256 $\times$ 256 using CUB dataset.
-As can be seen in Table\ref{tab:local_loss}, we can see that by removing local image loss (denoted as "No Local"), the inception score drop from \textcolor{red}{4.27} to \textcolor{red}{3.8}.
-To quantitatively compare the results, we also show generated results using two model in Figure \ref{local_or_not}, We can see that, although both models can successfully capture the semantic correspondence between image and sentence, 256$\times$ 256 results generated by model trained with local image loss provide more local fine-grained details, thus improving the visual quality.
+We also study the effectiveness of the proposed local image loss.
+We conduct experiments with using architecture with side output 64$\times$64, 128$\times$128 and 256 $\times$ 256 using Oxford dataset.
+As can be seen in Table\ref{tab:ablation}, we can see that by removing local image loss (denoted as "wo/ Local"), the inception score drop from \textcolor{red}{3.45} to \textcolor{red}{3.12}, which proven that adding local image loss can help to improve the visual quality of the generated images.
+Besides, local image loss also helps to improve the visual-semantic matching evidenced by the higher VS score of w/local.
+We hypothesis that it is because adding separate local image loss can help the pair-wise loss to focus on learning the pair-wise matching task.
+
+\textcolor{red}{To quantitatively compare the results, we also show generated results using two model in Figure \ref{local_or_not}, We can see that, although both models can successfully capture the semantic correspondence between image and sentence, 256$\times$ 256 results generated by model trained with local image loss provide more local fine-grained details, thus improving the visual quality.
 }
@@
 
-\begin{table}[t] % retrieval
-	\small
-	\begin{minipage}[b]{0.5\linewidth}
-			\begin{tabularx}{.98\textwidth}{c@{\hskip1pt}|c@{\hskip1pt}c@{\hskip1pt}}
-				\specialrule{1.5pt}{0pt}{0pt}  
-				Metric 			&   VS 	 & MS-SSMI   	\\  \hline
-				w/o Img         &   $.25{\pm}.16$      &   $.215$           \\  \hline
-				w/ global       &   $-$      &   $-$           \\ \hline
-				w/local         &   $-$ 	 &   $-$		    \\ \hline
-			\end{tabularx}
-		\vspace{-0.8cm}
-	\end{minipage} %\hfill
-	\begin{minipage}[b]{0.49\linewidth}
-		\begin{tabularx}{.98\textwidth}{ccc|c}
-			\specialrule{1.5pt}{0pt}{0pt}  
-			\multicolumn{3}{c|}{Components}	&  \multirow{2}{*}{\thead{Inception \\ score}}	\\ \cline{1-3}
-			64	& 128	& 256 			& 		\\ \hline
-			&  		&	\checkmark	&	${3.52{\pm}.04}$	\\ 
-			&  	\checkmark	&	\checkmark	&	${3.99{\pm}.04}$	\\
-			\checkmark	&  			&	\checkmark	&  ${4.14{\pm}.03}$		\\
-			\checkmark	&  \checkmark		&	\checkmark	&	${4.15{\pm}.05}$ \\ \hline
-
-		\end{tabularx}
-	\end{minipage}
-	\vspace{-0.2cm}
-	\caption{Ablation study on the local adversarial loss (left table) and hierarchically-nested adversarial learning (right table). See text for detailed explanation.} \label{tab:ablation}
-\end{table}
-
 \subsection{Design principles}
@@
 \section{Conclusion}
-In this paper, we present an effective and end-to-end method to tackle the problem of generating high-resolution images conditioned on text descriptions.
-We introduce a novel hierarchical-nested adversarial discriminators to regularize the mid-level representations of a generator.
-To improve the model's capability to render fine-grained local details, we propose a multi-purpose discriminator loss to emphasize local patch realism as well as matching aware pair.
+In this paper, we present a novel, effective, and end-to-end method to tackle the problem of generating high resolution images using text description.
+We introduce the hierarchical-nested adversarial discriminators to help generator training.
+To improve the model's capability to render fine-grained local details, we propose a hierarchal local image loss to emphasize local patch realism.
 We also introduce a new evaluation metric for text-to-image synthesis to evaluate the semantic consistency between generated images and conditioned text.

### 2017-11-14 cvpr2018.tex

--- 2017-11-13 cvpr2018.tex
@@
 
-\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
+\def\cvprPaperID{2823} % *** Enter the CVPR Paper ID here
 \def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
@@
 Furthermore, we introduce a new visual-semantic similarity measure to evaluate the semantic consistency of generated images.
-With extensive experimental validation on three major datasets, our method significantly improves previous state of the arts on all datasets over different evaluation metrics. 
+With extensive experimental validation on three major datasets, our method significantly improves previous state of the arts on all datasets over different evaluation metrics (e.g.
+a ${11.86}$ Inception score on COCO).
 \end{abstract}
@@
 Reed \etal \cite{reed2016generative} address this task through a GAN based framework. But this method only handles image up to $64^2$ resolution and can barely generate vivid object details.
-Based on this method, Zhang \etal \cite{han2017stackgan} present a successful two-state training approach (StackGAN) by stacking another low-to-high resolution GAN to generate high-quality $256^2$ images.
-Later on, Dong \etal \cite{dong2017semantic} propose to bypass the difficult of translate vector embedding to RGB images and treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-rendering an arbitrary-style training ($128^2$) image conditioned on a targeting description.
+Based on this method, StackGAN  \cite{han2017stackgan} is a successful method that stacks another low-to-high resolution GAN to generate high-quality $256^2$ images, with two training stages.
+Later on, \cite{dong2017semantic} proposes to bypass the difficult of learning mappings from vector embeddings to RGB images but treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-rendering an arbitrary-style training $128^2$ image conditioned on a targeting description.
 But its high-resolution synthesis ability is unclear.
@@
 To guarantee the image diversity and semantic consistency,
-\textcolor{red}{we enforce nested discriminators at different hierarchies to simultaneously differentiate real-and-fake image-text pairs as well as real-and-fake global images or local image patches with certain focal ranges.}
+we enforce nested discriminators at different hierarchies to simultaneously differentiate real-and-fake image-text pairs as well as real-and-fake global images or local image patches with certain focal ranges.
 This multi-purpose conditional adversary is mutually beneficial to allow each focus on its respect duty. 
@@
 \textbf{A} and \textbf{C} can be viewed as decomposing high-resolution tasks to multi-stage low-to-high resolution tasks.
-\textbf{D} is our proposed framework that uses a single-stream generator with hierarchically-nested discriminators trained end-to-end.} \label{fig:archs-review}
+\textbf{D} is our proposed framework that uses a single-stream generator with hierarchically-nested discriminators trained end-to-end.} \label{fig:archs-review} \vspace{-.4cm}
 \end{figure*}
@@
 %We conjecture that adding hierarchical adversarial objective using side outputs can
-act as regularizers to the hidden space of $\mathcal{G}$, which can reduce the training instability and also offer a short path for better error signals.
-
-The proposed $\mathcal{G}$ is a CNN (defined in Section 3.4) with side outputs:
-
+act as regularizers to the hidden space of $\mathcal{G}$, which can reduce the training instability and also offer a short path for better error signal flows.
+
+The proposed $\mathcal{G}$ is a CNN (defined in Section 3.4) with multiple side outputs:
 %This architecture resemble the proposed inverse architectures in edge detection\cite{xie2015holistically} and classification \cite{lee2015deeply}, which demonstrate that additional supervision to hidden layers can improve model generalization and boost optimization.
@@
 where  $\bm t\sim p(data)$ denotes a sentence embedding vector in the real training data distribution (generated by a text character encoder).
-$\mathcal{G}$ produces $s-1$ side outputs (size-growing images) and a final output $X_s$ with the highest resolution.
+$\mathcal{G}$ produces $s-1$ side outputs $\{X_1,...,X_{s-1}\}$ (size-growing images) and a final output $X_s$ with the highest resolution.
 
@@
 %%Discriminators do not share weights with each other, which offers them full flexibility to focus on learning diverse discriminative features in different contextual scales.
-In principle, the lower-resolution side output is forced to learn semantic consistent image structures (e.g., object sketch, color, and background), and the subsequent higher-resolution side outputs are used to render details to the images.
-Since the model is trained in an end-to-end fashion, the lower-resolution outputs can fully enjoy top-down knowledge from higher resolutions.
-We hypothesize such consistency reduces the model instability.
-As an evidence, we can obtain significantly more consistent information exhibited in both low- and high-resolution outputs compared with StackGAN (see experiments). 
-%%We present the following multi-purpose adversarial loss to support more effective generator training.
+In principle, the lower-resolution side output is forced to learn semantic consistent image structures (e.g., object sketch, color, and background), and the subsequent higher-resolution side outputs are used to render details to images and preserve these image structures.
+Since our method is trained in an end-to-end fashion, the lower-resolution outputs can also fully enjoy top-down knowledge from discriminators for higher resolutions.
+We can observe consistent image structures and styles in both low and high resolutions.
+We think such consistency is able to reduce the model instability.
+As an evidence, we can obtain significantly more consistent results exhibited in both low- and high-resolution outputs compared with StackGAN (see experiments). 
+%% %We present the following multi-purpose adversarial loss to support more effective generator training.
 
@@
 The pair loss is designed to guarantee the global semantic consistency.
-However, there is no explicit loss that forces the discriminator to differentiate real images from fake images.
+However, there is no explicit loss that forces the discriminator to differentiate pure real images from fake images.
 As the image resolution goes higher, discriminators might loss focus for local fine-grained image details.
@@
 
-To guarantee image fidelity, our solution is to add local adversarial image losses on image patches. 
+To guarantee the image fidelity, our solution is to add local adversarial image losses on image patches. 
 %The insights are two folds:
@@
 We expect the low-resolution discriminator to focus on global structures, while high-resolution outputs focus more on local image details.
-Therefore, through the pyramid of the size-growing side outputs, we configure the focal range (the size of each non-overlapping image patch need to classify) to be also growing.
-The local image adversarial loss is implemented as a fully CNN \cite{shrivastava2016learning,zhu2017unpaired}.  
+We validate this analysis in the experiments.
+Through the pyramid of the size-growing side outputs, we configure the focal range (the size of each image patch need to classify) to be adaptive.
+The local image adversarial loss is implemented as a fully CNN \cite{shrivastava2016learning,zhu2017unpaired},  with an extra branch of the discriminator for the pair loss (see Section 3.4).
 Figure \ref{fig:loss} illustrates how hierarchically-nested discriminators compute the two losses on generated images.
@@
 	\includegraphics[width=0.49\textwidth]{figure/loss.pdf}
-	\vspace{-.5cm}
+	\vspace{-.7cm}
 	\caption{Given a set of images from the side output pyramid of the generator, the corresponding discriminator $D_i$ computes the matching-aware pair loss and adaptive local image loss (outputting a $R{\times}R$ probability map to classify real or fake patches).
@@
 
-\textcolor{red}{All other intermediate conv layers for both generators and discriminators use $3{\times}3$ kernels (with reflection padding).
-We also experimented other normalization (i.e.
-instance normalization \cite{ulyanov2016instance} and layer normalization \cite{ba2016layer}) used by recent advances \cite{zhu2017unpaired,chen2017photographic}.
-Both are not satisfactory.
-}
-
-\subsection{Training Details}
-%The algorithm that summarizes the training process of our model is given in Algorithm 1. 
-%We train and evaluate our model with a devbox machine. $\alpha$ is set to 0.5, $\beta$ is set to 4.
-The Adam optimizer is used for all experiments.
-The initial learning rate is set as 0.0002 and decreased by half for every 100 epochs (30 for COCO).
-The CUB and Oxford-102 datasets are trained for 500 epochs in total (250 epochs for COCO).
-For the local image loss, we set $R=1$ and for $64^2$ and $128^2$ side outputs and $R=5$ for $256^2$ and $512^2$ outputs.
-We use 1-repeat residual block for the generator till $256^2$ resolution.
-\textcolor{red}{To generate $512^2$ images, we pre-train the generator to $256^2$ due to the limitation of GPU memory.
-We use $3$-repeat res-block followed by the stretching and linear compression layer.
-Since the $256^2$ image already captures the overall semantics and details, to encourage the $512^2$ maintain these information, we use a l1 reconstruction loss to self-regularize the generator in case the discriminator confuses the expected output.}
+The training is similar with the standard GAN alternative training strategy. Please refer to the supplementary material for training details.
+
 %for the consideration of memory saving and faster convergence.
@@
 \textbf{Dataset} 
-\textcolor{red}{We test on three widely used datasets.
+We test on three widely used datasets.
 The CUB dataset \cite{welinder2010caltech} contains 11,788 bird images belonging to 200 different categories.
@@
 Each image in both datasets is associated with 10 text descriptions.
-\textcolor{red}{In the COCO dataset, \cite{lin2014microsoft} there are 80k training images and a validation 40k images.
+In the COCO dataset, \cite{lin2014microsoft} there are 80k training images and a validation 40k images.
 Each image has 5 text descriptions.
-}
 We use the pre-trained text encoder model provided in \cite{reed2016generative} to encode each text description into a 1024 embedding vector.
 %During the training stage, we randomly pick-up a crop view from the original images, and pick 4 image sentence embedding and use the mean as conditioning vector.
-}
 
@@
 3) Visual-semantic similarity.
-The problem of the aforementioned metrics is that they can not measure the alignment between the generated images and conditioned text.
+The aforementioned metrics are widely used for general GANs.
+The problem of them is that they can not measure the alignment between the generated images and conditioned text.
 We introduce a new qualitative measurement, namely visual-semantic similarity (VS similarity) inspired by \cite{vsemb}.
-Denote $\bm{v}$ as the image feature vector extract by a pre-trained CNN on ImageNet $f_v$.
+Denote $\bm{v}$ as the image feature vector extracted by a Inception CNN.
 We define a scoring function $C(\bm{x}, \bm{y})=\frac{\bm{x}\cdot \bm{y}}{||\bm{x}||\cdot ||\bm{y}||}$. 
-We learn two mapping functions $f_v$ and $f_t$, which map both image and sentence embeddings into one semantic space $\mathbb{R}^{512}$, by minimizing the following bi-directional ranking loss:
+Then, we learn two mapping functions $f_v$ and $f_t$, which map both image and sentence embeddings into a common space in $\mathbb{R}^{512}$, by minimizing the following bi-directional ranking loss:
 \begin{equation}\vspace{-.2cm}
@@
 $\{\bm{v}, \bm{t}\}$ is a ground truth image text pair, and $\{\bm v, \bm t_{\overline{v}} \}$ and $\{ \bm v_{\overline{v}}, \bm{t} \}$ denote mismatched image-text pairs.
-In the testing stage, given an text embedding $\bm{t}$, and the generated images $o$, the corresponding vs-similarity will be calculated as $s(f_{cnn}(o), \bm{t})$.
-Higher score indicates higher semantic consistency.
+In the testing stage, given an text embedding $\bm{t}$, and the generated image encoded by the Inception-CNN $\bm v$, the VS score is calculated as $C(\bm v, \bm{t})$.
+Higher score indicates better semantic consistency, i.e.
+stronger alignment between generated images and conditioned text.
 
@@
 			\multirow{2}{*}{Method}	& \multicolumn{3}{c}{Dataset}	\\ \cline{2-4}
-							 		&	 CUB		&	Oxford  & COCO		     \\ \hline
+							 		&	 CUB		&	Oxford-102  & COCO		     \\ \hline
 			GAN-INT-CLS 	&	$2.88{\pm}.04$		& 	$2.66{\pm}.03$		& $7.88{\pm}.07$	 \\
@@
 			TAC-GAN	 &	-		&		$3.45{\pm}.05$		& -	\\	\hline
-			HDGAN 		&	$\bm{4.15{\pm}.05}$	&	$ \bm{3.45{\pm}.07}$	&  $ \bm{11.29{\pm}.18}$  \\ \hline
+%			HDGAN 		&	$\bm{4.15{\pm}.05}$	&	$ \bm{3.45{\pm}.07}$	&  $ \bm{11.29{\pm}.18}$  \\ \hline
+			HDGAN 		&	$\bm{4.15{\pm}.05}$	&	$ \bm{3.45{\pm}.07}$	&  $ \bm{11.86{\pm}.18}$  \\ \hline
 		\end{tabularx} 
@@
 \end{table}
-
-%\begin{table}[t] % retrieval
-%	\begin{center}
-%		\begin{tabularx}{.32\textwidth}{c|cc}
-%			\specialrule{1.5pt}{0pt}{0pt}
-%			Scale 						& StackGAN & HDGAN 					\\ 				\hline
-%			$64{\times}64$              &   ${2.95{\pm}.02}$       &  	$\bm{3.53{\pm}.03}$ \\
-%			$128{\times}128$             &   ${3.35{\pm}.02}$      &  $\bm{3.97{\pm}.03}$		\\
-%			$256{\times}256$             &   $3.70{\pm}.04$     &	$\bm{4.15{\pm}.05}$ \\ \hline
-%		\end{tabularx}
-%	\end{center} \vspace{-.4cm}
-%	\caption{Multi-scale inception score comparison. See text for explanation.} \label{table:multiscales}
-%\end{table}
 
@@
 			\multirow{2}{*}{Method}	& \multicolumn{3}{c}{Dataset}	\\ \cline{2-4}
-			&	 CUB		&	Oxford  & COCO		     \\ \hline
+			&	 CUB		&	Oxford-102  & COCO		     \\ \hline
 			Ground Truth	&	${.302{\pm}.151}$	&	$ {.336{\pm}.138}$			& $.426{\pm}.157$  \\ \hline
@@
 	\vspace{-.4cm}
-	\caption{The VS similarity evaluation on the three datasets. The higher score represents higher semantic consistency between the generated images and the text information. } \label{table:vss}
+	\caption{The VS similarity evaluation on the three datasets.
+The higher score represents higher semantic consistency between the generated images and the text information.
+The groundtruth score is shown in the first row.} \label{table:vss} \vspace{-.3cm}
 \end{table}
@@
 \subsection{Comparative Results}
-To validate our method, we compare our results with GAN-INT-CLS \cite{reed2016generative}, GAWWN \cite{reed2016learning}, TAC-GAN \cite{dash2017tac}, StackGAN \cite{han2017stackgan} and also its improved version StackGAN++ \cite{han2017stackganv2}, and Progressive GAN \cite{Karras2017progressive}\footnote{StackGAN++ and Prog.GAN are two very recently released preprints we noticed.
+To validate our proposed HDGAN, we compare our results with GAN-INT-CLS \cite{reed2016generative}, GAWWN \cite{reed2016learning}, TAC-GAN \cite{dash2017tac}, StackGAN \cite{han2017stackgan} and also its improved version StackGAN++ \cite{han2017stackganv2}, and Progressive GAN \cite{Karras2017progressive}\footnote{StackGAN++ and Prog.GAN are two very recently released preprints we noticed.
 We acknowledge them as they also target at generating high-resolution images.
@@
 
-Table \ref{table:score} shows the quantitative inception-score evaluation. We follow StackGAN' experiment setting to sample ${~}30,000$ $256^2$ images for evaluation.
+Table \ref{table:score} shows the quantitative inception-score evaluation. We follow StackGAN' experiment setting to sample ${\sim}30,000$ $256^2$ images for evaluation.
 HDGAN achieves significantly improvement compared against other methods. For example, it improves StackGAN by $.45$ and StackGAN++ by $.31$ on CUB.
@@
 Figure \ref{fig:vis-cub} and Figure \ref{fig:vis-oxford} show the results compared with StackGAN and strongly demonstrate the superiority of HDGAN.
-Mover, we also qualitatively test the diversity of samples conditioned on the same text in Figure \ref{fig:multiple-test} left.
-It also demonstrates how well the model learned to cover the input distribution.
-HDGAN shows obvious more successful samples than StackGAN.
-
-Table \ref{table:vss} shows the qualitative vs-similarity comparison results on three datasets.
+Moreover, we qualitatively evaluate the diversity of samples conditioned on the same text (with different input noises) in Figure \ref{fig:multiple-test} left.
+HDGAN can generate obviously more successful samples than StackGAN.
+
+Table \ref{table:vss} compares the VS results on the three datasets.
 We also add the evaluation results on the ground truth image and sentence pair for reference.
-Our proposed method achieves much better results on both CUB and Oxford-102 datasets.
-Since we do not have a pre-trained  StackGAN model for coco dataset, we omit the comparison.
-This results demonstrate that HDGAN is better at capturing visual semantic correlation.
+HDGAN achieves consistent better performance on both CUB and Oxford-102 datasets.
+This results demonstrate that HDGAN can better capture the visual semantic information in generated images and results in higher visual similarity.
+%%Our proposed method achieves much better results on both CUB and Oxford-102 datasets. Since we do not have a pre-trained  StackGAN model for coco dataset, we omit the comparison.
 
@@
 
-Table \ref{fig:msssmi} compares the MS-SSMI image quality evaluation score with StackGAN and Prog.GAN for bird image generation.
+Table \ref{fig:msssmi} compares the MS-SSMI image quality evaluation score with StackGAN and \textcolor{red}{Prog.GAN for bird} image generation.
 StackGAN and our HDGAN use the semantic text as input so the generated images are separable in class.
@@
 %%We fix the random noise input to make the object and background consistent.
-As is shown in Figure~\ref{fig:interp}, the generated images show smooth style transformation and well reflect the semantic details in sentences. 
+As shown in Figure~\ref{fig:interp}, the generated images show smooth style transformation and well reflect the semantic details in sentences. 
 In the first row, the generated birds gradually turn the color from yellow to brown.
-In the second row, more complicated sentences containing more detailed appearance information (e.g., blue peaks and yellow wing) are used, we can see that our model is still be able to successfully capture these subtle information and tune the bird appearance gradually.
+In the second row, more complicated sentences with detailed appearance descriptions (e.g., blue peaks and yellow wing) are used, we can see that our model is still be able to successfully capture these subtle features and tune the bird appearance gradually.
 
@@
 \subsection{On the effects of Individual Components}
-\subsubsection{Hierarchically-nested adversarial training}
-Our hierarchically-nested adversarial discriminators a role of regularizing the layer representations (at scale $\{64, 128, 256\}$). 
+%%\subsubsection{Hierarchically-nested adversarial training}
+\textbf{Hierarchically-nested adversarial training} Our hierarchically-nested discriminators play a role of regularizing the layer representations (at scale $\{64, 128, 256\}$). 
 %Our full method applies it on feature maps at $\{64, 128, 256\}$. 
-In Table \ref{tab:ablation} right, we compare the results by removing part of discriminators. 
+In Table \ref{table:multiscales}, we compare the performance of HDGAN by removing part of discriminators on both CUB and COCO datasets. 
 As can be seen, increasing the usage of discriminators at different scales have positive effectives.
 And using discriminators on $64^2$ is critical (by comparing 64-256 and 128-256 cases).
-For now, we are unsure if adding more discriminators and adding on lower resolution would be helpful.
+For now, we are unsure if adding more discriminators and even on lower resolution would be helpful.
 Further investigation will be conducted to validate it.
-StackGAN emphasizes the importance of using text embeddings with mid-level features of the $256^2$ generator by showing an large drop from $3.7$ to $3.45$ without doing so, which helps maintains the diversity and semantic consistency.
-While in our method, we only use text embeddings at the input.
-Our significantly improved results demonstrate that effectiveness of the hierarchically-nested adversarial training to achieve this goal.
-
-\subsubsection{On the Local Image Loss}
-
-\textcolor{red}{We also study the effectiveness of the proposed local image loss.
-We conduct experiments with using architecture with side output 64$\times$64, 128$\times$128 and 256 $\times$ 256 using CUB dataset.
-As can be seen in Table\ref{tab:local_loss}, we can see that by removing local image loss (denoted as "No Local"), the inception score drop from \textcolor{red}{4.27} to \textcolor{red}{3.8}.
-To quantitatively compare the results, we also show generated results using two model in Figure \ref{local_or_not}, We can see that, although both models can successfully capture the semantic correspondence between image and sentence, 256$\times$ 256 results generated by model trained with local image loss provide more local fine-grained details, thus improving the visual quality.
-}
+StackGAN emphasizes the importance of combining text embeddings with intermediate features of the $256^2$ generator by showing a large drop from $3.7$ to $3.45$ without doing so.
+While our method only uses text embeddings at the input.
+Our significantly improved results demonstrate the effectiveness of our strategy to maintain such semantic information and high inception score.
 
@@
 \end{figure}
+
+%\begin{table}[t] % retrieval
+%	\small
+%	\begin{minipage}[b]{0.49\linewidth}
+%		\begin{tabularx}{1\textwidth}{c@{\hskip1.5pt}|c@{\hskip3pt}|c@{\hskip0.5pt}}
+%			\specialrule{1.5pt}{0pt}{0pt}  
+%			 			&   Inc. score 	 & VS   	\\  \hline
+%			\thead{w/o \\ local}        &   $3.12{\pm}.02$      & $.263{\pm}.130$           \\  \hline
+%			\thead{w/ \\ local}        &   $3.45{\pm}.07$ 	 &   $.296{\pm}.130$		    \\ \hline
+%		\end{tabularx}
+%		\vspace{-0.995cm}
+%	\end{minipage} %\hfill
+%	\begin{minipage}[b]{0.49\linewidth}
+%		\begin{tabularx}{.98\textwidth}{ccc|c}
+%			\specialrule{1.5pt}{0pt}{0pt}  
+%			\multicolumn{3}{c|}{Components}	&  \multirow{2}{*}{\thead{Inception \\ score}}	\\ \cline{1-3}
+%			64	& 128	& 256 			& 		\\ \hline
+%			&  		&	\checkmark	&	${3.52{\pm}.04}$	\\ 
+%			&  	\checkmark	&	\checkmark	&	${3.99{\pm}.04}$	\\
+%			\checkmark	&  			&	\checkmark	&  ${4.14{\pm}.03}$		\\
+%			\checkmark	&  \checkmark		&	\checkmark	&	${4.15{\pm}.05}$ \\ \hline
+%			
+%		\end{tabularx}
+%	\end{minipage}
+%	\vspace{-0.2cm}
+%	\caption{Ablation study on the local adversarial loss (left table) and hierarchically-nested adversarial discriminators (right table).
+\checkmark indicates whether a discriminator at a certain scale is used.
+See text for detailed explanation.} \label{tab:ablation} \vspace{-0.3cm}
+%\end{table}
+\begin{table}[t] % retrieval
+	\begin{center}
+		\begin{tabularx}{.36\textwidth}{ccc|cc}
+			\specialrule{1.5pt}{0pt}{0pt}  
+			\multicolumn{3}{c|}{Components}	&  \multicolumn{2}{c}{Inception score}	\\ \hline
+			64	& 128	& 256 			& 	CUB		&	 COCO \\ \hline
+			&  		&	\checkmark	&	${3.52{\pm}.04}$& -	\\ 
+			&  	\checkmark	&	\checkmark	&	${3.99{\pm}.04}$&-	\\
+			\checkmark	&  			&	\checkmark	&  ${4.14{\pm}.03}$	& ${11.29{\pm}.18}$	\\
+			\checkmark	&  \checkmark		&	\checkmark	&	${4.15{\pm}.05}$& ${11.86{\pm}.18}$ \\ \hline
+
+		\end{tabularx}
+	\end{center} \vspace{-.4cm}
+	\caption{Ablation study of hierarchically-nested adversarial discriminators on CUB and COO.
+$\checkmark $ indicates whether a discriminator at a certain scale is used.
+See text for detailed explanation.} \label{table:multiscales}
+\end{table}
+
+%
+
+%\begin{table}[t] % retrieval
+%	\small
+%	\begin{minipage}[b]{0.49\linewidth}
+%		\begin{tabularx}{1\textwidth}{c@{\hskip1.5pt}|c@{\hskip1pt}|c@{\hskip0.5pt}}
+%			\specialrule{1.5pt}{0pt}{0pt}  
+%			&   Inc. score 	 & VS   	\\  \hline
+%			\thead{w/o \\ local}        &   $3.12{\pm}.02$      & $.263{\pm}.130$           \\  \hline
+%			\thead{w/ \\ local}        &   $3.45{\pm}.07$ 	 &   $.296{\pm}.130$		    \\ \hline
+%		\end{tabularx}
+%		\vspace{-1.995cm}
+%	\end{minipage} %\hfill
+%	\begin{minipage}[b]{0.5\linewidth}
+%			\centering
+%			\includegraphics[width=0.245\textwidth]{figure/imgloss.pdf}
+%	\end{minipage}
+%	\vspace{-0.2cm}
+%	\caption{Ablation study on the local adversarial loss (left table) and hierarchically-nested adversarial learning (right table). See text for detailed explanation.} \label{tab:ablation}
+%\end{table}
+
+%\subsection{On the Local Image Loss}
+
+\textbf{On the Local Image Loss} We also study the effectiveness of the proposed local adversarial image loss. 
+Table \ref{table:multiscales} compares the case by removing the local loss (denoted as `w/o local').
+%We conduct experiments with using architecture with side output 64$\times$64, 128$\times$128 and 256 $\times$ 256 using Oxford dataset. 
+%As can be seen in Table\ref{tab:ablation}, 
+As can be seen, the inception score drop from 3.45 to 3.12.
+%, which proven that adding local image loss can help to improve the visual quality of the generated images. 
+Besides, the local image loss also helps improve the visual-semantic matching evidenced by the higher VS score of w/local.
+We hypothesis that it is because adding the separate local image loss can offer the pair loss more focuses on learning the semantic consistency.
+Furthermore, we also quantitatively compare the generated results in Figure \ref{fig:vis-imgloss}.
+Although both models can successfully capture the semantic details in text.
+The model with the local loss successfully generate more fine-grained structures described in text and thus improving the visual quality.
 
@@
 
-\begin{table}[t] % retrieval
-	\small
-	\begin{minipage}[b]{0.5\linewidth}
-			\begin{tabularx}{.98\textwidth}{c@{\hskip1pt}|c@{\hskip1pt}c@{\hskip1pt}}
-				\specialrule{1.5pt}{0pt}{0pt}  
-				Metric 			&   VS 	 & MS-SSMI   	\\  \hline
-				w/o Img         &   $.25{\pm}.16$      &   $.215$           \\  \hline
-				w/ global       &   $-$      &   $-$           \\ \hline
-				w/local         &   $-$ 	 &   $-$		    \\ \hline
-			\end{tabularx}
-		\vspace{-0.8cm}
-	\end{minipage} %\hfill
-	\begin{minipage}[b]{0.49\linewidth}
-		\begin{tabularx}{.98\textwidth}{ccc|c}
-			\specialrule{1.5pt}{0pt}{0pt}  
-			\multicolumn{3}{c|}{Components}	&  \multirow{2}{*}{\thead{Inception \\ score}}	\\ \cline{1-3}
-			64	& 128	& 256 			& 		\\ \hline
-			&  		&	\checkmark	&	${3.52{\pm}.04}$	\\ 
-			&  	\checkmark	&	\checkmark	&	${3.99{\pm}.04}$	\\
-			\checkmark	&  			&	\checkmark	&  ${4.14{\pm}.03}$		\\
-			\checkmark	&  \checkmark		&	\checkmark	&	${4.15{\pm}.05}$ \\ \hline
-
-		\end{tabularx}
-	\end{minipage}
-	\vspace{-0.2cm}
-	\caption{Ablation study on the local adversarial loss (left table) and hierarchically-nested adversarial learning (right table). See text for detailed explanation.} \label{tab:ablation}
-\end{table}
-
-\subsection{Design principles}
+%%\subsection{Design principles}
 %Note that for text-to-image synthesis, StackGAN is the only successful method to generate $256{\times}256$ images.
-StackGAN shows the difficulty of directly training a vanilla $256{\times}256$ GAN to generate meaningful images. 
-We test this extreme case using our method by removing all nested intermediate discriminators (the first row of Table \ref{tab:ablation} left). Our method still generates fairly good results. 
+\textbf{Design principles} StackGAN shows the difficulty of directly training a vanilla $256{\times}256$ GAN to generate meaningful images. 
+We test this extreme case using our method by removing all nested intermediate discriminators (the first row of Table \ref{table:multiscales}). Our method still generates fairly good results. 
 %Figure \ref{fig:vallina-res} shows the qualitatively results. 
@@
 However, we did not find benefits from this mechanism and our independent discriminators can be trained very stably.
+\begin{table}[t] % retrieval
+	\small
+	\centering
+	\begin{tabularx}{0.37\textwidth}{c|c|c}
+		\specialrule{1.5pt}{0pt}{0pt}  
+		&   Inc. score 	 & VS   	\\  \hline
+		w/o  local image loss      &   $3.12{\pm}.02$      & $.263{\pm}.130$           \\  \hline
+		w/  local  image loss      &   $3.45{\pm}.07$ 	 &   $.296{\pm}.130$		    \\ \hline
+	\end{tabularx}
+	\vspace{-0.2cm}
+	\caption{Ablation study on the local adversarial loss. See text for detailed explanation.} \label{tab:ablation-loss} \vspace{-0.3cm}
+\end{table}
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=0.491\textwidth,height=0.27\textwidth]{figure/imgloss.pdf}
+	\vspace{-.6cm}
+	\caption{Qualitative evaluation of the local adversarial loss.
+We can see the two images w/ the local image loss more accurately exhibit complex flower petal structures described in the (colored) text.} \label{fig:vis-imgloss}
+	\vspace{-.2cm}
+\end{figure}
 

### 2017-11-14 cvpr2018.tex
st

--- 2017-11-13 cvpr2018.tex
@@
 \textbf{Visual-semantic similarity~}
-\textcolor{red}{Since the aforementioned evaluation methods can not measure alignment between the generated images and the text description, we introduce a new qualitative measurement, namely visual-semantic similarity (VS similarity) inspired by \cite{vsemb}.} Denote $\bm{v}$ as the feature vector extract by a pre-trained CNN model $f_{cnn}$ (Inception-v2 \cite{inception} pre-trained on Imagenet), and $\bm{t}$ denote the text embedding.
+\textcolor{red}{Since the aforementioned evaluation methods can not measure the alignment between generated images and corresponding  text descriptions, we introduce a new quantitative measurement, namely visual-semantic similarity (VS similarity) inspired by \cite{vsemb}.} Denote $\bm{v}$ as the feature vector extracted by a pre-trained CNN model $f_{cnn}$ (Inception-v2 \cite{inception} pre-trained on Imagenet), and $\bm{t}$ denote the text embedding.
 We define a scoring function $s(\bm{x}, \bm{y})=\frac{\bm{x}\cdot \bm{y}}{||\bm{x}||\cdot ||\bm{y}||}$. 
-We learn two mapping functions $f_v$ and $f_t$, which map both image and sentence embeddings into one semantic space $\mathbb{R}^{512}$, by minimizing the following bi-directional ranking loss:
+We learn two mapping functions $f_v$ and $f_t$, which map both image features and sentence embeddings into one semantic space $\mathbb{R}^{512}$, by minimizing the following bi-directional ranking loss:
 \begin{equation}
+\vspace{-0.2cm}
 \begin{split}
@@
 \end{split}
+\vspace{-0.2cm}
 \end{equation}
+
 where $\delta$ is the margin, which is set as 0.2, every $(\bm{v}, \bm{t})$ is a ground truth image text pair, $\bm{t^-}$ denotes a mismatching text description for the image corresponding to $\bm{v}$, and vice-versa for $\bm{v^-}$.
@@
 			Metric 			&   Inception 	 & VS   	\\  \hline
-			wo/local        &   $3.12{\pm}.018$      &   $.263{\pm}.13$           \\  \hline
+			wo/local        &   $3.12{\pm}.02$      &   $.263{\pm}.13$           \\  \hline
 			w/local         &   $3.45{\pm}.07$ 	 &   $.296{\pm}.13$		    \\ \hline

### 2017-11-14 cvpr2018.tex
ss

@@
 			StackGAN     &	$.228{\pm}.162$	&	 $.278{\pm}.134$			&  $-{\pm}-$		\\ 
-			HDGAN 		&	$\bm{.246{\pm}.157}$	&	$ \bm{.296{\pm}.131}$ & $\bm{.178{\pm}.181}$  \\ \hline
+			HDGAN 		&	$\bm{.246{\pm}.157}$	&	$ \bm{.296{\pm}.131}$ & $\bm{.269{\pm}.102}$  \\ \hline
 		\end{tabularx} 

### 2017-11-14 cvpr2018.tex

--- 2017-11-14 cvpr2018.tex
@@
 \begin{abstract}
-This paper presents a novel method to deal with the challenging task of generating images conditioned on semantic image descriptions.
+This paper presents a novel method to deal with the challenging task of generating images conditioning on semantic image descriptions.
 We propose an effective end-to-end single-stream network that can generate photographic high-resolution images.
-Our method leverages the deep representations of convolutional layers and introduces accompanying hierarchical-nested adversarial games inside the network hierarchy, which regularize intermediate representations and assist training to capture the complex image statistics.
+\textcolor{red}{Our method leverages deep representations of convolutional layers and introduces accompanying hierarchical-nested adversarial games} inside the network hierarchy, which regularize intermediate representations and assist training to capture the complex image statistics.
 We present an extensile network architecture to cooperate with discriminators and push generated images to high resolutions.
-We adopt a multi-purpose adversarial training strategy at multiple nested side outputs to encourage more effective image-text alignment in order to guarantee the semantic consistency and image fidelity simultaneously.
-Furthermore, we introduce a new visual-semantic similarity measure to evaluate the semantic consistency of generated images.
-With extensive experimental validation on three major datasets, our method significantly improves previous state of the arts on all datasets over different evaluation metrics (e.g.
+We adopt a multi-purpose adversarial training strategy at multiple nested side outputs to encourage more effective image-text alignment in order to improve the semantic consistency and image fidelity simultaneously.
+Furthermore, we introduce a new visual-semantic similarity measure to evaluate the semantic consistency of generated images, thus alleviates the needs of human evaluation.
+With extensive experimental validation on three public datasets, our method significantly improves previous state of the arts on all datasets over different evaluation metrics (e.g.
 a ${11.86}$ Inception score on COCO).
@@
 \section{Introduction}
-Photographic text-to-image synthesis is a significant problem in generative model research \cite{reed2016generative}, which aims to learn a translation from a semantic text embedding space to a complex RGB image space.
-This task requires the generated images to be \textit{semantically consistent}, i.e., the generated images not only preserve sketch concepts in descriptions but also fine-grained descriptive details in image pixels.
-However, insufficient methods are developed to successfully address this task due to its particular challenges.
+Photographic text-to-image synthesis is a significant problem in generative model research \cite{reed2016generative}, which aims to learn a mapping from one semantic text embedding space to one complex RGB image space.
+This task requires the generated images to be not only realistic but also \textit{semantically consistent}.
+%i.e., the generated images not only preserve object sketch, color information in descriptions but also fine-grained descriptive details in image pixels. 
+However, this problem still remains unsolved due to its particular challenges. 
+%insufficient methods are developed to successfully address this task due to its particular challenges.
 
@@
 Generative adversarial networks (GANs) have become the main solution to this task. 
-Reed \etal \cite{reed2016generative} address this task through a GAN based framework. But this method only handles image up to $64^2$ resolution and can barely generate vivid object details.
-Based on this method, StackGAN  \cite{han2017stackgan} is a successful method that stacks another low-to-high resolution GAN to generate high-quality $256^2$ images, with two training stages.
-Later on, \cite{dong2017semantic} proposes to bypass the difficult of learning mappings from vector embeddings to RGB images but treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-rendering an arbitrary-style training $128^2$ image conditioned on a targeting description.
-But its high-resolution synthesis ability is unclear.
-At present, how to train from the low-dimensional text space to synthesize high-resolution and diverse images in a fully end-to-end manner is still an open and attractive question.
+Reed \etal \cite{reed2016generative} address this task through a GAN based framework. But this method only scale up to $64^2$ resolution and can barely generate vivid object details.
+Based on this method, StackGAN  \cite{han2017stackgan} propose a two-stage training strategy, which stacks another low-to-high resolution GAN to generate high-resolution $256^2$ images.
+Later on, \cite{dong2017semantic} proposes to bypass the difficult of learning mappings from vector embeddings to RGB images and treat it as a pixel-to-pixel translation problem \cite{isola2016image}.
+It works by re-rendering an arbitrary-style $128^2$ training  image conditioned on a targeting description.
+However, its high-resolution synthesis capability remains unclear.
+
+At present,\textcolor{red}{adversarial training of a generative model mapping a low-dimensional semantic space to  high-resolution and diverse images space in a fully end-to-end manner is still an open question.
+}
 
@@
 Text-to-image synthesis using GANs has two main difficulties.
-The first is the fundamental problem of balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}.
-%How to utilize the multimodal information between images and text in discriminator is extremely important to generate effective gradients.
+\textcolor{red}{The first is the fundamental problem of balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}.} %How to utilize the multimodal information between images and text in discriminator is extremely important to generate effective gradients.
 The second is stably modeling the huge pixel space in high-resolution images \cite{han2017stackgan}. 
@@
 
-Our generator resembles a simple vanilla GAN, without requiring any internal text conditioning like \cite{han2017stackgan} or outside image annotation supervision like \cite{dash2017tac}.
+Our generator resembles a simple vanilla GAN, without requiring any multiple internal text conditioning like \cite{han2017stackgan} or outside image annotation supervision like \cite{dash2017tac}.
 To tackle the problem of the big leap from the text space to the high-resolution image space, our insight is to leverage and regularize hierarchical representations with additional deep adversarial constraints.
 We introduce accompanying hierarchically-nested discriminators at multi-scale intermediate layers to play adversarial games and thereby encourage the generator approaching the real training data distribution.
-We also propose a novel convolutional neural network (CNN) framework for the generator to cooperate with our nested discriminators more effectively.
+We also propose a novel convolutional neural network (CNN) framework for the generator to \textcolor{red}{cooperate with} our nested discriminators more effectively.
 To guarantee the image diversity and semantic consistency,
-we enforce nested discriminators at different hierarchies to simultaneously differentiate real-and-fake image-text pairs as well as real-and-fake global images or local image patches with certain focal ranges.
-This multi-purpose conditional adversary is mutually beneficial to allow each focus on its respect duty. 
+we enforce nested discriminators at different hierarchies to simultaneously differentiate real-and-fake image-text pairs as well as real-and-fake global images or local image patches with certain \textcolor{red}{receptive field.
+This multi-purpose conditional adversary is mutually beneficial to allow each focus on its respect duty.}%focal ranges
+
+%To alleviate the need for manual human evaluation about the matching between generated images and text description, we propose to learn a visual-semantic embedding model, thus providing a measure for quantitative evaluation of the image sentence consistency.
 %% It is a regularization to limit the discriminators to use unexpected information to make decision.
+
+\textcolor{red}{To summarize, our contributions are:}
 
@@
 
-Deep generative models attract wide interests recently, including GANs \cite{goodfellow2014generative}, Variational Auto-encoders (VAE) \cite{kingma2013auto}, etc \cite{oord2016pixel}. 
+Deep generative models have attracted wide interests recently, including GANs \cite{goodfellow2014generative}, Variational Auto-encoders (VAE) \cite{kingma2013auto}, etc \cite{oord2016pixel}. 
 There are substantial existing methods investigating better usage of GANs for different applications, such as image synthesis \cite{radford2015unsupervised, shrivastava2016learning}, (unpaired) pixel-to-pixel translation \cite{isola2016image,zhu2017unpaired}, medical applications \cite{costa2017towards}, etc \cite{ledig2016photo,huang2016stacked}.
@@
 In brief, the two-player game in GANs \cite{goodfellow2014generative} is played by a generator $G$ network and a discriminator $D$ network, which are alternatively trained to compete with each other and thereby improve each other.
-The discriminator is optimized to distinguish synthesized images from real images, meanwhile, the generator is trained to generate realistic images to fool the discriminator.
+The discriminator is optimized to distinguish synthesized images from real images, meanwhile, the generator is trained to generate fake images to fool the discriminator.
 Concretely, the overall min-max optimization objective is defined as:
@@
 
-For each side output $X_i$, we propose to apply a discriminator $D_i$ to perform independently adversarial games. Therefore, our full min-max objective is defined as 
+For each side output $X_i$, we propose to apply a distinct discriminator $D_i$ to perform independently adversarial games. Therefore, our full min-max objective is defined as 
 \begin{equation}
@@
   \mathcal{G}^*, \mathcal{D}^*&  =  \arg~\underset{G}{\min}\ \underset{\mathcal{D}}{\max}~ \mathcal{V}(\mathcal{G},\mathcal{D}, \mathcal{Y}, \bm t, \bm z), \\
-  \text{where} \;\;	 \mathcal{D} & \in  \{D_1, ..., D_s\}, \; \mathcal{Y} = \{Y_1, ..., Y_s\},
+  %\text{where} \;\;	 \mathcal{D} & =  \{D_1, ..., D_s\}, \; \mathcal{Y} = \{Y_1, ..., Y_s\},
 \end{split}
 \end{equation}
-where $ \mathcal{Y}$ contains a set of training images at multi-scales, $\{1,...,s\}$.
+where $\mathcal{D}  =  \{D_1, ..., D_s\} $, and $\; \mathcal{Y} = \{Y_1, ..., Y_s\}$ denotes a set of training images at multi-scales, $\{1,...,s\}$.
 %where $\mathcal{D}$ contains the optimal discriminators $\{D_1^*, ..., D_o^*\}$, and $ \mathcal{L}(G,\mathcal{D}, \bm{X}, \bm{T} )$ is the full objective of this mini-max game.
@@
 To guarantee semantic consistency, we adopt the matching-aware pair loss proposed by \cite{reed2016generative}.
-The discriminator is designed to take image-text pairs as inputs and trained to identify two types of fakes: real image with mismatched text and fake image with conditioned text.
+The discriminator is designed to take image-text pairs as inputs and trained to identify two types of errors: real image with mismatched text and fake image with conditioned text.
 
@@
 However, there is no explicit loss that forces the discriminator to differentiate pure real images from fake images.
-As the image resolution goes higher, discriminators might loss focus for local fine-grained image details.
+Combining both tasks (generating realistic images and matching image with text) into one output further complicates the learning tasks, which is already challenging.
+Second, as the image resolution goes higher, it might be challenging for a global pair-loss discriminator to capture local fine-grained details.
+%As the image resolution goes higher, discriminators might loss focus for local fine-grained image details.
 %However, this loss has two major weaknesses. First, there is no explicit loss that force the discriminator to differentiate real images from fake images. 
@@
 \end{equation}
-where $L_2(x) = (x - \mathbb{I})^2$ is the mean-square loss (instead of the conventional cross-entropy loss) and $\overline{L_2}(x) =x^2$.
+where $L_2(x) = \mathbb{E}\big[(x - \mathbb{I})^2\big]$ is the mean-square loss (instead of the conventional cross-entropy loss) and $\overline{L_2}(x) =\mathbb{E}\big[x^2\big]$.
 For local image loss with varying focal ranges, the shape of $x, \mathbb{I} \in \mathbb{R}^{R{\times}R}$ varies accordingly (see Figure \ref{fig:loss}).
@@
 
-3) Visual-semantic similarity.
-The aforementioned metrics are widely used for general GANs.
+3) \textbf{Visual-semantic similarity.} The aforementioned metrics are widely used for general GANs.
 The problem of them is that they can not measure the alignment between the generated images and conditioned text.
 We introduce a new qualitative measurement, namely visual-semantic similarity (VS similarity) inspired by \cite{vsemb}.
-Denote $\bm{v}$ as the image feature vector extracted by a Inception CNN.
-We define a scoring function $C(\bm{x}, \bm{y})=\frac{\bm{x}\cdot \bm{y}}{||\bm{x}||\cdot ||\bm{y}||}$. 
+Denote $\bm{v}$ as the image feature vector extracted by a pre-trained Inception model $f_{cnn}$\cite{inception}.
+We define a scoring function $c(\bm{x}, \bm{y})=\frac{\bm{x}\cdot \bm{y}}{||\bm{x}||\cdot ||\bm{y}||}$. 
 Then, we learn two mapping functions $f_v$ and $f_t$, which map both image and sentence embeddings into a common space in $\mathbb{R}^{512}$, by minimizing the following bi-directional ranking loss:
+%\mathcal{L}_{vs} &=
 \begin{equation}\vspace{-.2cm}
 \begin{split}
-\mathcal{L}_{vs} &= \sum_{ \bm{v} }\sum_{ \bm{t}_{\overline{v}} }~\max( 0, \delta- C(f_v(\bm{v}), f_t( \bm{t}_{\overline{v}}))) \\
-&+ \sum_{ \bm{t} }\sum_{ \bm{v}_{\overline{v}} }~\max( 0,  \delta- C(f_t(\bm{t}), f_v( \bm{v}_{\overline{v}} )))
+ & \sum_{ \bm{v} }\sum_{ \bm{t}_{\overline{v}} }~\max( 0, \delta  - c(f_v(\bm{v}), f_t( \bm{t}_{{v}}) )+ c(f_v(\bm{v}), f_t( \bm{t}_{\overline{v}}) )     ) \\
+ & + \sum_{ \bm{t} }\sum_{ \bm{v}_{\overline{t}} }~\max( 0,  \delta  - c(f_t(\bm{t}), f_v( \bm{v}_{{v}} )) +  c(f_t(\bm{t}), f_v( \bm{v}_{\overline{t}} ))  )
 \end{split}
@@
 where $\delta$ is the margin, which is set as 0.2.
-$\{\bm{v}, \bm{t}\}$ is a ground truth image text pair, and $\{\bm v, \bm t_{\overline{v}} \}$ and $\{ \bm v_{\overline{v}}, \bm{t} \}$ denote mismatched image-text pairs.
-In the testing stage, given an text embedding $\bm{t}$, and the generated image encoded by the Inception-CNN $\bm v$, the VS score is calculated as $C(\bm v, \bm{t})$.
+$\{\bm{v}, \bm{t}\}$ is a ground truth image text pair, and $\{\bm v, \bm t_{\overline{v}} \}$ and $\{ \bm v_{\overline{t}}, \bm{t} \}$ denote mismatched image-text pairs.
+In the testing stage, given an text embedding $\bm{t}$, and the generated image $\bm{x}$, the VS score is calculated as $c(f_{cnn}(\bm{x}), \bm{t})$.
 Higher score indicates better semantic consistency, i.e.
@@
 			Ground Truth	&	${.302{\pm}.151}$	&	$ {.336{\pm}.138}$			& $.426{\pm}.157$  \\ \hline
-			StackGAN     &	$.228{\pm}.162$	&	 $.278{\pm}.134$			&  -		\\ 
-			HDGAN 		&	$\bm{.246{\pm}.157}$	&	$ \bm{.296{\pm}.131}$ & $\bm{.178{\pm}.181}$  \\ \hline
+			StackGAN     &	$.228{\pm}.162$	&	 $.278{\pm}.134$			&  $-{\pm}-$		\\ 
+			HDGAN 		&	$\bm{.246{\pm}.157}$	&	$ \bm{.296{\pm}.131}$ & $\bm{.199{\pm}.183}$  \\ \hline
 		\end{tabularx} 

### 2017-11-14 supp.tex

@@
 \begin{appendices}
+
+\section{Training Details}
+%The algorithm that summarizes the training process of our model is given in Algorithm 1. 
+%We train and evaluate our model with a devbox machine. $\alpha$ is set to 0.5, $\beta$ is set to 4.
+The Adam optimizer is used for all experiments.
+The initial learning rate is set as 0.0002 and decreased by half for every 100 epochs (50 for COCO).
+The CUB and Oxford-102 datasets are trained for 500 epochs in total (200 epochs for COCO).
+For the local image loss, we set $R=1$ and for $64^2$ and $128^2$ side outputs and $R=5$ for $256^2$ and $512^2$ outputs.
+
+All intermediate conv layers except from the specified ones for both generators and discriminators use $3{\times}3$ kernels (with reflection padding).
+We also experimented other normalization (i.e.
+instance normalization \cite{ulyanov2016instance} and layer normalization \cite{ba2016layer}) used by recent advances \cite{zhu2017unpaired,chen2017photographic}.
+Both are not satisfactory.
+
+We use 1-repeat residual block for the generator till $256^2$ resolution.
+The input of the generator is a $1024{\times}4{\times}4$ tensor.
+As the feature map size increases, the number of feature maps is downsampled by $2$ at $8, 32, 128, 256$ sizes in generator.
+To generate $512^2$ images, we pre-train the generator to $256^2$ due to the limitation of GPU memory. We use $3$-repeat res-block followed by the stretching and linear compression layer. 
+Since the $256^2$ image already captures the overall semantics and details, to encourage the $512^2$ maintain these information, we use a l1 reconstruction loss to self-regularize the generator in case the discriminator confuses the expected output.
+
 %\renewcommand{\thechapter}{A\arabic{chapter}}
@@
 
-%{\small
-%	\bibliographystyle{ieee}
-%	\bibliography{egbib}
-%}
+{\small
+	\bibliographystyle{ieee}
+	\bibliography{reference_zizhao,egbib}
+}
 

### 2017-11-14 cvpr2018.tex
for merge

@@
 \begin{abstract}
-This paper presents a novel method to deal with the challenging task of generating images conditioning on semantic image descriptions.
+This paper presents a novel method to deal with the challenging task of generating images conditioned on semantic image descriptions.
 We propose an effective end-to-end single-stream network that can generate photographic high-resolution images.
-\textcolor{red}{Our method leverages deep representations of convolutional layers and introduces accompanying hierarchical-nested adversarial games} inside the network hierarchy, which regularize intermediate representations and assist training to capture the complex image statistics.
+Our method leverages the deep representations of convolutional layers and introduces accompanying hierarchical-nested adversarial games inside the network hierarchy, which regularize intermediate representations and assist training to capture the complex image statistics.
 We present an extensile network architecture to cooperate with discriminators and push generated images to high resolutions.
-We adopt a multi-purpose adversarial training strategy at multiple nested side outputs to encourage more effective image-text alignment in order to improve the semantic consistency and image fidelity simultaneously.
-Furthermore, we introduce a new visual-semantic similarity measure to evaluate the semantic consistency of generated images, thus alleviates the needs of human evaluation.
-With extensive experimental validation on three public datasets, our method significantly improves previous state of the arts on all datasets over different evaluation metrics (e.g.
+We adopt a multi-purpose adversarial training strategy at multiple nested side outputs to encourage more effective image-text alignment in order to guarantee the semantic consistency and image fidelity simultaneously.
+Furthermore, we introduce a new visual-semantic similarity measure to evaluate the semantic consistency of generated images.
+With extensive experimental validation on three major datasets, our method significantly improves previous state of the arts on all datasets over different evaluation metrics (e.g.
 a ${11.86}$ Inception score on COCO).
@@
 \section{Introduction}
-Photographic text-to-image synthesis is a significant problem in generative model research \cite{reed2016generative}, which aims to learn a mapping from one semantic text embedding space to one complex RGB image space.
-This task requires the generated images to be not only realistic but also \textit{semantically consistent}.
-%i.e., the generated images not only preserve object sketch, color information in descriptions but also fine-grained descriptive details in image pixels. 
-However, this problem still remains unsolved due to its particular challenges. 
-%insufficient methods are developed to successfully address this task due to its particular challenges.
+Photographic text-to-image synthesis is a significant problem in generative model research \cite{reed2016generative}, which aims to learn a translation from a semantic text embedding space to a complex RGB image space.
+This task requires the generated images to be \textit{semantically consistent}, i.e., the generated images not only preserve sketch concepts in descriptions but also fine-grained descriptive details in image pixels.
+However, insufficient methods are developed to successfully address this task due to its particular challenges.
 
@@
 	\vspace{-.6cm}
-	\caption{Top: Overview of our hierarchically-nested adversarial network. Bottom: Two fine-grained generated results. \label{fig:intro}} 	
-	\vspace{-.8cm}
+	\caption{Top: Overview of our hierarchically-nested adversarial network. Bottom: Two generated results where fine-grained details are highlighted. \label{fig:intro}} 	
+	\vspace{-.6cm}
 	%\end{center}
@@
 Generative adversarial networks (GANs) have become the main solution to this task. 
-Reed \etal \cite{reed2016generative} address this task through a GAN based framework. But this method only scale up to $64^2$ resolution and can barely generate vivid object details.
-Based on this method, StackGAN  \cite{han2017stackgan} propose a two-stage training strategy, which stacks another low-to-high resolution GAN to generate high-resolution $256^2$ images.
-Later on, \cite{dong2017semantic} proposes to bypass the difficult of learning mappings from vector embeddings to RGB images and treat it as a pixel-to-pixel translation problem \cite{isola2016image}.
-It works by re-rendering an arbitrary-style $128^2$ training  image conditioned on a targeting description.
-However, its high-resolution synthesis capability remains unclear.
-
-At present,\textcolor{red}{adversarial training of a generative model mapping a low-dimensional semantic space to  high-resolution and diverse images space in a fully end-to-end manner is still an open question.
-}
+Reed \etal \cite{reed2016generative} address this task through a GAN based framework. But this method only handles image up to $64^2$ resolution and can barely generate vivid object details.
+Based on this method, StackGAN  \cite{han2017stackgan} is a successful method that stacks another low-to-high resolution GAN to generate high-quality $256^2$ images, with two training stages.
+Later on, \cite{dong2017semantic} proposes to bypass the difficult of learning mappings from vector embeddings to RGB images but treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-rendering an arbitrary-style training $128^2$ image conditioned on a targeting description.
+But its high-resolution synthesis ability is unclear.
+At present, how to train from the low-dimensional text space to synthesize high-resolution and diverse images in a fully end-to-end manner is still an open and attractive question.
 
@@
 Text-to-image synthesis using GANs has two main difficulties.
-\textcolor{red}{The first is the fundamental problem of balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}.} %How to utilize the multimodal information between images and text in discriminator is extremely important to generate effective gradients.
+The first is the fundamental problem of balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}.
+%How to utilize the multimodal information between images and text in discriminator is extremely important to generate effective gradients.
 The second is stably modeling the huge pixel space in high-resolution images \cite{han2017stackgan}. 
@@
 
-Our generator resembles a simple vanilla GAN, without requiring any multiple internal text conditioning like \cite{han2017stackgan} or outside image annotation supervision like \cite{dash2017tac}.
+Our generator resembles a simple vanilla GAN, without requiring any internal text conditioning like \cite{han2017stackgan} or outside image annotation supervision like \cite{dash2017tac}.
 To tackle the problem of the big leap from the text space to the high-resolution image space, our insight is to leverage and regularize hierarchical representations with additional deep adversarial constraints.
 We introduce accompanying hierarchically-nested discriminators at multi-scale intermediate layers to play adversarial games and thereby encourage the generator approaching the real training data distribution.
-We also propose a novel convolutional neural network (CNN) framework for the generator to \textcolor{red}{cooperate with} our nested discriminators more effectively.
+We also propose a novel convolutional neural network (CNN) framework for the generator to cooperate with our nested discriminators more effectively.
 To guarantee the image diversity and semantic consistency,
-we enforce nested discriminators at different hierarchies to simultaneously differentiate real-and-fake image-text pairs as well as real-and-fake global images or local image patches with certain \textcolor{red}{receptive field.
-This multi-purpose conditional adversary is mutually beneficial to allow each focus on its respect duty.}%focal ranges
-
-%To alleviate the need for manual human evaluation about the matching between generated images and text description, we propose to learn a visual-semantic embedding model, thus providing a measure for quantitative evaluation of the image sentence consistency.
+we enforce nested discriminators at different hierarchies to simultaneously differentiate real-and-fake image-text pairs as well as real-and-fake global images or local image patches with certain focal ranges.
+This multi-purpose conditional adversary is mutually beneficial to allow each focus on its respect duty. 
 %% It is a regularization to limit the discriminators to use unexpected information to make decision.
-
-\textcolor{red}{To summarize, our contributions are:}
 
@@
 
-Deep generative models have attracted wide interests recently, including GANs \cite{goodfellow2014generative}, Variational Auto-encoders (VAE) \cite{kingma2013auto}, etc \cite{oord2016pixel}. 
+Deep generative models attract wide interests recently, including GANs \cite{goodfellow2014generative}, Variational Auto-encoders (VAE) \cite{kingma2013auto}, etc \cite{oord2016pixel}. 
 There are substantial existing methods investigating better usage of GANs for different applications, such as image synthesis \cite{radford2015unsupervised, shrivastava2016learning}, (unpaired) pixel-to-pixel translation \cite{isola2016image,zhu2017unpaired}, medical applications \cite{costa2017towards}, etc \cite{ledig2016photo,huang2016stacked}.
@@
 In brief, the two-player game in GANs \cite{goodfellow2014generative} is played by a generator $G$ network and a discriminator $D$ network, which are alternatively trained to compete with each other and thereby improve each other.
-The discriminator is optimized to distinguish synthesized images from real images, meanwhile, the generator is trained to generate fake images to fool the discriminator.
+The discriminator is optimized to distinguish synthesized images from real images, meanwhile, the generator is trained to generate realistic images to fool the discriminator.
 Concretely, the overall min-max optimization objective is defined as:
@@
 
-For each side output $X_i$, we propose to apply a distinct discriminator $D_i$ to perform independently adversarial games. Therefore, our full min-max objective is defined as 
+For each side output $X_i$, we propose to apply a discriminator $D_i$ to perform independently adversarial games. Therefore, our full min-max objective is defined as 
 \begin{equation}
@@
   \mathcal{G}^*, \mathcal{D}^*&  =  \arg~\underset{G}{\min}\ \underset{\mathcal{D}}{\max}~ \mathcal{V}(\mathcal{G},\mathcal{D}, \mathcal{Y}, \bm t, \bm z), \\
-  %\text{where} \;\;	 \mathcal{D} & =  \{D_1, ..., D_s\}, \; \mathcal{Y} = \{Y_1, ..., Y_s\},
+  \text{where} \;\;	 \mathcal{D} & \in  \{D_1, ..., D_s\}, \; \mathcal{Y} = \{Y_1, ..., Y_s\},
 \end{split}
 \end{equation}
-where $\mathcal{D}  =  \{D_1, ..., D_s\} $, and $\; \mathcal{Y} = \{Y_1, ..., Y_s\}$ denotes a set of training images at multi-scales, $\{1,...,s\}$.
+where $ \mathcal{Y}$ contains a set of training images at multi-scales, $\{1,...,s\}$.
 %where $\mathcal{D}$ contains the optimal discriminators $\{D_1^*, ..., D_o^*\}$, and $ \mathcal{L}(G,\mathcal{D}, \bm{X}, \bm{T} )$ is the full objective of this mini-max game.
@@
 To guarantee semantic consistency, we adopt the matching-aware pair loss proposed by \cite{reed2016generative}.
-The discriminator is designed to take image-text pairs as inputs and trained to identify two types of errors: real image with mismatched text and fake image with conditioned text.
+The discriminator is designed to take image-text pairs as inputs and trained to identify two types of fakes: real image with mismatched text and fake image with conditioned text.
 
@@
 However, there is no explicit loss that forces the discriminator to differentiate pure real images from fake images.
-Combining both tasks (generating realistic images and matching image with text) into one output further complicates the learning tasks, which is already challenging.
-Second, as the image resolution goes higher, it might be challenging for a global pair-loss discriminator to capture local fine-grained details.
-%As the image resolution goes higher, discriminators might loss focus for local fine-grained image details.
+As the image resolution goes higher, discriminators might loss focus for local fine-grained image details.
 %However, this loss has two major weaknesses. First, there is no explicit loss that force the discriminator to differentiate real images from fake images. 
@@
 \end{equation}
-where $L_2(x) = \mathbb{E}\big[(x - \mathbb{I})^2\big]$ is the mean-square loss (instead of the conventional cross-entropy loss) and $\overline{L_2}(x) =\mathbb{E}\big[x^2\big]$.
+where $L_2(x) = (x - \mathbb{I})^2$ is the mean-square loss (instead of the conventional cross-entropy loss) and $\overline{L_2}(x) =x^2$.
 For local image loss with varying focal ranges, the shape of $x, \mathbb{I} \in \mathbb{R}^{R{\times}R}$ varies accordingly (see Figure \ref{fig:loss}).
@@
 
-3) \textbf{Visual-semantic similarity.} The aforementioned metrics are widely used for general GANs.
+3) Visual-semantic similarity.
+The aforementioned metrics are widely used for general GANs.
 The problem of them is that they can not measure the alignment between the generated images and conditioned text.
 We introduce a new qualitative measurement, namely visual-semantic similarity (VS similarity) inspired by \cite{vsemb}.
-Denote $\bm{v}$ as the image feature vector extracted by a pre-trained Inception model $f_{cnn}$\cite{inception}.
-We define a scoring function $c(\bm{x}, \bm{y})=\frac{\bm{x}\cdot \bm{y}}{||\bm{x}||\cdot ||\bm{y}||}$. 
+Denote $\bm{v}$ as the image feature vector extracted by a Inception CNN.
+We define a scoring function $C(\bm{x}, \bm{y})=\frac{\bm{x}\cdot \bm{y}}{||\bm{x}||\cdot ||\bm{y}||}$. 
 Then, we learn two mapping functions $f_v$ and $f_t$, which map both image and sentence embeddings into a common space in $\mathbb{R}^{512}$, by minimizing the following bi-directional ranking loss:
-%\mathcal{L}_{vs} &=
 \begin{equation}\vspace{-.2cm}
 \begin{split}
- & \sum_{ \bm{v} }\sum_{ \bm{t}_{\overline{v}} }~\max( 0, \delta  - c(f_v(\bm{v}), f_t( \bm{t}_{{v}}) )+ c(f_v(\bm{v}), f_t( \bm{t}_{\overline{v}}) )     ) \\
- & + \sum_{ \bm{t} }\sum_{ \bm{v}_{\overline{t}} }~\max( 0,  \delta  - c(f_t(\bm{t}), f_v( \bm{v}_{{v}} )) +  c(f_t(\bm{t}), f_v( \bm{v}_{\overline{t}} ))  )
+\mathcal{L}_{vs} &= \sum_{ \bm{v} }\sum_{ \bm{t}_{\overline{v}} }~\max( 0, \delta- C(f_v(\bm{v}), f_t( \bm{t}_{\overline{v}}))) \\
+&+ \sum_{ \bm{t} }\sum_{ \bm{v}_{\overline{v}} }~\max( 0,  \delta- C(f_t(\bm{t}), f_v( \bm{v}_{\overline{v}} )))
 \end{split}
@@
 where $\delta$ is the margin, which is set as 0.2.
-$\{\bm{v}, \bm{t}\}$ is a ground truth image text pair, and $\{\bm v, \bm t_{\overline{v}} \}$ and $\{ \bm v_{\overline{t}}, \bm{t} \}$ denote mismatched image-text pairs.
-In the testing stage, given an text embedding $\bm{t}$, and the generated image $\bm{x}$, the VS score is calculated as $c(f_{cnn}(\bm{x}), \bm{t})$.
+$\{\bm{v}, \bm{t}\}$ is a ground truth image text pair, and $\{\bm v, \bm t_{\overline{v}} \}$ and $\{ \bm v_{\overline{v}}, \bm{t} \}$ denote mismatched image-text pairs.
+In the testing stage, given an text embedding $\bm{t}$, and the generated image encoded by the Inception-CNN $\bm v$, the VS score is calculated as $C(\bm v, \bm{t})$.
 Higher score indicates better semantic consistency, i.e.
@@
 			Ground Truth	&	${.302{\pm}.151}$	&	$ {.336{\pm}.138}$			& $.426{\pm}.157$  \\ \hline
-			StackGAN     &	$.228{\pm}.162$	&	 $.278{\pm}.134$			&  $-{\pm}-$		\\ 
-			HDGAN 		&	$\bm{.246{\pm}.157}$	&	$ \bm{.296{\pm}.131}$ & $\bm{.199{\pm}.183}$  \\ \hline
+			StackGAN     &	$.228{\pm}.162$	&	 $.278{\pm}.134$			&  -		\\ 
+			HDGAN 		&	$\bm{.246{\pm}.157}$	&	$ \bm{.296{\pm}.131}$ & $\bm{.178{\pm}.181}$  \\ \hline
 		\end{tabularx} 

### 2017-11-14 cvpr2018.tex
sdsd

--- 2017-11-14 cvpr2018.tex
@@
 
-At present,\textcolor{red}{adversarial training of a generative model mapping a low-dimensional semantic space to  high-resolution and diverse images space in a fully end-to-end manner is still an open question.
+At present, \textcolor{red}{adversarial training of a generative model mapping a low-dimensional semantic space to  high-resolution and diverse images space in a fully end-to-end manner is still an open question.
 }
@@
 \subsection{Adversarial objective basics}
-In brief, the two-player game in GANs \cite{goodfellow2014generative} is played by a generator $G$ network and a discriminator $D$ network, which are alternatively trained to compete with each other and thereby improve each other.
-The discriminator is optimized to distinguish synthesized images from real images, meanwhile, the generator is trained to generate fake images to fool the discriminator.
-Concretely, the overall min-max optimization objective is defined as:
+Generative adversary networks (GANs) consists of a generator $G$ and a discriminator $D$, which are alternatively trained to compete with each other in a two-player minimax game.
+$D$ is optimized to distinguish synthesized images from real images, meanwhile, $G$ is trained to fool $D$ by generating fake images.
+Concretely, the optimal $G$ and $D$ can be obtained by playing the following two-player min-max game,
+%In brief, the two-player game in GANs \cite{goodfellow2014generative} is played by a generator $G$ network and a discriminator $D$ network, which are alternatively optimized to compete with each other.
+The discriminator is trained to distinguish synthesized images from real images, meanwhile, the generator is trained to generate fake images to fool the discriminator.
+Concretely, the optimal $G$ and $D$ can be obtained by:
 %where the optimal $G$ and $D$ can be obtained by 
@@
 Concretely, the overall training procedure can be analogous to the following two-player min-max game $\mathcal{L}(D, G)$, where the optimal $G$ and $D$ can be obtained by
+%\begin{equation}
+%\label{game}
+%\begin{split}
+%\underset{G}{\min}\ \underset{D}{\max}\ V(D, G) =  &\mathbb{E}_{x\sim p_{data}}[\log D(x)] +  \\
+%&\mathbb{E}_{z\sim p_{z}}[\log (1-D(G(z)))]		   
+%\end{split}
+%\end{equation}
+
 \begin{equation}
@@
 \end{equation}
-where $Y$ denotes training images and $\bm z\sim\mathcal{N}(0,1)$ denotes a random noise.
-The value function $\mathcal{V}$ aims to minimize the Jensen-Shannon divergence between the data and the model distribution.
-$G$ is learned to approximate $G(\bm z) \sim p(Y)$.
-The loss $\mathcal{L}$ for the valuation function is usually a cross-entropy loss, such that $\mathcal{V}(\cdot) = - \mathcal{L}(\cdot)$.
+%where $x$ is a real image sampled from the true data distribution $p_{data}$, $z$ is a noise vector usually sampled from some predefined distribution $p_{z}$ (e.g., Gaussian distribution).
+In this paper, we replace the negative log likelihood loss with a least square objective\cite{lsgan}.
+
+where $Y$ and $\bm z$ denotes training images and random noises, respectively. 
+%$G$ is learned to approximate $G(\bm z) \sim p(Y)$.  The loss $\mathcal{L}$ for the valuation function is usually a cross-entropy loss, such that $\mathcal{V}(\cdot) = - \mathcal{L}(\cdot)$. 
+$\mathcal{V}$ is the overall GAN loss, which usually takes the form $\mathbb{E}_{Y\sim p_{data}}\big[\log D(Y)\big] + \mathbb{E}_{\bm z\sim p_{z}}\big[\log (1-D(G(\bm z)))\big]$ or other variations\cite{lsgan}.
 
@@
 Numerous methods have demonstrated ways to unite generators and discriminators for image synthesis. Figure \ref{fig:archs-review} and Section 2 discuss some typical frameworks.
-Our method actually explores a new dimension of playing this adversarial game along the depth of a CNN (Figure \ref{fig:archs-review} D), which integrates additional discriminators at mid-level features of the generator $\mathcal{G}$.
+\textcolor{red}{Our method actually explores a new dimension of playing this adversarial game along the depth of a CNN} (Figure \ref{fig:archs-review} D), which integrates additional discriminators at \textcolor{red}{mid-level} features of the generator.
 The hierarchically-nested objectives 
@@
 \end{equation}
-where  $\bm t\sim p(data)$ denotes a sentence embedding vector in the real training data distribution (generated by a text character encoder).
+where  $\bm t\sim p(data)$ denotes a sentence embedding vector in the real training data distribution (generated by a pre-trained char RNN encoder\cite{reed2016generative}).
 $\mathcal{G}$ produces $s-1$ side outputs $\{X_1,...,X_{s-1}\}$ (size-growing images) and a final output $X_s$ with the highest resolution.
@@
 
-For each side output $X_i$, we propose to apply a distinct discriminator $D_i$ to perform independently adversarial games. Therefore, our full min-max objective is defined as 
+For each side output $X_i$, a distinct discriminator $D_i$ is associated to compete with it. Therefore, our full min-max objective is defined as 
 \begin{equation}
@@
 Compared with Eq.
-(\ref{equ:GAN}), one generator competes with multiple discriminators  $\{D_i\}$ at different hierarchies (Figure \ref{fig:archs-review} D), where each focus on learning diverse discriminative features in different contextual scales.
+(\ref{equ:GAN}), our generator competes with multiple discriminators  $\{D_i\}$ at different hierarchies (Figure \ref{fig:archs-review} D), where each focus on learning diverse discriminative features in different contextual scales.
 %%Discriminators do not share weights with each other, which offers them full flexibility to focus on learning diverse discriminative features in different contextual scales.
-In principle, the lower-resolution side output is forced to learn semantic consistent image structures (e.g., object sketch, color, and background), and the subsequent higher-resolution side outputs are used to render details to images and preserve these image structures.
-Since our method is trained in an end-to-end fashion, the lower-resolution outputs can also fully enjoy top-down knowledge from discriminators for higher resolutions.
-We can observe consistent image structures and styles in both low and high resolutions.
-We think such consistency is able to reduce the model instability.
+In principle, the lower-resolution side output can learn semantic consistent image structures (e.g., object sketch, color, and background), and the subsequent higher-resolution side outputs are used to render more details to images.
+Since our method is trained in an end-to-end fashion, the lower-resolution outputs can also fully utilize top-down knowledge from discriminators for higher resolutions.
+We can observe consistent image structures, color and styles in outputs of both low and high resolutions without using addition supervising term\cite{han2017stackganv2}.
+%We think such consistency is able to reduce the model instability.
 As an evidence, we can obtain significantly more consistent results exhibited in both low- and high-resolution outputs compared with StackGAN (see experiments). 
@@
 Furthermore, this separation of the image loss from the matching loss in our method opens further possibilities, such as utilizing the unlabeled image to improve both the generator and discriminator.
-\textcolor{red}{In the spirit of variational auto-encoder \cite{vae} and the practice of StackGAN \cite{han2017stackgan}, namely conditioning augmentation (CA), we sample the input text $\bm t$ from a Ganssian distribution $\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}))$, where $\mu$ and $\Sigma$ are functions of $\bm t$ (learned with the network), which produces a $256$-d text input.
-We add the Kullback-Leibler divergence regularization term, $D_{KL}(\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}) )|| \mathcal{N}(0, \bm{I}))$ \cite{vae}, to the $G$ loss to force the smooth sampling over the text embedding distribution.
+
+\textcolor{red}{In the spirit of variational auto-encoder \cite{vae} and the practice of StackGAN \cite{han2017stackgan}, instead of directly using deterministic text embedding, we sample a stochastic vector from a Ganssian distribution $\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}))$, where $\mu$ and $\Sigma$ are parameterized functions of $\bm t$.
+We add the Kullback-Leibler divergence regularization term, $D_{KL}(\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}) )|| \mathcal{N}(0, \bm{I}))$ \cite{vae}, to $G$ loss to prevent over-fitting and force smooth sampling over the text embedding distribution.
 }

### 2017-11-14 cvpr2018.tex
1th method

@@
 %$G$ is learned to approximate $G(\bm z) \sim p(Y)$.  The loss $\mathcal{L}$ for the valuation function is usually a cross-entropy loss, such that $\mathcal{V}(\cdot) = - \mathcal{L}(\cdot)$. 
-$\mathcal{V}$ is the overall GAN loss, which usually takes the form $\mathbb{E}_{Y\sim p_{data}}\big[\log D(Y)\big] + \mathbb{E}_{\bm z\sim p_{z}}\big[\log (1-D(G(\bm z)))\big]$ or other variations\cite{lsgan}.
+$\mathcal{V}$ is the overall GAN objective, which usually takes the form $\mathbb{E}_{Y\sim p_{data}}\big[\log D(Y)\big] + \mathbb{E}_{\bm z\sim p_{z}}\big[\log (1-D(G(\bm z)))\big]$ or other variations\cite{lsgan}.
 

### 2017-11-15 cvpr2018.tex

--- 2017-11-14 cvpr2018.tex
@@
 We propose an effective end-to-end single-stream network that can generate photographic high-resolution images.
-\textcolor{red}{Our method leverages deep representations of convolutional layers and introduces accompanying hierarchical-nested adversarial games} inside the network hierarchy, which regularize intermediate representations and assist training to capture the complex image statistics.
+Our method leverages deep representations of convolutional layers and introduces accompanying hierarchical-nested adversarial games inside the network hierarchy, which regularize intermediate representations and assist training to capture the complex image statistics.
 We present an extensile network architecture to cooperate with discriminators and push generated images to high resolutions.
@@
 \section{Introduction}
-Photographic text-to-image synthesis is a significant problem in generative model research \cite{reed2016generative}, which aims to learn a mapping from one semantic text embedding space to one complex RGB image space.
-This task requires the generated images to be not only realistic but also \textit{semantically consistent}.
-%i.e., the generated images not only preserve object sketch, color information in descriptions but also fine-grained descriptive details in image pixels. 
-However, this problem still remains unsolved due to its particular challenges. 
+Photographic text-to-image synthesis is a significant problem in generative model research \cite{reed2016generative}, which aims to learn a mapping from one semantic text space to one complex RGB image space.
+This task requires the generated images to be not only realistic but also \textit{semantically consistent}, i.e., the generated images not only preserve object color and sketch in descriptions but also fine-grained descriptive details in image pixels.
+%However, this problem still remains unsolved due to its particular challenges. 
 %insufficient methods are developed to successfully address this task due to its particular challenges.
@@
 However, its high-resolution synthesis capability remains unclear.
-
-At present, \textcolor{red}{adversarial training of a generative model mapping a low-dimensional semantic space to  high-resolution and diverse images space in a fully end-to-end manner is still an open question.
-}
-
-%We outline several empirical reasons for the challenges of 
-Text-to-image synthesis using GANs has two main difficulties.
-\textcolor{red}{The first is the fundamental problem of balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}.} %How to utilize the multimodal information between images and text in discriminator is extremely important to generate effective gradients.
+At present, training a generative model to map from a low-dimensional text space to a high-resolution and diverse image space in a fully end-to-end manner still remains unsolved.
+
+Text-to-image synthesis using GANs has two major difficulties.
+The first is balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}, which is actually a long-term problem in GANs.
 The second is stably modeling the huge pixel space in high-resolution images \cite{han2017stackgan}.
 An effective strategy to regularize generators is critical to help capture the complex image statistics \cite{huang2016stacked} as well as guarantee semantic consistency.
-%The first reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. 
-% Keeping semantic consistency as well as diversity
-%The first reason comes from the fundamental difficulty of balancing the stability between generators and discriminators.
+
+%%The first reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. 
+%% Keeping semantic consistency as well as diversity
+%%The first reason comes from the fundamental difficulty of balancing the stability between generators and discriminators.
 There are a rich number of literature trying to stabilize GAN training \cite{salimans2016improved} and regularize networks \cite{huang2016stacked}.
-%But especially for text-to-image synthesis, how to utilize the multimodal information between images and text in discriminator is extremely important and needs careful consideration.
+%%But especially for text-to-image synthesis, how to utilize the multimodal information between images and text in discriminator is extremely important and needs careful consideration.
 The second reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}.
@@
 We introduce accompanying hierarchically-nested discriminators at multi-scale intermediate layers to play adversarial games and thereby encourage the generator approaching the real training data distribution.
-We also propose a novel convolutional neural network (CNN) framework for the generator to \textcolor{red}{cooperate with} our nested discriminators more effectively.
+We also propose a new convolutional neural network (CNN) for generator to support connections of discriminators at side outputs more effectively.
 To guarantee the image diversity and semantic consistency,
-we enforce nested discriminators at different hierarchies to simultaneously differentiate real-and-fake image-text pairs as well as real-and-fake global images or local image patches with certain \textcolor{red}{receptive field.
-This multi-purpose conditional adversary is mutually beneficial to allow each focus on its respect duty.}%focal ranges
+we enforce nested discriminators at different hierarchies to simultaneously differentiate real-and-fake image-text pairs as well as real-and-fake global images or local image patches. 
+%%\textcolor{red}{This multi-purpose conditional adversary is mutually beneficial to allow each focus on its respect duty.}%focal ranges
 
@@
 %% It is a regularization to limit the discriminators to use unexpected information to make decision.
-
-\textcolor{red}{To summarize, our contributions are:}
 
@@
 
-Text-to-image synthesis not only requires diverse and high-quality image generation but also requires precise semantically consistent mapping in the image space.
-Reed \etal \cite{reed2016generative}  is th first to introduce a method that can generate $64^2$ resolution images, which is similar with DCGAN \cite{radford2015unsupervised}.
+Text-to-image synthesis is attractive problem in GANs.
+Reed \etal \cite{reed2016generative}  is the first to introduce a method that can generate $64^2$ resolution images, which is similar with DCGAN \cite{radford2015unsupervised}.
 This method presents a new strategy for image-text matching aware adversarial training.
@@
 Although GANs have made significant progress, there are still many unsolved difficulties, e.g.
-training instability and high-resolution extensions.
+training instability and high-resolution generation.
 Wide methods have been proposed to address the training instability, such as various training techniques \cite{salimans2016improved,arjovsky2017wasserstein,berthelot2017began,shrivastava2016learning,odena2016conditional}, regularization using extra knowledge (e.g.
 image labels, ImageNet CNNs, etc) \cite{dosovitskiy2016generating,ledig2016photo,dash2017tac,dash2017tac}, or different generator and discriminator combinations  \cite{metz2016unrolled,durugkar2016generative,yang2017lr,huang2016stacked}.
-\textit{While our method shows a new way to unite generators and discriminators and does not use any extra information apart from training paired text and images.} Additionally, it is easy to see the training difficulty increases significantly as targeting image resolution increases.
+\textit{While our method shows a new way to unite generators and discriminators and does not requires any extra knowledge apart from training paired text and images.} Additionally, it is easy to see the training difficulty increases significantly as targeting image resolution increases.
 
@@
 
-To synthesize high-resolution images, cascade networks are useful to decompose original difficult tasks to multiple subtasks (Figure \ref{fig:archs-review} A).
-Denton \etal \cite{denton2015deep} train a cascade of GANs within a Laplacian pyramid framework (LAPGAN) and use each to generate difference images, conditioned on random noises and the output from the last pyramid level, and thereby push up the output resolution through by-stage refinement.
-StackGAN also shares similar strategy with LAPGAN.
-Following this strategy, Chen \etal \cite{chen2017photographic} present a cascaded refinement network to synthesize high-resolution scene from semantic maps.
+To synthesize high-resolution images, cascade networks are effective to decompose originally difficult tasks to multiple subtasks (Figure \ref{fig:archs-review} A).
+Denton \etal \cite{denton2015deep} train a cascade of GANs in a Laplacian pyramid framework (LAPGAN) and use each to synthesis details and push up the output resolution through by-stage refinement.
+StackGAN also shares some similar idea with LAPGAN.
+Inspired by this strategy, Chen \etal \cite{chen2017photographic} present a cascaded refinement network to synthesize high-resolution scene from semantic maps.
 %%Huang \etal \cite{huang2016stacked} propose a top-down stacked GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method.
 However, this method needs multiple symmetric bottom-up pre-trained discriminators and the usage for high-resolution image is unclear.
-Recently, Karras \etal \cite{Karras2017progressive} propose a progressive training of GANs for very high-resolution image generation (Figure \ref{fig:archs-review} C).
-\textit{Compared with these strategies that train low-to-high resolution GANs progressively, our method has advantages of leveraging mid-level representations to encourage implicit subtask integration, which makes end-to-end high-resolution image synthesis in a single vanilla-like GAN possible.}
+Recently, Karras \etal \cite{Karras2017progressive} propose a progressive training of GANs for high-resolution image generation (Figure \ref{fig:archs-review} C).
+\textit{Compared with these strategies that train low-to-high resolution GANs progressively, our method has the advantages of leveraging mid-level representations to encourage implicit subtask integration, which makes end-to-end high-resolution image synthesis in a single vanilla-like GAN possible.}
 
@@
 Leveraging hierarchical representations of neural networks is an effective way to enhance implicit multi-scaling and ensembling for tasks such as image recognition \cite{lee2015deeply} and pixel or object classification \cite{xie2015holistically,cai2016unified,long2015fully}.
-Particularly, using deep supervision \cite{lee2015deeply} in hierarchical convolutional layers is shown to be ablue to increase the discriminativeness of feature representations.
-\textit{Our hierarchically-nested adversarial objective is inspired by these families of CNNs with deep supervision. }
+Particularly, using deep supervision \cite{lee2015deeply} in hierarchical convolutional layers can increase the discriminativeness of feature representations.
+\textit{Our hierarchically-nested adversarial objective is inspired by these families of deeply-supervised CNNs. }
 %Our proposed hierarchically-nested adversarial supervision enhances layer representations to support final high resolution outputs.
@@
 \subsection{Adversarial objective basics}
-Generative adversary networks (GANs) consists of a generator $G$ and a discriminator $D$, which are alternatively trained to compete with each other in a two-player minimax game.
-$D$ is optimized to distinguish synthesized images from real images, meanwhile, $G$ is trained to fool $D$ by generating fake images.
-Concretely, the optimal $G$ and $D$ can be obtained by playing the following two-player min-max game,
-%In brief, the two-player game in GANs \cite{goodfellow2014generative} is played by a generator $G$ network and a discriminator $D$ network, which are alternatively optimized to compete with each other.
-The discriminator is trained to distinguish synthesized images from real images, meanwhile, the generator is trained to generate fake images to fool the discriminator.
-Concretely, the optimal $G$ and $D$ can be obtained by:
+In brief, the two-player game in GANs \cite{goodfellow2014generative} is played by a generator $G$ network and a discriminator $D$ network, which are alternatively trained to compete with each other and thereby improve each other.
+The discriminator is optimized to distinguish synthesized images from real images, meanwhile, the generator is trained to generate fake images to fool the discriminator.
+Concretely, the overall min-max optimization objective is defined as:
 %where the optimal $G$ and $D$ can be obtained by 
@@
 Concretely, the overall training procedure can be analogous to the following two-player min-max game $\mathcal{L}(D, G)$, where the optimal $G$ and $D$ can be obtained by
-%\begin{equation}
-%\label{game}
-%\begin{split}
-%\underset{G}{\min}\ \underset{D}{\max}\ V(D, G) =  &\mathbb{E}_{x\sim p_{data}}[\log D(x)] +  \\
-%&\mathbb{E}_{z\sim p_{z}}[\log (1-D(G(z)))]		   
-%\end{split}
-%\end{equation}
-
 \begin{equation}
@@
 \end{equation}
-%where $x$ is a real image sampled from the true data distribution $p_{data}$, $z$ is a noise vector usually sampled from some predefined distribution $p_{z}$ (e.g., Gaussian distribution).
-In this paper, we replace the negative log likelihood loss with a least square objective\cite{lsgan}.
-
-where $Y$ and $\bm z$ denotes training images and random noises, respectively. 
-%$G$ is learned to approximate $G(\bm z) \sim p(Y)$.  The loss $\mathcal{L}$ for the valuation function is usually a cross-entropy loss, such that $\mathcal{V}(\cdot) = - \mathcal{L}(\cdot)$. 
-$\mathcal{V}$ is the overall GAN loss, which usually takes the form $\mathbb{E}_{Y\sim p_{data}}\big[\log D(Y)\big] + \mathbb{E}_{\bm z\sim p_{z}}\big[\log (1-D(G(\bm z)))\big]$ or other variations\cite{lsgan}.
+where $Y$ denotes training images and $\bm z\sim\mathcal{N}(0,1)$ denotes a random noise.
+The value function $\mathcal{V}$ aims to minimize the Jensen-Shannon divergence between the data and the model distribution.
+$G$ is learned to approximate $G(\bm z) \sim p(Y)$.
+The loss $\mathcal{L}$ for the valuation function is usually a cross-entropy loss, such that $\mathcal{V}(\cdot) = - \mathcal{L}(\cdot)$.
 
@@
 Numerous methods have demonstrated ways to unite generators and discriminators for image synthesis. Figure \ref{fig:archs-review} and Section 2 discuss some typical frameworks.
-\textcolor{red}{Our method actually explores a new dimension of playing this adversarial game along the depth of a CNN} (Figure \ref{fig:archs-review} D), which integrates additional discriminators at \textcolor{red}{mid-level} features of the generator.
+Our method actually explores a new dimension of playing this adversarial game along the depth of a CNN (Figure \ref{fig:archs-review} D), which integrates additional discriminators at mid-level features of the generator $\mathcal{G}$.
 The hierarchically-nested objectives 
@@
 \end{equation}
-where  $\bm t\sim p(data)$ denotes a sentence embedding vector in the real training data distribution (generated by a pre-trained char RNN encoder\cite{reed2016generative}).
-$\mathcal{G}$ produces $s-1$ side outputs $\{X_1,...,X_{s-1}\}$ (size-growing images) and a final output $X_s$ with the highest resolution.
+where  $\bm t\sim p(data)$ denotes a sentence embedding vector in the real training data distribution (generated by a text character encoder).
+$\mathcal{G}$ produces $s-1$ side outputs $\{X_1,...,X_{s-1}\}$ (resolution-growing images) and a final output $X_s$ with the highest resolution.
 
@@
 
-For each side output $X_i$, a distinct discriminator $D_i$ is associated to compete with it. Therefore, our full min-max objective is defined as 
+For each $X_i$, we propose to apply a distinct discriminator $D_i$ to perform adversarial games independently. Therefore, our full min-max objective is defined as 
 \begin{equation}
@@
 Compared with Eq.
-(\ref{equ:GAN}), our generator competes with multiple discriminators  $\{D_i\}$ at different hierarchies (Figure \ref{fig:archs-review} D), where each focus on learning diverse discriminative features in different contextual scales.
+(\ref{equ:GAN}), one generator competes with multiple discriminators  $\{D_i\}$ at different hierarchies (Figure \ref{fig:archs-review} D), which learns diverse discriminative features in different contextual scales, respectively.
 %%Discriminators do not share weights with each other, which offers them full flexibility to focus on learning diverse discriminative features in different contextual scales.
-In principle, the lower-resolution side output can learn semantic consistent image structures (e.g., object sketch, color, and background), and the subsequent higher-resolution side outputs are used to render more details to images.
-Since our method is trained in an end-to-end fashion, the lower-resolution outputs can also fully utilize top-down knowledge from discriminators for higher resolutions.
-We can observe consistent image structures, color and styles in outputs of both low and high resolutions without using addition supervising term\cite{han2017stackganv2}.
-%We think such consistency is able to reduce the model instability.
-As an evidence, we can obtain significantly more consistent results exhibited in both low- and high-resolution outputs compared with StackGAN (see experiments). 
+
+In principle, the lower-resolution side output is forced to learn semantic consistent image structures (e.g., object sketch, color, and background), and the subsequent higher-resolution side outputs are used to render details on these image structures.
+Since our method is able to be trained in an end-to-end fashion, the lower-resolution outputs can fully enjoy top-down knowledge from discriminators for higher resolutions, such that consistent image structures and styles appear in both low and high resolutions.
+As an evidence, we can obtain significantly more consistent results exhibited in both low- and high-resolution outputs than StackGAN (see experiments). 
+According to our empirical observation, our design is able to reduce the model instability, especially at the early stage of the training.
 %% %We present the following multi-purpose adversarial loss to support more effective generator training.
 
-\subsection{Functional adversarial losses}
+\subsection{Multi-purpose adversarial losses}
 Our generator produces size-growing side outputs which compose an image pyramid. 
@@
 The pair loss is designed to guarantee the global semantic consistency.
-However, there is no explicit loss that forces the discriminator to differentiate pure real images from fake images.
-Combining both tasks (generating realistic images and matching image with text) into one output further complicates the learning tasks, which is already challenging.
-Second, as the image resolution goes higher, it might be challenging for a global pair-loss discriminator to capture local fine-grained details.
+However, there lacks an explicit loss that forces the discriminator to differentiate pure real images from fake images.
+Combining both tasks (generating realistic images and matching image styles with text) into one loss complicates the already challenging learning tasks.
+Moreover, as the image resolution goes higher, it might be challenging for a global pair-loss discriminator to capture the local fine-grained details.
 %As the image resolution goes higher, discriminators might loss focus for local fine-grained image details.
@@
 %Second, as the image resolution goes higher, it might be challenging for a global pair-loss discriminator to capture local fine-grained details.  
-In addition, as pointed in \cite{shrivastava2016learning}, a single global discriminator may over-emphasize certain unexpected image features and lead to artifacts.
+In addition, as pointed in \cite{shrivastava2016learning}, a single global discriminator may over-emphasize certain biased local features and lead to artifacts.
 
@@
 We expect the low-resolution discriminator to focus on global structures, while high-resolution outputs focus more on local image details.
-We validate this analysis in the experiments.
-Through the pyramid of the size-growing side outputs, we configure the focal range (the size of each image patch need to classify) to be adaptive.
-The local image adversarial loss is implemented as a fully CNN \cite{shrivastava2016learning,zhu2017unpaired},  with an extra branch of the discriminator for the pair loss (see Section 3.4).
-Figure \ref{fig:loss} illustrates how hierarchically-nested discriminators compute the two losses on generated images.
+Through the pyramid of the size-growing side outputs, we configure the size of each image patch need to classify, termed  the focal range, to be adaptive.
+The local image adversarial loss can be implemented as an fully CNN \cite{shrivastava2016learning,zhu2017unpaired}, and it is the second branch of our discriminator for the pair loss (see Section 3.4).
+Figure \ref{fig:loss} illustrates how hierarchically-nested discriminators compute the two losses on generated image in the pyramid.
 
@@
 $R=1$ refers to the (largest local) global range.
-For the matching-aware pair loss,
+$D_i(X_i)$ denotes the image loss branch and $D_i(X_i, \bm{t}_{X_i})$ denotes the pair loss branch (conditioned on $\bm t$).
 $\{Y_i, \bm t_{Y}\}$ denotes a matched image-text pair and $\{Y_i, \bm{t}_{\overline{Y}}\}$ denotes a mismatched image-text pair.
@@
 Furthermore, this separation of the image loss from the matching loss in our method opens further possibilities, such as utilizing the unlabeled image to improve both the generator and discriminator.
-
-\textcolor{red}{In the spirit of variational auto-encoder \cite{vae} and the practice of StackGAN \cite{han2017stackgan}, instead of directly using deterministic text embedding, we sample a stochastic vector from a Ganssian distribution $\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}))$, where $\mu$ and $\Sigma$ are parameterized functions of $\bm t$.
-We add the Kullback-Leibler divergence regularization term, $D_{KL}(\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}) )|| \mathcal{N}(0, \bm{I}))$ \cite{vae}, to $G$ loss to prevent over-fitting and force smooth sampling over the text embedding distribution.
+\textcolor{red}{In the spirit of variational auto-encoder \cite{vae} and the practice of StackGAN \cite{han2017stackgan}, namely conditioning augmentation (CA), we sample the input text $\bm t$ from a Ganssian distribution $\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}))$, where $\mu$ and $\Sigma$ are functions of $\bm t$ (learned with the network), which produces a $256$-d text input.
+We add the Kullback-Leibler divergence regularization term, $D_{KL}(\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}) )|| \mathcal{N}(0, \bm{I}))$ \cite{vae}, to the $G$ loss to force the smooth sampling over the text embedding distribution.
 }
@@
 A single res-block in the $K$-repeat res-block is a modified\footnote{We remove ReLU after the skip-addition of each residual block, with an intention to reduce sparse gradients.} residual block \cite{he2016identity}, which contains two convolutional (conv) layers (with batch normalization (BN) \cite{ioffe2015batch} and ReLU).
-The stretching layer serves to reduce feature map size and dimension.
-It simply contains an scale-$2$ nearest up-sampling layer followed by a convolutional layer with BN+ReLU.
-The linear compression layer is one conv layer followed by a Tanh to directly compress features map to the RGB space (as side outputs) linearly.
-We prevent any non-linear functions that could impede the gradient signals.
+The stretching layer serves to change feature map size and dimension.
+It simply contains an scale-$2$ nearest up-sampling layer followed by a conv layer with BN+ReLU.
+The linear compression layer is a single conv layer followed by a Tanh to directly compress feature maps to the RGB space (as side outputs).
+We prevent any non-linear function in the compression layer that could impede the gradient signals.
 %, whose compact design enforces feature maps in conv blocks can linearly represent RGB images at arbitrary scales.
-Starting from a $1024{\times}4{\times}4$ embedding, which are computed by the CA output followed by a trainable embedding matrix, the generator simples use $M$ $K$-repeat res-blocks connected by $M{-}1$ in-between stretching layers until the feature maps reach to the targeting resolution.
-So for $256{\times}256$ resolution with $K{=}1$, there are $M{=}6$ $1$-repeat res-blocks and $5$ stretching layers. 
+Starting from a $1024{\times}4{\times}4$ embedding, which is computed by CA and a trained embedding matrix, the generator simply uses $M$ $K$-repeat res-blocks connected by $M{-}1$ in-between stretching layers until the feature maps reach to the targeting resolution.
+For example, for $256{\times}256$ resolution and $K{=}1$, there are $M{=}6$ $1$-repeat res-blocks and $5$ stretching layers. 
 %Such simple and symmetric design makes our generator helpful for gradient flows. We will verify in experiments. 
-With a predefined side-output scales $\{1,...,s\}$, we apply the compression layer at those scales to produce synthetic images (i.e., side outputs).
+With a pre-defined side-output position at scales $\{1,...,s\}$, we apply the compression layer at those positions to generate side output images.
 
 \textbf{Discriminator} The discriminator simply contains consecutive stride-2 conv layers with BN and LeakyReLU.
-There are two branches are added on the upper layer for the proposed functional discriminator design (see next section).
+There are two branches are added on the upper layer for the proposed functional discriminator design.
 One branch is a direct fully convolutional layers to produce a $R{\times}R$ probability map (see Figure \ref{fig:loss}) and classify each location as real or fake.
-Another branch first concatenates a $128{\times}4{\times}4$ text embedding (replicated by a reduced $128$-d text embedding).
-Then we use an $1{\times}1$ conv to fuse text and image information and  a $4{\times}4$ conv layer to classify the image-text pair is real or fake.
+Another branch first concatenates the $512{\times}4{\times}4$ feature map and a $128{\times}4{\times}4$ text embedding (replicated by a reduced $128$-d text embedding).
+Then we use an $1{\times}1$ conv to fuse text and image information and a $4{\times}4$ conv layer to classify the image-text pair to real or fake.
 %it is critical to guarantee the semantic consistency in the final results.
 
-The training is similar with the standard GAN alternative training strategy. Please refer to the supplementary material for training details.
+The training is similar with the standard alternative training strategy in GANs. Please refer to the supplementary material for training and more network details.
 
@@
 \section{Experiments}
-This section evaluates the proposed method both qualitatively and quantitatively on three public datasets.
+%%This section evaluates the proposed method both qualitatively and quantitatively on three public datasets. 
 We denote our method as \textbf{HDGAN}, referring as High-Definition results and the idea of Hierarchically-nested Discriminators.
@@
 \textbf{Dataset} 
-We test on three widely used datasets.
-The CUB dataset \cite{welinder2010caltech} contains 11,788 bird images belonging to 200 different categories.
-We pre-process and split the images following the same pipeline in \cite{reed2016generative,han2017stackgan}
+We test on three widely used datasets. The CUB dataset \cite{welinder2010caltech} contains 11,788 bird images belonging to 200 different categories. 
 %, which crops the bird region and ensure the foreground occupies greater than 0.75.  
@@
 %We follow \cite{han2017stackgan, reed2016generative} to split both of these datasets into class-disjoint training and testing sets. 
-Each image in both datasets is associated with 10 text descriptions.
-In the COCO dataset, \cite{lin2014microsoft} there are 80k training images and a validation 40k images.
+Each image in both datasets is annotated with 10 text descriptions provided by \cite{reed2016generative}.
+We pre-process and split the images of CUB and Oxford-102 following the same pipeline in \cite{reed2016generative,han2017stackgan}.
+In the COCO dataset \cite{lin2014microsoft}, there are 80k training images and 40k validation images.
 Each image has 5 text descriptions.
@@
 For CUB and Oxford-102, we use the fine-tuned inception model provided by StackGAN.
-For MS COCO dataset, we directly use the model pre-trained on ImageNet.
-2) We also adopt the multi-scale structural similarity (MS-SSIM) metric \cite{improvedGAN} for further validation.
+For COCO, we directly use the model pre-trained on ImageNet.
+2) Multi-scale structural similarity (MS-SSIM) metric \cite{improvedGAN} is used for further validation.
 It tests pair-wise variation of generated outputs and can find mode collapses reliably \cite{odena2016conditional}.
@@
 
-3) \textbf{Visual-semantic similarity.} The aforementioned metrics are widely used for general GANs.
+3) \textbf{Visual-semantic similarity} The aforementioned metrics are widely used for general GANs.
 The problem of them is that they can not measure the alignment between the generated images and conditioned text.
@@
 Our results have significantly higher quality and preserve more semantic details, for example, ``the brown and white feathers and read head'' in the last column is much better reflected in our images.
-Moreover, we observed our birds have more diverse poses (e.g.
-the frontal view in the the second and the back view forth columns).}
+Moreover, we observed our birds exhibit richer poses (e.g.
+the frontal/back views in the second/forth columns).}
 	\vspace{-0.2cm}
@@
 TAC-GAN uses image labels to increase the discriminability of generators, while we do not use any extra knowledge.
-Figure \ref{fig:vis-cub} and Figure \ref{fig:vis-oxford} show the results compared with StackGAN and strongly demonstrate the superiority of HDGAN.
-Moreover, we qualitatively evaluate the diversity of samples conditioned on the same text (with different input noises) in Figure \ref{fig:multiple-test} left.
-HDGAN can generate obviously more successful samples than StackGAN.
+Figure \ref{fig:vis-cub} and Figure \ref{fig:vis-oxford} compare the qualitative results with StackGAN, by demonstrating more semantics details, richer poses, and more complex generated structures, which strongly prove the superiority of HDGAN.
+Moreover, we qualitatively compare the diversity of samples conditioned on the same text (with different input noises) in Figure \ref{fig:multiple-test} left.
+HDGAN can generate obviously more successful samples.
+Please refer to the supplementary material for more results.
 
 Table \ref{table:vss} compares the VS results on the three datasets.
-We also add the evaluation results on the ground truth image and sentence pair for reference.
-HDGAN achieves consistent better performance on both CUB and Oxford-102 datasets.
-This results demonstrate that HDGAN can better capture the visual semantic information in generated images and results in higher visual similarity.
-%%Our proposed method achieves much better results on both CUB and Oxford-102 datasets. Since we do not have a pre-trained  StackGAN model for coco dataset, we omit the comparison.
+The results of the ground truth image-text pair are shown for reference.
+HDGAN achieves consistently better performance on both CUB and Oxford-102.
+This results demonstrate that HDGAN can better capture the visual semantic information in generated images.
 
@@
 	\vspace{-.2cm}
-	\caption{Left: Diversity test given a single input text.
+	\caption{Left: Diverse samples are shown given a single input text.
 The proposed HDGAN (top) show obviously more details and higher diversity.
 Right: Side outputs of HDGAN with increasing resolutions.
-Different resolutions are semantically consistent and semantic details emerges as resolution increases.
+Different resolutions are semantically consistent and semantic details appear as the resolution increases.
 \label{fig:multiple-test}} 	\vspace{-.3cm}
@@
 The points below the equality line represent classes our HDGAN wins.
-The inter-class std is shown in axis titles.
-Right: Overall (no class-wise)  MS-SSMI evaluation.} \label{fig:msssmi}
+The inter-class std is shown in axis text.
+Right: Overall (not class-wised)  MS-SSMI evaluation.} \label{fig:msssmi}
 	\vspace{-0.4cm}
@@
 
-Table \ref{fig:msssmi} compares the MS-SSMI image quality evaluation score with StackGAN and \textcolor{red}{Prog.GAN for bird} image generation.
-StackGAN and our HDGAN use the semantic text as input so the generated images are separable in class.
-We randomly sample ${~}20,000$ image pairs (400 per class) and show the class-wise score in the left figure.
+\textcolor{red}{Table \ref{fig:msssmi} compares the MS-SSMI image quality evaluation score with StackGAN and Prog.GAN for bird image generation.} StackGAN and our HDGAN use text as input so the generated images are separable in class.
+We randomly sample ${\sim}20,000$ image pairs (400 per class) and show the class-wise score in the left figure.
 HDGAN outperforms StackGAN in majority of classes and also has lower inter-class standard deviation ($.023$ vs.
 $.032$).
-Prog.GAN uses noise input rather than text.
-We can compare with it for general measure of synthesis diversity.
-Following the procedure of Prog.GAN, we randomly sample ${~}10,000$ image pairs from all generated samples (We use $256^2$ images provided by the Prog.GAN online) and show the results in Table \ref{fig:msssmi} right.
-Our HDGAN outperforms both methods.
+Note that Prog.GAN uses noise input rather than text.
+We can compare with it for the general measure of image diversity.
+Following the procedure of Prog.GAN, we randomly sample ${\sim}10,000$ image pairs from all generated samples (We use $256^2$ images provided by Prog.GAN) and show the results in Table \ref{fig:msssmi} right.
+HDGAN outperforms both methods.
 
@@
 %Table \ref{table:multiscales}
-The right figure compares the the multi-resolution inception score on CUB.
+The right figure compares the multi-resolution inception score on CUB.
 Our results are from the side outputs of a single model.
-As can be observed, our $64^2$ images outperforms $128^2$ images of StackGAN and our $128^2$ images outperforms $256^2$ images of StackGAN substantially.
+As can be observed, our $64^2$ results outperform the $128^2$ results of StackGAN and our $128^2$ results also outperform $256^2$ results of StackGAN substantially.
 It strongly demonstrates our HDGAN better preserves semantically consistent information in all resolutions.
 Figure \ref{fig:multiple-test} right qualitatively validate this property.
-However, in StackGAN, the low resolution and high resolution image sometimes are visually inconsistent (see examples in Figure \ref{fig:vis-cub} and Figure \ref{fig:vis-oxford}).
+However, we observed that, in StackGAN, the low-resolution images and high-resolution images sometimes are visually inconsistent (see examples in Figure \ref{fig:vis-cub} and Figure \ref{fig:vis-oxford}).
 
@@
 Ideally, a well trained model should learn a smooth linear latent manifold of the images.
-To demonstrate the generalization capability of HDGAN, we generate images using the linearly interpolated embeddings between two source sentences.
+To demonstrate this ability of HDGAN, we generate images using the linearly interpolated embeddings between a source sentence and a target sentence.
 %%We fix the random noise input to make the object and background consistent.
@@
 In the first row, the generated birds gradually turn the color from yellow to brown.
-In the second row, more complicated sentences with detailed appearance descriptions (e.g., blue peaks and yellow wing) are used, we can see that our model is still be able to successfully capture these subtle features and tune the bird appearance gradually.
+In the second row, two sentences with more complicated appearance descriptions is used, we can see that our model successfully captures these subtle features and tune the bird appearance gradually.
 
@@
 In Table \ref{table:multiscales}, we compare the performance of HDGAN by removing part of discriminators on both CUB and COCO datasets. 
-As can be seen, increasing the usage of discriminators at different scales have positive effectives.
-And using discriminators on $64^2$ is critical (by comparing 64-256 and 128-256 cases).
+As can be seen, increasing the usage of discriminators at different scales have positive effects.
+And using discriminators at $64^2$ is critical (by comparing 64-256 and 128-256 cases).
 For now, we are unsure if adding more discriminators and even on lower resolution would be helpful.
-Further investigation will be conducted to validate it.
-StackGAN emphasizes the importance of combining text embeddings with intermediate features of the $256^2$ generator by showing a large drop from $3.7$ to $3.45$ without doing so.
+Further validation will be conducted.
+StackGAN emphasizes the importance of using text embeddings not only at input but also with intermediate features of the generator, by showing a large drop from $3.7$ to $3.45$ without doing so.
 While our method only uses text embeddings at the input.
-Our significantly improved results demonstrate the effectiveness of our strategy to maintain such semantic information and high inception score.
+Our significantly improved results demonstrate the effectiveness of our hierarchically-nested adversarial training to maintain such semantic information and high inception score.
 
@@
 Table \ref{table:multiscales} compares the case by removing the local loss (denoted as `w/o local').
-%We conduct experiments with using architecture with side output 64$\times$64, 128$\times$128 and 256 $\times$ 256 using Oxford dataset. 
-%As can be seen in Table\ref{tab:ablation}, 
-As can be seen, the inception score drop from 3.45 to 3.12.
-%, which proven that adding local image loss can help to improve the visual quality of the generated images. 
-Besides, the local image loss also helps improve the visual-semantic matching evidenced by the higher VS score of w/local.
-We hypothesis that it is because adding the separate local image loss can offer the pair loss more focuses on learning the semantic consistency.
+Besides, the local image loss also helps improve the visual-semantic matching evidenced by the higher VS score of `w/ local'.
+We hypothesis that it is because adding the separate local image loss can offer the pair loss more ``focus'' on learning the semantic consistency.
 Furthermore, we also quantitatively compare the generated results in Figure \ref{fig:vis-imgloss}.
-Although both models can successfully capture the semantic details in text.
-The model with the local loss successfully generate more fine-grained structures described in text and thus improving the visual quality.
+Although both models can successfully capture the semantic details in text, the model with the local loss more precisely generate object structures described in conditioned text.
 
@@
 %Note that for text-to-image synthesis, StackGAN is the only successful method to generate $256{\times}256$ images.
-\textbf{Design principles} StackGAN shows the difficulty of directly training a vanilla $256{\times}256$ GAN to generate meaningful images. 
-We test this extreme case using our method by removing all nested intermediate discriminators (the first row of Table \ref{table:multiscales}). Our method still generates fairly good results. 
-%Figure \ref{fig:vallina-res} shows the qualitatively results. 
-Based on our experience, the success is because of our effective generator designs that helps gradient flows.
-
-Initially, we tried to share top layers of the hierarchical discriminators of HDGAN inspired by \cite{liu2017unsupervised} with an intuition to reduce their variances and unify their common goal (i.e.
-differentiates real and fake despite difficult scales).
-However, we did not find benefits from this mechanism and our independent discriminators can be trained very stably.
+\textbf{Design principles} StackGAN shows the failure of directly training a vanilla $256{\times}256$ GAN to generate meaningful images. 
+We test this extreme case using our method by removing all nested discriminators (the first row of Table \ref{table:multiscales}).
+Our method still generates fairly good results, which demonstrate the effectiveness of our design framework (see Section 3.4).
+%%Figure \ref{fig:vallina-res} shows the qualitatively results. 
+%%Based on our experience, our effective generator designs better preserve gradient flows.
+
+Initially, we tried to share the top layers of the hierarchical-nested discriminators of HDGAN inspired by \cite{liu2017unsupervised}.
+The intuition is that all discriminators have a common goal to differentiate real and fake despite difficult scales and such sharing would reduce their inter-variances.
+However, we did not observe benefits from this mechanism and our independent discriminators can be trained very stably.
+
 \begin{table}[t] % retrieval
@@
 \section{Conclusion}
-In this paper, we present an effective and end-to-end method to tackle the problem of generating high-resolution images conditioned on text descriptions.
-We introduce a novel hierarchical-nested adversarial discriminators to regularize the mid-level representations of a generator.
-To improve the model's capability to render fine-grained local details, we propose a multi-purpose discriminator loss to emphasize local patch realism as well as matching aware pair.
-We also introduce a new evaluation metric for text-to-image synthesis to evaluate the semantic consistency between generated images and conditioned text.
-Extensive experiment results demonstrate that our method, namely HDGAN, performs significantly better than existing state of the arts.
+In this paper, we present a novel and effective method to tackle the problem of generating images conditioned on text descriptions.
+We present a new dimension of playing adversarial games along the depth of the generator using the hierarchical-nested adversarial objectives, which regularizes the mid-level representations with multi-purpose adversarial losses and help the generator to generate high-resolution photographic images.
+We also introduce a new evaluation metric to evaluate the semantic consistency between generated images and conditioned text.
+Extensive experiment results demonstrate that our method, namely HDGAN, performs significantly better than existing state of the arts on three public datasets.
 

### 2017-11-15 cvpr2018.tex

@@
 \begin{abstract}
-This paper presents a novel method to deal with the challenging task of generating images conditioning on semantic image descriptions.
-We propose an effective end-to-end single-stream network that can generate photographic high-resolution images.
-Our method leverages deep representations of convolutional layers and introduces accompanying hierarchical-nested adversarial games inside the network hierarchy, which regularize intermediate representations and assist training to capture the complex image statistics.
-We present an extensile network architecture to cooperate with discriminators and push generated images to high resolutions.
-We adopt a multi-purpose adversarial training strategy at multiple nested side outputs to encourage more effective image-text alignment in order to improve the semantic consistency and image fidelity simultaneously.
-Furthermore, we introduce a new visual-semantic similarity measure to evaluate the semantic consistency of generated images, thus alleviates the needs of human evaluation.
-With extensive experimental validation on three public datasets, our method significantly improves previous state of the arts on all datasets over different evaluation metrics (e.g.
-a ${11.86}$ Inception score on COCO).
+This paper presents a novel method to deal with the challenging task of generating photographic images conditioned on semantic image descriptions.
+Our method introduces accompanying hierarchical-nested adversarial objectives inside the network hierarchies, which regularize mid-level representations and assist generator training to capture the complex image statistics.
+We present an extensile single-stream generator architecture to better adapt the jointed discriminators and push generated images up to high resolutions.
+We adopt a multi-purpose adversarial loss to encourage more effective image and text information usage in order to improve the semantic consistency and image fidelity simultaneously.
+Furthermore, we introduce a new visual-semantic similarity measure to evaluate the semantic consistency of generated images, which also alleviates the cost of human evaluation.
+With extensive experimental validation on three public datasets, our method significantly improves previous state of the arts on all datasets over different evaluation metrics.
+
 \end{abstract}
@@
 \section{Introduction}
-Photographic text-to-image synthesis is a significant problem in generative model research \cite{reed2016generative}, which aims to learn a mapping from one semantic text space to one complex RGB image space.
-This task requires the generated images to be not only realistic but also \textit{semantically consistent}, i.e., the generated images not only preserve object color and sketch in descriptions but also fine-grained descriptive details in image pixels.
+Photographic text-to-image synthesis is a significant problem in generative model research \cite{reed2016generative}, which aims to learn a mapping from a semantic text space to a complex RGB image space.
+This task requires the generated images to be not only realistic but also \textit{semantically consistent}, i.e., the generated images preserve the object color and sketch described in text and fine-grained descriptive details in image pixels as well.
+
 %However, this problem still remains unsolved due to its particular challenges. 
@@
 	\caption{Top: Overview of our hierarchically-nested adversarial network. Bottom: Two generated results where fine-grained details are highlighted. \label{fig:intro}} 	
-	\vspace{-.6cm}
+	\vspace{-.5cm}
 	%\end{center}
@@
 %\end{figure}
-Generative adversarial networks (GANs) have become the main solution to this task. 
+Recently, generative adversarial networks (GANs) have become the main solution to this task. 
 Reed \etal \cite{reed2016generative} address this task through a GAN based framework. But this method only scale up to $64^2$ resolution and can barely generate vivid object details.
-Based on this method, StackGAN  \cite{han2017stackgan} propose a two-stage training strategy, which stacks another low-to-high resolution GAN to generate high-resolution $256^2$ images.
-Later on, \cite{dong2017semantic} proposes to bypass the difficult of learning mappings from vector embeddings to RGB images and treat it as a pixel-to-pixel translation problem \cite{isola2016image}.
+Based on this method, StackGAN  \cite{han2017stackgan} is a successful approach, which stacks another low-to-high resolution GAN to generate high-resolution $256^2$ images in a two-stage training strategy.
+Later on, \cite{dong2017semantic} proposes to bypass the difficult of learning a mapping from text to RGB images and treat it as a pixel-to-pixel translation problem \cite{isola2016image}.
 It works by re-rendering an arbitrary-style $128^2$ training  image conditioned on a targeting description.
-However, its high-resolution synthesis capability remains unclear.
-At present, training a generative model to map from a low-dimensional text space to a high-resolution and diverse image space in a fully end-to-end manner still remains unsolved.
-
-Text-to-image synthesis using GANs has two major difficulties.
+However, its high-resolution synthesis capability is still unclear.
+At present, training a generative model to map from a low-dimensional text space to a high-resolution image space in a fully end-to-end manner still remains unsolved.
+
+This paper pays attention to two major difficulties for text-to-image synthesis using GANs.
 The first is balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}, which is actually a long-term problem in GANs.
-The second is stably modeling the huge pixel space in high-resolution images \cite{han2017stackgan}.
-An effective strategy to regularize generators is critical to help capture the complex image statistics \cite{huang2016stacked} as well as guarantee semantic consistency.
-
-%%The first reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. 
-%% Keeping semantic consistency as well as diversity
-%%The first reason comes from the fundamental difficulty of balancing the stability between generators and discriminators.
-There are a rich number of literature trying to stabilize GAN training \cite{salimans2016improved} and regularize networks \cite{huang2016stacked}.
-%%But especially for text-to-image synthesis, how to utilize the multimodal information between images and text in discriminator is extremely important and needs careful consideration.
-The second reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}.
-Keeping semantic consistency as well as diversity in generated images needs more specialized designs for discriminators to generate effective gradients, as well as generators to prevent gradient vanishing.
-With careful consideration of these problems, in this paper, we propose a novel end-to-end method that can directly model high-resolution image statistics and generate semantically consistent and photographic image (see Figure \ref{fig:intro}).
+The second is stably modeling the huge pixel space in high-resolution images and guaranteeing semantic consistency \cite{han2017stackgan}.
+An effective strategy to regularize generators is critical to stabilize the training and help capture the complex image statistics \cite{huang2016stacked}.
+
+In this paper, we propose a novel end-to-end method that can directly model high-resolution image statistics and generate semantically consistent and photographic images (see Figure \ref{fig:intro}).
 The contributions are described as follows.
@@
 Our generator resembles a simple vanilla GAN, without requiring any multiple internal text conditioning like \cite{han2017stackgan} or outside image annotation supervision like \cite{dash2017tac}.
-To tackle the problem of the big leap from the text space to the high-resolution image space, our insight is to leverage and regularize hierarchical representations with additional deep adversarial constraints.
-We introduce accompanying hierarchically-nested discriminators at multi-scale intermediate layers to play adversarial games and thereby encourage the generator approaching the real training data distribution.
-We also propose a new convolutional neural network (CNN) for generator to support connections of discriminators at side outputs more effectively.
+To tackle the problem of the big leap from the text space to the high-resolution image space, our insight is to leverage and regularize hierarchical representations with additional `deep' adversarial constraints.
+We introduce accompanying hierarchically-nested discriminators at multi-scale intermediate layers to play adversarial games and jointly encourage the generator approaching the real training data distribution.
+We also propose a new convolutional neural network (CNN) design for the generator to support accompanied discriminators more effectively in an end-to-end training manner.
 To guarantee the image diversity and semantic consistency,
-we enforce nested discriminators at different hierarchies to simultaneously differentiate real-and-fake image-text pairs as well as real-and-fake global images or local image patches. 
+we enforce discriminators at scale-different generator side outputs to simultaneously differentiate real-and-fake image-text pairs as well as real-and-fake
+local image patches.
+
 %%\textcolor{red}{This multi-purpose conditional adversary is mutually beneficial to allow each focus on its respect duty.}%focal ranges
-
 %To alleviate the need for manual human evaluation about the matching between generated images and text description, we propose to learn a visual-semantic embedding model, thus providing a measure for quantitative evaluation of the image sentence consistency.
@@
 We validate our proposed method on three datasets, CUB birds \cite{welinder2010caltech}, Oxford-102 flowers \cite{Nilsback08}, and large-scale MSCOCO \cite{lin2014microsoft}.
-In complement of existing evaluation metric (inception score \cite{improvedGAN}) for generative models, we also introduce a new visual-semantic similarity metric to evaluate the alignment between generated images and conditioned text.
+In complement of existing evaluation metric (e.g.
+Inception score \cite{improvedGAN}) for generative models, we also introduce a new visual-semantic similarity metric to evaluate the alignment between generated images and conditioned text.
 Extensive experimental results and analysis demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts on three metrics.
+
 All source code will be released.
@@
 
-Text-to-image synthesis is attractive problem in GANs.
+Text-to-image synthesis is a significant problem in GANs.
 Reed \etal \cite{reed2016generative}  is the first to introduce a method that can generate $64^2$ resolution images, which is similar with DCGAN \cite{radford2015unsupervised}.
 This method presents a new strategy for image-text matching aware adversarial training.
-Reed \etal \cite{reed2016learning} propose generative
+Reed \etal \cite{reed2016learning} propose a generative
 adversarial what-where network (GAWWN) to enable location and content instructions in text-to-image synthesis.
@@
 Recently, Dong \etal \cite{dong2017semantic} propose to learn a joint embedding of images and text so as to re-render a prototype image conditioned on a targeting description.
-Cha \etal \cite{char2017perceptual} explore the usage of the perceptional loss with a CNN pretrained on ImageNet \cite{johnson2016perceptual} and Dash \etal \cite{dash2017tac} make use of auxiliary classifiers (similar with \cite{odena2016conditional}) to assist GAN training for text-to-image synthesis.
+Cha \etal \cite{char2017perceptual} explore the usage of the perceptional loss \cite{johnson2016perceptual} with a CNN pretrained on ImageNet  and Dash \etal \cite{dash2017tac} make use of auxiliary classifiers (similar with \cite{odena2016conditional}) to assist GAN training for text-to-image synthesis.
 
@@
 image labels, ImageNet CNNs, etc) \cite{dosovitskiy2016generating,ledig2016photo,dash2017tac,dash2017tac}, or different generator and discriminator combinations  \cite{metz2016unrolled,durugkar2016generative,yang2017lr,huang2016stacked}.
-\textit{While our method shows a new way to unite generators and discriminators and does not requires any extra knowledge apart from training paired text and images.} Additionally, it is easy to see the training difficulty increases significantly as targeting image resolution increases.
+\textit{While our method shows a new way to unite generators and discriminators and does not requires any extra knowledge apart from training paired text and images.} Additionally, it is easy to see the training difficulty increases significantly as the targeting image resolution increases.
 
@@
 To synthesize high-resolution images, cascade networks are effective to decompose originally difficult tasks to multiple subtasks (Figure \ref{fig:archs-review} A).
-Denton \etal \cite{denton2015deep} train a cascade of GANs in a Laplacian pyramid framework (LAPGAN) and use each to synthesis details and push up the output resolution through by-stage refinement.
+Denton \etal \cite{denton2015deep} train a cascade of GANs in a Laplacian pyramid framework (LAPGAN) and use each to synthesize and refine image details and push up the output resolution stage-by-stage.
 StackGAN also shares some similar idea with LAPGAN.
 Inspired by this strategy, Chen \etal \cite{chen2017photographic} present a cascaded refinement network to synthesize high-resolution scene from semantic maps.
-%%Huang \etal \cite{huang2016stacked} propose a top-down stacked GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method.
+%%% Huang \etal \cite{huang2016stacked} propose a top-down stacked GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method.
 However, this method needs multiple symmetric bottom-up pre-trained discriminators and the usage for high-resolution image is unclear.
-Recently, Karras \etal \cite{Karras2017progressive} propose a progressive training of GANs for high-resolution image generation (Figure \ref{fig:archs-review} C).
-\textit{Compared with these strategies that train low-to-high resolution GANs progressively, our method has the advantages of leveraging mid-level representations to encourage implicit subtask integration, which makes end-to-end high-resolution image synthesis in a single vanilla-like GAN possible.}
+Recently, Karras \etal \cite{Karras2017progressive} propose a progressive training of GANs.
+The idea is adding symmetric generator and discriminator layers gradually for high-resolution image generation (Figure \ref{fig:archs-review} C).
+\textit{Compared with these strategies that train low-to-high resolution GANs stage-by-stage or progressively, our method has the advantage of leveraging mid-level representations to encourage implicit subtask integration, which makes end-to-end high-resolution image synthesis in a single vanilla-like GAN possible.}
 
@@
 Leveraging hierarchical representations of neural networks is an effective way to enhance implicit multi-scaling and ensembling for tasks such as image recognition \cite{lee2015deeply} and pixel or object classification \cite{xie2015holistically,cai2016unified,long2015fully}.
-Particularly, using deep supervision \cite{lee2015deeply} in hierarchical convolutional layers can increase the discriminativeness of feature representations.
+Particularly, using deep supervision \cite{lee2015deeply} in hierarchical convolutional layers provides short error paths and increases the discriminativeness of feature representations.
 \textit{Our hierarchically-nested adversarial objective is inspired by these families of deeply-supervised CNNs. }
-%Our proposed hierarchically-nested adversarial supervision enhances layer representations to support final high resolution outputs.
+%%%Our proposed hierarchically-nested adversarial supervision enhances layer representations to support final high resolution outputs.
 
@@
 \subsection{Adversarial objective basics}
-In brief, the two-player game in GANs \cite{goodfellow2014generative} is played by a generator $G$ network and a discriminator $D$ network, which are alternatively trained to compete with each other and thereby improve each other.
-The discriminator is optimized to distinguish synthesized images from real images, meanwhile, the generator is trained to generate fake images to fool the discriminator.
+In brief, a GAN \cite{goodfellow2014generative} consists of a generator $G$ network and a discriminator $D$ network, which are playing an adversarial game to compete with each other.
+The discriminator is optimized to distinguish synthesized images from real images, meanwhile the generator is optimized to generate fake images to fool the discriminator.
 Concretely, the overall min-max optimization objective is defined as:
-%where the optimal $G$ and $D$ can be obtained by 
-%The discriminator is optimized to distinguish synthesized images from real images, meanwhile, the generator is trained to fool the discriminator and transform an input distribution $p_z$ to the true data distribution $p_{data}$.
-Concretely, the overall training procedure can be analogous to the following two-player min-max game $\mathcal{L}(D, G)$, where the optimal $G$ and $D$ can be obtained by
 \begin{equation}
@@
 \end{equation}
-where $Y$ denotes training images and $\bm z\sim\mathcal{N}(0,1)$ denotes a random noise.
-The value function $\mathcal{V}$ aims to minimize the Jensen-Shannon divergence between the data and the model distribution.
-$G$ is learned to approximate $G(\bm z) \sim p(Y)$.
-The loss $\mathcal{L}$ for the valuation function is usually a cross-entropy loss, such that $\mathcal{V}(\cdot) = - \mathcal{L}(\cdot)$.
+where $Y$ and $\bm z \sim \mathcal{N}(0,1)$ denote training images and random noises, respectively. 
+%$G$ is learned to approximate $G(\bm z) \sim p(Y)$.  The loss $\mathcal{L}$ for the valuation function is usually a cross-entropy loss, such that $\mathcal{V}(\cdot) = - \mathcal{L}(\cdot)$. 
+$\mathcal{V}$ is the overall GAN objective, which usually takes the (cross-entropy loss) form $\mathbb{E}_{Y\sim p_{data}}\big[\log D(Y)\big] + \mathbb{E}_{\bm z\sim p_{z}}\big[\log (1-D(G(\bm z)))\big]$ or other variations \cite{lsgan,berthelot2017began}.
 
@@
 \subsection{Hierarchical-nested adversarial objectives}
-%Directly predicting high resolution synthesized images are challenging, not only because of the difficulties in training but also due to the large variation and instability in the hidden layers.
-Numerous methods have demonstrated ways to unite generators and discriminators for image synthesis. Figure \ref{fig:archs-review} and Section 2 discuss some typical frameworks.
-Our method actually explores a new dimension of playing this adversarial game along the depth of a CNN (Figure \ref{fig:archs-review} D), which integrates additional discriminators at mid-level features of the generator $\mathcal{G}$.
-The hierarchically-nested objectives 
-%We conjecture that adding hierarchical adversarial objective using side outputs can
-act as regularizers to the hidden space of $\mathcal{G}$, which can reduce the training instability and also offer a short path for better error signal flows.
-
-The proposed $\mathcal{G}$ is a CNN (defined in Section 3.4) with multiple side outputs:
+Numerous GAN methods have demonstrated ways to unite generators and discriminators for image synthesis. Figure \ref{fig:archs-review} and Section 2 discuss some typical frameworks.
+Our method actually explores a new dimension of playing this adversarial game along the depth of a generator (Figure \ref{fig:archs-review} D), which integrates additional hierarchical-nested  discriminators at intermediate layers of the generator.
+The proposed objectives act as regularizers to the hidden space of $\mathcal{G}$, which also offer a short path for better error signal flow and helps reduce the training instability.
+
+The proposed $\mathcal{G}$ is a CNN (defined in Section 3.4) with multiple resolution-growing side outputs:
 %This architecture resemble the proposed inverse architectures in edge detection\cite{xie2015holistically} and classification \cite{lee2015deeply}, which demonstrate that additional supervision to hidden layers can improve model generalization and boost optimization.
@@
 \end{equation}
-where  $\bm t\sim p(data)$ denotes a sentence embedding vector in the real training data distribution (generated by a text character encoder).
-$\mathcal{G}$ produces $s-1$ side outputs $\{X_1,...,X_{s-1}\}$ (resolution-growing images) and a final output $X_s$ with the highest resolution.
+where  $\bm t\sim p_{data}$ denotes a sentence embedding vector in the real training data distribution (generated by a pre-trained char RNN encoder).
+$\{X_1,...,X_{s-1}\}$ are resolution-growing images and $X_s$ is the final output with the highest resolution.
 
@@
 
-For each $X_i$, we propose to apply a distinct discriminator $D_i$ to perform adversarial games independently. Therefore, our full min-max objective is defined as 
+For each side output $X_i$ from the generator, a distinct discriminator $D_i$ is associated to compete with it. Therefore, our full min-max objective is defined as 
 \begin{equation}
@@
 \begin{split}
-  \mathcal{G}^*, \mathcal{D}^*&  =  \arg~\underset{G}{\min}\ \underset{\mathcal{D}}{\max}~ \mathcal{V}(\mathcal{G},\mathcal{D}, \mathcal{Y}, \bm t, \bm z), \\
+  \mathcal{G}^*, \mathcal{D}^*&  =  \arg~\underset{\mathcal{G}}{\min}\ \underset{\mathcal{D}}{\max}~ \mathcal{V}(\mathcal{G},\mathcal{D}, \mathcal{Y}, \bm t, \bm z), \\
   %\text{where} \;\;	 \mathcal{D} & =  \{D_1, ..., D_s\}, \; \mathcal{Y} = \{Y_1, ..., Y_s\},
@@
 \end{equation}
-where $\mathcal{D}  =  \{D_1, ..., D_s\} $, and $\; \mathcal{Y} = \{Y_1, ..., Y_s\}$ denotes a set of training images at multi-scales, $\{1,...,s\}$.
-%where $\mathcal{D}$ contains the optimal discriminators $\{D_1^*, ..., D_o^*\}$, and $ \mathcal{L}(G,\mathcal{D}, \bm{X}, \bm{T} )$ is the full objective of this mini-max game.
-%Please note that in this setting, 
+where $\mathcal{D}  =  \{D_1, ..., D_s\} $ and $\; \mathcal{Y} = \{Y_1, ..., Y_s\}$ is a set of training images at multi-scales, $\{1,...,s\}$.
 Compared with Eq.
-(\ref{equ:GAN}), one generator competes with multiple discriminators  $\{D_i\}$ at different hierarchies (Figure \ref{fig:archs-review} D), which learns diverse discriminative features in different contextual scales, respectively.
-%%Discriminators do not share weights with each other, which offers them full flexibility to focus on learning diverse discriminative features in different contextual scales.
-
-In principle, the lower-resolution side output is forced to learn semantic consistent image structures (e.g., object sketch, color, and background), and the subsequent higher-resolution side outputs are used to render details on these image structures.
-Since our method is able to be trained in an end-to-end fashion, the lower-resolution outputs can fully enjoy top-down knowledge from discriminators for higher resolutions, such that consistent image structures and styles appear in both low and high resolutions.
-As an evidence, we can obtain significantly more consistent results exhibited in both low- and high-resolution outputs than StackGAN (see experiments). 
-According to our empirical observation, our design is able to reduce the model instability, especially at the early stage of the training.
+(\ref{equ:GAN}), one generator competes with multiple discriminators  $\{D_i\}$ at different hierarchies (Figure \ref{fig:archs-review} D), which learn discriminative features in different contextual scales, respectively.
+
+In principle, the lower-resolution side output is used to learn semantic consistent image structures (e.g.
+object sketches, colors, and background), and the subsequent higher-resolution side outputs are used to render fine-grained details.
+Since our method is trained in an end-to-end manner, the lower-resolution side outputs can fully enjoy the top-down knowledge from higher resolutions, such that we can observe consistent image structures and styles appear in both low and high resolutions.
+The experiment demonstrates this advantage compared with StackGAN. 
+% % According to our empirical observation, our design is able to reduce the model instability, especially at the early stage of the training.
+
 %% %We present the following multi-purpose adversarial loss to support more effective generator training.
@@
 \subsection{Multi-purpose adversarial losses}
-Our generator produces size-growing side outputs which compose an image pyramid. 
-We leverage this hierarchy property and allow adversarial losses to be multi-purpose to capture different (conditioned and unconditioned) statistics, with a goal to guarantee both semantic consistency and image fidelity.
-
-To guarantee semantic consistency, we adopt the matching-aware pair loss proposed by \cite{reed2016generative}.
-The discriminator is designed to take image-text pairs as inputs and trained to identify two types of errors: real image with mismatched text and fake image with conditioned text.
+Our generator produces resolution-growing side outputs, which compose an image pyramid. 
+We leverage this hierarchy property and allow adversarial losses to capture different statistics, with a goal to guarantee both semantic consistency and image fidelity.
+
+In order to guarantee semantic consistency, we adopt the matching-aware pair loss proposed by \cite{reed2016generative}.
+The discriminator is designed to take image-text pairs as inputs and be trained to differentiate two types of errors: a real image with mismatched text and a fake image with conditioned text.
 
 The pair loss is designed to guarantee the global semantic consistency.
-However, there lacks an explicit loss that forces the discriminator to differentiate pure real images from fake images.
-Combining both tasks (generating realistic images and matching image styles with text) into one loss complicates the already challenging learning tasks.
-Moreover, as the image resolution goes higher, it might be challenging for a global pair-loss discriminator to capture the local fine-grained details.
+However, there lacks an explicit loss that forces the discriminator to differentiate real images from fake images.
+And combining both tasks (generating realistic images and matching image styles with text) into one loss complicates the already challenging learning tasks.
+Moreover, as the image resolution goes higher, it might be challenging for a global pair-loss discriminator to capture the local fine-grained details (results are validated in experiments).
 %As the image resolution goes higher, discriminators might loss focus for local fine-grained image details.
@@
 
-To guarantee the image fidelity, our solution is to add local adversarial image losses on image patches. 
+To alleviate these issues and guarantee image fidelity, our solution is to add local adversarial image losses.
+%as inspired by \cite{shrivastava2016learning}. 
 %The insights are two folds:
@@
 %\end{itemize}
-We expect the low-resolution discriminator to focus on global structures, while high-resolution outputs focus more on local image details.
-Through the pyramid of the size-growing side outputs, we configure the size of each image patch need to classify, termed  the focal range, to be adaptive.
-The local image adversarial loss can be implemented as an fully CNN \cite{shrivastava2016learning,zhu2017unpaired}, and it is the second branch of our discriminator for the pair loss (see Section 3.4).
-Figure \ref{fig:loss} illustrates how hierarchically-nested discriminators compute the two losses on generated image in the pyramid.
+We expect the low-resolution discriminator to focus on global structures, while the high-resolution discriminator to focus  on local image details.
+Each discriminator consists of two branches (see Section 3.4), one computes a single scalar value for the pair loss and another branch computes a $R{\times}R$ probability map. 
+Each location differentiates whether an overlapping image patch is real or fake.
+Through the pyramid of the size-growing side outputs, we control $R$ accordingly. Specifically, a larger $R$ value results in a smaller local range and finer focus of discriminators.
+The local image adversarial loss can be implemented as an fully CNN \cite{shrivastava2016learning,zhu2017unpaired,isola2016image}.
+Figure \ref{fig:loss} illustrates how hierarchically-nested discriminators compute the two losses on the generated images in the pyramid.
 
@@
 	\vspace{-.7cm}
-	\caption{Given a set of images from the side output pyramid of the generator, the corresponding discriminator $D_i$ computes the matching-aware pair loss and adaptive local image loss (outputting a $R{\times}R$ probability map to classify real or fake patches).
-The focal range decreases as the image size grows.
-}  \vspace{-.3cm}
+	\caption{Given a set of images from the side output pyramid of the generator, the corresponding discriminator $D_i$ computes the matching-aware pair loss and local image loss (outputting a $R{\times}R$ probability map to classify real or fake image patches).
+$R$ increases as the image size grows.
+}  \vspace{-.2cm}
 	\label{fig:loss}
@@
 
-\textbf{Full Objective } Overall, our hierarchically-nested discriminators $\{D_i\}$ minimize the following loss\footnote{The objective of the generator is omitted as it can be easily inferred.}:
+\textbf{Full Objective } Overall, our full min-max adversarial objective is defined as 
+%%hierarchically-nested discriminators $\{D_i\}$ optimize the following objective:
 \vspace{-.2cm}
@@
 \begin{split}
-\mathcal{L}(& \mathcal{G}, \mathcal{D})  = \sum_{i=1}^{s} \Big(  L_2\big(D_i({Y}_i)\big) +  L_2\big(D_i({Y}_i, \bm t_{Y})\big) \, + \\ 
+\mathcal{V}(& \mathcal{G},\mathcal{D}, \mathcal{Y}, \bm t, \bm z) = \sum_{i=1}^{s} \Big(  L_2\big(D_i({Y}_i)\big) +  L_2\big(D_i({Y}_i, \bm t_{Y})\big) \, + \\ 
 & \overline{L_2}\big(D_i({X}_i)\big)  + \overline{L_2}\big(D_i({X}_i, \bm{t}_{X_i})\big) + \overline{L_2}\big(D_i({Y}_i,  \bm{t}_{\overline{Y}})\big) \Big),
@@
 where $L_2(x) = \mathbb{E}\big[(x - \mathbb{I})^2\big]$ is the mean-square loss (instead of the conventional cross-entropy loss) and $\overline{L_2}(x) =\mathbb{E}\big[x^2\big]$. 
-For local image loss with varying focal ranges, the shape of $x, \mathbb{I} \in \mathbb{R}^{R{\times}R}$ varies accordingly (see Figure \ref{fig:loss}).
+This objective is maximized by $\mathcal{D}$. While for $\mathcal{G}$ practically, we minimize 
+$\sum_{i=1}^{s} (L_2(D_i(\mathcal{G}(\bm t, \bm z)_i)) +  L_2\big(D_i(\mathcal{G}(\bm t, \bm z)_i, \bm{t}_{X_i})))$.
+For the local image loss, the shape of $x, \mathbb{I} \in \mathbb{R}^{R{\times}R}$ vary accordingly (see Figure \ref{fig:loss}).
 $R=1$ refers to the (largest local) global range.
-$D_i(X_i)$ denotes the image loss branch and $D_i(X_i, \bm{t}_{X_i})$ denotes the pair loss branch (conditioned on $\bm t$).
+$D_i(X_i)$ is the image loss branch and $D_i(X_i, \bm{t}_{X_i})$ is the pair loss branch (conditioned on $\bm{t}_{X_i}$).
 $\{Y_i, \bm t_{Y}\}$ denotes a matched image-text pair and $\{Y_i, \bm{t}_{\overline{Y}}\}$ denotes a mismatched image-text pair.
 
-Furthermore, this separation of the image loss from the matching loss in our method opens further possibilities, such as utilizing the unlabeled image to improve both the generator and discriminator.
-\textcolor{red}{In the spirit of variational auto-encoder \cite{vae} and the practice of StackGAN \cite{han2017stackgan}, namely conditioning augmentation (CA), we sample the input text $\bm t$ from a Ganssian distribution $\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}))$, where $\mu$ and $\Sigma$ are functions of $\bm t$ (learned with the network), which produces a $256$-d text input.
-We add the Kullback-Leibler divergence regularization term, $D_{KL}(\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}) )|| \mathcal{N}(0, \bm{I}))$ \cite{vae}, to the $G$ loss to force the smooth sampling over the text embedding distribution.
-}
+In the spirit of variational auto-encoder \cite{vae} and the practice of StackGAN \cite{han2017stackgan} (namely conditioning augmentation (CA)), instead of directly using deterministic text embedding, we sample a stochastic vector from a Ganssian distribution $\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}))$, where $\mu$ and $\Sigma$ are parameterized functions of $\bm t$.
+We add the Kullback-Leibler divergence regularization term, $D_{KL}(\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}) )|| \mathcal{N}(0, \bm{I}))$ \cite{vae}, to $\mathcal{G}$ loss to prevent over-fitting and force smooth sampling over the text embedding distribution.
 
@@
 A single res-block in the $K$-repeat res-block is a modified\footnote{We remove ReLU after the skip-addition of each residual block, with an intention to reduce sparse gradients.} residual block \cite{he2016identity}, which contains two convolutional (conv) layers (with batch normalization (BN) \cite{ioffe2015batch} and ReLU).
-The stretching layer serves to change feature map size and dimension.
-It simply contains an scale-$2$ nearest up-sampling layer followed by a conv layer with BN+ReLU.
+The stretching layer serves to change the feature map size and dimension.
+It simply contains a scale-$2$ nearest up-sampling layer followed by a conv layer with BN+ReLU.
 The linear compression layer is a single conv layer followed by a Tanh to directly compress feature maps to the RGB space (as side outputs).
@@
 %Such simple and symmetric design makes our generator helpful for gradient flows. We will verify in experiments. 
-With a pre-defined side-output position at scales $\{1,...,s\}$, we apply the compression layer at those positions to generate side output images.
-
-\textbf{Discriminator} The discriminator simply contains consecutive stride-2 conv layers with BN and LeakyReLU.
-There are two branches are added on the upper layer for the proposed functional discriminator design.
+At pre-defined side-output positions at scales $\{1,...,s\}$, we apply the compression layer to generate side output images, for the input of the discriminator.
+
+\textbf{Discriminator} The discriminator simply contains consecutive stride-2 conv layers with BN+LeakyReLU.
+There are two branches are added on the upper layer of the discriminator.
 One branch is a direct fully convolutional layers to produce a $R{\times}R$ probability map (see Figure \ref{fig:loss}) and classify each location as real or fake.
-Another branch first concatenates the $512{\times}4{\times}4$ feature map and a $128{\times}4{\times}4$ text embedding (replicated by a reduced $128$-d text embedding).
+Another branch first concatenates a $512{\times}4{\times}4$ feature map and a $128{\times}4{\times}4$ text embedding (replicated by a reduced $128$-d text embedding).
 Then we use an $1{\times}1$ conv to fuse text and image information and a $4{\times}4$ conv layer to classify the image-text pair to real or fake.
-%it is critical to guarantee the semantic consistency in the final results.
-
-The training is similar with the standard alternative training strategy in GANs. Please refer to the supplementary material for training and more network details.
+%%it is critical to guarantee the semantic consistency in the final results.
+
+The optimization is similar with the standard alternative training strategy in GANs. Please refer to the supplementary material for more training and network details.
 
@@
 \textbf{Dataset} 
-We test on three widely used datasets. The CUB dataset \cite{welinder2010caltech} contains 11,788 bird images belonging to 200 different categories. 
+We test on three widely used datasets. The CUB dataset \cite{welinder2010caltech} contains 11,788 bird images belonging to 200 categories. 
 %, which crops the bird region and ensure the foreground occupies greater than 0.75.  
-The Oxford-102 dataset \cite{Nilsback08} contains 8189 flow images in 102 different categories. 
+The Oxford-102 dataset \cite{Nilsback08} contains 8,189 flow images in 102 categories. 
 %We follow \cite{han2017stackgan, reed2016generative} to split both of these datasets into class-disjoint training and testing sets. 
-Each image in both datasets is annotated with 10 text descriptions provided by \cite{reed2016generative}.
+Each image in both datasets is annotated with 10 descriptions provided by \cite{reed2016generative}.
 We pre-process and split the images of CUB and Oxford-102 following the same pipeline in \cite{reed2016generative,han2017stackgan}.
-In the COCO dataset \cite{lin2014microsoft}, there are 80k training images and 40k validation images.
-Each image has 5 text descriptions.
-We use the pre-trained text encoder model provided in \cite{reed2016generative} to encode each text description into a 1024 embedding vector.
+The COCO dataset \cite{lin2014microsoft} contains 82,783 training images and 40,504 validation images.
+Each image has 5 descriptions.
+We use the pre-trained text RNN encoder provided in \cite{reed2016generative} to encode each sentence into a 1024-d text embedding vector.
 %During the training stage, we randomly pick-up a crop view from the original images, and pick 4 image sentence embedding and use the mean as conditioning vector.
@@
 \textbf{Evaluation metric}
-We use three different quantitative metrics to evaluate our method.
-%\textcolor{red}{\textbf{Inception score.}}  To evaluate the quality of generated images, we resort to the recently proposed qualitative evaluation measurement "inception score"\cite{improvedGAN},
+We use three kinds of quantitative metrics to evaluate our method.
+%\textcolor{red}{\textbf{Inception score.}}  To evaluate the quality of generated images, we resort to the recently proposed qualitative evaluation measurement "Inception score"\cite{improvedGAN},
 % \begin{equation}
@@
 % \end{equation}
-% where $\bm{x}$ denotes generated sample images, $y$ the class label, $p(y|\bm{x})$ represents the conditional label distribution calculated by the Inception model\cite{inception}. 
-1) Inception score \cite{improvedGAN} is a measurement of both objectiveness and diversity of generated images, it is closely correlated with human judgment on the image quality.
-For CUB and Oxford-102, we use the fine-tuned inception model provided by StackGAN.
-For COCO, we directly use the model pre-trained on ImageNet.
+% where $\bm{x}$ denotes generated sample images, $y$ the class label, $p(y|\bm{x})$ represents the conditional label distribution calculated by the Inception model\cite{Inception}. 
+1) Inception score \cite{improvedGAN} is a measurement of both objectiveness and diversity of generated images. Evaluating this score needs a pre-trained Inception model on ImageNet. 
+For CUB and Oxford-102, we use the fine-tuned Inception models on the training sets of the two datasets, respectively, provided by StackGAN. 
 2) Multi-scale structural similarity (MS-SSIM) metric \cite{improvedGAN} is used for further validation.
-It tests pair-wise variation of generated outputs and can find mode collapses reliably \cite{odena2016conditional}.
+It tests pair-wise similarity of generated images and can identity mode collapses reliably \cite{odena2016conditional}.
 Lower score indicates higher diversity of generated images (i.e.
@@
 3) \textbf{Visual-semantic similarity} The aforementioned metrics are widely used for general GANs.
-The problem of them is that they can not measure the alignment between the generated images and conditioned text.
-We introduce a new qualitative measurement, namely visual-semantic similarity (VS similarity) inspired by \cite{vsemb}.
-Denote $\bm{v}$ as the image feature vector extracted by a pre-trained Inception model $f_{cnn}$\cite{inception}.
-We define a scoring function $c(\bm{x}, \bm{y})=\frac{\bm{x}\cdot \bm{y}}{||\bm{x}||\cdot ||\bm{y}||}$. 
+The problem of them is that they can not measure the alignment between the generated images and conditioned text, i.e., semantic consistency.
+\cite{han2017stackgan} conducted human evaluation to measure.
+But this procedure is expensive and difficult to conduct.
+As inspired by \cite{vsemb}, we introduce a new qualitative measurement, namely visual-semantic similarity (VS similarity), that can alleviate the cost. 
+Denote $\bm{v}$ as the image feature vector extracted by a pre-trained Inception model $f_{cnn}$.
+We define a scoring function $c(\bm{x}, \bm{y})=\frac{\bm{x}\cdot \bm{y}}{||\bm{x}||_2\cdot ||\bm{y}||_2}$. 
 Then, we learn two mapping functions $f_v$ and $f_t$, which map both image and sentence embeddings into a common space in $\mathbb{R}^{512}$, by minimizing the following bi-directional ranking loss:
@@
 \begin{split}
- & \sum_{ \bm{v} }\sum_{ \bm{t}_{\overline{v}} }~\max( 0, \delta  - c(f_v(\bm{v}), f_t( \bm{t}_{{v}}) )+ c(f_v(\bm{v}), f_t( \bm{t}_{\overline{v}}) )     ) \\
- & + \sum_{ \bm{t} }\sum_{ \bm{v}_{\overline{t}} }~\max( 0,  \delta  - c(f_t(\bm{t}), f_v( \bm{v}_{{v}} )) +  c(f_t(\bm{t}), f_v( \bm{v}_{\overline{t}} ))  )
+  \sum_{ \bm{v} }\sum_{ \bm{t}_{\overline{v}} }~ &\max( 0, \delta  - c(f_v(\bm{v}), f_t( \bm{t}_{{v}}) )+ c(f_v(\bm{v}), f_t( \bm{t}_{\overline{v}}) )     ) +\\
+   \sum_{ \bm{t} }\sum_{ \bm{v}_{\overline{t}} }~ &\max( 0,  \delta  - c(f_t(\bm{t}), f_v( \bm{v}_{{v}} )) +  c(f_t(\bm{t}), f_v( \bm{v}_{\overline{t}} ))  ),
 \end{split}
@@
 where $\delta$ is the margin, which is set as 0.2.
-$\{\bm{v}, \bm{t}\}$ is a ground truth image text pair, and $\{\bm v, \bm t_{\overline{v}} \}$ and $\{ \bm v_{\overline{t}}, \bm{t} \}$ denote mismatched image-text pairs.
+$\{\bm{v}, \bm{t}\}$ is a ground truth image-text pair, and $\{\bm v, \bm t_{\overline{v}} \}$ and $\{ \bm v_{\overline{t}}, \bm{t} \}$ denote mismatched image-text pairs.
 In the testing stage, given an text embedding $\bm{t}$, and the generated image $\bm{x}$, the VS score is calculated as $c(f_{cnn}(\bm{x}), \bm{t})$.
-Higher score indicates better semantic consistency, i.e.
-stronger alignment between generated images and conditioned text.
+Higher score indicates better semantic consistency.
 
@@
 	\end{tablenotes} \vspace{-.1cm}
-	\caption{The inception-score evaluation on three datasets.
-The higher score reflects more meaningful synthetic images and higher diversity.
-The proposed HDGAN outperforms others significantly.} \label{table:score}
+	\caption{The Inception-score comparison on the three datasets. HDGAN outperforms others significantly.} \label{table:score}
 \end{table}
@@
 	\vspace{-.2cm}
-	\caption{The generated images on CUB compared with StackGAN.
+	\caption{Generated images on CUB compared with StackGAN.
 Each sample shows the input text and generated $64^2$ (left) and $256^2$ (right) images.
 Our results have significantly higher quality and preserve more semantic details, for example, ``the brown and white feathers and read head'' in the last column is much better reflected in our images.
-Moreover, we observed our birds exhibit richer poses (e.g.
-the frontal/back views in the second/forth columns).}
-	\vspace{-0.2cm}
+Moreover, we observed our birds exhibit nicer poses (e.g.
+the frontal/back views in the second/forth columns).
+Zoom-in for better observation.}
+	\vspace{-0.3cm}
 	\label{fig:vis-cub}
@@
 	\vspace{-.2cm}
-	\caption{The generated images on Oxford-102 compared with StackGAN.
+	\caption{Generated images on Oxford-102 compared with StackGAN.
 Our generated images perform more natural satisfiability and higher contrast and can generate complex flower structures (e.g.
-spiked petals) like the third example.} \label{fig:vis-oxford}
-	\vspace{-.2cm}
+spiked petals in the third example).} \label{fig:vis-oxford}
+	\vspace{-.5cm}
 \end{figure*}
@@
 			Ground Truth	&	${.302{\pm}.151}$	&	$ {.336{\pm}.138}$			& $.426{\pm}.157$  \\ \hline
-			StackGAN     &	$.228{\pm}.162$	&	 $.278{\pm}.134$			&  $-{\pm}-$		\\ 
+			StackGAN     &	$.228{\pm}.162$	&	 $.278{\pm}.134$			&  $-$		\\ 
 			HDGAN 		&	$\bm{.246{\pm}.157}$	&	$ \bm{.296{\pm}.131}$ & $\bm{.199{\pm}.183}$  \\ \hline
@@
 	\caption{The VS similarity evaluation on the three datasets.
-The higher score represents higher semantic consistency between the generated images and the text information.
+The higher score represents higher semantic consistency between the generated images and conditioned text.
 The groundtruth score is shown in the first row.} \label{table:vss} \vspace{-.3cm}
 \end{table}
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=0.48\textwidth]{figure/coco2.pdf}
+	\vspace{-.6cm}
+	\caption{Samples on the COCO validation set, which contain descriptions across different scenes. } \label{fig:coco}
+	\vspace{-.7cm}
+\end{figure}
 
@@
 }.
-We especially compare with the current state of the art, StackGAN (results are obtained from its provided models).
-
-% Similarly with our HDGAN, it now can train $64{-}256$ directly.
-Each generator still take images from the bottom generator and supervised by a discriminator.
-Differently, our network is more like a simple Vanilla network (or a pure inverse ImageNet CNN).}.
-
-%StackGAN \cite{han2017stackgan} generates synthetic images up to $256{\times}256$ resolution. We show that our method can generates images up to $512{\times}512$.
-
-Table \ref{table:score} shows the quantitative inception-score evaluation. We follow StackGAN' experiment setting to sample ${\sim}30,000$ $256^2$ images for evaluation.
-HDGAN achieves significantly improvement compared against other methods. For example, it improves StackGAN by $.45$ and StackGAN++ by $.31$ on CUB.
+We especially compare with StackGAN in details (results are obtained from its provided models).
+
+Table \ref{table:score} compares the Inception score. We follow StackGAN' experiment setting to sample ${\sim}30,000$ $256^2$ images for evaluation.
+HDGAN achieves significantly improvement compared against other methods. For example, it significantly improves StackGAN by $.45$ and StackGAN++ by $.31$ on CUB.
 HDGAN achieves competitive results with TAC-GAN on Oxford-102.
 TAC-GAN uses image labels to increase the discriminability of generators, while we do not use any extra knowledge.
-Figure \ref{fig:vis-cub} and Figure \ref{fig:vis-oxford} compare the qualitative results with StackGAN, by demonstrating more semantics details, richer poses, and more complex generated structures, which strongly prove the superiority of HDGAN.
-Moreover, we qualitatively compare the diversity of samples conditioned on the same text (with different input noises) in Figure \ref{fig:multiple-test} left.
+Figure \ref{fig:vis-cub} and Figure \ref{fig:vis-oxford} compare the qualitative results with StackGAN on CUB and Oxford-102, respectively, by demonstrating more, semantic details, natural color, and complex object structures.
+Moreover, we qualitatively compare the diversity of samples conditioned on the same text (with random input noises) in Figure \ref{fig:multiple-test} left.
 HDGAN can generate obviously more successful samples.
+See figure captions for explanations.
+The demonstrated results strongly prove the superiority of HDGAN.
+
+Different from CUB and Oxford-102, COCO is much more challenging and contains largely diverse natural scenes. 
+Our method obtains significantly improvement on COCO (Table \ref{table:score}). 
+Figure \ref{fig:coco} also shows some generated samples in several different scenes.
 Please refer to the supplementary material for more results.
 
-Table \ref{table:vss} compares the VS results on the three datasets.
-The results of the ground truth image-text pair are shown for reference.
+Table \ref{table:vss} compares the proposed VS results on the three datasets.
+The score of the groundtruth image-text pair are also shown for reference.
 HDGAN achieves consistently better performance on both CUB and Oxford-102.
-This results demonstrate that HDGAN can better capture the visual semantic information in generated images.
+These results demonstrate that HDGAN can better capture the visual semantic information in generated images.
 
@@
 	\caption{Left: Diverse samples are shown given a single input text.
-The proposed HDGAN (top) show obviously more details and higher diversity.
+The proposed HDGAN (top) show obviously more fine-grained details.
 Right: Side outputs of HDGAN with increasing resolutions.
@@
 
+\begingroup
+\setlength{\intextsep}{-4pt}%
+\setlength{\columnsep}{0pt}%
+\begin{wrapfigure}{r}{0.24\textwidth}
+	\centering
+	\includegraphics[width=0.245\textwidth]{figure/multiscale_Inception_2.pdf}
+	\vspace{-12pt}
+\end{wrapfigure}
+%Table \ref{table:multiscales}
+The right figure compares the multi-resolution Inception score on CUB.
+Our results are from the side outputs of a single model.
+As can be observed, our $64^2$ results outperform the $128^2$ results of StackGAN and our $128^2$ results also outperform $256^2$ results of StackGAN substantially.
+It strongly demonstrates our HDGAN better preserves semantically consistent information in all resolutions (as stated in Section 3.2).
+Figure \ref{fig:multiple-test} right validate this property qualitatively.
+However, we observed that, in StackGAN, the low-resolution images and high-resolution images sometimes are visually inconsistent with respect to colors and structures (see examples in Figure \ref{fig:vis-cub} and Figure \ref{fig:vis-oxford}).
+
+Table \ref{fig:msssmi} compares the MS-SSMI score with StackGAN and Prog.GAN for bird image generation.
+StackGAN and our HDGAN use text as input so the generated images are separable in class.
+We randomly sample ${\sim}20,000$ image pairs (400 per class) and compare the class-wise score in the left figure.
+HDGAN outperforms StackGAN in majority of classes and also has a lower standard deviation ($.023$ vs.
+$.032$).
+Note that Prog.GAN uses noise input rather than text.
+We can compare with it for the general measure of the image diversity.
+Following the procedure of Prog.GAN, we randomly sample ${\sim}10,000$ image pairs from all generated samples\footnote{We use $256^2$ bird images provided by Prog.GAN at \url{https://github.com/tkarras/progressive_growing_of_gans}.
+Note that Prog.GAN is trained on the LSUN \cite{yu2015lsun} bird set, which contains ${\sim}2$ million bird images.} and show the results in Table \ref{fig:msssmi} right.
+HDGAN outperforms both methods.
 \begin{table}[t] % retrieval
@@
 
-\textcolor{red}{Table \ref{fig:msssmi} compares the MS-SSMI image quality evaluation score with StackGAN and Prog.GAN for bird image generation.} StackGAN and our HDGAN use text as input so the generated images are separable in class.
-We randomly sample ${\sim}20,000$ image pairs (400 per class) and show the class-wise score in the left figure.
-HDGAN outperforms StackGAN in majority of classes and also has lower inter-class standard deviation ($.023$ vs.
-$.032$).
-Note that Prog.GAN uses noise input rather than text.
-We can compare with it for the general measure of image diversity.
-Following the procedure of Prog.GAN, we randomly sample ${\sim}10,000$ image pairs from all generated samples (We use $256^2$ images provided by Prog.GAN) and show the results in Table \ref{fig:msssmi} right.
-HDGAN outperforms both methods.
-
-\begingroup
-\setlength{\intextsep}{-4pt}%
-\setlength{\columnsep}{0pt}%
-\begin{wrapfigure}{r}{0.24\textwidth}
-	\centering
-	\includegraphics[width=0.245\textwidth]{figure/multiscale_inception_2.pdf}
-	\vspace{-12pt}
-\end{wrapfigure}
-%Table \ref{table:multiscales}
-The right figure compares the multi-resolution inception score on CUB.
-Our results are from the side outputs of a single model.
-As can be observed, our $64^2$ results outperform the $128^2$ results of StackGAN and our $128^2$ results also outperform $256^2$ results of StackGAN substantially.
-It strongly demonstrates our HDGAN better preserves semantically consistent information in all resolutions.
-Figure \ref{fig:multiple-test} right qualitatively validate this property.
-However, we observed that, in StackGAN, the low-resolution images and high-resolution images sometimes are visually inconsistent (see examples in Figure \ref{fig:vis-cub} and Figure \ref{fig:vis-oxford}).
-
 \subsection{Style Transfer Using Sentence Interpolation}
@@
 To demonstrate this ability of HDGAN, we generate images using the linearly interpolated embeddings between a source sentence and a target sentence.
-%%We fix the random noise input to make the object and background consistent.
 As shown in Figure~\ref{fig:interp}, the generated images show smooth style transformation and well reflect the semantic details in sentences. 
-In the first row, the generated birds gradually turn the color from yellow to brown.
-In the second row, two sentences with more complicated appearance descriptions is used, we can see that our model successfully captures these subtle features and tune the bird appearance gradually.
+%% In the first row, the generated birds gradually turn the color from yellow to brown. 
+For example, in the second row, two sentences with complicated appearance descriptions are used.
+We can see that our model successfully captures these subtle features and tune the bird appearance gradually.
 
@@
 
-\subsection{On the effects of Individual Components}
+\subsection{Ablation Study and Discussion}
 %%\subsubsection{Hierarchically-nested adversarial training}
@@
 And using discriminators at $64^2$ is critical (by comparing 64-256 and 128-256 cases).
-For now, we are unsure if adding more discriminators and even on lower resolution would be helpful.
+For now, it is uncertain if adding more discriminators and even on lower resolutions would be helpful.
 Further validation will be conducted.
-StackGAN emphasizes the importance of using text embeddings not only at input but also with intermediate features of the generator, by showing a large drop from $3.7$ to $3.45$ without doing so.
+StackGAN emphasizes the importance of using text embeddings not only at the input but also with intermediate features of the generator, by showing a large drop from $3.7$ to $3.45$ without doing so.
 While our method only uses text embeddings at the input.
-Our significantly improved results demonstrate the effectiveness of our hierarchically-nested adversarial training to maintain such semantic information and high inception score.
+Our results strongly demonstrate the effectiveness of our hierarchically-nested adversarial training to maintain such semantic information and a high Inception score.
 
@@
 	\includegraphics[width=0.48\textwidth]{figure/interp.pdf}
-	\vspace{-.5cm}
+	\vspace{-.6cm}
 	\caption{Text embedding interpolation from the source to target sentence results in smooth image style changes to match the targeting sentence. } \label{fig:interp}
@@
 		\end{tabularx}
-	\end{center} \vspace{-.4cm}
+	\end{center} \vspace{-.5cm}
 	\caption{Ablation study of hierarchically-nested adversarial discriminators on CUB and COO.
 $\checkmark $ indicates whether a discriminator at a certain scale is used.
-See text for detailed explanation.} \label{table:multiscales}
+See text for detailed explanation.} \label{table:multiscales} \vspace{-.3cm}
 \end{table}
@@
 
-\textbf{On the Local Image Loss} We also study the effectiveness of the proposed local adversarial image loss. 
-Table \ref{table:multiscales} compares the case by removing the local loss (denoted as `w/o local').
-Besides, the local image loss also helps improve the visual-semantic matching evidenced by the higher VS score of `w/ local'.
+\textbf{The local image loss} We analyze the effectiveness of the proposed local adversarial image loss. 
+Table \ref{table:multiscales} compares the case without using it (denoted as `w/o local image loss').
+The local image loss helps improve the visual-semantic matching evidenced by a higher VS score.
 We hypothesis that it is because adding the separate local image loss can offer the pair loss more ``focus'' on learning the semantic consistency.
-Furthermore, we also quantitatively compare the generated results in Figure \ref{fig:vis-imgloss}.
-Although both models can successfully capture the semantic details in text, the model with the local loss more precisely generate object structures described in conditioned text.
+Furthermore, the local image loss helps generate fine-grained image details.
+As demonstrated in Figure \ref{fig:vis-imgloss}, although both models can successfully capture the semantic details in text, the `w/ local' model generate complex object structures described in the conditioned text more precisely.
 
@@
 %Note that for text-to-image synthesis, StackGAN is the only successful method to generate $256{\times}256$ images.
-\textbf{Design principles} StackGAN shows the failure of directly training a vanilla $256{\times}256$ GAN to generate meaningful images. 
-We test this extreme case using our method by removing all nested discriminators (the first row of Table \ref{table:multiscales}).
-Our method still generates fairly good results, which demonstrate the effectiveness of our design framework (see Section 3.4).
-%%Figure \ref{fig:vallina-res} shows the qualitatively results. 
-%%Based on our experience, our effective generator designs better preserve gradient flows.
+\textbf{Design principles} StackGAN claims the failure of directly training a vanilla $256{\times}256$ GAN to generate meaningful images. 
+We test this extreme case using our method by removing all nested discriminators.
+Our method still generates fairly meaningful results (the first row of Table \ref{table:multiscales}), which demonstrate the effectiveness of our proposed framework (see Section 3.4).
 
@@
 
+%\textbf{Advantages}
+%The advantages of our hierarchical-nested adversary are clearer from different views, compared with the popular stacking GAN strategy \cite{}. 
+%First, it is memory efficient. 
+%When viewing it as ensembled multi-scale GAN (Figure \ref{}), each GAN fully uses the parameters of its lower resolution GAN.
+Usually, a deeper generator is necessary to compact a discriminator.
+Since the depth of discriminator increases as image resolution increases, if stacking separate GANs based on low resolution GAN outputs, much more layers are needed in generators as wells.
+While in our method, for instance, from a $64^2$ GAN to a $128^2$ GAN, only a minimum two conv layers ($1$-repeat res-blocks) are needed.
+%
+%Second, it fully enjoys top-down knowledge. 
+%The low resolution can not use high resolution information in the stacking GAN strategy.
+While in our method, it is easy to see the low resolution GAN enjoys knowledge from higher resolution.
+As an evidence, our $64^2$ synthetic images have higher Inception score than $64^2$ and even $128^2$ images of StackGAN (see Section 5).
+
+\section{Conclusion}
+In this paper, we present a novel and effective method to tackle the problem of generating images conditioned on text descriptions.
+We present a new dimension of playing adversarial games along the depth of the generator using the hierarchical-nested adversarial objectives.
+A multi-purpose adversarial loss is adopted to help render fine-grained image details.
+We also introduce a new evaluation metric to evaluate the semantic consistency between generated images and conditioned text.
+Extensive experiment results demonstrate that our method, namely HDGAN, can generate high-resolution photographic images and performs significantly better than existing state of the arts on three public datasets.
 \begin{table}[t] % retrieval
@@
 	\vspace{-0.2cm}
-	\caption{Ablation study on the local adversarial loss. See text for detailed explanation.} \label{tab:ablation-loss} \vspace{-0.3cm}
+	\caption{Ablation study on the local image loss on Oxford-102. See text for detailed explanation.} \label{tab:ablation-loss} \vspace{-0.3cm}
 \end{table}
@@
 	\centering
-	\includegraphics[width=0.491\textwidth,height=0.27\textwidth]{figure/imgloss.pdf}
+	\includegraphics[width=0.491\textwidth,height=0.29\textwidth]{figure/imgloss.pdf}
 	\vspace{-.6cm}
-	\caption{Qualitative evaluation of the local adversarial loss.
-We can see the two images w/ the local image loss more accurately exhibit complex flower petal structures described in the (colored) text.} \label{fig:vis-imgloss}
+	\caption{Qualitative evaluation of the local image loss.
+The two images w/ the local image loss more precisely exhibit the complex flower petal structures described in the (colored) text.} \label{fig:vis-imgloss}
 	\vspace{-.2cm}
 \end{figure}
-
-%\textbf{Advantages}
-%The advantages of our hierarchical-nested adversary are clearer from different views, compared with the popular stacking GAN strategy \cite{}. 
-%First, it is memory efficient. 
-%When viewing it as ensembled multi-scale GAN (Figure \ref{}), each GAN fully uses the parameters of its lower resolution GAN.
-Usually, a deeper generator is necessary to compact a discriminator.
-Since the depth of discriminator increases as image resolution increases, if stacking separate GANs based on low resolution GAN outputs, much more layers are needed in generators as wells.
-While in our method, for instance, from a $64^2$ GAN to a $128^2$ GAN, only a minimum two conv layers ($1$-repeat res-blocks) are needed.
-%
-%Second, it fully enjoys top-down knowledge. 
-%The low resolution can not use high resolution information in the stacking GAN strategy.
-While in our method, it is easy to see the low resolution GAN enjoys knowledge from higher resolution.
-As an evidence, our $64^2$ synthetic images have higher inception score than $64^2$ and even $128^2$ images of StackGAN (see Section 5).
-
-\section{Conclusion}
-In this paper, we present a novel and effective method to tackle the problem of generating images conditioned on text descriptions.
-We present a new dimension of playing adversarial games along the depth of the generator using the hierarchical-nested adversarial objectives, which regularizes the mid-level representations with multi-purpose adversarial losses and help the generator to generate high-resolution photographic images.
-We also introduce a new evaluation metric to evaluate the semantic consistency between generated images and conditioned text.
-Extensive experiment results demonstrate that our method, namely HDGAN, performs significantly better than existing state of the arts on three public datasets.
 

### 2017-11-15 supp.tex

@@
 
-\cvprfinalcopy % *** Uncomment this line for the final submission
+%\cvprfinalcopy % *** Uncomment this line for the final submission
 
-\def\cvprPaperID{2871} % *** Enter the CVPR Paper ID here
+\def\cvprPaperID{2823} % *** Enter the CVPR Paper ID here
 \def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
@@
 %\ifcvprfinal\pagestyle{empty}\fi
+
 \setcounter{page}{1}
@@
 %\title{Supplementary Materials for "Understanding, Describing, and Visualizing Medical Images Through Reading Diagnostic Report Text"}
-
+\title{Supplementary material for Photographic Text-to-Image Synthesis \\ with a Hierarchically-nested Adversarial Network}
 %\author{First Author\\
@@
 
-%\maketitle
+\maketitle
 %\thispagestyle{empty}
@@
 %%%%%%%%% BODY TEXT
-\begin{appendices}
 
@@
 %\renewcommand{\thechapter}{A\arabic{chapter}}
-\section{Results on the CUB bird dataset}
+\section{Results on the CUB Bird Dataset}
 
-\end{appendices}
+\section{Results on the Oxford-102 Flower Dataset}
 

### 2017-11-15 cvpr2018.tex
almostfinal

@@
 Photographic text-to-image synthesis is a significant problem in generative model research \cite{reed2016generative}, which aims to learn a mapping from a semantic text space to a complex RGB image space.
-This task requires the generated images to be not only realistic but also \textit{semantically consistent}, i.e., the generated images preserve the object color and sketch described in text and fine-grained descriptive details in image pixels as well.
+This task requires the generated images to be not only realistic but also \textit{semantically consistent}, For example, the generated images should preserve the object shape and color information described in the text.
+
+%the generated images preserve the object color and sketch described in text and fine-grained descriptive details in image pixels as well.
 
@@
 %\end{figure}
-Recently, generative adversarial networks (GANs) have become the main solution to this task. 
-Reed \etal \cite{reed2016generative} address this task through a GAN based framework. But this method only scale up to $64^2$ resolution and can barely generate vivid object details.
-Based on this method, StackGAN  \cite{han2017stackgan} is a successful approach, which stacks another low-to-high resolution GAN to generate high-resolution $256^2$ images in a two-stage training strategy.
-Later on, \cite{dong2017semantic} proposes to bypass the difficult of learning a mapping from text to RGB images and treat it as a pixel-to-pixel translation problem \cite{isola2016image}.
+Recently, Generative adversarial networks (GANs) have become the main solution to this task. 
+Reed \etal \cite{reed2016generative} address this task through a GAN based framework. But this method only scales up to $64^2$ resolution and can barely generate vivid object details.
+Based on this method, StackGAN  \cite{han2017stackgan} propose a two-stage training strategy to generate high-resolution $256^2$ images.
+But this methods requires training two separate GANs.
+Later on, \cite{dong2017semantic} proposes to bypass the difficulty of learning mappings from vector embeddings to RGB images and treat it as a pixel-to-pixel translation problem \cite{isola2016image}.
 It works by re-rendering an arbitrary-style $128^2$ training image conditioned on a targeting description.
-However, its high-resolution synthesis capability is still unclear.
-At present, training a generative model to map from a low-dimensional text space to a high-resolution image space in a fully end-to-end manner still remains unsolved.
-
-This paper pays attention to two major difficulties for text-to-image synthesis using GANs.
+However, its high-resolution synthesis capability remains unclear.
+
+This paper pays attention to two major difficulties for text-to-image synthesis with GANs.
 The first is balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}, which is actually a long-term problem in GANs.
@@
 
-Our generator resembles a simple vanilla GAN, without requiring any multiple internal text conditioning like \cite{han2017stackgan} or outside image annotation supervision like \cite{dash2017tac}.
+Our generator resembles a simple vanilla GAN, without without requiring multi-stage training and multiple internal text conditioning like \cite{han2017stackgan} or additional class label supervision like \cite{dash2017tac}.
 To tackle the problem of the big leap from the text space to the high-resolution image space, our insight is to leverage and regularize hierarchical representations with additional `deep' adversarial constraints.
 We introduce accompanying hierarchically-nested discriminators at multi-scale intermediate layers to play adversarial games and jointly encourage the generator approaching the real training data distribution.
-We also propose a new convolutional neural network (CNN) design for the generator to support accompanied discriminators more effectively in an end-to-end training manner.
-To guarantee the image diversity and semantic consistency,
-we enforce discriminators at scale-different generator side outputs to simultaneously differentiate real-and-fake image-text pairs as well as real-and-fake
-local image patches.
+We also propose a new convolutional neural network (CNN) design for the generator to support accompanying discriminators more effectively in an end-to-end training manner.
+To guarantee the image diversity and semantic consistency, we enforce discriminators at multiple side outputs of the generator to simultaneously differentiate real-and-fake image-text pairs as well as real-and-fake local image patches.
+%For more details, please refer to Section~\ref{sec:localloss}%focal
 
@@
 Inception score \cite{improvedGAN}) for generative models, we also introduce a new visual-semantic similarity metric to evaluate the alignment between generated images and conditioned text.
-Extensive experimental results and analysis demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts on three metrics.
+Extensive experimental results and analysis demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts on all three evaluation metrics.
 
@@
 \section{Related Work}
-We discussed related work and further clarify the novelty of our method by comparing with them.
+%We discusse related work and further clarify the novelty of our method by comparing with them.
 
@@
 
-Text-to-image synthesis is a significant problem in GANs.
-Reed \etal \cite{reed2016generative}  is the first to introduce a method that can generate $64^2$ resolution images, which is similar with DCGAN \cite{radford2015unsupervised}.
+Text-to-image synthesis is an interesting application of GANs.
+Reed \etal \cite{reed2016generative}  first introduce a method that can generate $64^2$ resolution images, which is similar with DCGAN \cite{radford2015unsupervised}.
 This method presents a new strategy for image-text matching aware adversarial training.
@@
 image labels, ImageNet CNNs, etc) \cite{dosovitskiy2016generating,ledig2016photo,dash2017tac,dash2017tac}, or different generator and discriminator combinations  \cite{metz2016unrolled,durugkar2016generative,yang2017lr,huang2016stacked}.
-\textit{While our method shows a new way to unite generators and discriminators and does not requires any extra knowledge apart from training paired text and images.} Additionally, it is easy to see the training difficulty increases significantly as the targeting image resolution increases.
+\textit{While our method shows a new way to unite generators and discriminators and does not requires any extra knowledge apart from training paired text and images.} In addition, it is easy to see the training difficulty increases significantly as the targeting image resolution increases.
 
@@
 Recently, Karras \etal \cite{Karras2017progressive} propose a progressive training of GANs.
-The idea is adding symmetric generator and discriminator layers gradually for high-resolution image generation (Figure \ref{fig:archs-review} C).
-\textit{Compared with these strategies that train low-to-high resolution GANs stage-by-stage or progressively, our method has the advantage of leveraging mid-level representations to encourage implicit subtask integration, which makes end-to-end high-resolution image synthesis in a single vanilla-like GAN possible.}
+The idea is to add symmetric generator and discriminator layers gradually for high-resolution image generation (Figure \ref{fig:archs-review} C).
+\textit{Compared with these strategies that train low-to-high resolution GANs stage-by-stage or progressively, our method has the advantage of leveraging mid-level representations to encourage the integration of multiple subtasks, which makes end-to-end high-resolution image synthesis in a single vanilla-like GAN possible.}
 
@@
 \subsection{Adversarial objective basics}
-In brief, a GAN \cite{goodfellow2014generative} consists of a generator $G$ network and a discriminator $D$ network, which are playing an adversarial game to compete with each other.
-The discriminator is optimized to distinguish synthesized images from real images, meanwhile the generator is optimized to generate fake images to fool the discriminator.
-Concretely, the overall min-max optimization objective is defined as:
+In brief, a GAN \cite{goodfellow2014generative} consists of a generator $G$ and a discriminator $D$, which are alternatively trained to compete with each other.
+$D$ is optimized to distinguish synthesized images from real images, meanwhile, $G$ is trained to fool $D$ by synthesizing fake images.
+Concretely, the optimal $G$ and $D$ can be obtained by playing the following two-player min-max game,
+
 \begin{equation}
@@
 %$G$ is learned to approximate $G(\bm z) \sim p(Y)$.  The loss $\mathcal{L}$ for the valuation function is usually a cross-entropy loss, such that $\mathcal{V}(\cdot) = - \mathcal{L}(\cdot)$. 
-$\mathcal{V}$ is the overall GAN objective, which usually takes the (cross-entropy loss) form $\mathbb{E}_{Y\sim p_{data}}\big[\log D(Y)\big] + \mathbb{E}_{\bm z\sim p_{z}}\big[\log (1-D(G(\bm z)))\big]$ or other variations \cite{lsgan,berthelot2017began}.
+$\mathcal{V}$ is the overall GAN objective, which usually takes the form $\mathbb{E}_{Y\sim p_{data}}\big[\log D(Y)\big] + \mathbb{E}_{\bm z\sim p_{z}}\big[\log (1-D(G(\bm z)))\big]$ (cross-entropy loss) or other variations \cite{lsgan,berthelot2017began}.
 
@@
 
-The proposed $\mathcal{G}$ is a CNN (defined in Section 3.4) with multiple resolution-growing side outputs:
+The proposed $\mathcal{G}$ is a CNN (defined in Section 3.4) producing multiple outputs with gradually increasing size:
 %This architecture resemble the proposed inverse architectures in edge detection\cite{xie2015holistically} and classification \cite{lee2015deeply}, which demonstrate that additional supervision to hidden layers can improve model generalization and boost optimization.
@@
 \end{equation}
-where  $\bm t\sim p_{data}$ denotes a sentence embedding vector in the real training data distribution (generated by a pre-trained char RNN encoder).
-$\{X_1,...,X_{s-1}\}$ are resolution-growing images and $X_s$ is the final output with the highest resolution.
+where  $\bm t\sim p_{data}$ denotes a sentence embedding (generated by a pre-trained char RNN text encoder\cite{reed2016generative}).
+$\mathcal{G}$ produces $s-1$ side outputs $\{X_1,...,X_{s-1}\}$  and one final output $X_s$ with the highest resolution.
 
@@
 \end{equation}
-where $\mathcal{D}  =  \{D_1, ..., D_s\} $ and $\; \mathcal{Y} = \{Y_1, ..., Y_s\}$ is a set of training images at multi-scales, $\{1,...,s\}$.
+where $\mathcal{D}  =  \{D_1, ..., D_s\} $ and $\; \mathcal{Y} = \{Y_1, ..., Y_s\}$ denotes one training image at multi-scales, $\{1,...,s\}$, forming an image pyramid.
 Compared with Eq.
-(\ref{equ:GAN}), one generator competes with multiple discriminators  $\{D_i\}$ at different hierarchies (Figure \ref{fig:archs-review} D), which learn discriminative features in different contextual scales, respectively.
+(\ref{equ:GAN}), our generator competes with multiple discriminators  $\{D_i\}$ at different hierarchies (Figure \ref{fig:archs-review} D), each focuses on learning discriminative features in different contextual scale.
 
 In principle, the lower-resolution side output is used to learn semantic consistent image structures (e.g.
-object sketches, colors, and background), and the subsequent higher-resolution side outputs are used to render fine-grained details.
-Since our method is trained in an end-to-end manner, the lower-resolution side outputs can fully enjoy the top-down knowledge from higher resolutions, such that we can observe consistent image structures and styles appear in both low and high resolutions.
-The experiment demonstrates this advantage compared with StackGAN. 
+object shape, colors, and background), and the subsequent higher-resolution side outputs are used to render fine-grained details.
+Since our method is trained in an end-to-end fashion, the lower-resolution outputs can also fully utilize top-down knowledge from discriminators at higher resolutions.
+As a result, we can observe consistent image structures, color and styles in outputs of both low and high resolutions without using addition regularization terms.
+
+%Since our method is trained in an end-to-end manner, the lower-resolution side outputs can fully enjoy the top-down knowledge from higher resolutions, such that we can observe consistent image structures and styles appear in both low and high resolutions.
+%The experiment demonstrates this advantage compared with StackGAN. 
 % % According to our empirical observation, our design is able to reduce the model instability, especially at the early stage of the training.
-
 %% %We present the following multi-purpose adversarial loss to support more effective generator training.
@@
 \subsection{Multi-purpose adversarial losses}
-Our generator produces resolution-growing side outputs, which compose an image pyramid. 
-We leverage this hierarchy property and allow adversarial losses to capture different statistics, with a goal to guarantee both semantic consistency and image fidelity.
+Our generator produces resolution-growing side outputs composing an image pyramid. 
+We leverage this hierarchy property and allow adversarial losses to capture hierarchical image statistics, with a goal to guarantee both semantic consistency and image fidelity.
 
 In order to guarantee semantic consistency, we adopt the matching-aware pair loss proposed by \cite{reed2016generative}.
-The discriminator is designed to take image-text pairs as inputs and be trained to differentiate two types of errors: a real image with mismatched text and a fake image with conditioned text.
+The discriminator is designed to take image-text pairs as inputs and be trained to identify two types of errors: a real image with mismatched text and a fake image with conditioned text.
 
 The pair loss is designed to guarantee the global semantic consistency.
-However, there lacks an explicit loss that forces the discriminator to differentiate real images from fake images.
-And combining both tasks (generating realistic images and matching image styles with text) into one loss complicates the already challenging learning tasks.
+However, there is no explicit loss to guide the discriminator to differentiate real images from fake images.
+And combining both tasks (generating realistic images and matching image styles with text) into one network output complicates the already challenging learning tasks.
 Moreover, as the image resolution goes higher, it might be challenging for a global pair-loss discriminator to capture the local fine-grained details (results are validated in experiments).
@@
 %\end{itemize}
-We expect the low-resolution discriminator to focus on global structures, while the high-resolution discriminator to focus  on local image details.
-Each discriminator consists of two branches (see Section 3.4), one computes a single scalar value for the pair loss and another branch computes a $R{\times}R$ probability map. 
-Each location differentiates whether an overlapping image patch is real or fake.
-Through the pyramid of the size-growing side outputs, we control $R$ accordingly. Specifically, a larger $R$ value results in a smaller local range and finer focus of discriminators.
-The local image adversarial loss can be implemented as an fully CNN \cite{shrivastava2016learning,zhu2017unpaired,isola2016image}.
+We expect the low-resolution discriminators to focus on global structures, while the high-resolution discriminators to focus  on local image details.
+Each discriminator $D_i$ consists of two branches (see Section 3.4), one computes a single scalar value for the pair loss and another branch computes  $R_i{\times}R_i$ 2D output maps $O_i$ for local image loss.
+%with an extra branch of the discriminator for the pair loss (see Section 3.4).
+%computes a $R{\times}R$ probability map. 
+Each element in $O_i$ differentiates whether a corresponding local image patch is real or fake.
+For each $D_i$, we control $R_i$ accordingly to tune the receptive field of each element of $O_i$. 
+%In practice, the local image adversarial loss can be implemented as an fully CNN \cite{shrivastava2016learning,zhu2017unpaired,isola2016image}. 
 Figure \ref{fig:loss} illustrates how hierarchically-nested discriminators compute the two losses on the generated images in the pyramid.
+
+%Specifically, a larger $R_i$ value results in a smaller local range and finer focus of discriminators.
 
@@
 	\vspace{-.7cm}
-	\caption{Given a set of images from the side output pyramid of the generator, the corresponding discriminator $D_i$ computes the matching-aware pair loss and local image loss (outputting a $R{\times}R$ probability map to classify real or fake image patches).
-$R$ increases as the image size grows.
+	\caption{Given a set of images from the side output pyramid of the generator, the corresponding discriminator $D_i$ computes the matching-aware pair loss and local image loss (outputting a $R_i{\times}R_i$ probability map to classify real or fake image patches).
 }  \vspace{-.2cm}
@@
 
-\textbf{Full Objective } Overall, our full min-max adversarial objective is defined as 
+\textbf{Full Objective } Overall, our full min-max adversarial objective can be defined as 
 %%hierarchically-nested discriminators $\{D_i\}$ optimize the following objective:
@@
 where $L_2(x) = \mathbb{E}\big[(x - \mathbb{I})^2\big]$ is the mean-square loss (instead of the conventional cross-entropy loss) and $\overline{L_2}(x) =\mathbb{E}\big[x^2\big]$. 
-This objective is maximized by $\mathcal{D}$. While for $\mathcal{G}$ practically, we minimize 
-$\sum_{i=1}^{s} (L_2(D_i(\mathcal{G}(\bm t, \bm z)_i)) +  L_2\big(D_i(\mathcal{G}(\bm t, \bm z)_i, \bm{t}_{X_i})))$.
-For the local image loss, the shape of $x, \mathbb{I} \in \mathbb{R}^{R{\times}R}$ vary accordingly (see Figure \ref{fig:loss}).
-$R=1$ refers to the (largest local) global range.
+This objective is directly minimized by $\mathcal{D}$. For generator $\mathcal{G}$ in practice, we minimize 
+$\sum_{i=1}^{s} (L_2(D_i(\mathcal{G}(\bm t, \bm z)_i)) +  L_2\big(D_i(\mathcal{G}(\bm t, \bm z)_i, \bm{t}_{X_i})))$ instead.
+For the local image loss, the shape of $x, \mathbb{I} \in \mathbb{R}^{R_i{\times}R_i}$ vary accordingly (see Figure \ref{fig:loss}).
+$R_i=1$ refers to the (largest local) global range.
 $D_i(X_i)$ is the image loss branch and $D_i(X_i, \bm{t}_{X_i})$ is the pair loss branch (conditioned on $\bm{t}_{X_i}$).
@@
 
-In the spirit of variational auto-encoder \cite{vae} and the practice of StackGAN \cite{han2017stackgan} (namely conditioning augmentation (CA)), instead of directly using deterministic text embedding, we sample a stochastic vector from a Ganssian distribution $\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}))$, where $\mu$ and $\Sigma$ are parameterized functions of $\bm t$.
-We add the Kullback-Leibler divergence regularization term, $D_{KL}(\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}) )|| \mathcal{N}(0, \bm{I}))$ \cite{vae}, to $\mathcal{G}$ loss to prevent over-fitting and force smooth sampling over the text embedding distribution.
+In the spirit of variational auto-encoder \cite{vae} and the practice of StackGAN \cite{han2017stackgan}, instead of directly using the deterministic text embedding, we sample a stochastic vector from a Ganssian distribution $\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}))$, where $\mu$ and $\Sigma$ are parameterized functions of $\bm t$.
+We add the Kullback-Leibler divergence regularization term, $D_{KL}(\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}) )|| \mathcal{N}(0, \bm{I}))$, to the GAN objective to prevent over-fitting and force smooth sampling over the text embedding distribution.
 
@@
 % \end{algorithm}
-%
 
@@
 
-\textbf{Generator} The generator is simply composed by three kinds of modules, termed as $K$-repeat res-blocks, stretching layers, and linear compression layers.
+\textbf{Generator} The generator is simply composed of three kinds of modules, termed as $K$-repeat res-blocks, stretching layers, and linear compression layers.
 A single res-block in the $K$-repeat res-block is a modified\footnote{We remove ReLU after the skip-addition of each residual block, with an intention to reduce sparse gradients.} residual block \cite{he2016identity}, which contains two convolutional (conv) layers (with batch normalization (BN) \cite{ioffe2015batch} and ReLU).
@@
 \textbf{Discriminator} The discriminator simply contains consecutive stride-2 conv layers with BN+LeakyReLU.
-There are two branches are added on the upper layer of the discriminator.
+There are two branches are added to the upper layer of the discriminator.
 One branch is a direct fully convolutional layers to produce a $R{\times}R$ probability map (see Figure \ref{fig:loss}) and classify each location as real or fake.
@@
 
-The optimization is similar with the standard alternative training strategy in GANs. Please refer to the supplementary material for more training and network details.
+The optimization is similar to the standard alternative training strategy in GANs. Please refer to the supplementary material for more training and network details.
 
@@
 %%This section evaluates the proposed method both qualitatively and quantitatively on three public datasets. 
-We denote our method as \textbf{HDGAN}, referring as High-Definition results and the idea of Hierarchically-nested Discriminators.
+We denote our method as \textbf{HDGAN}, referring to High-Definition results and the idea of Hierarchically-nested Discriminators.
 
 \textbf{Dataset} 
-We test on three widely used datasets. The CUB dataset \cite{welinder2010caltech} contains 11,788 bird images belonging to 200 categories. 
+We evaluate our model on three widely used datasets. The CUB dataset \cite{welinder2010caltech} contains 11,788 bird images belonging to 200 categories. 
 %, which crops the bird region and ensure the foreground occupies greater than 0.75.  
@@
 The COCO dataset \cite{lin2014microsoft} contains 82,783 training images and 40,504 validation images.
-Each image has 5 descriptions.
-We use the pre-trained text RNN encoder provided in \cite{reed2016generative} to encode each sentence into a 1024-d text embedding vector.
-%During the training stage, we randomly pick-up a crop view from the original images, and pick 4 image sentence embedding and use the mean as conditioning vector.
+Each image has 5 text annotations.
+We use the pre-trained charRNN text encoder provided by \cite{reed2016generative} to encode each sentence into a 1024-d text embedding vector.
+%During the training stage, we randomly pick-up a cropped view of the original images, and pick 4 image sentence embedding and use the mean as conditioning vector.
 
@@
 % where $\bm{x}$ denotes generated sample images, $y$ the class label, $p(y|\bm{x})$ represents the conditional label distribution calculated by the Inception model\cite{Inception}. 
-1) Inception score \cite{improvedGAN} is a measurement of both objectiveness and diversity of generated images. Evaluating this score needs a pre-trained Inception model on ImageNet. 
+1) Inception score \cite{improvedGAN} is a measurement of both objectiveness and diversity of generated images.
+Evaluating this score needs a pre-trained Inception model~\cite{inception} on ImageNet.
 For CUB and Oxford-102, we use the fine-tuned Inception models on the training sets of the two datasets, respectively, provided by StackGAN.
@@
 3) \textbf{Visual-semantic similarity} The aforementioned metrics are widely used for general GANs.
-The problem of them is that they can not measure the alignment between the generated images and conditioned text, i.e., semantic consistency.
-\cite{han2017stackgan} conducted human evaluation to measure.
-But this procedure is expensive and difficult to conduct.
-As inspired by \cite{vsemb}, we introduce a new qualitative measurement, namely visual-semantic similarity (VS similarity), that can alleviate the cost. 
+However, they can not measure the alignment between generated images and the conditioned text, i.e., semantic consistency.
+\cite{han2017stackgan} resorts to human evaluation, but this procedure is expensive and difficult to conduct.
+To tackle this issue, we introduce a new qualitative measurement, namely visual-semantic similarity (VS similarity) inspired by \cite{vsemb}.
 Denote $\bm{v}$ as the image feature vector extracted by a pre-trained Inception model $f_{cnn}$.
@@
 $\{\bm{v}, \bm{t}\}$ is a ground truth image-text pair, and $\{\bm v, \bm t_{\overline{v}} \}$ and $\{ \bm v_{\overline{t}}, \bm{t} \}$ denote mismatched image-text pairs.
-In the testing stage, given an text embedding $\bm{t}$, and the generated image $\bm{x}$, the VS score is calculated as $c(f_{cnn}(\bm{x}), \bm{t})$.
+In the testing stage, given an text embedding $\bm{t}$, and the generated image $\bm{x}$, the VS score can be calculated as $c(f_{cnn}(\bm{x}), \bm{t})$.
 Higher score indicates better semantic consistency.
@@
 \subsection{Comparative Results}
-To validate our proposed HDGAN, we compare our results with GAN-INT-CLS \cite{reed2016generative}, GAWWN \cite{reed2016learning}, TAC-GAN \cite{dash2017tac}, StackGAN \cite{han2017stackgan} and also its improved version StackGAN++ \cite{han2017stackganv2}, and Progressive GAN \cite{Karras2017progressive}\footnote{StackGAN++ and Prog.GAN are two very recently released preprints we noticed.
+To validate our proposed HDGAN, we compare our results with GAN-INT-CLS \cite{reed2016generative}, GAWWN \cite{reed2016learning}, TAC-GAN \cite{dash2017tac},  Progressive GAN \cite{Karras2017progressive}, StackGAN \cite{han2017stackgan} and also its improved version StackGAN++ \cite{han2017stackganv2}\footnote{StackGAN++ and Prog.GAN are two very recently released preprints we noticed.
 We acknowledge them as they also target at generating high-resolution images.
@@
 Moreover, we qualitatively compare the diversity of samples conditioned on the same text (with random input noises) in Figure \ref{fig:multiple-test} left.
-HDGAN can generate obviously more successful samples.
+HDGAN can generate obviously more compelling samples.
 See figure captions for explanations.
@@
 
-Table \ref{table:vss} compares the proposed VS results on the three datasets.
+Table \ref{table:vss} compares the proposed visual semantic similarity (VS) results on three datasets.
 The score of the groundtruth image-text pair are also shown for reference.
@@
 	\centering
-	\includegraphics[width=0.245\textwidth]{figure/multiscale_Inception_2.pdf}
+	\includegraphics[width=0.245\textwidth]{figure/multiscale_inception_2.pdf}
 	\vspace{-12pt}
@@
 As can be observed, our $64^2$ results outperform the $128^2$ results of StackGAN and our $128^2$ results also outperform $256^2$ results of StackGAN substantially.
-It strongly demonstrates our HDGAN better preserves semantically consistent information in all resolutions (as stated in Section 3.2).
+It  demonstrates that our HDGAN better preserves semantically consistent information in all resolutions (as stated in Section 3.2).
 Figure \ref{fig:multiple-test} right validate this property qualitatively.
-However, we observed that, in StackGAN, the low-resolution images and high-resolution images sometimes are visually inconsistent with respect to colors and structures (see examples in Figure \ref{fig:vis-cub} and Figure \ref{fig:vis-oxford}).
+On the other hand, we observe that, in StackGAN, the low-resolution images and high-resolution images sometimes are visually inconsistent with respect to colors and structures (see examples in Figure \ref{fig:vis-cub} and Figure \ref{fig:vis-oxford}).
 
@@
 Ideally, a well trained model should learn a smooth linear latent manifold of the images.
-To demonstrate this ability of HDGAN, we generate images using the linearly interpolated embeddings between a source sentence and a target sentence.
+To demonstrate the generalization capability of our proposed HDGAN, we generate images using the linearly interpolated embeddings between two source sentences.
 As shown in Figure~\ref{fig:interp}, the generated images show smooth style transformation and well reflect the semantic details in sentences. 
-%% In the first row, the generated birds gradually turn the color from yellow to brown. 
-For example, in the second row, two sentences with complicated appearance descriptions are used.
-We can see that our model successfully captures these subtle features and tune the bird appearance gradually.
+%For example, in the first row, the generated birds gradually turn the color from yellow to gray. In the second row, 
+For example, in the second row, complicated sentences with detailed appearance descriptions (e.g.,pointy peaks and black wing) are used, our model could still successfully capture these subtle features and tune the birds' appearance smoothly.
+
+%In the first row, the generated birds gradually turn the color from yellow to brown.
+In the second row, more complicated sentences with detailed appearance descriptions (e.g., blue peaks and yellow wing) are used, we can see that our model is still able to successfully capture these subtle features and tune the birds' appearance gradually.
 
@@
 The intuition is that all discriminators have a common goal to differentiate real and fake despite difficult scales and such sharing would reduce their inter-variances.
-However, we did not observe benefits from this mechanism and our independent discriminators can be trained very stably.
+However, we did not observe benefits from this mechanism and our independent discriminators can be trained fairly stably.
 
@@
 In this paper, we present a novel and effective method to tackle the problem of generating images conditioned on text descriptions.
-We present a new dimension of playing adversarial games along the depth of the generator using the hierarchical-nested adversarial objectives.
+We explore a new dimension of playing adversarial games along the depth of the generator using the hierarchical-nested adversarial objectives.
 A multi-purpose adversarial loss is adopted to help render fine-grained image details.

### 2017-11-15 cvpr2018.tex
almostfinalv2

@@
 Photographic text-to-image synthesis is a significant problem in generative model research \cite{reed2016generative}, which aims to learn a mapping from a semantic text space to a complex RGB image space.
-This task requires the generated images to be not only realistic but also \textit{semantically consistent}, For example, the generated images should preserve the object shape and color information described in the text.
+This task requires the generated images to be not only realistic but also \textit{semantically consistent}, for example, the generated images should preserve the object shape and color information described in the text.
 

### 2017-11-15 cvpr2018.tex
almostfinalv2

@@
 Based on this method, StackGAN  \cite{han2017stackgan} propose a two-stage training strategy to generate high-resolution $256^2$ images.
-But this methods requires training two separate GANs.
+But this method requires training two separate GANs.
 Later on, \cite{dong2017semantic} proposes to bypass the difficulty of learning mappings from vector embeddings to RGB images and treat it as a pixel-to-pixel translation problem \cite{isola2016image}.
@@
 
-Our generator resembles a simple vanilla GAN, without without requiring multi-stage training and multiple internal text conditioning like \cite{han2017stackgan} or additional class label supervision like \cite{dash2017tac}.
+Our generator resembles a simple vanilla GAN, without requiring multi-stage training and multiple internal text conditioning like \cite{han2017stackgan} or additional class label supervision like \cite{dash2017tac}.
 To tackle the problem of the big leap from the text space to the high-resolution image space, our insight is to leverage and regularize hierarchical representations with additional `deep' adversarial constraints.
@@
 %To alleviate the need for manual human evaluation about the matching between generated images and text description, we propose to learn a visual-semantic embedding model, thus providing a measure for quantitative evaluation of the image sentence consistency.
-%% It is a regularization to limit the discriminators to use unexpected information to make decision.
+%% It is a regularization to limit the discriminators to use the unexpected information to make the decision.
 
@@
 \section{Related Work}
-%We discusse related work and further clarify the novelty of our method by comparing with them.
+%We discuss related work and further clarify the novelty of our method by comparing with them.
 
@@
 image labels, ImageNet CNNs, etc) \cite{dosovitskiy2016generating,ledig2016photo,dash2017tac,dash2017tac}, or different generator and discriminator combinations  \cite{metz2016unrolled,durugkar2016generative,yang2017lr,huang2016stacked}.
-\textit{While our method shows a new way to unite generators and discriminators and does not requires any extra knowledge apart from training paired text and images.} In addition, it is easy to see the training difficulty increases significantly as the targeting image resolution increases.
-
-%for example, label smoothing and discriminator feature matching \cite{salimans2016improved, }, training stronger discriminator is beneficial to encourage generators \cite{arjovsky2017wasserstein}.
-Balancing through a equilibrium enforcing method \cite{berthelot2017began}
+\textit{While our method shows a new way to unite generators and discriminators and does not require any extra knowledge apart from training paired text and images.} In addition, it is easy to see the training difficulty increases significantly as the targeting image resolution increases.
+
+%for example, label smoothing, and discriminator feature matching \cite{salimans2016improved, }, training stronger discriminator is beneficial to encourage generators \cite{arjovsky2017wasserstein}.
+Balancing through an equilibrium enforcing method \cite{berthelot2017began}
 %Preventing discriminators from forgetting past samples and re-introduces artifacts \cite{shrivastava2016learning}.
@@
 %%% Huang \etal \cite{huang2016stacked} propose a top-down stacked GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method.
-However, this method needs multiple symmetric bottom-up pre-trained discriminators and the usage for high-resolution image is unclear.
+However, this method needs multiple symmetric bottom-up pre-trained discriminators and the usage of high-resolution image is unclear.
 Recently, Karras \etal \cite{Karras2017progressive} propose a progressive training of GANs.
@@
 For simplicity, we do not differentiate text description and it's corresponding text embedding vector in this paper.
-Our goal is to learn a generator $G$ that could produce high resolution images of high visual quality as well as variability giving an input text description $t$.
+Our goal is to learn a generator $G$ that could produce high-resolution images of high visual quality as well as variability giving an input text description $t$.
 %
@@
 %Denote the image dimension, text embedding dimension and the dimension of the noise input as $I$, $T$ and $Z$, respectively.
-Please note that, $G$ has multiple branches and generates multiple images of different sizes.
+Please note that $G$ has multiple branches and generates multiple images of different sizes.
 For each image size, we have a distinct discriminator $D$ associated with it.
@@
 %\setlength\itemsep{-0.3em}
-%\item Further forcing the generated samples to have only only global but also local similar statistics to real image patches, which is beneficial for rendering fine-grained details. 
-%
-%\item \textcolor{red}{Image loss without using paired text can be beneficial in the sense that it focus more on image information.
+%\item Further forcing the generated samples to have only global but also local similar statistics to real image patches, which is beneficial for rendering fine-grained details. 
+%
+%\item \textcolor{red}{Image loss without using paired text can be beneficial in the sense that it focuses more on image information.
 The richness of discriminator supervision usually has advantages for generalization.
@@
 For each $D_i$, we control $R_i$ accordingly to tune the receptive field of each element of $O_i$. 
-%In practice, the local image adversarial loss can be implemented as an fully CNN \cite{shrivastava2016learning,zhu2017unpaired,isola2016image}. 
+%In practice, the local image adversarial loss can be implemented as a fully CNN \cite{shrivastava2016learning,zhu2017unpaired,isola2016image}. 
 Figure \ref{fig:loss} illustrates how hierarchically-nested discriminators compute the two losses on the generated images in the pyramid.
@@
 %In addition, at the very beginning of the training,  generated images are usually far away from true image distribution, the discriminator can very easily judge a pair as invalid without using much pair information.
-\textcolor{red}{need more explanationn.}
-%We not only want the whole image is classified as true image by the discriminator, but also want to restrict the discriminator to classify all the local patches of high resolution output as true as well.
+\textcolor{red}{need more explanation.}
+%We not only want the whole image is classified as true image by the discriminator, but also want to restrict the discriminator to classify all the local patches of high-resolution output as true as well.
 
@@
 %Given a pair of image and text embedding $(x, \psi{t})$ as input, in the discriminator $D_i$, we first transfer $x$  to an image code $Code_x$.
-$Code_x$ along with $f_{sent}(\psi_t)$ is concatenated and fed to the matching aware branch to compute a final scale value indicating the probability of the pair being real or fake, where $f_{sent}$ consists of one linear layer and one leaky ReLU transformation,  the matching-aware branch is a set of residual blocks with strid-2 convolution, more details of the architecture will be provided in the appendix.
+$Code_x$ along with $f_{sent}(\psi_t)$ is concatenated and fed to the matching aware branch to compute a final scale value indicating the probability of the pair being real or fake, where $f_{sent}$ consists of one linear layer and one leaky ReLU transformation,  the matching-aware branch is a set of residual blocks with stride-2 convolution, more details of the architecture will be provided in the appendix.
 Besides that, the image code is also fed to an image-disc branch, whose structure is very similar to the matching-aware branch, to judge the probability of the input image being real or fake.
@@
 %The generator $G$ and discriminator $D$ are optimized alternatively using their corresponding loss function. 
-%Therefore, the discriminator are designed to take image and sentence pair as input and should be able to identify two types of errors: real image with mismatch conditional text information and fake image with real text.
+%Therefore, the discriminator is designed to take image and sentence pair as input and should be able to identify two types of errors: real image with mismatch conditional text information and fake image with real text.
 In our case, the discriminator is explicitly trained with three pair configurations, namely: real image with right text as positive training sample, and the aforementioned two sources of error pairs as negative training samples.
@@
 Table \ref{table:score} compares the Inception score. We follow StackGAN' experiment setting to sample ${\sim}30,000$ $256^2$ images for evaluation.
-HDGAN achieves significantly improvement compared against other methods. For example, it significantly improves StackGAN by $.45$ and StackGAN++ by $.31$ on CUB.
+HDGAN achieves significant improvement compared against other methods. For example, it significantly improves StackGAN by $.45$ and StackGAN++ by $.31$ on CUB.
 HDGAN achieves competitive results with TAC-GAN on Oxford-102.
@@
 Table \ref{table:vss} compares the proposed visual semantic similarity (VS) results on three datasets.
-The score of the groundtruth image-text pair are also shown for reference.
+The scores of the ground truth image-text pair are also shown for reference.
 HDGAN achieves consistently better performance on both CUB and Oxford-102.
@@
 \subsection{Style Transfer Using Sentence Interpolation}
-Ideally, a well trained model should learn a smooth linear latent manifold of the images.
+Ideally, a well-trained model should learn a smooth linear latent manifold of the images.
 To demonstrate the generalization capability of our proposed HDGAN, we generate images using the linearly interpolated embeddings between two source sentences.
@@
 %For example, in the first row, the generated birds gradually turn the color from yellow to gray. In the second row, 
-For example, in the second row, complicated sentences with detailed appearance descriptions (e.g.,pointy peaks and black wing) are used, our model could still successfully capture these subtle features and tune the birds' appearance smoothly.
+For example, in the second row, complicated sentences with detailed appearance descriptions (e.g., pointy peak and black wings) are used, our model could still successfully capture these subtle features and tune the birds' appearance smoothly.
 
@@
 The local image loss helps improve the visual-semantic matching evidenced by a higher VS score.
-We hypothesis that it is because adding the separate local image loss can offer the pair loss more ``focus'' on learning the semantic consistency.
+We hypothesise that it is because adding the separate local image loss can offer the pair loss more ``focus'' on learning the semantic consistency.
 Furthermore, the local image loss helps generate fine-grained image details.
-As demonstrated in Figure \ref{fig:vis-imgloss}, although both models can successfully capture the semantic details in text, the `w/ local' model generate complex object structures described in the conditioned text more precisely.
+As demonstrated in Figure \ref{fig:vis-imgloss}, although both models can successfully capture the semantic details in the text, the `w/ local' model generate complex object structures described in the conditioned text more precisely.
 
@@
 Usually, a deeper generator is necessary to compact a discriminator.
-Since the depth of discriminator increases as image resolution increases, if stacking separate GANs based on low resolution GAN outputs, much more layers are needed in generators as wells.
+Since the depth of discriminator increases as image resolution increases, if stacking separate GANs based on low-resolution GAN outputs, much more layers are needed in generators as wells.
 While in our method, for instance, from a $64^2$ GAN to a $128^2$ GAN, only a minimum two conv layers ($1$-repeat res-blocks) are needed.
@@
 %Second, it fully enjoys top-down knowledge. 
-%The low resolution can not use high resolution information in the stacking GAN strategy.
-While in our method, it is easy to see the low resolution GAN enjoys knowledge from higher resolution.
+%The low resolution can not use high-resolution information in the stacking GAN strategy.
+While in our method, it is easy to see the low-resolution GAN enjoys knowledge from higher resolution.
 As an evidence, our $64^2$ synthetic images have higher Inception score than $64^2$ and even $128^2$ images of StackGAN (see Section 5).

### 2017-11-17 cvpr2018.tex
submit verison

@@
 We adopt a multi-purpose adversarial loss to encourage more effective image and text information usage in order to improve the semantic consistency and image fidelity simultaneously.
-Furthermore, we introduce a new visual-semantic similarity measure to evaluate the semantic consistency of generated images, which also alleviates the cost of human evaluation.
+Furthermore, we introduce a new visual-semantic similarity measure to evaluate the semantic consistency of generated images.
 With extensive experimental validation on three public datasets, our method significantly improves previous state of the arts on all datasets over different evaluation metrics.
@@
 Photographic text-to-image synthesis is a significant problem in generative model research \cite{reed2016generative}, which aims to learn a mapping from a semantic text space to a complex RGB image space.
-This task requires the generated images to be not only realistic but also \textit{semantically consistent}, for example, the generated images should preserve the object shape and color information described in the text.
+This task requires the generated images to be not only realistic but also \textit{semantically consistent}, i.e., the generated images should preserve specific object sketches and semantic details described in text.
 
@@
     \vspace{-.6cm}
-    \caption{Top: Overview of our hierarchically-nested adversarial network. Bottom: Two generated results where fine-grained details are highlighted. \label{fig:intro}}     
+    \caption{Top: Overview of our hierarchically-nested adversarial network, which produces side output images with growing resolutions.
+Each side output is associated with a discriminator.
+Bottom: Two test sample results where fine-grained details are highlighted.
+\label{fig:intro}}
     \vspace{-.5cm}
@@
 %\end{figure}
+
 Recently, Generative adversarial networks (GANs) have become the main solution to this task. 
-Reed \etal \cite{reed2016generative} address this task through a GAN based framework. But this method only scales up to $64^2$ resolution and can barely generate vivid object details.
-Based on this method, StackGAN  \cite{han2017stackgan} propose a two-stage training strategy to generate high-resolution $256^2$ images.
+Reed \etal \cite{reed2016generative} address this task through a GAN based framework. But this method only generates $64^2$ images and can barely generate vivid object details.
+Based on this method, StackGAN \cite{han2017stackgan} proposes to stack another low-to-high resolution GAN to generate $256^2$ images.
 But this method requires training two separate GANs.
-Later on, \cite{dong2017semantic} proposes to bypass the difficulty of learning mappings from vector embeddings to RGB images and treat it as a pixel-to-pixel translation problem \cite{isola2016image}.
+Later on, \cite{dong2017semantic} proposes to bypass the difficulty of learning mappings from text to RGB images and treat it as a pixel-to-pixel translation problem \cite{isola2016image}.
 It works by re-rendering an arbitrary-style $128^2$ training image conditioned on a targeting description.
-However, its high-resolution synthesis capability remains unclear.
+However, its high-resolution synthesis capability is unclear. 
+At present, training a generative model to map from a low-dimensional text space to a high-resolution image space in a fully end-to-end manner still remains unsolved.
 
 This paper pays attention to two major difficulties for text-to-image synthesis with GANs.
-The first is balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}, which is actually a long-term problem in GANs.
+The first is balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}, which is a common problem in GANs.
 The second is stably modeling the huge pixel space in high-resolution images and guaranteeing semantic consistency \cite{han2017stackgan}.
@@
 
-In this paper, we propose a novel end-to-end method that can directly model high-resolution image statistics and generate semantically consistent and photographic images (see Figure \ref{fig:intro}).
+In this paper, we propose a novel end-to-end method that can directly model high-resolution image statistics and generate photographic images (see Figure \ref{fig:intro} bottom).
 The contributions are described as follows.
@@
 Our generator resembles a simple vanilla GAN, without requiring multi-stage training and multiple internal text conditioning like \cite{han2017stackgan} or additional class label supervision like \cite{dash2017tac}.
-To tackle the problem of the big leap from the text space to the high-resolution image space, our insight is to leverage and regularize hierarchical representations with additional `deep' adversarial constraints.
-We introduce accompanying hierarchically-nested discriminators at multi-scale intermediate layers to play adversarial games and jointly encourage the generator approaching the real training data distribution.
-We also propose a new convolutional neural network (CNN) design for the generator to support accompanying discriminators more effectively in an end-to-end training manner.
+To tackle the problem of the big leap from the text space to the image space, our insight is to leverage and regularize hierarchical representations with additional `deep' adversarial constraints (see Figure \ref{fig:intro} top).
+We introduce accompanying hierarchically-nested discriminators at multi-scale intermediate layers to play adversarial games and jointly encourage the generator to approach the real training data distribution.
+We also propose a new convolutional neural network (CNN) design for the generator to support accompanying discriminators more effectively.
 To guarantee the image diversity and semantic consistency, we enforce discriminators at multiple side outputs of the generator to simultaneously differentiate real-and-fake image-text pairs as well as real-and-fake local image patches.
-%For more details, please refer to Section~\ref{sec:localloss}%focal
+%%For more details, please refer to Section~\ref{sec:localloss}%focal
 
@@
 We validate our proposed method on three datasets, CUB birds \cite{welinder2010caltech}, Oxford-102 flowers \cite{Nilsback08}, and large-scale MSCOCO \cite{lin2014microsoft}.
-In complement of existing evaluation metric (e.g.
+In complement of existing evaluation metrics (e.g.
 Inception score \cite{improvedGAN}) for generative models, we also introduce a new visual-semantic similarity metric to evaluate the alignment between generated images and conditioned text.
+It alleviates the issue of the expensive human evaluation.
 Extensive experimental results and analysis demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts on all three evaluation metrics.
@@
 
-Deep generative models have attracted wide interests recently, including GANs \cite{goodfellow2014generative}, Variational Auto-encoders (VAE) \cite{kingma2013auto}, etc \cite{oord2016pixel}. 
-There are substantial existing methods investigating better usage of GANs for different applications, such as image synthesis \cite{radford2015unsupervised, shrivastava2016learning}, (unpaired) pixel-to-pixel translation \cite{isola2016image,zhu2017unpaired}, medical applications \cite{costa2017towards}, etc \cite{ledig2016photo,huang2016stacked}.
+Deep generative models have attracted wide interests recently, including GANs \cite{goodfellow2014generative,radford2015unsupervised}, Variational Auto-encoders (VAE) \cite{kingma2013auto}, etc \cite{oord2016pixel}.
+There are substantial existing methods investigating the better usage of GANs for different applications, such as image synthesis \cite{radford2015unsupervised, shrivastava2016learning}, (unpaired) pixel-to-pixel translation \cite{isola2016image,zhu2017unpaired}, medical applications \cite{costa2017towards}, etc \cite{ledig2016photo,huang2016stacked}.
 
 Text-to-image synthesis is an interesting application of GANs.
-Reed \etal \cite{reed2016generative}  first introduce a method that can generate $64^2$ resolution images, which is similar with DCGAN \cite{radford2015unsupervised}.
-This method presents a new strategy for image-text matching aware adversarial training.
+Reed \etal \cite{reed2016generative} is the first to introduce a method that can generate $64^2$ resolution images.
+This method also presents a new strategy for image-text matching aware adversarial training.
 Reed \etal \cite{reed2016learning} propose a generative
 adversarial what-where network (GAWWN) to enable location and content instructions in text-to-image synthesis.
-StackGAN \etal \cite{han2017stackgan} propose a two-stage stacking GAN training approach that is able to generate $256^2$ compelling images.
+Zhang \etal \cite{han2017stackgan} propose a two-stage training strategy that is able to generate $256^2$ compelling images.
 Recently, Dong \etal \cite{dong2017semantic} propose to learn a joint embedding of images and text so as to re-render a prototype image conditioned on a targeting description.
@@
 
-Learning a continuous mapping from a low-dimensional embedding manifold to a complex real data distribution is a long-standing problem.
-Although GANs have made significant progress, there are still many unsolved difficulties, e.g.
-training instability and high-resolution generation.
+Learning a continuous mapping from a low-dimensional manifold to a complex real image distribution is a long-standing problem.
+Although GANs have made significant progress, there are still many unsolved difficulties, e.g., training instability and high-resolution generation.
 Wide methods have been proposed to address the training instability, such as various training techniques \cite{salimans2016improved,arjovsky2017wasserstein,berthelot2017began,shrivastava2016learning,odena2016conditional}, regularization using extra knowledge (e.g.
@@
 Denton \etal \cite{denton2015deep} train a cascade of GANs in a Laplacian pyramid framework (LAPGAN) and use each to synthesize and refine image details and push up the output resolution stage-by-stage.
-StackGAN also shares some similar idea with LAPGAN.
-Inspired by this strategy, Chen \etal \cite{chen2017photographic} present a cascaded refinement network to synthesize high-resolution scene from semantic maps.
+StackGAN also shares similar ideas with LAPGAN.
+Inspired by this strategy, Chen \etal \cite{chen2017photographic} present a cascaded refinement network to synthesize high-resolution scenes from semantic maps.
 %%% Huang \etal \cite{huang2016stacked} propose a top-down stacked GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method.
@@
 
-Leveraging hierarchical representations of neural networks is an effective way to enhance implicit multi-scaling and ensembling for tasks such as image recognition \cite{lee2015deeply} and pixel or object classification \cite{xie2015holistically,cai2016unified,long2015fully}.
-Particularly, using deep supervision \cite{lee2015deeply} in hierarchical convolutional layers provides short error paths and increases the discriminativeness of feature representations.
-\textit{Our hierarchically-nested adversarial objective is inspired by these families of deeply-supervised CNNs. }
+Leveraging hierarchical representations of CNNs is an effective way to enhance implicit multi-scaling and ensembling for tasks such as image recognition \cite{lee2015deeply} and pixel or object classification \cite{xie2015holistically,cai2016unified,long2015fully}.
+Particularly, using deep supervision \cite{lee2015deeply} at intermediate convolutional layers provides short error paths and increases the discriminativeness of feature representations.
+\textit{Our hierarchically-nested adversarial objective is inspired by the family of deeply-supervised CNNs.}
 %%%Our proposed hierarchically-nested adversarial supervision enhances layer representations to support final high resolution outputs.
@@
 Concretely, the optimal $G$ and $D$ can be obtained by playing the following two-player min-max game,
-
 \begin{equation}
@@
 Our method actually explores a new dimension of playing this adversarial game along the depth of a generator (Figure \ref{fig:archs-review} D), which integrates additional hierarchical-nested discriminators at intermediate layers of the generator.
-The proposed objectives act as regularizers to the hidden space of $\mathcal{G}$, which also offer a short path for better error signal flow and helps reduce the training instability.
-
-The proposed $\mathcal{G}$ is a CNN (defined in Section 3.4) producing multiple outputs with gradually increasing size:
+The proposed objectives act as regularizers to the hidden space of $\mathcal{G}$, which also offer a short path for error signal flows and help reduce the training instability.
+
+The proposed $\mathcal{G}$ is a CNN (defined in Section 3.4), which produces multiple side outputs:
 %This architecture resemble the proposed inverse architectures in edge detection\cite{xie2015holistically} and classification \cite{lee2015deeply}, which demonstrate that additional supervision to hidden layers can improve model generalization and boost optimization.
@@
 \end{equation}
-where  $\bm t\sim p_{data}$ denotes a sentence embedding (generated by a pre-trained char RNN text encoder\cite{reed2016generative}).
-$\mathcal{G}$ produces $s-1$ side outputs $\{X_1,...,X_{s-1}\}$  and one final output $X_s$ with the highest resolution.
+where  $\bm t\sim p_{data}$ denotes a sentence embedding (generated by a pre-trained char-RNN text encoder \cite{reed2016generative}).
+$\{X_1,...,X_{s-1}\}$ are images with gradually growing resolutions and $X_s$ is the final output with the highest resolution.
 
@@
 
-For each side output $X_i$ from the generator, a distinct discriminator $D_i$ is associated to compete with it. Therefore, our full min-max objective is defined as 
+For each side output $X_i$ from the generator, a distinct discriminator $D_i$ is used to compete with it. Therefore, our full min-max objective is defined as 
 \begin{equation}
@@
 \end{equation}
-where $\mathcal{D}  =  \{D_1, ..., D_s\} $ and $\; \mathcal{Y} = \{Y_1, ..., Y_s\}$ denotes one training image at multi-scales, $\{1,...,s\}$, forming an image pyramid.
+where $\mathcal{D} = \{D_1, ..., D_s\} $ and $\; \mathcal{Y} = \{Y_1, ..., Y_s\}$ denotes training images at multi-scales, $\{1,...,s\}$.
 Compared with Eq.
-(\ref{equ:GAN}), our generator competes with multiple discriminators  $\{D_i\}$ at different hierarchies (Figure \ref{fig:archs-review} D), each focuses on learning discriminative features in different contextual scale.
+(\ref{equ:GAN}), our generator competes with multiple discriminators $\{D_i\}$ at different hierarchies (Figure \ref{fig:archs-review} D), which jointly learn discriminative features in different contextual scales.
 
 In principle, the lower-resolution side output is used to learn semantic consistent image structures (e.g.
-object shape, colors, and background), and the subsequent higher-resolution side outputs are used to render fine-grained details.
+object sketches, colors, and background), and the subsequent higher-resolution side outputs are used to render fine-grained details.
 Since our method is trained in an end-to-end fashion, the lower-resolution outputs can also fully utilize top-down knowledge from discriminators at higher resolutions.
-As a result, we can observe consistent image structures, color and styles in outputs of both low and high resolutions without using addition regularization terms.
+As a result, we can observe consistent image structures, color and styles in the outputs of both low and high resolution images.
+The experiment demonstrates this advantage compared with StackGAN.
 
@@
 To alleviate these issues and guarantee image fidelity, our solution is to add local adversarial image losses.
-%as inspired by \cite{shrivastava2016learning}. 
-%The insights are two folds:
-%\begin{itemize}\vspace{-.1cm}
-%\setlength\itemsep{-0.3em}
-%\item Further forcing the generated samples to have only global but also local similar statistics to real image patches, which is beneficial for rendering fine-grained details. 
-%
-%\item \textcolor{red}{Image loss without using paired text can be beneficial in the sense that it focuses more on image information.
-The richness of discriminator supervision usually has advantages for generalization.
-}
-%\vspace{-.2cm}
-%\end{itemize}
 We expect the low-resolution discriminators to focus on global structures, while the high-resolution discriminators to focus on local image details.
-Each discriminator $D_i$ consists of two branches (see Section 3.4), one computes a single scalar value for the pair loss and another branch computes  $R_i{\times}R_i$ 2D output maps $O_i$ for local image loss.
-%with an extra branch of the discriminator for the pair loss (see Section 3.4).
-%computes a $R{\times}R$ probability map. 
-Each element in $O_i$ differentiates whether a corresponding local image patch is real or fake.
-For each $D_i$, we control $R_i$ accordingly to tune the receptive field of each element of $O_i$. 
-%In practice, the local image adversarial loss can be implemented as a fully CNN \cite{shrivastava2016learning,zhu2017unpaired,isola2016image}. 
+Each discriminator $D_i$ consists of two branches (see Section 3.4), one computes a single scalar value for the pair loss and another branch computes a $R_i{\times}R_i$ 2D probability map $O_i$ for the local image loss.
+For each $D_i$, we control $R_i$ accordingly to tune the receptive field of each element in $O_i$, which 
+differentiates whether a corresponding local image patch is real or fake.
+The local GAN loss is also used for pixel-to-pixel translation tasks \cite{shrivastava2016learning,zhu2017unpaired,isola2016image}. 
 Figure \ref{fig:loss} illustrates how hierarchically-nested discriminators compute the two losses on the generated images in the pyramid.
@@
     \vspace{-.7cm}
-    \caption{Given a set of images from the side output pyramid of the generator, the corresponding discriminator $D_i$ computes the matching-aware pair loss and local image loss (outputting a $R_i{\times}R_i$ probability map to classify real or fake image patches).
-}  \vspace{-.2cm}
+    \caption{For each side out image in the pyramid from the generator, the corresponding discriminator $D_i$ computes the matching-aware pair loss and the local image loss (outputting a $R_i{\times}R_i$ probability map to classify real or fake image patches).
+}  \vspace{-.4cm}
     \label{fig:loss}
@@
 & \overline{L_2}\big(D_i({X}_i)\big)  + \overline{L_2}\big(D_i({X}_i, \bm{t}_{X_i})\big) + \overline{L_2}\big(D_i({Y}_i,  \bm{t}_{\overline{Y}})\big) \Big),
-\end{split}
+\end{split} \vspace{-.6cm}
 \end{equation}
 where $L_2(x) = \mathbb{E}\big[(x - \mathbb{I})^2\big]$ is the mean-square loss (instead of the conventional cross-entropy loss) and $\overline{L_2}(x) =\mathbb{E}\big[x^2\big]$. 
-This objective is directly minimized by $\mathcal{D}$. For generator $\mathcal{G}$ in practice, we minimize 
+This objective is minimized by $\mathcal{D}$. While in practice, $\mathcal{G}$ minimizes
 $\sum_{i=1}^{s} (L_2(D_i(\mathcal{G}(\bm t, \bm z)_i)) +  L_2\big(D_i(\mathcal{G}(\bm t, \bm z)_i, \bm{t}_{X_i})))$ instead.
-For the local image loss, the shape of $x, \mathbb{I} \in \mathbb{R}^{R_i{\times}R_i}$ vary accordingly (see Figure \ref{fig:loss}).
+For the local image loss, the shape of $x, \mathbb{I} \in \mathbb{R}^{R_i{\times}R_i}$ varies accordingly (see Figure \ref{fig:loss}).
 $R_i=1$ refers to the (largest local) global range.
@@
 
-In the spirit of variational auto-encoder \cite{vae} and the practice of StackGAN \cite{han2017stackgan}, instead of directly using the deterministic text embedding, we sample a stochastic vector from a Ganssian distribution $\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}))$, where $\mu$ and $\Sigma$ are parameterized functions of $\bm t$.
+In the spirit of variational auto-encoder \cite{vae} and the practice of StackGAN \cite{han2017stackgan} (termed conditioning augmentation (CA)), instead of directly using the deterministic text embedding, we sample a stochastic vector from a Ganssian distribution $\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}))$, where $\mu$ and $\Sigma$ are parameterized functions of $\bm t$.
 We add the Kullback-Leibler divergence regularization term, $D_{KL}(\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}) )|| \mathcal{N}(0, \bm{I}))$, to the GAN objective to prevent over-fitting and force smooth sampling over the text embedding distribution.
@@
 
-\textbf{Generator} The generator is simply composed of three kinds of modules, termed as $K$-repeat res-blocks, stretching layers, and linear compression layers.
+\textbf{Generator} The generator is simply composed of three kinds of modules, termed $K$-repeat res-blocks, stretching layers, and linear compression layers.
 A single res-block in the $K$-repeat res-block is a modified\footnote{We remove ReLU after the skip-addition of each residual block, with an intention to reduce sparse gradients.} residual block \cite{he2016identity}, which contains two convolutional (conv) layers (with batch normalization (BN) \cite{ioffe2015batch} and ReLU).
@@
 It simply contains a scale-$2$ nearest up-sampling layer followed by a conv layer with BN+ReLU.
-The linear compression layer is a single conv layer followed by a Tanh to directly compress feature maps to the RGB space (as side outputs).
+The linear compression layer is a single conv layer followed by a Tanh to directly compress feature maps to the RGB space.
 We prevent any non-linear function in the compression layer that could impede the gradient signals.
@@
 %Such simple and symmetric design makes our generator helpful for gradient flows. We will verify in experiments. 
-At pre-defined side-output positions at scales $\{1,...,s\}$, we apply the compression layer to generate side output images, for the input of the discriminator.
+At pre-defined side-output positions at scales $\{1,...,s\}$, we apply the compression layer to generate side output images, for the inputs of discriminators.
 
@@
 There are two branches are added to the upper layer of the discriminator.
-One branch is a direct fully convolutional layers to produce a $R{\times}R$ probability map (see Figure \ref{fig:loss}) and classify each location as real or fake.
+One branch is a direct fully convolutional layers to produce a $R_i{\times}R_i$ probability map (see Figure \ref{fig:loss}) and classify each location as real or fake.
 Another branch first concatenates a $512{\times}4{\times}4$ feature map and a $128{\times}4{\times}4$ text embedding (replicated by a reduced $128$-d text embedding).
-Then we use an $1{\times}1$ conv to fuse text and image information and a $4{\times}4$ conv layer to classify the image-text pair to real or fake.
+Then we use an $1{\times}1$ conv to fuse text and image features and a $4{\times}4$ conv layer to classify an image-text pair to real or fake.
 %%it is critical to guarantee the semantic consistency in the final results.
@@
 Each image has 5 text annotations.
-We use the pre-trained charRNN text encoder provided by \cite{reed2016generative} to encode each sentence into a 1024-d text embedding vector.
+We use the pre-trained char-RNN text encoder provided by \cite{reed2016generative} to encode each sentence into a 1024-d text embedding vector.
 %During the training stage, we randomly pick-up a cropped view of the original images, and pick 4 image sentence embedding and use the mean as conditioning vector.
@@
 
-3) \textbf{Visual-semantic similarity} The aforementioned metrics are widely used for general GANs.
+3) \textbf{Visual-semantic similarity} The aforementioned metrics are widely used for evaluating GANs.
 However, they can not measure the alignment between generated images and the conditioned text, i.e., semantic consistency.
 \cite{han2017stackgan} resorts to human evaluation, but this procedure is expensive and difficult to conduct.
-To tackle this issue, we introduce a new qualitative measurement, namely visual-semantic similarity (VS similarity) inspired by \cite{vsemb}.
-Denote $\bm{v}$ as the image feature vector extracted by a pre-trained Inception model $f_{cnn}$.
+To tackle this issue, we introduce a new measurement inspired by \cite{vsemb}, namely visual-semantic similarity (VS similarity).
+Denote $\bm{v}$ as an image feature vector extracted by an Inception model $f_{cnn}$.
 We define a scoring function $c(\bm{x}, \bm{y})=\frac{\bm{x}\cdot \bm{y}}{||\bm{x}||_2\cdot ||\bm{y}||_2}$. 
-Then, we learn two mapping functions $f_v$ and $f_t$, which map both image and sentence embeddings into a common space in $\mathbb{R}^{512}$, by minimizing the following bi-directional ranking loss:
+Then, we train two mapping functions $f_v$ and $f_t$, which map both real images and paired text embeddings into a common space in $\mathbb{R}^{512}$, by minimizing the following bi-directional ranking loss:
 %\mathcal{L}_{vs} &=
@@
 
+\subsection{Comparative Results}
+To validate our proposed HDGAN, we compare our results with GAN-INT-CLS \cite{reed2016generative}, GAWWN \cite{reed2016learning}, TAC-GAN \cite{dash2017tac},  Progressive GAN \cite{Karras2017progressive}, StackGAN \cite{han2017stackgan} and also its improved version StackGAN++ \cite{han2017stackganv2}\footnote{StackGAN++ and Prog.GAN are two very recently released preprints we noticed.
+We acknowledge them as they also target at generating high-resolution images.
+}.
+We especially compare with StackGAN in details (results are obtained from its provided models).
+
+Table \ref{table:score} compares the Inception score. We follow the experiment settings of StackGAN to sample ${\sim}30,000$ $256^2$ images for computing the score.
+HDGAN achieves significant improvement compared against other methods. For example, it improves StackGAN by $.45$ and StackGAN++ by $.31$ on CUB.
+HDGAN achieves competitive results with TAC-GAN on Oxford-102. TAC-GAN uses image labels to increase the discriminability of generators, while we do not use any extra knowledge. 
+Figure \ref{fig:vis-cub} and Figure \ref{fig:vis-oxford} compare the qualitative results with StackGAN on CUB and Oxford-102, respectively, by demonstrating more, semantic details, natural color, and complex object structures.
+Moreover, we qualitatively compare the diversity of samples conditioned on the same text (with random input noises) in Figure \ref{fig:multiple-test} left.
+HDGAN can generate substantially more compelling samples.
+%%The demonstrated results strongly prove the superiority of our method.
+
+Different from CUB and Oxford-102, COCO is a much more challenging dataset and contains largely diverse natural scenes. 
+Our method significantly outperforms StackGAN as well (Table \ref{table:score}). 
+Figure \ref{fig:coco} also shows some generated samples in several different scenes. Please refer to the supplementary material for more results.
+
+\begingroup
+\setlength{\intextsep}{-4pt}%
+\setlength{\columnsep}{0pt}%
+\begin{wrapfigure}{r}{0.24\textwidth}
+	\centering
+	\includegraphics[width=0.245\textwidth]{figure/multiscale_inception_2.pdf}
+	\vspace{-12pt}
+\end{wrapfigure}
+Furthermore, the right figure compares the multi-resolution Inception score on CUB.
+Our results are from the side outputs of a single model.
+As can be observed, our $64^2$ results outperform the $128^2$ results of StackGAN and our $128^2$ results also outperform $256^2$ results of StackGAN substantially.
+It demonstrates that our HDGAN better preserves semantically consistent information in all resolutions (as stated in Section 3.2).
+Figure \ref{fig:multiple-test} right validates this property qualitatively.
+On the other hand, we observe that, in StackGAN, the low-resolution images and high-resolution images sometimes are visually inconsistent (see examples in Figure \ref{fig:vis-cub} and \ref{fig:vis-oxford}).
+
+Table \ref{table:vss} compares the proposed visual-semantic similarity (VS) results on three datasets.
+The scores of the groundtruth image-text pair are also shown for reference.
+HDGAN achieves consistently better performance on both CUB and Oxford-102.
+These results demonstrate that HDGAN can better capture the visual semantic information in generated images.
+
 \begin{figure}[t]
@@
 \end{figure}
-
-\subsection{Comparative Results}
-To validate our proposed HDGAN, we compare our results with GAN-INT-CLS \cite{reed2016generative}, GAWWN \cite{reed2016learning}, TAC-GAN \cite{dash2017tac},  Progressive GAN \cite{Karras2017progressive}, StackGAN \cite{han2017stackgan} and also its improved version StackGAN++ \cite{han2017stackganv2}\footnote{StackGAN++ and Prog.GAN are two very recently released preprints we noticed.
-We acknowledge them as they also target at generating high-resolution images.
-}.
-We especially compare with StackGAN in details (results are obtained from its provided models).
-
-Table \ref{table:score} compares the Inception score. We follow StackGAN' experiment setting to sample ${\sim}30,000$ $256^2$ images for evaluation.
-HDGAN achieves significant improvement compared against other methods. For example, it significantly improves StackGAN by $.45$ and StackGAN++ by $.31$ on CUB.
-HDGAN achieves competitive results with TAC-GAN on Oxford-102.
-TAC-GAN uses image labels to increase the discriminability of generators, while we do not use any extra knowledge.
-Figure \ref{fig:vis-cub} and Figure \ref{fig:vis-oxford} compare the qualitative results with StackGAN on CUB and Oxford-102, respectively, by demonstrating more, semantic details, natural color, and complex object structures.
-Moreover, we qualitatively compare the diversity of samples conditioned on the same text (with random input noises) in Figure \ref{fig:multiple-test} left.
-HDGAN can generate obviously more compelling samples.
-See figure captions for explanations.
-The demonstrated results strongly prove the superiority of HDGAN.
-
-Different from CUB and Oxford-102, COCO is much more challenging and contains largely diverse natural scenes. 
-Our method obtains significantly improvement on COCO (Table \ref{table:score}). 
-Figure \ref{fig:coco} also shows some generated samples in several different scenes.
-Please refer to the supplementary material for more results.
-
-Table \ref{table:vss} compares the proposed visual semantic similarity (VS) results on three datasets.
-The scores of the ground truth image-text pair are also shown for reference.
-HDGAN achieves consistently better performance on both CUB and Oxford-102.
-These results demonstrate that HDGAN can better capture the visual semantic information in generated images.
 
@@
     \vspace{-.2cm}
-    \caption{Left: Diverse samples are shown given a single input text.
+    \caption{Left: Multiple samples are shown given a single input text.
 The proposed HDGAN (top) show obviously more fine-grained details.
@@
 
-\begingroup
-\setlength{\intextsep}{-4pt}%
-\setlength{\columnsep}{0pt}%
-\begin{wrapfigure}{r}{0.24\textwidth}
-    \centering
-    \includegraphics[width=0.245\textwidth]{figure/multiscale_inception_2.pdf}
-    \vspace{-12pt}
-\end{wrapfigure}
-%Table \ref{table:multiscales}
-The right figure compares the multi-resolution Inception score on CUB.
-Our results are from the side outputs of a single model.
-As can be observed, our $64^2$ results outperform the $128^2$ results of StackGAN and our $128^2$ results also outperform $256^2$ results of StackGAN substantially.
-It demonstrates that our HDGAN better preserves semantically consistent information in all resolutions (as stated in Section 3.2).
-Figure \ref{fig:multiple-test} right validate this property qualitatively.
-On the other hand, we observe that, in StackGAN, the low-resolution images and high-resolution images sometimes are visually inconsistent with respect to colors and structures (see examples in Figure \ref{fig:vis-cub} and Figure \ref{fig:vis-oxford}).
-
 Table \ref{fig:msssmi} compares the MS-SSMI score with StackGAN and Prog.GAN for bird image generation.
@@
 $.032$).
-Note that Prog.GAN uses noise input rather than text.
-We can compare with it for the general measure of the image diversity.
+Note that Prog.GAN uses a noise input rather than text.
+We can compare with it for a general measure of the image diversity.
 Following the procedure of Prog.GAN, we randomly sample ${\sim}10,000$ image pairs from all generated samples\footnote{We use $256^2$ bird images provided by Prog.GAN at \url{https://github.com/tkarras/progressive_growing_of_gans}.
@@
 HDGAN outperforms both methods.
+
 \begin{table}[t] % retrieval
@@
 \subsection{Style Transfer Using Sentence Interpolation}
-Ideally, a well-trained model should learn a smooth linear latent manifold of the images.
-To demonstrate the generalization capability of our proposed HDGAN, we generate images using the linearly interpolated embeddings between two source sentences.
-As shown in Figure~\ref{fig:interp}, the generated images show smooth style transformation and well reflect the semantic details in sentences. 
+Ideally, a well-trained model can generalize to a smooth linear latent data manifold.
+To demonstrate this capability, we generate images using the linearly interpolated embeddings between two source sentences.
+As shown in Figure~\ref{fig:interp}, our generated images show smooth style transformation and well reflect the semantic details in sentences. 
 %For example, in the first row, the generated birds gradually turn the color from yellow to gray. In the second row, 
-For example, in the second row, complicated sentences with detailed appearance descriptions (e.g., pointy peak and black wings) are used, our model could still successfully capture these subtle features and tune the birds' appearance smoothly.
+For example, in the second row, complicated sentences with detailed appearance descriptions (e.g.
+pointy peaks and black wings) are used, our model could still successfully capture these subtle features and tune the bird's appearance smoothly.
 
@@
 %Our full method applies it on feature maps at $\{64, 128, 256\}$. 
-In Table \ref{table:multiscales}, we compare the performance of HDGAN by removing part of discriminators on both CUB and COCO datasets. 
+In Table \ref{table:multiscales}, we demonstrate their effectiveness and show the performance by removing parts of discriminators on both CUB and COCO datasets. 
 As can be seen, increasing the usage of discriminators at different scales have positive effects.
-And using discriminators at $64^2$ is critical (by comparing 64-256 and 128-256 cases).
+And using discriminators at $64^2$ is critical (by comparing the 64-256 and 128-256 cases).
 For now, it is uncertain if adding more discriminators and even on lower resolutions would be helpful.
@@
             \specialrule{1.5pt}{0pt}{0pt}  
-            \multicolumn{3}{c|}{Components}    &  \multicolumn{2}{c}{Inception score}    \\ \hline
+            \multicolumn{3}{c|}{Discriminators}    &  \multicolumn{2}{c}{Inception score}    \\ \hline
             64    & 128    & 256             &     CUB        &     COCO \\ \hline
@@
 $\checkmark $ indicates whether a discriminator at a certain scale is used.
-See text for detailed explanation.} \label{table:multiscales} \vspace{-.3cm}
+See text for detailed explanations.} \label{table:multiscales} \vspace{-.3cm}
 \end{table}
@@
 The local image loss helps improve the visual-semantic matching evidenced by a higher VS score.
-We hypothesise that it is because adding the separate local image loss can offer the pair loss more ``focus'' on learning the semantic consistency.
-Furthermore, the local image loss helps generate fine-grained image details.
-As demonstrated in Figure \ref{fig:vis-imgloss}, although both models can successfully capture the semantic details in the text, the `w/ local' model generate complex object structures described in the conditioned text more precisely.
+We hypothesize that it is because adding the separate local image loss can offer the pair loss more ``focus'' on learning the semantic consistency.
+Furthermore, the local image loss helps generate more vivid image details.
+As demonstrated in Figure \ref{fig:vis-imgloss}, although both models can successfully capture the semantic details in the text, the `w/ local' model generates complex object structures described in the conditioned text more precisely.
 
@@
 %Note that for text-to-image synthesis, StackGAN is the only successful method to generate $256{\times}256$ images.
-\textbf{Design principles} StackGAN claims the failure of directly training a vanilla $256{\times}256$ GAN to generate meaningful images. 
-We test this extreme case using our method by removing all nested discriminators.
+\textbf{Design principles} StackGAN claims the failure of directly training a vanilla $256^2$ GAN to generate meaningful images. 
+We test this extreme case using our method by removing all nested discriminators without the last one.
 Our method still generates fairly meaningful results (the first row of Table \ref{table:multiscales}), which demonstrate the effectiveness of our proposed framework (see Section 3.4).
@@
 Initially, we tried to share the top layers of the hierarchical-nested discriminators of HDGAN inspired by \cite{liu2017unsupervised}.
-The intuition is that all discriminators have a common goal to differentiate real and fake despite difficult scales and such sharing would reduce their inter-variances.
+The intuition is that all discriminators have a common goal to differentiate real and fake despite difficult scales, and such sharing would reduce their inter-variances.
 However, we did not observe benefits from this mechanism and our independent discriminators can be trained fairly stably.
@@
     \vspace{-0.2cm}
-    \caption{Ablation study on the local image loss on Oxford-102. See text for detailed explanation.} \label{tab:ablation-loss} \vspace{-0.3cm}
+    \caption{Ablation study of the local image loss on Oxford-102. See text for detailed explanations.} \label{tab:ablation-loss} \vspace{-0.3cm}
 \end{table}

### 2017-11-20 supp.tex
supplementary

--- 2017-11-13 supp.tex
@@
 %%%%%%%%% BODY TEXT
-\begin{appendices}
+
+\section{Training and Architecture Details}
+%The algorithm that summarizes the training process of our model is given in Algorithm 1. 
+%We train and evaluate our model with a devbox machine. $\alpha$ is set to 0.5, $\beta$ is set to 4.
+The training is similar to the standard alternative training strategy in GANs, which alternatively updates the generator and discriminators.
+The Adam optimizer \cite{kingma2014adam} is used.
+The initial learning rate is set as 0.0002 and decreased by half for every 100 epochs (50 for COCO).
+The model is trained for 500 epochs in total (200 epochs for COCO).
+We configure  the side outputs at 4 different scales where the feature map resolution is equal to $64^2,128^2,256^2$, and $512^2$, respectively.
+For the local image loss of these 4 side outputs, we set $R_1=1, R_2=1, R_3=5, R_4=5$.
+For example, $R_1$ refers to $64^2$.
+These numbers are not fine-tuned but are set empirically.
+We believe there exists better configurations.
+
+All intermediate conv layers except from the specified ones in Section 3.4 use $3{\times}3$ kernels (with reflection padding).
+Some other normalization layers are experimented (i.e.
+instance normalization \cite{ulyanov2016instance} and layer normalization \cite{ba2016layer}) since they are used by recent advances \cite{zhu2017unpaired,chen2017photographic}.
+But they are not satisfactory.
+
+With respect to the generator, we use 1-repeat residual blocks for the generator till the $256^2$ resolution.
+The input of the generator is a $1024{\times}4{\times}4$ tensor.
+As the feature map resolution increases by 2, the number of feature maps is downsampled also by $2$, at $8, 32, 128, 256$ sizes.
+To generate $512^2$ images, we pre-train the generator to $256^2$ due to the limitation of the GPU memory.
+We use a $3$-repeat res-block followed by a stretching layer to upscale the feature map size to $32{\times}512{\times}512$.
+and a linear compression layer to generate images.
+Since the $256^2$ image already captures the overall semantics and details, to encourage the $512^2$ maintain these information, we use a l1 reconstruction loss to `self-regularize' the generator in case the discriminator confuses the expected output.
+
+All source code will be released for better understanding.
+
+\section{More Qualitative Results and Analysis}
+In this section, we demonstrate more sample results for the three datasets.
+
+Figure \ref{fig:bird2} compares our results with StackGAN. For each input, 6 images are randomly sampled. The results demonstrate better visual quality than StackGAN.
+Figure \ref{fig:bird} shows the results on the CUB bird dataset.
+All the outputs of a model with different resolutions are also shown.
+As can be observed in the two figures, our method can generate fairly vivid images with different poses, shape, background, etc.
+Moreover, the images with different resolutions, which are side outputs of a single model, have very consistent information.
+More and more image details can be observed as the resolution increases.
+Figure \ref{fig:flower} shows the results on the Oxford-102 flower dataset. Very detailed petals can be generated with photographic colors and saturability.
+
+Figure \ref{fig:coco} shows the examples on the COCO dataset.
+COCO is much more challenging than the other two datasets since it contains natural images from very different scenes containing hundreds of different objects.
+As can be observed in the shown samples, our method generate semantically consistent and meaningful images, which correctly interpret the input text.
+
+However, it is worth to notice that, although our method significantly improves existing methods \cite{han2017stackgan,reed2016generative} on COCO, we realize that generating fine-grained details of natural scenes is still challenging.
+The  generation of the real natural image domain remains unsolved.
+We expect to address this problem as the future study.
+
+\newpage
+
 %\renewcommand{\thechapter}{A\arabic{chapter}}
-\section{Results on the CUB bird dataset}
+%\subsection{Results on the CUB bird dataset}
+\begin{figure}[th!]
+	\centering
+	\includegraphics[width=0.83\textwidth]{figure/supp_bird2.pdf}
 
-\end{appendices}
+	\caption{Sample results on CUB compared with StackGAN.
+For each input, 6 samples are shown with resolutions of $64^2$ and $256^2$, respectively.
+As can be obviously seen, our HDGAN can generate very consistent content in images of different resolutions.
+Moreover, our generated images show more photographic color and contrast.
+}
+	\label{fig:bird2}
+\end{figure}
+\newpage
+\begin{figure}[th!]
+	\centering
+	\includegraphics[width=0.9\textwidth]{figure/supp_bird.pdf}
 
-%{\small
-%	\bibliographystyle{ieee}
-%	\bibliography{egbib}
-%}
+	\caption{Sample results on CUB. For each input, 6 samples with resolutions of $64^2$, $128^2$, $256^2$, and $512^2$ are shown in 4 rows, respectively. }  
+	\label{fig:bird}
+\end{figure}
+
+\newpage
+
+%\subsection{Results on the Oxford-102 flower dataset}
+
+\begin{figure}[th!]
+	\centering
+	\includegraphics[width=0.999\textwidth]{figure/supp_flower.pdf}
+
+	\caption{Sample results on Oxford-102. For each input,  6 samples with resolutions of $64^2$, $128^2$, and $256^2$ are shown in 3 rows, respectively. }  
+	\label{fig:flower}
+\end{figure}
+%\subsection{More results on COCO}
+\begin{figure}[ht!]
+	\centering
+	\includegraphics[width=0.8\textwidth,width=0.8\textwidth]{figure/supp_coco.pdf}
+
+	\caption{Sample results on COCO. We show 8 $256^2$ samples in very different scenes. }  
+	\label{fig:coco}
+\end{figure}
+
+{\small
+	\bibliographystyle{ieee}
+	\bibliography{reference_zizhao,egbib}
+}
 

### 2017-11-20 supp.tex
minorrevision

@@
 %We train and evaluate our model with a devbox machine. $\alpha$ is set to 0.5, $\beta$ is set to 4.
-The training is similar to the standard alternative training strategy in GANs, which alternatively updates the generator and discriminators.
+The training procedure is similar to the one used in standard GANs, which alternatively updates the generator and discriminators until converge.
+
 The Adam optimizer \cite{kingma2014adam} is used.
@@
 These numbers are not fine-tuned but are set empirically.
-We believe there exists better configurations.
+We believe there exists better configurations to be explored.
 
@@
 instance normalization \cite{ulyanov2016instance} and layer normalization \cite{ba2016layer}) since they are used by recent advances \cite{zhu2017unpaired,chen2017photographic}.
-But they are not satisfactory.
+But the results are not satisfactory.
 
@@
 The input of the generator is a $1024{\times}4{\times}4$ tensor.
-As the feature map resolution increases by 2, the number of feature maps is downsampled also by $2$, at $8, 32, 128, 256$ sizes.
+As the feature map resolution increases by 2, the number of feature maps is halved at $8, 32, 128, 256$ sizes.
 To generate $512^2$ images, we pre-train the generator to $256^2$ due to the limitation of the GPU memory.
@@
 and a linear compression layer to generate images.
-Since the $256^2$ image already captures the overall semantics and details, to encourage the $512^2$ maintain these information, we use a l1 reconstruction loss to `self-regularize' the generator in case the discriminator confuses the expected output.
+Since the $256^2$ image already captures the overall semantics and details, to boost the training and encourage the $512^2$ maintain this information, we use a l1 reconstruction loss to `self-regularize' the generator.
+% in case the discriminator confuses the expected output.
 
-All source code will be released for better understanding.
+All source code will be released. % for better understanding.
 
@@
 All the outputs of a model with different resolutions are also shown.
-As can be observed in the two figures, our method can generate fairly vivid images with different poses, shape, background, etc.
+As can be observed in this two figures, our method can generate fairly vivid images with different poses, shape, background, etc.
 Moreover, the images with different resolutions, which are side outputs of a single model, have very consistent information.
@@
 
-Figure \ref{fig:coco} shows the examples on the COCO dataset.
-COCO is much more challenging than the other two datasets since it contains natural images from very different scenes containing hundreds of different objects.
-As can be observed in the shown samples, our method generate semantically consistent and meaningful images, which correctly interpret the input text.
+Figure \ref{fig:coco} shows some sampled results on the COCO dataset.
+COCO is much more challenging than the other two datasets since it contains natural images from a wide variety of scenes containing hundreds of different objects.
+As can be observed in the shown samples, our method can still generate semantically consistent images. %, which correctly interpret the input text.
 
-However, it is worth to notice that, although our method significantly improves existing methods \cite{han2017stackgan,reed2016generative} on COCO, we realize that generating fine-grained details of natural scenes is still challenging.
+However, it is worth to notice that, although our method significantly improves existing methods \cite{han2017stackgan,reed2016generative} on COCO, we realize that generating fine-grained details of complex natural scenes is still challenging.
 The generation of the real natural image domain remains unsolved.

### 2018-01-19 rebuttal/egrebuttal.tex
add rebuttal

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{array,booktabs,arydshln,xcolor} % for widening table line
\usepackage{amsthm,bm}
\usepackage{epstopdf}
\usepackage[flushleft]{threeparttable}
\usepackage{amsthm}
\usepackage{multirow}
\usepackage{tabularx} % in the preamble
\usepackage{float}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{capt-of}% or \usepackage{caption}
\usepackage{booktabs}
\usepackage{varwidth}
\usepackage{wrapfig}
\usepackage{makecell}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{2823} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Photographic Text-to-Image Synthesis with a Hierarchically-nested Adversarial Network}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

\noindent
We appreciate the insightful comments and instructive suggestions by three reviewers. In brief, our paper presents a simple yet effective generative adversarial network (GAN) with hierarchically-nested discriminators to perform photographic text-to-image generation, which achieves state-of-the-art performance with sufficient experiments.

\noindent
\textbf{To Reviewer 1:} 1) \textit{Novelty of hierarchically nested discriminators:} Although the idea of `multi-resolution branch' is used in several other fields mentioned by the reviewer and Related Work, it is completely novel in GANs. Note that training high-resolution GAN is known to be highly challenge. Previous methods rely on stacking a set of small GANs and train them progressively (see paragraph 4, Section 2). Differently, our method firstly shows that incorporating such hierarchical discriminators can effectively regularize mid-level representations and assist generator training to capture the complex image statistics and enable the training of high-resolution GANs in a fully end-to-end manner.

\noindent
2) \textit{Missing details in Figure 2}: We will carefully revise the figure to make it intuitive and clear.

\noindent
3) \textit{Beyond text-to-image synthesis:} Text-to-image synthesis is a relative new but key task in GANs. Itself already has enough problems that worth studies in a full paper. To be specific, keeping high diversity and semantic consistency simultaneously of high-resolution samples conditioned one sentence is non-trivial at all, although with provided text charRNN encodings. Besides the explained designs, there are also some technical details to guarantee them in the discriminator designs. We will further explain these merits in the final version. The evaluation of text-to-image synthesis also needs consideration.
We propose the visual-semantic metric to alleviate the previously used labor evaluation in complementary of the Inception-score and MS-SSIM for general GANs. But as the reviewer mentioned, our method can be general to other image datasets clearly. We will test them as a future study and open source code to the community for wide validation.

\noindent
\textbf{To Reviewer 2:} 1) \textit{Insufficient comparison: } Prog.GAN is currently recognized as the most effective method to generate high-resolution images from noises. GANs are developing fast. Outperforming recent Prog.GAN already implies that our method outperforms much earlier LAPGAN (proposed in 2015). Moreover, LAPGAN can only generate up to $96^2$ images, while our capability for high-resolution also demonstrates more advantages. The cascaded refinement network is an image-to-image generative model, which is clearly not relevant. Moreover, all of the three are actually not for text-to-image synthesis, so are not main comparable methods. We mentioned them as they share similar high-level motivations with ours. But we tried our best to show the state-of-the-art performance compared with most existing text-to-image synthesis methods on three datasets with three metrics. The sufficiency and solidity of our experiments are highlighted by the other two Reviewers as well.

%%%Compared with previous related methods, we argue our experiment is sufficient to demonstrate the ability to generate high-resolution images.

\noindent
2) \textit{Comparison to [28]: } We appreciate the recommended new metrics in [28]. We tested our trained model on the CUB bird dataset following the procedure advised in [28] (i.e. query text, the inception model, and a bird word list used to match the ImageNet bird categories). Our method achieves a high (top-1) accuracy of 98.7 ($256^2$ images) compared with [28]'s $85\%$ (To be careful, for a few bird category names in ImageNet do not have an exact match in the bird word list, we manually checked image-by-image). Particularly, less than ten images completely failed and the rest misclassified images still look like birds visually. We will complete the evaluation with this metric in the final version. The author ordering of [28] will be corrected. All results with source code will be released for wide test. % We believe this score further demonstrates the effectiveness of our method.

\noindent
4) \textit{Qualitative results of failed cases}: We will discuss the failure cases in the revision. Based on our observation, our method shows generally more realistic results, with clearly less sharp pixel transitions and more photographic colors as well as nature saturability (see the supplementary material). The reason we did not add failure cases in the first version is that it is hard to explain why a certain case looks worse than another. But we thought quantitative results (class-wise comparison in Table 3) are helpful.

\noindent
3) \textit{Using style transfer loss helps the inception score?:} %We agree with the nice study in [28] that the perpetual loss is helpful. 
%%Note that we investigate a simple vanilla-like GAN with hierarchically-nested discriminator to address this challenge. 
We agree that adding semantic information in the intermediate outputs (like StackGAN), adding some style losses like [28], or even adding an inception-score loss, can push the inception score. But it not clear if it can enable end-to-end high-resolution GAN training as our method is capable of.  Also please note, it is admitted that the inception score is not "perfect" and can not be the sufficient condition/proof of high-quality and semantic consistency images, considering the fact that CNNs (inception) can be "fooled" by only pixel changes without overall visual quality improvement.  All-round improvement of qualitative results and other scores is necessary. Our paper has a careful consideration and thorough evaluation for them.

\noindent
\textbf{To Reviewer 3:} 1) \textit{Writing issues:} Thanks for pointing them out. We will definitely revise the manuscript to better explain the proposed visual similarity metric and correct the misspelling of MS-SSIM.

\noindent
2) \textit{Choosing $R_i$} The actual size of $R_i$ for discriminators is described in the supplementary material. Our preliminary experience is that choosing small $R_i$ at low resolution and a bit larger one at high resolution.

%Pls also see our supplementary material to check the clearly better visual results than StackGAN.

%\begin{table}[h] % retrieval
%	\small
%	\begin{center}
%		\begin{tabularx}{.33\textwidth}{c|cc}
%			\specialrule{1.5pt}{0pt}{0pt}  
%			\multirow{2}{*}{Method}    & \multicolumn{2}{c}{Dataset}    \\ \cline{2-3}
%						&     Bird        &    Flower              \\ \hline
%			[28]    	&    -/-/85.0    &       0.89         \\ \hline
%			StackGAN    &    \textbf{99.0}/-/69.1    &                 \\ \hline
%			HDGAN    &    \textbf{98.7}/-/84.2    &                 \\ \hline
%		
%		\end{tabularx} 
%	\end{center}
%	\vspace{-.4cm}
%	%\caption{} \vspace{-.3cm}
%\end{table}

%
%{\small
%\bibliographystyle{ieee}
%\bibliography{egbib}
%}

\end{document}

### 2018-01-19 latex/supp.tex
add rebuttal

--- 2017-11-20 supp.tex
@@
 We configure the side outputs at 4 different scales where the feature map resolution is equal to $64^2,128^2,256^2$, and $512^2$, respectively.
-For the local image loss of these 4 side outputs, we set $R_1=1, R_2=1, R_3=5, R_4=5$.
+For the local image loss of these 4 side outputs, we set $R_1=1, R_2=1, R_3=5, \text{and } R_4=5$.
 For example, $R_1$ refers to $64^2$.
@@
 
-All intermediate conv layers except from the specified ones in Section 3.4 use $3{\times}3$ kernels (with reflection padding).
-Some other normalization layers are experimented (i.e.
+All intermediate conv layers, except from the specified ones in Section 3.4, use $3{\times}3$ kernels (with reflection padding).
+Some other normalization also layers are experimented (i.e.
 instance normalization \cite{ulyanov2016instance} and layer normalization \cite{ba2016layer}) since they are used by recent advances \cite{zhu2017unpaired,chen2017photographic}.
@@
 
-Figure \ref{fig:bird2} compares our results with StackGAN. For each input, 6 images are randomly sampled. The results demonstrate better visual quality than StackGAN.
+Figure \ref{fig:bird2} compares our results with StackGAN.
+For each input, 6 images are randomly sampled.
+Furthermore, we visualize zoomed-in samples compared with StackGAN in Figure \ref{fig:bird3}.
+Our results demonstrate obviously better quality, less artifacts, and less sharp pixel transitions.
+
 Figure \ref{fig:bird} shows the results on the CUB bird dataset.
@@
 
-However, it is worth to notice that, although our method significantly improves existing methods \cite{han2017stackgan,reed2016generative} on COCO, we realize that generating fine-grained details of complex natural scenes is still challenging.
-The generation of the real natural image domain remains unsolved.
-We expect to address this problem as the future study.
+However, it is worth to notice that, although our method significantly improves existing methods \cite{han2017stackgan,reed2016generative} on COCO, we realize that generating fine-grained details of complex natural scenes with various objects is still challenging.
+Based on this study, we expect to further address this problem as the future study.
 
@@
     \label{fig:bird2}
+\end{figure}
+\newpage
+\begin{figure}[th!]
+	\centering
+	\includegraphics[width=0.99\textwidth]{figure/supp_bird3.pdf}
+
+	\caption{Zoomed-in samples compared with StackGAN.
+The best sample among 6 samples given an input text is selected.
+It can be clearly observed that our results show more smooth visual results.
+Especially, much less sharp pixel transitions exist in our results.
+}
+	\label{fig:bird3}
 \end{figure}

### 2018-01-22 rebuttal/egrebuttal.tex
rebuttal

@@
 We appreciate the insightful comments and instructive suggestions by three reviewers.
-In brief, our paper presents a simple yet effective generative adversarial network (GAN) with hierarchically-nested discriminators to perform photographic text-to-image generation, which achieves state-of-the-art performance with sufficient experiments.
+In brief, our paper presents a simple yet effective generative adversarial network (GAN) with hierarchically-nested discriminators to perform photographic text-to-image generation, which achieves state-of-the-art performance on three public datasets.
 
@@
 \textbf{To Reviewer 1:} 1) \textit{Novelty of hierarchically nested discriminators:} Although the idea of `multi-resolution branch' is used in several other fields mentioned by the reviewer and Related Work, it is completely novel in GANs.
-Note that training high-resolution GAN is known to be highly challenge.
+Training high-resolution GAN is known to be highly challenge.
 Previous methods rely on stacking a set of small GANs and train them progressively (see paragraph 4, Section 2).
-Differently, our method firstly shows that incorporating such hierarchical discriminators can effectively regularize mid-level representations and assist generator training to capture the complex image statistics and enable the training of high-resolution GANs in a fully end-to-end manner.
+Differently, our method firstly shows that incorporating such hierarchical discriminators can effectively regularize mid-level representations and assist generator training of high-resolution GANs in a fully end-to-end manner.
 
@@
 3) \textit{Beyond text-to-image synthesis:} Text-to-image synthesis is a relative new but key task in GANs.
-Itself already has enough problems that worth studies in a full paper.
-To be specific, keeping high diversity and semantic consistency simultaneously of high-resolution samples conditioned one sentence is non-trivial at all, although with provided text charRNN encodings.
-Besides the explained designs, there are also some technical details to guarantee them in the discriminator designs.
-We will further explain these merits in the final version.
-The evaluation of text-to-image synthesis also needs consideration.
-We propose the visual-semantic metric to alleviate the previously used labor evaluation in complementary of the Inception-score and MS-SSIM for general GANs.
-But as the reviewer mentioned, our method can be general to other image datasets clearly.
-We will test them as a future study and open source code to the community for wide validation.
+Itself already has plenty of problems that worth studies in a full paper.
+To be specific, keeping high diversity and semantic consistency simultaneously of high-resolution samples conditioned one sentence is non-trivial at all, although with provided charRNN encodings.
+There are essential technical details to guarantee them in the discriminator designs.
+The evaluation of text-to-image synthesis also needs rethinking.
+We propose the visual-semantic metric to alleviate labor evaluation in [44] in complementary of the Inception-score and MS-SSIM for general GANs.
+The used datasets are also large (especially for COO) and representative.
+Nevertheless, as the reviewer indicated, our method is definitely general to other datasets. We will test them in the next version and open code to the community for wide validation.
 
@@
 Outperforming recent Prog.GAN already implies that our method outperforms much earlier LAPGAN (proposed in 2015).
-Moreover, LAPGAN can only generate up to $96^2$ images, while our capability for high-resolution also demonstrates more advantages.
+Moreover, LAPGAN can only generate up to $96^2$ images, while our capability for high-resolution also demonstrates significant advantages.
 The cascaded refinement network is an image-to-image generative model, which is clearly not relevant.
-Moreover, all of the three are actually not for text-to-image synthesis, so are not main comparable methods.
-We mentioned them as they share similar high-level motivations with ours.
-But we tried our best to show the state-of-the-art performance compared with most existing text-to-image synthesis methods on three datasets with three metrics.
-The sufficiency and solidity of our experiments are highlighted by the other two Reviewers as well.
+Moreover, all of the three are actually not for text-to-image synthesis, so are essential comparable methods.
+We discussed them as they share similar high-level motivations and solutions with ours.
+We tried our best to show the state-of-the-art performance compared with most existing text-to-image synthesis methods on three datasets (including the best inception score on the large COCO dataset) with three metrics.
+The sufficiency and solidity of our experiments are highlighted by other two Reviewers as well.
 
@@
 \noindent
-2) \textit{Comparison to [28]: } We appreciate the recommended new metrics in [28].
-We tested our trained model on the CUB bird dataset following the procedure advised in [28] (i.e.
+2) \textit{Comparison to [28]: } We appreciate the recommended new metrics.
+We tested our model on the CUB bird dataset following the procedure advised in [28] (i.e.
 query text, the inception model, and a bird word list used to match the ImageNet bird categories).
@@
 All results with source code will be released for wide test.
+
 % We believe this score further demonstrates the effectiveness of our method.
@@
 4) \textit{Qualitative results of failed cases}: We will discuss the failure cases in the revision.
-Based on our observation, our method shows generally more realistic results, with clearly less sharp pixel transitions and more photographic colors as well as nature saturability (see the supplementary material).
-The reason we did not add failure cases in the first version is that it is hard to explain why a certain case looks worse than another.
-But we thought quantitative results (class-wise comparison in Table 3) are helpful.
+Based on our observation, our method shows generally more realistic results, with clearly less sharp pixel transitions, more photographic colors, and nature saturability (see the supplementary material).
+%We also refer the reviewer to the showed samples in our paper and in the StacGAN paper. You can easily feel differences. 
+The reason we did not add failure cases is that it is hard to explain why a certain case looks worse than another.
+But Table 3 left compares class-wise scores to StackGAN, which is helpful for the concerns.
 
@@
 %%Note that we investigate a simple vanilla-like GAN with hierarchically-nested discriminator to address this challenge. 
-We agree that adding semantic information in the intermediate outputs (like StackGAN), adding some style losses like [28], or even adding an inception-score loss, can push the inception score.
-But it not clear if it can enable end-to-end high-resolution GAN training as our method is capable of.
-Also please note, it is admitted that the inception score is not "perfect" and can not be the sufficient condition/proof of high-quality and semantic consistency images, considering the fact that CNNs (inception) can be "fooled" by only pixel changes without overall visual quality improvement.
-All-round improvement of qualitative results and other scores is necessary.
-Our paper has a careful consideration and thorough evaluation for them.
+We agree that adding semantic information in the intermediate outputs (like StackGAN), adding some style losses like [28], or even adding an inception-score loss directly, can push the inception score.
+But it not clear these approaches can enable end-to-end high-resolution GAN training as our method is capable of.
+And Investigation of them is out of our focus.
+Please note, it is admitted that the inception score is not "perfect" and can not be the sufficient condition/proof of high-quality and semantic consistency images, considering the fact that CNNs (inception) can be "fooled" by only pixel changes without overall visual quality improvement.
+All-round improvement of qualitative results and other metrics is necessary.
+Our paper has a careful consideration and thorough demonstration for them.
 
@@
 \textbf{To Reviewer 3:} 1) \textit{Writing issues:} Thanks for pointing them out.
-We will definitely revise the manuscript to better explain the proposed visual similarity metric and correct the misspelling of MS-SSIM.
+We will definitely revise the manuscript to better explain the intuition of the proposed visual similarity metric and correct the misspelling of MS-SSIM.
 

### 2018-01-22 rebuttal/egrebuttal.tex
revise rebuttal

@@
 We appreciate the insightful comments and instructive suggestions by three reviewers.
-In brief, our paper presents a simple yet effective generative adversarial network (GAN) with hierarchically-nested discriminators to perform photographic text-to-image generation, which achieves state-of-the-art performance on three public datasets.
+In brief, our paper presents a simple yet effective generative adversarial network (GAN) with hierarchically-nested discriminators to perform photographic text-to-image generation, which \textcolor{red}{is end-to-end trainable and} achieves state-of-the-art performance on three public datasets.
 
 \noindent
-\textbf{To Reviewer 1:} 1) \textit{Novelty of hierarchically nested discriminators:} Although the idea of `multi-resolution branch' is used in several other fields mentioned by the reviewer and Related Work, it is completely novel in GANs.
-Training high-resolution GAN is known to be highly challenge.
-Previous methods rely on stacking a set of small GANs and train them progressively (see paragraph 4, Section 2).
-Differently, our method firstly shows that incorporating such hierarchical discriminators can effectively regularize mid-level representations and assist generator training of high-resolution GANs in a fully end-to-end manner.
+\textbf{To Reviewer 1:} 1) \textit{Novelty of hierarchically nested discriminators:} Although the idea of `multi-resolution branch' has been exploited in several other fields mentioned by the reviewer and Related Works, but it's effectiveness has not been studied in GANs.
+Training high-resolution GAN is known to be highly challenging.
+Previous methods resort to stacking a set of small GANs and train them progressively (see paragraph 4, Section 2).
+Differently, our method firstly shows that incorporating such hierarchical discriminators can effectively regularize mid-level representations and assist generator training of high-resolution GANs in a fully end-to-end manner, and extensive experiment results demonstrate the superiority of our method.
 
 \noindent
-2) \textit{Missing details in Figure 2}: We will carefully revise the figure to make it intuitive and clear.
+2) \textit{\textcolor{red}{Additional citations} and Missing details in Figure 2}: Thanks for pointing out the additional related works, we will cite them properly.
+We will also carefully revise the figure to make it intuitive and clear.
 
 \noindent
-3) \textit{Beyond text-to-image synthesis:} Text-to-image synthesis is a relative new but key task in GANs.
-Itself already has plenty of problems that worth studies in a full paper.
-To be specific, keeping high diversity and semantic consistency simultaneously of high-resolution samples conditioned one sentence is non-trivial at all, although with provided charRNN encodings.
+3) \textit{Beyond text-to-image synthesis:} Text-to-image synthesis is a relative new but challenging task in GANs. Itself already has plenty of problems that worth studies in a full paper. 
+Nevertheless, as the reviewer indicated, our method looks universal to other type of image generation problems, but in this work, we focus on the text-to-images synthesis,  we also want to emphasis that the used datasets are also large (especially for COO), representative and are capable of proving the effectiveness of our method.
+We believe that exploiting other image generation problems using our method will also be an interesting research area left open for the community.
+We will test them in the future work and open source our code to the community for future study.
+The evaluation of text-to-image synthesis also needs rethinking.
+We propose the visual-semantic metric to alleviate labor evaluation used in [44] in complementary of the Inception-score and MS-SSIM for general GANs.
+
+%To be specific, keeping high diversity and semantic consistency simultaneously of high-resolution samples conditioned one sentence is non-trivial at all, although with provided charRNN encodings.
 There are essential technical details to guarantee them in the discriminator designs.
-The evaluation of text-to-image synthesis also needs rethinking.
-We propose the visual-semantic metric to alleviate labor evaluation in [44] in complementary of the Inception-score and MS-SSIM for general GANs.
-The used datasets are also large (especially for COO) and representative.
-Nevertheless, as the reviewer indicated, our method is definitely general to other datasets. We will test them in the next version and open code to the community for wide validation.
 
 \noindent
-\textbf{To Reviewer 2:} 1) \textit{Insufficient comparison: } Prog.GAN is currently recognized as the most effective method to generate high-resolution images from noises.
-GANs are developing fast.
+\textbf{To Reviewer 2:} 1) \textit{Insufficient comparison: } Prog.GAN is currently recognized as one of the most effective methods to generate high-resolution images from noises.
+%GANs are evolving fast.
 Outperforming recent Prog.GAN already implies that our method outperforms much earlier LAPGAN (proposed in 2015).
-Moreover, LAPGAN can only generate up to $96^2$ images, while our capability for high-resolution also demonstrates significant advantages.
-The cascaded refinement network is an image-to-image generative model, which is clearly not relevant.
-Moreover, all of the three are actually not for text-to-image synthesis, so are essential comparable methods.
-We discussed them as they share similar high-level motivations and solutions with ours.
-We tried our best to show the state-of-the-art performance compared with most existing text-to-image synthesis methods on three datasets (including the best inception score on the large COCO dataset) with three metrics.
+Moreover, LAPGAN only reports images of resolution up to $96^2$ , while our capability for high-resolution also demonstrates significant advantages.
+The cascaded refinement network is an image-to-image generative model with pixelwise semantic layout input, which is not relevant.
+Moreover, all of the three are actually not for text-to-image synthesis,% so are essential comparable methods.
+we discussed them as they share similar high-level motivations and solutions with ours.
+We have showed the state-of-the-art performance compared with most recent existing text-to-image synthesis methods on three datasets (including the best inception score on the large COCO dataset) with three evaluation metrics.
 The sufficiency and solidity of our experiments are highlighted by other two Reviewers as well.
@@
 \noindent
-4) \textit{Qualitative results of failed cases}: We will discuss the failure cases in the revision.
+4) \textit{Qualitative results of failed cases}: Thanks for pointing this out.
+We will show more diverse qualitative results and discuss failure cases (especially in COCO dataset) in the revision.
 Based on our observation, our method shows generally more realistic results, with clearly less sharp pixel transitions, more photographic colors, and nature saturability (see the supplementary material).
+And the evaluation results with three metrics also confirm our conclusion.
+
 %We also refer the reviewer to the showed samples in our paper and in the StacGAN paper. You can easily feel differences. 
-The reason we did not add failure cases is that it is hard to explain why a certain case looks worse than another.
+%The reason we did not add failure cases is that it is hard to explain why a certain case looks worse than another.
 But Table 3 left compares class-wise scores to StackGAN, which is helpful for the concerns.
@@
 \noindent
-3) \textit{Using style transfer loss helps the inception score?:} %We agree with the nice study in [28] that the perpetual loss is helpful. 
+3) \textit{Using style transfer loss helps the inception score?:} 
+We agree with the nice study in [28] that the perpetual loss is helpful to improve the classification accuracy.
+But we also have the concern that adding such strong deterministic loss might lead to model collapse and impede the diversity of the generated images, since balancing the generator and discriminator can be a very tricky task.
+However, we agree that finding an effective way to utilize the inception intermediate representation can be a future research topic that worth studies.
+
+%But we believe  this is an open question that worth future stduies.
+
+%Please note, it is admitted that the inception score is not "perfect" and can not be the sufficient condition/proof of high-quality and semantic consistency images, considering the fact that CNNs (inception) can be "fooled" by only pixel changes without overall visual quality improvement.
+All-round improvement of qualitative results and other metrics is necessary.
+Our paper has a careful consideration and thorough demonstration for them.
+
+%We agree with the nice study in [28] that the perpetual loss is helpful. 
 %%Note that we investigate a simple vanilla-like GAN with hierarchically-nested discriminator to address this challenge. 
-We agree that adding semantic information in the intermediate outputs (like StackGAN), adding some style losses like [28], or even adding an inception-score loss directly, can push the inception score.
+% We agree that adding semantic information in the intermediate outputs (like StackGAN), adding some style losses like [28], or even adding an inception-score loss directly, can push the inception score.
 But it not clear these approaches can enable end-to-end high-resolution GAN training as our method is capable of.
@@
 \textbf{To Reviewer 3:} 1) \textit{Writing issues:} Thanks for pointing them out.
-We will definitely revise the manuscript to better explain the intuition of the proposed visual similarity metric and correct the misspelling of MS-SSIM.
+We will definitely revise the manuscript to better explain the intuition between the proposed visual similarity metric and correct the misspelling of MS-SSIM.
 
 \noindent
-2) \textit{Choosing $R_i$} The actual size of $R_i$ for discriminators is described in the supplementary material.
+2) \textit{Choosing $R_i$} The actual size of $R_i$ for discriminators is described in the Training and Architecture Details section in the supplementary material.
 Our preliminary experience is that choosing small $R_i$ at low resolution and a bit larger one at high resolution.

### 2018-01-22 rebuttal/egrebuttal.tex
rebuttal fix typo

@@
 We agree with the nice study in [28] that the perpetual loss is helpful to improve the classification accuracy.
-But we also have the concern that adding such strong deterministic loss might lead to model collapse and impede the diversity of the generated images, since balancing the generator and discriminator can be a very tricky task.
-However, we agree that finding an effective way to utilize the inception intermediate representation can be a future research topic that worth studies.
+But we also have the concern (as confirmed by our early experiment using intermediate representation of discriminator) that adding such strong loss might lead to model collapse and impede the diversity of the generated images, since balancing the generator and discriminator can be a very tricky task.
+However, we agree that finding an effective way to utilize the mentioned style transfer loss can be a future research topic that worth studies.
 
@@
 \textbf{To Reviewer 3:} 1) \textit{Writing issues:} Thanks for pointing them out.
-We will definitely revise the manuscript to better explain the intuition between the proposed visual similarity metric and correct the misspelling of MS-SSIM.
+We will definitely revise the manuscript to better explain the intuition behind the proposed visual similarity metric and correct the misspelling of MS-SSIM.
 

### 2018-01-22 rebuttal/egrebuttal.tex
page limit

@@
 query text, the inception model, and a bird word list used to match the ImageNet bird categories).
-Our method achieves a high (top-1) accuracy of 98.7 ($256^2$ images) compared with [28]'s $85\%$ (To be careful, for a few bird category names in ImageNet do not have an exact match in the bird word list, we manually checked image-by-image).
+Our method achieves a high (top-1) accuracy of 98.7 ($256^2$ images) compared with [28]'s $85\%$ (for a few bird category names in ImageNet do not have an exact match in the bird word list, we manually checked image-by-image).
 Particularly, less than ten images completely failed and the rest misclassified images still look like birds visually.
@@
 % We believe this score further demonstrates the effectiveness of our method. 
-
 \noindent
 4) \textit{Qualitative results of failed cases}: Thanks for pointing this out.
-We will show more diverse qualitative results and discuss failure cases (especially in COCO dataset) in the revision.
+We will show more diverse qualitative results and discuss failure cases in the revision.
 Based on our observation, our method shows generally more realistic results, with clearly less sharp pixel transitions, more photographic colors, and nature saturability (see the supplementary material).
@@
 \noindent
-3) \textit{Using style transfer loss helps the inception score?:} 
+3) \textit{About the style transfer loss:} 
 We agree with the nice study in [28] that the perpetual loss is helpful to improve the classification accuracy.
@@
 \noindent
-2) \textit{Choosing $R_i$} The actual size of $R_i$ for discriminators is described in the Training and Architecture Details section in the supplementary material.
+2) \textit{Choosing $R_i$:} The actual size of $R_i$ for discriminators is described in the Training and Architecture Details section in the supplementary material.
 Our preliminary experience is that choosing small $R_i$ at low resolution and a bit larger one at high resolution.

### 2018-01-24 rebuttal/egrebuttal.tex
revise

@@
 \noindent
-We appreciate the insightful comments and instructive suggestions by three reviewers.
-In brief, our paper presents a simple yet effective generative adversarial network (GAN) with hierarchically-nested discriminators to perform photographic text-to-image generation, which \textcolor{red}{is end-to-end trainable and} achieves state-of-the-art performance on three public datasets.
+We would like to thank the three reviewers for their thoughtful review of the this manuscript and for their insightful comments and instructive suggestions, which help to improve quality of the manuscript.
+Our response follows.
+%In brief, our paper presents a simple yet effective generative adversarial network (GAN) with hierarchically-nested discriminators to perform photographic text-to-image generation, which is end-to-end trainable and achieves state-of-the-art performance on three public datasets.
 
 \noindent
-\textbf{To Reviewer 1:} 1) \textit{Novelty of hierarchically nested discriminators:} Although the idea of `multi-resolution branch' has been exploited in several other fields mentioned by the reviewer and Related Works, but it's effectiveness has not been studied in GANs.
+\textbf{To Reviewer 1:} 1) \textit{Novelty of hierarchically nested discriminators:} Although the concept of `multi-resolution branch' has been used in several other fields mentioned by the reviewer and Related Works, but it's effectiveness has not been studied in GANs.
 Training high-resolution GAN is known to be highly challenging.
 Previous methods resort to stacking a set of small GANs and train them progressively (see paragraph 4, Section 2).
-Differently, our method firstly shows that incorporating such hierarchical discriminators can effectively regularize mid-level representations and assist generator training of high-resolution GANs in a fully end-to-end manner, and extensive experiment results demonstrate the superiority of our method.
+Differently, our method firstly shows that incorporating such hierarchical discriminators can overcome unsolved difficulties and assist the training of high-resolution GANs in an end-to-end manner.
+Extensive experiment results demonstrate the superiority of our method.
+
+%\textbf{To Reviewer 1:} 1) \textit{Novelty of hierarchically nested discriminators:} Although the concept of `multi-resolution branch' is used in several other fields, it is completely novel in GANs.
+Training high-resolution GAN is known to be highly challenge.
+Previous methods stack a set of small GANs and train them progressively (see paragraph 4, Section 2).
+Differently, our method firstly shows that incorporating such hierarchical discriminators can overcome unsolved difficulties and assist the training of high-resolution GANs in an end-to-end manner.
 
 \noindent
-2) \textit{\textcolor{red}{Additional citations} and Missing details in Figure 2}: Thanks for pointing out the additional related works, we will cite them properly.
+2) \textit{Additional citations and Missing details in Figure 2}: Thanks for pointing out the additional related works, we will cite them properly.
 We will also carefully revise the figure to make it intuitive and clear.
@@
 \noindent
-3) \textit{Beyond text-to-image synthesis:} Text-to-image synthesis is a relative new but challenging task in GANs. Itself already has plenty of problems that worth studies in a full paper. 
-Nevertheless, as the reviewer indicated, our method looks universal to other type of image generation problems, but in this work, we focus on the text-to-images synthesis,  we also want to emphasis that the used datasets are also large (especially for COO), representative and are capable of proving the effectiveness of our method.
-We believe that exploiting other image generation problems using our method will also be an interesting research area left open for the community.
-We will test them in the future work and open source our code to the community for future study.
-The evaluation of text-to-image synthesis also needs rethinking.
-We propose the visual-semantic metric to alleviate labor evaluation used in [44] in complementary of the Inception-score and MS-SSIM for general GANs.
+3) \textit{Scope of text-to-image synthesis:} 
+We focus on text-to-image synthesis as it is a relative new but key task in GANs, which already has plenty of difficulties that worth studies in a full paper.
+To be specific, achieving high diversity and semantic consistency simultaneously in high-resolution samples generation is a highly difficult problem even with provided charRNN text encodings.
+%And there are essential technical details to guarantee them in generator/discriminator designs.
+Nevertheless, as the reviewer indicated, our method looks universal to other type of image generation problems; We believe that exploiting other image generation tasks using our method will also be an interesting research area left open for the community.
+We will test them in the next version and open source our code to the community for future study.
+we also want to emphasis that the used datasets are also large (especially for COO), representative and are capable of proving the effectiveness of our method.
+In addition, the evaluation of text-to-image synthesis also needs rethinking.
+We propose the visual-semantic metric to alleviate labor evaluation used in [44] for  text-to-image synthesis evaluation.
+%in complementary of the Inception-score and MS-SSIM for general GANs.
 
-%To be specific, keeping high diversity and semantic consistency simultaneously of high-resolution samples conditioned one sentence is non-trivial at all, although with provided charRNN encodings.
-There are essential technical details to guarantee them in the discriminator designs.
+%3) \textit{Scope of text-to-image synthesis:} We focus on text-to-image synthesis as it is a relative new but key task in GANs, which already has plenty of difficulties that worth studies in a full paper.
+To be specific, keeping high diversity and semantic consistency simultaneously in high-resolution samples is non-trivial at all, although with provided charRNN encodings.
+And there are essential technical details to guarantee them in generator/discriminator designs.
+%The evaluation of text-to-image synthesis also needs rethinking, so we propose the visual-semantic metric in complementary of the Inception-score and MS-SSIM for general GANs.
+In addition, the used datasets are also large and representative (especially for COO).
+%Nevertheless, as the reviewer indicated, our method is definitely generic to other datasets. We will test them in the next version and also open source code for wide validation.
 
@@
 Moreover, all of the three are actually not for text-to-image synthesis,% so are essential comparable methods.
-we discussed them as they share similar high-level motivations and solutions with ours.
-We have showed the state-of-the-art performance compared with most recent existing text-to-image synthesis methods on three datasets (including the best inception score on the large COCO dataset) with three evaluation metrics.
+we discussed them in the related work as they share similar high-level motivations with ours.
+We have showed the state-of-the-art performance compared with most recent existing text-to-image synthesis methods on three datasets (including the best performance on the large COCO dataset) with three evaluation metrics.
 The sufficiency and solidity of our experiments are highlighted by other two Reviewers as well.
@@
 \noindent
-4) \textit{Qualitative results of failed cases}: Thanks for pointing this out.
+4) \textit{Qualitative results of failed cases}: 
+We definitely agree with the reviewer that it is better to show some failure cases for completeness.
+We will try our best to compare and discuss this in the revision.
+In addition, Table 3 left compares class-wise MS-SSIM scores to StackGAN, which illustrates that our method does not  outperform StackGAN 100\% of the time.
+We hope this will also be helpful for the concerns.
+
+%Thanks for pointing this out.
 We will show more diverse qualitative results and discuss failure cases in the revision.
@@
 \textbf{To Reviewer 3:} 1) \textit{Writing issues:} Thanks for pointing them out. 
-We will definitely revise the manuscript to better explain the intuition behind the proposed visual similarity metric and correct the misspelling of MS-SSIM.
+The intuition behind VS-similarity is to increase the score $c$ (cosine similarity) between matching pairs while decrease these between the mismatching pairs.
+We will definitely revise the manuscript to better explain the intuition and correct the misspelling of MS-SSIM.
 

### 2018-01-24 rebuttal/backup/zzz.tex
revise

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{array,booktabs,arydshln,xcolor} % for widening table line
\usepackage{amsthm,bm}
\usepackage{epstopdf}
\usepackage[flushleft]{threeparttable}
\usepackage{amsthm}
\usepackage{multirow}
\usepackage{tabularx} % in the preamble
\usepackage{float}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{capt-of}% or \usepackage{caption}
\usepackage{booktabs}
\usepackage{varwidth}
\usepackage{wrapfig}
\usepackage{makecell}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{2823} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Photographic Text-to-Image Synthesis with a Hierarchically-nested Adversarial Network}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

\noindent
We appreciate the insightful comments and instructive suggestions by three reviewers. In brief, our paper presents a simple yet effective generative adversarial network (GAN) with hierarchically-nested discriminators to perform photographic text-to-image generation, which achieves state-of-the-art performance on three public datasets.

\noindent
\textbf{To Reviewer 1:} 1) \textit{Novelty of hierarchically nested discriminators:} Although the concept of `multi-resolution branch' is used in several other fields, it is completely novel in GANs. Training high-resolution GAN is known to be highly challenge. Previous methods stack a set of small GANs and train them progressively (see paragraph 4, Section 2). Differently, our method firstly shows that incorporating such hierarchical discriminators can overcome unsolved difficulties and assist the training of high-resolution GANs in an end-to-end manner.

\noindent
2) \textit{Missing details in Figure 2}: We will carefully revise the figure to make it intuitive and clear.

\noindent
3) \textit{Scope of text-to-image synthesis:} We focus on text-to-image synthesis as it is a relative new but key task in GANs, which already has plenty of difficulties that worth studies in a full paper. To be specific, keeping high diversity and semantic consistency simultaneously in high-resolution samples is non-trivial at all, although with provided charRNN encodings. And there are essential technical details to guarantee them in generator/discriminator designs. 
The evaluation of text-to-image synthesis also needs rethinking, so we propose the visual-semantic metric in complementary of the Inception-score and MS-SSIM for general GANs. In addition, the used datasets are also large and representative (especially for COO). 
Nevertheless, as the reviewer indicated, our method is definitely generic to other datasets. We will test them in the next version and also open source code for wide validation.

\noindent
\textbf{To Reviewer 2:} 1) \textit{Insufficient comparison: } The reviewer misunderstood the feasibility of comparing these three mentioned methods in Table 1\&2. First, the cascaded refinement network is an image-to-image generative model, which is clearly not relevant.  
Second, Prog.GAN and LAPGAN are actually not for text-to-image synthesis, while the metrics in Table 1 and Table 2 requires the paired text information to compute the scores (see metric introduction in Section 4).
In terms of the high-resolution generation effectiveness, 
Prog.GAN and StackGAN are currently recognized as the most effective methods to generate high-resolution images from noises and text, respectively, for our best knowledge. Outperforming them already implies that our method outperforms much earlier LAPGAN (2015). We acknowledged them as they share similar high-level motivations and solutions with ours.  
In terms of the relevant text-to-image synthesis methods,  
we tried our best to show the state-of-the-art performance compared with most existing methods. The sufficiency and solidity of our experiments are actually highlighted by other two Reviewers.

%\textcolor{red}{Moreover, LAPGAN can only generate up to $96^2$ images, while our capability for up to $512^2$ also demonstrates significant strengths.}
%Prog.GAN is currently recognized as the most effective method to generate high-resolution images from noises. GANs are developing fast. Outperforming recent Prog.GAN and StackGAN already implies that our method outperforms much earlier LAPGAN (proposed in 2015). Moreover, LAPGAN can only generate up to $96^2$ images, while our capability for up to $512^2$ also demonstrates significant strengths. The cascaded refinement network is an image-to-image generative model, which is clearly not relevant. 
%Moreover, all of the three are actually not for text-to-image synthesis.
%These methods are not comparable in Table 1\&2 since Table 1 requires the label information (bird category) according to the configuration in StackGAN's paper and Table 2 uses text and image together. Prog.GAN and LAPGAN only takes noises as input and does not have text.
%, so are not essential comparable methods. 
%%%Compared with previous related methods, we argue our experiment is sufficient to demonstrate the ability to generate high-resolution images.

\noindent
2) \textit{Comparison to [28] with its new metric: } We thank for the recommended new metric. We tested our model on the CUB bird dataset following the procedure advised in [28] (i.e. the three query text, the inception model, and the bird word list used to match the ImageNet bird categories). Our method achieves a high (top-1) accuracy of 98.7 (with $256^2$ resolution) compared with [28]'s $85\%$ (To be careful, for a few bird category names in ImageNet do not have an exact match in the bird word list, we manually checked image-by-image). Particularly, less than ten images completely failed and the rest misclassified images still look like birds visually. We will complete the evaluation with this metric. The author ordering of [28] will be corrected. All results with source code will be released for wide test.

% We believe this score further demonstrates the effectiveness of our method.

\noindent
4) \textit{Qualitative results of failed cases}: We definitely agree with the reviewer that it is better to show some qualitative failures for completeness. We will try our best to compare and discuss in the revision. 
%%Based on our observation, our method shows more realistic results generally, with clearly less sharp pixel transitions, more photographic colors, and nature saturability (see the supplementary material). 
%%We also refer the reviewer to the showed samples in our paper and in the StacGAN paper. You can easily feel differences. 
The reason we did not add failure cases is that it is hard to explain why a certain sample looks worse than another. In addition, Table 3 left compares class-wise MS-SSIM scores to StackGAN, which illustrates that our method does not 100\% outperform StackGAN. We guess this may be helpful for the concerns.

\noindent
3) \textit{Using style transfer loss helps the inception score?:} %We agree with the nice study in [28] that the perpetual loss is helpful. 
%%Note that we investigate a simple vanilla-like GAN with hierarchically-nested discriminator to address this challenge. 
We agree that adding semantic information in the intermediate outputs [44], adding some style losses [28], or even adding an inception-score loss directly, may help the inception score. But it not clear whether these approaches can enable end-to-end high-resolution GAN training as our method is capable of. The investigation of them is out of our focus. Please note, it is admitted that the inception score is not "perfect" and can not be the sufficient condition/proof of high-quality and semantic consistency images, considering the fact that CNNs (inception) can be "fooled" by only pixel changes without overall visual quality improvement. All-round improvement of qualitative results and other metrics is necessary. Our paper has a careful consideration and thorough demonstration for them.

\noindent
\textbf{To Reviewer 3:} 1) \textit{Writing issues:} Thanks for pointing them out. We will definitely revise the manuscript to better explain the intuition of the proposed visual similarity metric and correct the misspelling of MS-SSIM.

\noindent
2) \textit{Choosing $R_i$} The actual size of $R_i$ for discriminators is described in the supplementary material. Our preliminary experience is that choosing small $R_i$ at low resolution and a bit larger one at high resolution.

%Pls also see our supplementary material to check the clearly better visual results than StackGAN.

%\begin{table}[h] % retrieval
%	\small
%	\begin{center}
%		\begin{tabularx}{.33\textwidth}{c|cc}
%			\specialrule{1.5pt}{0pt}{0pt}  
%			\multirow{2}{*}{Method}    & \multicolumn{2}{c}{Dataset}    \\ \cline{2-3}
%						&     Bird        &    Flower              \\ \hline
%			[28]    	&    -/-/85.0    &       0.89         \\ \hline
%			StackGAN    &    \textbf{99.0}/-/69.1    &                 \\ \hline
%			HDGAN    &    \textbf{98.7}/-/84.2    &                 \\ \hline
%		
%		\end{tabularx} 
%	\end{center}
%	\vspace{-.4cm}
%	%\caption{} \vspace{-.3cm}
%\end{table}

%
%{\small
%\bibliographystyle{ieee}
%\bibliography{egbib}
%}

\end{document}
